---
title: FFI Database Calculations
subtitle: Northeast Region
author: Alexandra Lalor
output:
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# PURPOSE

This code is for adding columns for graphing and reporting. This will add summary statistics [per plot]{.underline}. It does not summarize across plots, save this step for the reporting script.

## Before Starting

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
```

```{r load packages, include=FALSE}
# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(stringr)
library(DT)
library(fs)
```

### Adjust File Paths

```{r file paths, include=FALSE}
path_main <- "E:/Allie/FireFX_NER/FFI_DATA_MANAGEMENT/"
#path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Clean/FFI/")
path_save <- paste0(path_main, "Exports_Reporting/FFI/")
```

### Load Data {.hidden}

```{r load data, include=FALSE}
Fuels1000 <- read.csv(paste0(path_data, "english_surface_fuels_thousand_hr.csv"))
FuelsDuffLitt <- read.csv(paste0(path_data, "english_surface_fuels_duff_litter.csv"))
FuelsFine <- read.csv(paste0(path_data, "english_surface_fuels_fine.csv"))

Trees <- read.csv(paste0(path_data, "metric_trees_individuals.csv"))
Seedlings <- read.csv(paste0(path_data, "metric_density_quadrats.csv"))

HerbsPoints <- read.csv(paste0(path_data, "metric_cover_points.csv"))
HerbsSpComp <- read.csv(paste0(path_data, "metric_cover_species_composition.csv"))

# PostBurn <- read.csv(paste0(path_data, "metric_post_burn_severity.csv"))

SpeciesReport <- read.csv(paste0(path_data, "all_species_info.csv"))
```

### Define Codes

```{r}
Substrates <- SpeciesReport %>%
  filter(Species_LifeFormNameLocal == "Undefined")
Substrates <- unique(Substrates$Species_SymbolLocal)
  
Unknowns_MysteryPlants <- SpeciesReport %>%
  filter(Species_LifeFormNameLocal == "Unknown")
Unknowns_MysteryPlants <- unique(Unknowns_MysteryPlants$Species_SymbolLocal)

Unknowns_LifeFormOnly <- SpeciesReport %>%
  filter(!Species_LifeFormNameLocal %in% c("Undefined", "Unknown"),
         is.na(Species_Family) & is.na(Species_Genus))
Unknowns_LifeFormOnly <- unique(Unknowns_LifeFormOnly$Species_SymbolLocal)

Unknowns_FamilyOnly <- SpeciesReport %>%
  filter(!Species_LifeFormNameLocal %in% c("Undefined", "Unknown"),
         !is.na(Species_Family) & is.na(Species_Genus) & is.na(Species_ScientificName))
Unknowns_FamilyOnly <- unique(Unknowns_FamilyOnly$Species_SymbolLocal)

Unknowns_GenusOnly <- SpeciesReport %>%
  filter(Species_ScientificName == Species_Genus)
Unknowns_GenusOnly <- unique(Unknowns_GenusOnly$Species_SymbolLocal)


Unknowns <- c(Unknowns_MysteryPlants, Unknowns_LifeFormOnly, Unknowns_FamilyOnly, Unknowns_GenusOnly)
```

### Add Columns

```{r filter data, include=FALSE}
# Clean up data frame
df_names <- c("Fuels1000", "FuelsDuffLitt", "FuelsFine", "Trees", "Seedlings", "HerbsSpComp", "HerbsPoints")

for (name in df_names) {
  # load data
  current_df <- get(name)
  
  # add year
  filtered_df <- current_df %>% 
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date)) %>% 
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date)
  
    # rename and save
  assign(name, filtered_df)
}

#############################################################################################################

# Clean up data frame
df_names <- c("Trees", "Seedlings", "HerbsSpComp", "HerbsPoints")

for (name in df_names) {
  # load data
  current_df <- get(name)
  
  # add nativity
  filtered_df <- current_df %>% 
    mutate(Species_NativityLocal = toupper(Species_NativityLocal),
           Species_Invasive = toupper(Species_Invasive)) %>% 
    mutate(Species_NativityStatus = ifelse(Species_SymbolLocal %in% Unknowns & Species_NativityLocal %in% c("FALSE","F") & Species_Invasive %in% c("FALSE","F"), "Unknown",
                                   ifelse(Species_LifeFormNameLocal == "Undefined", "Substrate",
                                          ifelse(Species_NativityLocal %in% c("TRUE","T"), "Native",
                                                 ifelse(Species_Invasive %in% c("TRUE","T"), "Invasive", "Nonnative")))))
  
    # rename and save
  assign(name, filtered_df)
}
```

### Columns Keep

```{r}
columns_keep <- c("AdminUnit_Name","Macroplot_Purpose","Macroplot_Type","Macroplot_UV1","Macroplot_UV2","Macroplot_UV3","Macroplot_UV4","Macroplot_UV5","Macroplot_UV6","Macroplot_UV7","Macroplot_UV8","Macroplot_Name","MonitoringStatus_Name","MonitoringStatus_Prefix","MonitoringStatus_Base","MonitoringStatus_Suffix","MonitoringStatus_Order","SampleEvent_TreatmentUnit","SampleEvent_Date","SampleEvent_Date_Year")
```

# Fuels

## Summary Statistics

### Fuels 1000

```{r calculate fuel loads thousand hour, include=FALSE}
# -------------------------- #
# ---- 1,000-Hour Fuels ---- #
# -------------------------- #

# Assign data
fuels_df <- Fuels1000

  # ---- Step 1: Ensure values are numeric before calculations ---- #
  fuels_df <- fuels_df %>% 
    mutate(
      MethodData_Transect = suppressWarnings(as.numeric(MethodData_Transect)),
      MethodData_DecayCl = suppressWarnings(as.numeric(MethodData_DecayCl)),
      MethodData_Dia = suppressWarnings(as.numeric(MethodData_Dia))
      )
  
  # ---- Step 2: Create full grid of expected transects per plot ---- #
  transect_all <- fuels_df %>%
    select(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, SampleEvent_Date, MethodData_NumTran, MethodData_TranLen) %>% 
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, SampleEvent_Date) %>%
    # takes total number of trasects and separates into one row per transect
    tidyr::uncount(weights = MethodData_NumTran, .id = "MethodData_Transect") %>%
    # make sure transect column is numeric
    mutate(MethodData_Transect = suppressWarnings(as.numeric(MethodData_Transect))) %>%
    # rename "TranLen" column into "ThousHrTranLen"
    dplyr::rename(MethodData_ThousHrTranLen = MethodData_TranLen) %>% 
    unique()
  
  # ---- Step 3: Log-level calculations ---- #
  log_level <- fuels_df %>%
    # group all "sound" decay class codes into category 3 
    # and all "rotten" decay class codes into category 4
    mutate(MethodData_DecayCl = ifelse(MethodData_DecayCl %in% c(1,2,3), 3, 4)) %>%
    # calculate fuel loads using fuel constants
    mutate(
      a = 1.0,
      s_sound = 0.4,
      s_rotten = 0.3,
      conversion_factor = 11.64,
      D2 = MethodData_Dia^2,
      s = if_else(MethodData_DecayCl == 3, s_sound, s_rotten),
      slope_correction = sqrt(1 + (MethodData_Slope / 100)^2),
      Load = (conversion_factor * D2 * s * a * slope_correction) / MethodData_TranLen
      #,Load_Adjusted = Load / MethodData_NumTran
    )
  
  # ---- Step 4A: Transect-level values ---- #
  transect_level_step1 <- log_level %>% 
   group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, SampleEvent_Date, MethodData_Transect) %>% 
    dplyr::reframe(
      MethodData_ThousHrTranLen     = MethodData_TranLen,
      MethodData_ThousHrSound       = sum((MethodData_DecayCl == 3), na.rm = TRUE),
      MethodData_ThousHrRott        = sum((MethodData_DecayCl == 4), na.rm = TRUE),
      MethodData_ThousHr            = sum((MethodData_DecayCl %in% c(3,4)), na.rm = TRUE),
      Tran_ThousHrSound_FuelLoad    = sum(Load[MethodData_DecayCl == 3], na.rm = TRUE),
      Tran_ThousHrRott_FuelLoad     = sum(Load[MethodData_DecayCl == 4], na.rm = TRUE),
      Tran_ThousHr_FuelLoad         = sum(Load, na.rm = TRUE)
    )
  
  # ---- Step 4B: Bring zeros back in for transects with no logs ---- #
  transect_level <- transect_all %>%
    left_join(transect_level_step1,
              by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "SampleEvent_Date", "MethodData_ThousHrTranLen", "MethodData_Transect")) %>%
    mutate(
      MethodData_ThousHrSound       = replace_na(MethodData_ThousHrSound, 0),
      MethodData_ThousHrRott        = replace_na(MethodData_ThousHrRott, 0),
      MethodData_ThousHr            = replace_na(MethodData_ThousHr, 0),
      Tran_ThousHrSound_FuelLoad    = replace_na(Tran_ThousHrSound_FuelLoad, 0),
      Tran_ThousHrRott_FuelLoad     = replace_na(Tran_ThousHrRott_FuelLoad, 0),
      Tran_ThousHr_FuelLoad         = replace_na(Tran_ThousHr_FuelLoad, 0)
    ) %>% 
    unique()

  
  # ---- Step 5: Plot-level values---- #
  plot_level <- transect_level %>%
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, SampleEvent_Date) %>%
    dplyr::reframe(
      
      # ---- KEEP TRANSECT FUEL COUNTS ---- #
      MethodData_Transect            = MethodData_Transect,
      MethodData_ThousHrTranLen      = MethodData_ThousHrTranLen,
      MethodData_ThousHrSound        = MethodData_ThousHrSound,
      MethodData_ThousHrRott         = MethodData_ThousHrRott,
      MethodData_ThousHr             = MethodData_ThousHr,
      
      # ---- KEEP TRANSECT FUEL LOADS ---- #
      Tran_ThousHrSound_FuelLoad     = Tran_ThousHrSound_FuelLoad,
      Tran_ThousHrRott_FuelLoad      = Tran_ThousHrRott_FuelLoad,
      Tran_ThousHr_FuelLoad          = Tran_ThousHr_FuelLoad,
      
      # ---- plot-level counts ---- #
      MethodData_ThousHrSound_Total  = sum((MethodData_ThousHrSound), na.rm = TRUE),
      MethodData_ThousHrRott_Total   = sum((MethodData_ThousHrRott), na.rm = TRUE),
      MethodData_ThousHr_Total       = sum((MethodData_ThousHr), na.rm = TRUE),
      
      # ---- plot-level fuels ---- #
      Plot_ThousHrSound_FuelLoad      = mean(Tran_ThousHrSound_FuelLoad, na.rm = TRUE),
      Plot_ThousHrRott_FuelLoad       = mean(Tran_ThousHrRott_FuelLoad, na.rm = TRUE),
      Plot_ThousHr_FuelLoad           = mean(Tran_ThousHr_FuelLoad, na.rm = TRUE)
    )
  
  
  # Summary file
  Fuels1000_sum <- plot_level
```

### Fuels Duff Litter

```{r calculate fuel loads duff litt, include=FALSE}
# -------------------------------------- #  
# ---- Litter and Duff Measurements ---- #
# -------------------------------------- #

# Assign data
fuels_df <- FuelsDuffLitt
  
  # ---- Step 1: Ensure values are numeric before calculations ---- #
  fuels_df <- fuels_df %>% 
    mutate(
      MethodData_Transect = suppressWarnings(as.numeric(MethodData_Transect))
      )

  # ---- Step 2: Transect-level values ---- #
  transect_level <- fuels_df %>%
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, SampleEvent_Date, MethodData_Transect, MethodData_NumTran) %>% 
    # calculate average litter/duff depth by transect
    dplyr::reframe(
      Tran_LittDep = mean(MethodData_LittDep, na.rm = TRUE),
      Tran_DuffDep = mean(MethodData_DuffDep, na.rm = TRUE)
    ) %>%
    # replace empty values with 0
    mutate(
      Tran_LittDep = ifelse(is.nan(Tran_LittDep), 0, Tran_LittDep),
      Tran_DuffDep = ifelse(is.nan(Tran_DuffDep), 0, Tran_DuffDep)
    ) %>% 
    # keep only valid transects
    filter(MethodData_Transect <= MethodData_NumTran) %>%   
    # calculate fuel loads using fuel constants
    mutate(
      # FFI default bulk density for litter (2.75)
      litter_bd = 2.75 * 1.815, 
      # FFI default bulk density for duff (5.5)
      duff_bd   = 5.5  * 1.815, 
      Tran_Litt_FuelLoad = Tran_LittDep * litter_bd,
      Tran_Duff_FuelLoad   = Tran_DuffDep * duff_bd,
      Tran_LittDuff_FuelLoad  = Tran_Litt_FuelLoad + Tran_Duff_FuelLoad
    )
  
  # ---- Step 3: Plot-level values---- #
  plot_level <- transect_level %>%
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, SampleEvent_Date) %>%
    dplyr::reframe(
      
      # ---- KEEP TRANSECT FUEL VALUES ---- #
      MethodData_Transect = MethodData_Transect,
      Tran_LittDep = Tran_LittDep,
      Tran_DuffDep = Tran_DuffDep,
      Tran_Litt_FuelLoad = Tran_Litt_FuelLoad,
      Tran_Duff_FuelLoad   = Tran_Duff_FuelLoad,
      Tran_LittDuff_FuelLoad  = Tran_LittDuff_FuelLoad,
      
      # ---- plot-level depth ---- #
      Plot_LittDep = mean(Tran_LittDep, na.rm = TRUE),
      Plot_DuffDep = mean(Tran_DuffDep, na.rm = TRUE),
  
      # ---- plot-level fuels ---- #
      Plot_Litt_FuelLoad = mean(Tran_Litt_FuelLoad, na.rm = TRUE),
      Plot_Duff_FuelLoad   = mean(Tran_Duff_FuelLoad, na.rm = TRUE),
      Plot_LittDuff_FuelLoad  = mean(Tran_LittDuff_FuelLoad, na.rm = TRUE)
  ) %>% 
    mutate(Plot_LittDep = na_if(Plot_LittDep, NaN),
           Plot_DuffDep = na_if(Plot_DuffDep, NaN),
           Plot_Litt_FuelLoad = na_if(Plot_Litt_FuelLoad, NaN),
           Plot_Duff_FuelLoad = na_if(Plot_Duff_FuelLoad, NaN),
           Plot_LittDuff_FuelLoad = na_if(Plot_LittDuff_FuelLoad, NaN)
           )

  # Summary file
  FuelsDuffLitt_sum <- plot_level
```

### Fuels Fine

```{r calculate fuel loads fine, include=FALSE}
# ------------------------------------- #
# ---- Fine Fuels (1,10,100-Hours) ---- #
# ------------------------------------- #

# Assign data
fuels_df <- FuelsFine

  # ---- Step 1: Transect-level values ---- #
  transect_level <- fuels_df %>%
    mutate(
      d2_1hr = 0.0151,
      d2_10hr = 0.289, 
      d2_100hr = 2.76, 
      s_1hr_10hr = 0.48,
      s_100hr = 0.40,
      a = 1.13,
      c = sqrt(1 + (MethodData_Slope / 100)^2),
      Tran_OneHr_FuelLoad = (11.64 * MethodData_OneHr * d2_1hr   * s_1hr_10hr * a * c) / MethodData_OneHrTranLen,
      Tran_TenHr_FuelLoad = (11.64 * MethodData_TenHr * d2_10hr  * s_1hr_10hr * a * c) / MethodData_TenHrTranLen,
      Tran_HunHr_FuelLoad = (11.64 * MethodData_HunHr * d2_100hr * s_100hr    * a * c) / MethodData_HunHrTranLen,
      Tran_Fine_FuelLoad = Tran_OneHr_FuelLoad + Tran_TenHr_FuelLoad + Tran_HunHr_FuelLoad
    )
  
  
  # ---- Step 2: Plot-level values---- #
  plot_level <- transect_level %>%
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, SampleEvent_Date) %>%
    dplyr::reframe(
      # ---- KEEP TRANSEC LEVEL INFO ---- #
      MethodData_NumTran = MethodData_NumTran,
      MethodData_OneHrTranLen = MethodData_OneHrTranLen,
      MethodData_TenHrTranLen = MethodData_TenHrTranLen,
      MethodData_HunHrTranLen = MethodData_HunHrTranLen,
      
      # ---- KEEP TRANSECT FUEL COUNTS ---- #
      MethodData_Transect = MethodData_Transect,
      MethodData_OneHr = MethodData_OneHr,
      MethodData_TenHr = MethodData_TenHr,
      MethodData_HunHr = MethodData_HunHr,
      
      # ---- KEEP TRANSECT FUEL LOADS ---- #
      Tran_OneHr_FuelLoad   = Tran_OneHr_FuelLoad,
      Tran_TenHr_FuelLoad  = Tran_TenHr_FuelLoad,
      Tran_HunHr_FuelLoad  = Tran_HunHr_FuelLoad,
      
      # ---- plot-level counts ---- #
      MethodData_OneHr_Total = sum((MethodData_OneHr), na.rm = TRUE),
      MethodData_TenHr_Total = sum((MethodData_TenHr), na.rm = TRUE),
      MethodData_HunHr_Total = sum((MethodData_HunHr), na.rm = TRUE),
      
      # ---- plot-level fuels ---- #
      Plot_OneHr_FuelLoad = mean(Tran_OneHr_FuelLoad, na.rm = TRUE),
      Plot_TenHr_FuelLoad   = mean(Tran_TenHr_FuelLoad, na.rm = TRUE),
      Plot_HunHr_FuelLoad  = mean(Tran_HunHr_FuelLoad, na.rm = TRUE)
    )

  # Summary file
  FuelsFine_sum <- plot_level
```

## Combine Fuels

```{r combine dataframes fuels, include=FALSE}
# ============================================================= #
# ====  Select metadata columns to keep for graphing data  ==== #
# ============================================================= #
FuelsFine_meta <- FuelsFine %>% 
  select(all_of(columns_keep), MethodData_Transect) %>%
  unique()

# ============================================================= #
# ==== Join 1-100-hr, litter-duff, and 1,000-hr dataframes ==== #
# ============================================================= #
Fuels_calc <- FuelsFine_meta %>%
  dplyr::full_join(FuelsFine_sum, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "SampleEvent_Date", "MethodData_Transect")) %>%
  dplyr::full_join(FuelsDuffLitt_sum, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "SampleEvent_Date", "MethodData_Transect")) %>% 
  dplyr::full_join(Fuels1000_sum, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "SampleEvent_Date", "MethodData_Transect")) %>% 
  relocate(MethodData_ThousHrTranLen, .after = MethodData_HunHrTranLen) %>% 
  relocate(MethodData_Transect, .after = MethodData_ThousHrTranLen) %>%
  relocate(MethodData_OneHr_Total, .after = MethodData_OneHr) %>%
  relocate(MethodData_TenHr_Total, .after = MethodData_TenHr) %>%
  relocate(MethodData_HunHr_Total, .after = MethodData_HunHr) %>%
  relocate(MethodData_ThousHrSound, .after = MethodData_HunHr_Total) %>% 
  relocate(MethodData_ThousHrSound_Total, .after = MethodData_ThousHrSound) %>% 
  relocate(MethodData_ThousHrRott, .after = MethodData_ThousHrSound_Total) %>%
  relocate(MethodData_ThousHrRott_Total, .after = MethodData_ThousHrRott) %>%
  relocate(MethodData_ThousHr, .after = MethodData_ThousHrRott_Total) %>%
  relocate(MethodData_ThousHr_Total, .after = MethodData_ThousHr)
```

```{r}
write.csv(Fuels_calc, paste0(path_save, "fuels.csv"), quote = FALSE, row.names = FALSE)
```

# Trees

## Poles & Overstory

```{r}
# ------------------------------------- #
# ------           Trees         ------ #
# ------------------------------------- #
#trees_df <- Trees
# ---- Function to calculate tree density for any park dataset ---- #
calculate_trees_dens <- function(trees_df) {
  

  # ---- Step 1: Compute useful values ---- #
  plot_level <- trees_df %>%
    mutate(
      Hectar = (MethodData_SubFrac * 1000) / 10000,
      Acre = Hectar * 2.47105,
      SizeCl = if_else(MethodData_DBH < 15.0, "Pole", "Overstory"),
      Ht_m = MethodData_Ht,
      Ht_ft = round((MethodData_Ht * 3.28084), 2),
      DBH_cm = MethodData_DBH,
      DBH_in = round((MethodData_DBH * 0.39370079), 2),
      BA_m2 = pi * (DBH_cm / 200)^2,
      BA_ft2 = pi *((DBH_in / 12)/2)^2
    )

      
  # ---- Step 2: Plot-level summaries ---- #
  ## ------------ Pole-Sized ------------ ##
  plot_level_pole <- plot_level %>% 
    filter(SizeCl == "Pole") %>% 
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_Genus, Species_ScientificName, MethodData_Status) %>% 
    dplyr::reframe(
      Avg_Pole_Ht_m = round(mean(Ht_m), 1),
      Avg_Pole_Ht_ft = round(mean(Ht_ft), 1),
      Avg_Pole_Dia_cm = round(mean(DBH_cm), 1),
      Avg_Pole_Dia_in = round(mean(DBH_in), 1),
      Pole_Count = n_distinct(MethodData_TagNo),
      #Pole_Species = paste(na.omit(unique(Species_SymbolLocal)), collapse = "; "),
      Pole_Dens_ha = round(Pole_Count / Hectar),
      Pole_Dens_ac = round(Pole_Count / Acre),
      Pole_BA_m2 = round((sum(BA_m2)/Hectar), 2),
      Pole_BA_ft2 = round((sum(BA_ft2)/Acre), 2)
    ) %>% 
    unique()
    
  ## ------------- Overstory ------------- ##
  plot_level_overstory <- plot_level %>% 
    filter(SizeCl == "Overstory") %>% 
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_Genus, Species_ScientificName, MethodData_Status) %>% 
    dplyr::reframe(
      Avg_Overstory_Dia_cm = round(mean(DBH_cm), 1),
      Avg_Overstory_Dia_in = round(mean(DBH_in), 1),
      Overstory_Count = n_distinct(MethodData_TagNo),
      #Overstory_Species = paste(na.omit(unique(Species_SymbolLocal)), collapse = "; "),
      Overstory_Dens_ha = round(Overstory_Count / Hectar),
      Overstory_Dens_ac = round(Overstory_Count / Acre),
      Overstory_BA_m2 = round((sum(BA_m2)/Hectar), 2),
      Overstory_BA_ft2 = round((sum(BA_ft2)/Acre), 2)
    ) %>% 
    unique()

  
  # ---- Step 3: COMBINE ---- #
  plot_level_merge <- plot_level %>% 
    select(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_Genus, Species_ScientificName, MethodData_Status) %>% 
    unique()
  
  plot_level_sum <- plot_level_merge %>% 
    full_join(plot_level_pole, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_Genus", "Species_ScientificName", "MethodData_Status")) %>% 
    full_join(plot_level_overstory, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_Genus", "Species_ScientificName", "MethodData_Status")) %>% 
    mutate(
      Pole_Count     = replace_na(Pole_Count, 0),
      Pole_Dens_ha   = replace_na(Pole_Dens_ha, 0),
      Pole_Dens_ac   = replace_na(Pole_Dens_ac, 0),
      Pole_BA_m2     = replace_na(Pole_BA_m2, 0),
      Pole_BA_ft2    = replace_na(Pole_BA_ft2, 0),
      Overstory_Count      = replace_na(Overstory_Count, 0),
      Overstory_Dens_ha    = replace_na(Overstory_Dens_ha, 0),
      Overstory_Dens_ac    = replace_na(Overstory_Dens_ac, 0),
      Overstory_BA_m2      = replace_na(Overstory_BA_m2, 0),
      Overstory_BA_ft2     = replace_na(Overstory_BA_ft2, 0),
    )
}
```

## Seedlings

```{r}
# ------------------------------------- #
# ----           Seedlings         ---- #
# ------------------------------------- #
#seedlings_df <- Seedlings
# ---- Function to calculate seedling density for any park dataset ---- #
calculate_seedlings_dens <- function(seedlings_df) {
  

  # ---- Step 1: Compute per-transect fuel load ---- #
  plot_level <- seedlings_df %>%
    mutate(
      SizeCl = if_else(MethodData_Height <= 4, "Seedling (< 1m ht)", "Sapling (> 1m ht)"),
      Area = MethodData_QuadLen * MethodData_QuadWid,
      Hectar = Area / 10000,
      Acre = Hectar * 2.47105
    ) %>% 
    relocate(MethodData_Count, .after = Acre) %>% 
    relocate(Species_Genus, .after = Acre) %>% 
    relocate(SizeCl, .after = Acre)

      
  # ---- Step 2: Plot-level summaries ---- #
  ## ------------- Seedlings ------------ ##
  plot_level_seedling <- plot_level %>% 
    filter(SizeCl == "Seedling (< 1m ht)") %>% 
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_Genus, Species_ScientificName, MethodData_Status) %>% 
    dplyr::reframe(
      Seedling_Count = sum(MethodData_Count),
      #Seedling_Species = paste(na.omit(unique(Species_SymbolLocal)), collapse = "; "),
      Seedling_Dens_ha = round(Seedling_Count / Hectar),
      Seedling_Dens_ac = round(Seedling_Count / Acre)
    ) %>% 
    unique()
  ## ------------- Saplings ------------- ##
  plot_level_sapling <- plot_level %>% 
    filter(SizeCl == "Sapling (> 1m ht)") %>% 
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_Genus, Species_ScientificName, MethodData_Status) %>% 
    dplyr::reframe(
      Sapling_Count = sum(MethodData_Count),
      #Sapling_Species = paste(na.omit(unique(Species_SymbolLocal)), collapse = "; "),
      Sapling_Dens_ha = round(Sapling_Count / Hectar),
      Sapling_Dens_ac = round(Sapling_Count / Acre)
    ) %>% 
    unique()

  
  # ---- Step 3: COMBINE ---- #
  plot_level_merge <- plot_level %>% 
    select(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_Genus, Species_ScientificName, MethodData_Status) %>% 
    unique()
  
  plot_level_sum <- plot_level_merge %>% 
    full_join(plot_level_seedling, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_Genus", "Species_ScientificName", "MethodData_Status")) %>% 
    full_join(plot_level_sapling, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_Genus", "Species_ScientificName", "MethodData_Status")) %>% 
    mutate(
      Seedling_Count     = replace_na(Seedling_Count, 0),
      Seedling_Dens_ha   = replace_na(Seedling_Dens_ha, 0),
      Seedling_Dens_ac   = replace_na(Seedling_Dens_ac, 0),
      Sapling_Count      = replace_na(Sapling_Count, 0),
      Sapling_Dens_ha    = replace_na(Sapling_Dens_ha, 0),
      Sapling_Dens_ac    = replace_na(Sapling_Dens_ac, 0)
    )
}
```

## Combine Trees

```{r}
Trees_meta <- Trees %>% 
  select(all_of(columns_keep), Species_Genus, Species_ScientificName, MethodData_Status) %>% 
  unique()
Seedlings_meta <- Seedlings %>%
  select(all_of(columns_keep), Species_Genus, Species_ScientificName, MethodData_Status) %>%
  unique()

Trees_sum <- calculate_trees_dens(Trees)
Seedlings_sum <- calculate_seedlings_dens(Seedlings)
```

```{r combine dataframes trees, include=FALSE}
Trees_calc <- Trees_meta %>% 
  dplyr::full_join(Trees_sum, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_Genus", "Species_ScientificName", "MethodData_Status")) %>% 
  unique()

Seedlings_calc <- Seedlings_meta %>% 
  dplyr::full_join(Seedlings_sum, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_Genus", "Species_ScientificName", "MethodData_Status")) %>% 
  unique()

Trees_all_calc <-  Trees_calc %>% 
  dplyr::full_join(Seedlings_calc, by = c(columns_keep, "Species_Genus", "Species_ScientificName", "MethodData_Status")) %>% 
  mutate(
    Seedling_Count     = replace_na(Seedling_Count, 0),
    Seedling_Dens_ha   = replace_na(Seedling_Dens_ha, 0),
    Seedling_Dens_ac   = replace_na(Seedling_Dens_ac, 0),
    Sapling_Count      = replace_na(Sapling_Count, 0),
    Sapling_Dens_ha    = replace_na(Sapling_Dens_ha, 0),
    Sapling_Dens_ac    = replace_na(Sapling_Dens_ac, 0),
    Pole_Count         = replace_na(Pole_Count, 0),
    Pole_Dens_ha       = replace_na(Pole_Dens_ha, 0),
    Pole_Dens_ac       = replace_na(Pole_Dens_ac, 0),
    Pole_BA_m2         = replace_na(Pole_BA_m2, 0),
    Pole_BA_ft2        = replace_na(Pole_BA_ft2, 0),
    Overstory_Count    = replace_na(Overstory_Count, 0),
    Overstory_Dens_ha  = replace_na(Overstory_Dens_ha, 0),
    Overstory_Dens_ac  = replace_na(Overstory_Dens_ac, 0),
    Overstory_BA_m2    = replace_na(Overstory_BA_m2, 0),
    Overstory_BA_ft2   = replace_na(Overstory_BA_ft2, 0)
  )
```

```{r}
# write.csv(Trees_calc, paste0(path_save, "Data_Trees.csv"), quote = FALSE, row.names = FALSE)
# write.csv(Seedlings_calc, paste0(path_save, "Data_Seedlings.csv"), quote = FALSE, row.names = FALSE)
write.csv(Trees_all_calc, paste0(path_save, "trees.csv"), quote = FALSE, row.names = FALSE)
```

# Cover

## Build list of species not in Herbs Points

```{r}
# isolate unique species in all protocols
UniqueSpecies_HerbsPoints <- HerbsPoints %>% 
  group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name) %>%
  filter(MethodData_Status == "L",
         !(is.na(Species_ScientificName))) %>% 
  distinct(Species_LifeFormNameLocal, Species_Genus, Species_ScientificName, Species_NativityStatus)

UniqueSpecies_HerbsSpComp <- HerbsSpComp %>% 
  group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name) %>%
  filter(!is.na(Species_ScientificName)) %>% 
  distinct(Species_LifeFormNameLocal, Species_Genus, Species_ScientificName, Species_NativityStatus)

# identify species found in HerbsSpComp but not in HerbsPoints
UniqueSpecies_missing <- anti_join(UniqueSpecies_HerbsSpComp, UniqueSpecies_HerbsPoints)
```

## Cover Points

```{r}
# ------------------------------------- #
# ------           Herbs         ------ #
# ------------------------------------- #
cover_df <- HerbsPoints
# ---- Function to calculate herbaceous cover for any park dataset ---- #
calculate_Points_cover <- function(cover_df) {
  
  # ---- Step 1: Plot-level summaries ---- #
  ## ------------- Total Plot ------------ ##
  # plot_level <- cover_df %>%
  #   group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name) %>% 
  #   dplyr::reframe(
  #     n_species_plot = n_distinct(Species_ScientificName)
  #     ) %>% 
  #   unique()
  ## ------------- By Species ------------ ##
  plot_level_species <- cover_df %>% 
    mutate(MethodData_NumPtsTran = ifelse(MethodData_NumPtsTran == 0, 100, MethodData_NumPtsTran)) %>% 
    group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_LifeFormNameLocal, Species_Genus, Species_ScientificName, Species_NativityStatus) %>% 
    dplyr::reframe(
      #Species = paste(na.omit(unique(Species_SymbolLocal)), collapse = "; "),
      Hits = n(),
      PctCover = round(((Hits / (MethodData_NumPtsTran * MethodData_NumTran)) * 100), 1),
      Avg_Ht_m = round(mean(MethodData_Height, na.rm = TRUE), 2),
      Avg_Ht_ft = round((Avg_Ht_m * 3.28084), 1)
      ) %>% 
    mutate(
      Avg_Ht_m    = replace_na(Avg_Ht_m, 0),
      Avg_Ht_ft   = replace_na(Avg_Ht_ft, 0)
    ) %>% 
    unique()
  
  
  
  # ---- Step 2: COMBINE ---- #
  plot_level_merge <- cover_df %>%
    select(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_LifeFormNameLocal, Species_Genus, Species_ScientificName, Species_NativityStatus) %>%
    unique()
  
  plot_level_sum <- plot_level_merge %>% 
    # full_join(plot_level, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name")) %>% 
    full_join(plot_level_species, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_LifeFormNameLocal", "Species_Genus", "Species_ScientificName", "Species_NativityStatus"))
  
}
```

## Cover Species Comp

```{r}
# ------------------------------------- #
# ---- Cover Species Composition   ---- #
# ------------------------------------- #
#cover_df <- HerbsSpComp
# ---- Function to calculate 1-100-hr fuels for any park dataset ---- #
calculate_SpComp_cover <- function(cover_df) {

  
  # ---- Step 1: Add useful columns ---- #
  plot_level_sum <- UniqueSpecies_missing

  
  # plot_level <- UniqueSpecies_HerbsSpComp %>%
  #   group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name) %>%
  #   dplyr::reframe(
  #     n_species_plot = n_distinct(Species_ScientificName)
  #   )
  # 
  # plot_level_species <- UniqueSpecies_HerbsSpComp %>%
  #   group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_LifeFormNameLocal, Species_Genus, Species_ScientificName, Species_NativityStatus) %>%
  #   dplyr::reframe(
  #     Hits = 0,
  #     PctCover = 0.1,
  #     Avg_Ht_m = 0,
  #     Avg_Ht_ft = round((Avg_Ht_m * 3.28084), 1)
  #   )
  # 
  # 
  #   # ---- Step 2: COMBINE ---- #
  # plot_level_merge <- cover_df %>%
  #   select(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name, Species_LifeFormNameLocal, Species_Genus, Species_ScientificName, Species_NativityStatus) %>%
  #   unique()
  # 
  # 
  # plot_level_sum <- plot_level_merge %>% 
  #   full_join(plot_level, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name")) %>% 
  #   full_join(plot_level_species, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_LifeFormNameLocal", "Species_Genus", "Species_ScientificName", "Species_NativityStatus"))
  
}
```

## Combine Cover

```{r}
HerbsPoints_sum <- calculate_Points_cover(HerbsPoints)
HerbsSpComp_sum <- calculate_SpComp_cover(HerbsSpComp)
```

```{r}
Cover_Points_meta <- HerbsPoints %>% 
  select(all_of(columns_keep), Species_LifeFormNameLocal, Species_Genus, Species_ScientificName, Species_NativityStatus) %>%
  unique()

Cover_SpComp_meta <- HerbsSpComp %>%
  select(all_of(columns_keep), Species_LifeFormNameLocal, Species_Genus, Species_ScientificName, Species_NativityStatus) %>%
  unique()

Cover_Points_calc <- Cover_Points_meta %>%
  dplyr::full_join(HerbsPoints_sum, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_LifeFormNameLocal", "Species_Genus", "Species_ScientificName", "Species_NativityStatus"))

Cover_SpComp_calc <- Cover_SpComp_meta %>%
  dplyr::full_join(HerbsSpComp_sum, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name", "Species_LifeFormNameLocal", "Species_Genus", "Species_ScientificName", "Species_NativityStatus"))
```

```{r}
Cover_all_merge <- Cover_Points_calc %>% 
  dplyr::full_join(Cover_SpComp_calc, by = c(columns_keep, "Species_LifeFormNameLocal", "Species_Genus", "Species_ScientificName", "Species_NativityStatus")) %>% 
  arrange(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, SampleEvent_Date, Species_ScientificName) %>% 
  mutate(
    Hits       = replace_na(Hits, 0),
    PctCover   = replace_na(PctCover, 0.1),
    Avg_Ht_m   = replace_na(Avg_Ht_m, 0),
    Avg_Ht_ft  = replace_na(Avg_Ht_ft, 0)
  )


plot_level <- Cover_all_merge %>%
  group_by(AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, MonitoringStatus_Name) %>%
  dplyr::reframe(
    n_species_plot = n_distinct(Species_ScientificName)
    )
  
  
Cover_all_calc <- Cover_all_merge %>%
  full_join(plot_level, by = c("AdminUnit_Name", "Macroplot_Purpose", "Macroplot_Type", "Macroplot_Name", "MonitoringStatus_Name"))
```

```{r}
# write.csv(Cover_Points_calc, paste0(path_save, "cover_points.csv"), quote = FALSE, row.names = FALSE)
# write.csv(Cover_SpComp_calc, paste0(path_save, "cover_comp.csv"), quote = FALSE, row.names = FALSE)
write.csv(Cover_all_calc, paste0(path_save, "cover.csv"), quote = FALSE, row.names = FALSE)
```
