---
title: FFI Database Calculations
author: NPS Northeast Region Fire Effects Monitoring Program
output:
  word_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# PURPOSE

This code is for adding columns to metadata for graphing and reporting.

-   all_metadata.csv
-   all_species_info.csv

## Before Starting {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
```

```{r load packages, include=FALSE}
# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
library(stringr)
library(DT)
library(fs)
```

### Adjust File Paths {.hidden}

```{r file paths, include=FALSE}
path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Clean/FFI/")
path_save <- paste0(path_main, "Exports_Reporting/FFI/")
```

### Load Data {.hidden}

```{r load data, include=FALSE}
MetadataReport <- read.csv(paste0(path_data, "all_metadata.csv"))
SpeciesReport <- read.csv(paste0(path_data, "all_species_info.csv"))
```

### Define Codes

```{r}
zone_NewEngland <- c("ACAD", "CACO")
zone_MidAtlantic <- c("DEWA", "GATE", "GETT", "SARA", "VAFO")
zone_NCA <- c("ANTI", "CATO", "MONO", "PRWI")
zone_Allegheny <- c("CUVA", "NERI")
zone_MTTS <- c("APCO", "FRSP", "RICH", "SHEN")
zone_North <- c(zone_NewEngland, zone_MidAtlantic)
zone_South <- c(zone_Allegheny, zone_MTTS)
```

# Metadata Report

### Basic Columns

-   Region (NER)

-   Zone (e.g. South)

-   Unit (e.g. MTTS)

-   Purpose Code (FMH, CBI, RA, I&M)

-   Plot Type combines Purpose and Type (FMH - Forest, FMH - Grassland, ...)

-   Macroplot_Num (01, 02...)

```{r}
MetadataReport_all <- MetadataReport %>% 
  # Region
  mutate(AdminUnit_Region = ifelse(AdminUnit_Name %in% c(zone_NCA), "NCR", "NER")) %>% 
  # Zone
  mutate(AdminUnit_Zone = ifelse(AdminUnit_Name %in% zone_North, "North",
                       ifelse(AdminUnit_Name %in% zone_South, "South", 
                              "NCA"))) %>% 
  # Unit
  mutate(AdminUnit_Unit = ifelse(AdminUnit_Name %in% zone_NewEngland, "NewEngland",
                       ifelse(AdminUnit_Name %in% zone_MidAtlantic, "MidAtlantic",
                              ifelse(AdminUnit_Name %in% zone_Allegheny,"Allegheny",
                                    ifelse(AdminUnit_Name %in% zone_MTTS, "MTTS", 
                                           "NCA"))))) %>%
  # Purpose Code
  mutate(Macroplot_PurposeCode = ifelse(Macroplot_Purpose == "Fire Monitoring Handbook", "FMH",
                            ifelse(Macroplot_Purpose == "Inventory & Monitoring", "I&M",
                                   ifelse(Macroplot_Purpose == "Composite Burn Index", "CBI",
                                          ifelse(Macroplot_Purpose == "Rapid Assessment","RA", "FMH"))))) %>%
  # Plot Type
  mutate(Macroplot_PurposeType = paste0(Macroplot_PurposeCode, " - ", Macroplot_Type)) %>% 
  # Macroplot code and number
  extract(Macroplot_Name, regex = "([0-9]+)", into = c("Macroplot_Num"), remove = F) %>% 
  separate(Macroplot_Name, sep = "(?=[0-9])", into = c("Macroplot_Code"), remove = F) %>%
  mutate(Macroplot_Num = ifelse(is.na(Macroplot_Num), 0, Macroplot_Num)) %>% 
  mutate(Macroplot_Num = as.numeric(Macroplot_Num)) %>% 
  # Add years to all date columns
  mutate(Macroplot_DateIn = as.Date(Macroplot_DateIn)) %>% 
  mutate(Macroplot_DateIn_Year = year(Macroplot_DateIn)) %>% 
  mutate(Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit)) %>% 
  mutate(Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit)) %>% 
  mutate(Macroplot_DateOut = as.Date(Macroplot_DateOut)) %>% 
  mutate(Macroplot_DateOut_Year = year(Macroplot_DateOut)) %>% 
  mutate(SampleEvent_Date = as.Date(SampleEvent_Date)) %>% 
  mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
  # Reorganize columns
  relocate(AdminUnit_Region, .before = AdminUnit_Name) %>% 
  relocate(AdminUnit_Zone, .before = AdminUnit_Name) %>%
  relocate(AdminUnit_Unit, .before = AdminUnit_Name) %>% 
  relocate(Macroplot_PurposeCode, .after = Macroplot_Purpose) %>% 
  relocate(Macroplot_PurposeType, .after = Macroplot_Type) %>% 
  relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
  relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
  relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>% 
  relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
  # Remove columns
  select(!c(Macroplot_LocatedBy, Macroplot_StartPoint, Macroplot_Directions, Macroplot_Comment, Macroplot_Metadata, SampleEvent_Who, SampleEvent_Comment, SampleEvent_LegacyMonitoringStatus,
            Macroplot_UtmX_m, Macroplot_UtmY_m, Macroplot_UtmZone, Macroplot_Datum, Macroplot_Pdop, Macroplot_Precision))
```

### Calculations

```{r}
MetadataReport_all <- MetadataReport_all %>% 
  # Calculations
  group_by(AdminUnit_Name, Macroplot_PurposeType) %>%
  dplyr::mutate(n_plots_ByPurposeType = n_distinct(Macroplot_Name)) %>% 
  group_by(AdminUnit_Name, Macroplot_PurposeType, Macroplot_UV1) %>% 
  dplyr::mutate(n_plots_ByProjectUnit = n_distinct(Macroplot_Name)) %>%
  group_by(AdminUnit_Name, Macroplot_PurposeType, Macroplot_UV2) %>% 
  dplyr::mutate(n_plots_ByMonitoringType = n_distinct(Macroplot_Name)) %>% 
  ungroup()
```

### Split MetadataReport

```{r}
MetadataReport_Disturbances <- MetadataReport_all %>% 
  filter(MonitoringStatus_Name %in% c("", "Burn", "Herbicide", "Mechanical", "Mow")) %>%  
  mutate(Disturbance_Date = SampleEvent_Date) %>% 
  mutate(Disturbance_Date_Year = SampleEvent_Date_Year)


MetadataReport_Reads <- MetadataReport_all %>% 
  filter(!MonitoringStatus_Name %in% c("", "Burn", "Herbicide", "Mechanical", "Mow")) %>% 
  mutate(Disturbance_Date = NA) %>% 
  mutate(Disturbance_Date_Year = NA)
```

#### MonStatus

-   Entry / Prefix (0, 1, 2, 3 , 4...)

-   Status (pre, post)

-   TimeSince / Suffix (0, 1, 2, 5, 10, 20)

```{r}
MonStatus <- MetadataReport_Reads %>%
  select(MonitoringStatus_Name) %>%
  filter(!is.na(MonitoringStatus_Name))
MonStatus <- unique(MonStatus)

# Create column with consistent naming
MonStatus <- MonStatus %>%
  mutate(MonStatus_new = ifelse(MonitoringStatus_Name %in%  c("Pre", "PRE", "00Pre", "Preyr00", "Measure", "2001Density", "2001Measure", "2002Density", "2002Measure", "2003Density", "2003Measure", "2004Measure"), "00 Pre",
                                ifelse(MonitoringStatus_Name %in% c("Pre 2", "Pre 02"), "00 PR1",
                                       ifelse(MonitoringStatus_Name %in% c("Pre 3"), "00 PR2",
                                              ifelse(MonitoringStatus_Name %in% c("Pre 4"), "00 PR3",
                                                     ifelse(MonitoringStatus_Name %in% c("Pre 5"), "00 PR4",
                                                            ifelse(MonitoringStatus_Name %in% c("01Post", "01PostBurn"), "01 Post 00",
                                                                   ifelse(MonitoringStatus_Name %in% c("01yr01", "01Year01"), "01 Yr 01",
                                                                          ifelse(MonitoringStatus_Name %in% c("01Yr02"), "01 Yr 02",
                                                                                 ifelse(MonitoringStatus_Name %in% c("01Yr03"), "01 Yr 03",
                                                                                        ifelse(MonitoringStatus_Name %in% c("06 yr 05"), "06 Yr 05", 
                                                                                               ifelse(MonitoringStatus_Name %in% c("00 Post (Initial CBI)", "01 Post (Extended CBI)", "01 Post (Initial CBI)", "02 Post (Extended CBI)", "03 Post (Extended CBI)", "Severity"), "01 Post 00", MonitoringStatus_Name))))))))))))

#order <- seq(1, nrow(MonStatus))

# Extract info
MonStatus <- MonStatus %>%
  arrange(MonStatus_new) %>%
  dplyr::mutate(MonitoringStatus_Order = row_number()) %>%
  separate(MonStatus_new, sep = " ", into = c("Entry","Status","TimeSince"), remove = F) %>%
  # fix up classifications
  mutate(Status = ifelse(Status %in% c("Yr", "yr"), "Year", Status)) %>%
  mutate(Status = ifelse(Status %in%  c("PR1", "PR2", "PR3", "PR4"), "Pre", Status)) %>%
  mutate(TimeSince = ifelse(Status == "Post", 0, TimeSince)) %>% 
  # make columns numeric
  mutate(Entry = as.numeric(Entry),
         TimeSince = as.numeric(TimeSince)) %>%
  select(!MonStatus_new)
```

#### Disturbance

-   Disturbance_Type (Burn, Herbicide, Mechanical, Mow)

-   Disturbance_Year (actual year)

```{r}
Disturbances <- MetadataReport_Disturbances %>% 
  filter(MonitoringStatus_Name == "Burn") %>% 
  arrange(AdminUnit_Name, Macroplot_Name, SampleEvent_Date) %>% 
  group_by(AdminUnit_Name, Macroplot_Name) %>% 
  dplyr::mutate(Entry = row_number(),
         Status = "Post",
         TimeSince = 0,
         MonitoringStatus_Order = NA) %>% 
  ungroup() %>% 
  select(AdminUnit_Name, Macroplot_Name, SampleEvent_Date, Entry, Status, TimeSince, MonitoringStatus_Order)
```

#### Merge

```{r}
# Disturbance
MetadataReport_Disturbances <- merge(MetadataReport_Disturbances, Disturbances, all = T)

# Mon Status
MetadataReport_Reads <- merge(MetadataReport_Reads, MonStatus, by = c("MonitoringStatus_Name"), all = T)

# Merge all
MetadataReport_all <- rbind(MetadataReport_Disturbances, MetadataReport_Reads) %>%
  arrange(AdminUnit_Name, Macroplot_Name, SampleEvent_Date)
```

### Other? {.hidden}

-   Disturbance_Entry (to match with MonStatus)

-   Disturbance_Desc (RX, WF-SUPP, WFU, WF)

-   Disturbance_Name (e.g. Cape Final)

-   Disturbance_Severity (Unaltered, Low, Low/Moderate, Moderate, Moderate/High, High)

-   FuelType (PIPO, PIED, etc.)

### Save

```{r}
write.csv(MetadataReport_all, paste0(path_save, "all_metadata.csv"), quote = FALSE, row.names = FALSE)
```

# Species Report

### Define Unknowns

```{r}
Substrates <- SpeciesReport %>%
  filter(Species_LifeFormNameLocal == "Undefined")
Substrates <- unique(Substrates$Species_LocalSpeciesSymbol)
  
Unknowns_MysteryPlants <- SpeciesReport %>%
  filter(Species_LifeFormNameLocal == "Unknown")
Unknowns_MysteryPlants <- unique(Unknowns_MysteryPlants$Species_LocalSpeciesSymbol)

Unknowns_LifeFormOnly <- SpeciesReport %>%
  filter(!Species_LifeFormNameLocal %in% c("Undefined", "Unknown"),
         is.na(Species_Family) & is.na(Species_Genus))
Unknowns_LifeFormOnly <- unique(Unknowns_LifeFormOnly$Species_LocalSpeciesSymbol)

Unknowns_FamilyOnly <- SpeciesReport %>%
  filter(!Species_LifeFormNameLocal %in% c("Undefined", "Unknown"),
         !is.na(Species_Family) & is.na(Species_Genus) & is.na(Species_ScientificName))
Unknowns_FamilyOnly <- unique(Unknowns_FamilyOnly$Species_LocalSpeciesSymbol)

Unknowns_GenusOnly <- SpeciesReport %>%
  filter(Species_ScientificName == Species_Genus)
Unknowns_GenusOnly <- unique(Unknowns_GenusOnly$Species_LocalSpeciesSymbol)



Unknowns <- c(Unknowns_MysteryPlants, Unknowns_LifeFormOnly, Unknowns_FamilyOnly, Unknowns_GenusOnly)
```

### Basic Columns

```{r}
SpeciesReport_all <- SpeciesReport %>% 
  mutate(Species_Nativity = ifelse(Species_LocalSpeciesSymbol %in% Unknowns & Species_NativityLocal == "False" & Species_Invasive == "False", "Unknown",
                                   ifelse(Species_LifeFormNameLocal == "Undefined", "Substrate",
                                          ifelse(Species_NativityLocal == "True", "Native",
                                                 ifelse(Species_Invasive == "True", "Invasive", "Nonnative"))))) %>% 
  select(c(AdminUnit_Name, Species_LocalSpeciesSymbol, Species_Family, Species_Genus, Species_ScientificName, Species_CommonNameLocal, Species_LifeFormNameLocal, Species_Nativity, Species_NativityLocal, Species_Invasive, Species_LifeCycleLocal, Species_UV1, Species_UV2, Species_UV3))
```

### Save

```{r}
write.csv(SpeciesReport_all, paste0(path_save, "all_species_info.csv"), quote = FALSE, row.names = FALSE)
```
