---
title: "SHEN Report"
subtitle: Northeast Region
output:
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
  pdf_document:
    toc: true
    toc_depth: 2
  word_document:
    toc: true
    toc_depth: 2
---

# Annual Report

### Setup {.hidden}

```{r}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
```

```{r}
## Load Packages

# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
library(stringr)
library(DT)
library(fs)
library(ggplot2)
library(patchwork)
```

### Adjust File Paths {.hidden}

```{r}
## Adjust File Paths
#path_file <- "E:/Allie/FireFX_NER/FFI Data Management/R Outputs/"
path_file <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/R Outputs/"
path_data <- paste0(path_file, "ALL/Calculations/ALL_")
```

### Load Data {.hidden}

```{r}
# Load in data
MetadataReport <- read.csv(paste0(path_data, "MetadataReport.csv"))
Fuels <- read.csv(paste0(path_data, "Data_Surface Fuels.csv"))
Trees <- read.csv(paste0(path_data, "Data_Trees-Seedlings.csv"))
Cover <- read.csv(paste0(path_data, "Data_Cover.csv"))

# Trees <- read.csv(paste0(path_data, "Data_Trees - Individuals (metric).csv"))
# Seedlings <- read.csv(paste0(path_data, "Data_Density - Quadrats (metric).csv"))
#HerbsSpComp <- read.csv(paste0(path_data, "Data_Cover - Species Composition (metric).csv"))
# HerbsPoints <- read.csv(paste0(path_data, "Data_Cover - Points (metric).csv"))


# SpeciesReport <- read.csv(paste0(path_data, "SpeciesReport.csv"))
# Fuels1000 <- read.csv(paste0(path_data, "Data_Surface Fuels - 1000Hr.csv"))
# FuelsDuffLitt <- read.csv(paste0(path_data, "Data_Surface Fuels - Duff_Litter.csv"))
# FuelsFine <- read.csv(paste0(path_data, "Data_Surface Fuels - Fine.csv"))
# PostBurn <- read.csv(paste0(path_data, "Data_Post Burn Severity (metric).csv"))
# Shrubs <- read.csv(paste0(path_data, "Data_Density - Belts (metric).csv"))
```

### Target Values {.hidden}

```{r}
target_park <- c("RICH")
target_type <- c("Forest")
target_years <- c(2025)
year_max <- as.numeric(format(Sys.Date(), "%Y"))
date_max <- as.Date(paste0(year_max, "-12-31"))

    MetadataReport_graph <- MetadataReport %>% 
      filter(
        AdministrationUnit_Name == target_park,
        Type == target_type
        )

year_min <- as.numeric(min(MetadataReport_graph$SampleEventDate_Year))
date_min <- as.Date(min(MetadataReport_graph$SampleEventDate))

    MetadataReport_graph %>% 
      #filter(Purpose == "Fire Monitoring Handbook") %>% 
      select(MacroPlot.UV1) %>% 
      unique()

target_project <- c("Cold Harbor")
```

# Background

# Methods

# Monitoring Objective Table

# Results Summary

# Graphs

## Disturbance History

### Prep {.hidden}

```{r}
Disturbances <- MetadataReport_graph %>% 
  filter(MonStatus %in% c("Burn", "Herbicide", "Mechanical", "Mow"))

Disturbances_graph <- Disturbances %>%
  group_by(Region, Zone, Unit, AdministrationUnit_Name, Plot_Type, DisturbanceDate, DisturbanceDate_Year, SampleEventDate_Year, MonStatus) %>%
  filter(DisturbanceDate_Year == SampleEventDate_Year) %>%
  dplyr::summarize(n_Macroplot = n()) %>%
  mutate(DisturbanceDate = as.Date(DisturbanceDate),
         Macroplot_Num = "All") %>%
  arrange(desc(MonStatus))
```

### Graph

```{r}
p_disturbance <- MetadataReport_graph %>%
  ggplot(aes(x = DisturbanceDate, y = Macroplot_Num)) +
  geom_line(aes(group = Macroplot_Num),
            data = Disturbances_graph) +
  geom_point(aes(X = DisturbanceDate, y = Macroplot_Num, fill = MonStatus),
             data = Disturbances_graph, shape = 21) +
  geom_line(aes(X = DisturbanceDate, y = Macroplot_Num, fill = MonStatus),
            data = Disturbances_graph) +
  geom_point(aes(X = DisturbanceDate, y = Macroplot_Num, fill = MonStatus),
             data = Disturbances_graph, shape = 21, size = 2.5) +
  facet_grid(~MacroPlot.UV1) +
  labs(title = "Disturbance History",
       y = "",
       x = "Year",
       fill = "") +
  scale_x_date(
    limits = c(date_min, date_max),
    date_breaks = "1 year",
    date_labels = "%Y",
    expand = expansion(mult = c(0, 0))
  ) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
        legend.position = "top")

#p_disturbance
```

## Surface Fuels

### Prep {.hidden}

```{r}
Fuels_graph <- Fuels %>% 
  filter(
    AdministrationUnit_Name == target_park,
    MacroPlot.UV1 == target_project,
    Type == target_type
    ) %>% 
  mutate(
    SampleEventDate_Year = as.numeric(SampleEventDate_Year)
    #,SampleEventDate = as.factor(SampleEventDate)
    ) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year) %>% 
  dplyr::summarise(
    n_plots = n_distinct(Macroplot),
    ThousHr_FuelLoad = mean(ThousHr_FuelLoad, na.rm = TRUE),
    ThousHrRott_FuelLoad = mean(ThousHrRott_FuelLoad, na.rm = TRUE),
    ThousHrSound_FuelLoad = mean(ThousHrSound_FuelLoad, na.rm = TRUE),
    Fine_FuelLoad = mean(Fine_FuelLoad, na.rm = TRUE),
    HunHr_FuelLoad = mean(HunHr_FuelLoad, na.rm = TRUE),
    TenHr_FuelLoad = mean(TenHr_FuelLoad, na.rm = TRUE),
    OneHr_FuelLoad = mean(OneHr_FuelLoad, na.rm = TRUE),
    Avg_LittDuff_FuelLoad = mean(Avg_LittDuff_FuelLoad, na.rm = TRUE),
    Avg_Litt_FuelLoad  = mean(Avg_Litt_FuelLoad, na.rm = TRUE),
    Avg_Duff_FuelLoad = mean(Avg_Duff_FuelLoad, na.rm = TRUE),
    .groups = "drop"
    ) %>% 
  pivot_longer(
    cols = c(
      ThousHr_FuelLoad,
      ThousHrRott_FuelLoad,
      ThousHrSound_FuelLoad,
      Fine_FuelLoad,
      HunHr_FuelLoad,
      TenHr_FuelLoad,
      OneHr_FuelLoad,
      Avg_LittDuff_FuelLoad,
      Avg_Litt_FuelLoad,
      Avg_Duff_FuelLoad
    ),
    names_to  = "FuelClass",
    values_to = "FuelLoad"
  ) %>% 
    mutate(
    FuelClass = factor(
      FuelClass,
      levels = c(
        "ThousHr_FuelLoad",
        "ThousHrRott_FuelLoad",
        "ThousHrSound_FuelLoad",
        "Fine_FuelLoad",
        "HunHr_FuelLoad",
        "TenHr_FuelLoad",
        "OneHr_FuelLoad",
        "Avg_LittDuff_FuelLoad",
        "Avg_Litt_FuelLoad",
        "Avg_Duff_FuelLoad"
      )
    )
  ) %>%
    mutate(
    FuelClass = recode(
      FuelClass,
      ThousHr_FuelLoad        = "1000-hr",
      ThousHrRott_FuelLoad    = "1000-hr Rotten",
      ThousHrSound_FuelLoad   = "1000-hr Sound",
      Fine_FuelLoad           = "Fine",
      HunHr_FuelLoad          = "100-hr",
      TenHr_FuelLoad          = "10-hr",
      OneHr_FuelLoad          = "1-hr",
      Avg_LittDuff_FuelLoad   = "Litter/Duff",
      Avg_Litt_FuelLoad       = "Litter",
      Avg_Duff_FuelLoad       = "Duff"
    )
  )
```

### Select Treatment Units

```{r}
Fuels_graph %>% 
  select(SampleEvent_TreatmentUnit) %>% 
  unique()

target_TreatmentUnits <- c("Cold Harbor I")
```

### Graph - 2025 Report Replicate

```{r}
p_fuels_classic <- Fuels_graph %>% 
  filter(
    SampleEvent_TreatmentUnit %in% c(target_TreatmentUnits)
    ) %>% 
  filter(FuelClass %in% c(
    #"1000-hr",
    #"1000-hr Rotten",
    #"1000-hr Sound",
    "Fine"
    #"100-hr",
    #"10-hr",
    #"1-hr",
    #"Litter/Duff",
    #"Litter",
    #"Duff"
  )) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year) %>% 
  mutate(Total_FuelLoad = sum(FuelLoad)) %>% 
  
  ggplot(aes(x = SampleEventDate_Year, y = FuelLoad, fill = FuelClass)) +
  geom_line() +
  geom_point() +
  facet_wrap(~ SampleEvent_TreatmentUnit, ncol = 1) +
  labs(
    x = "Year",
    y = "Tons / Acre",
    #fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Loading")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  ylim(0, 3) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )

p_fuels_classic
```

### Graph - All Fuels {.hidden}

```{r}
p_fuels <- Fuels_graph %>% 
  filter(
    SampleEvent_TreatmentUnit %in% c(target_TreatmentUnits)
    ) %>% 
  filter(FuelClass %in% c(
    #"1000-hr",
    "1000-hr Rotten",
    "1000-hr Sound",
    #"Fine",
    "100-hr",
    "10-hr",
    "1-hr",
    #"Litter/Duff",
    "Litter",
    "Duff"
  )) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year) %>% 
  mutate(Total_FuelLoad = sum(FuelLoad)) %>% 
  
  ggplot() +
  geom_bar(aes(x = SampleEventDate_Year, y = FuelLoad, fill = FuelClass),
           position = "stack", stat = "identity") + 
  facet_wrap(~ SampleEvent_TreatmentUnit, ncol = 1) +
  labs(
    x = "Year",
    y = "Tons / Acre",
    #fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Loading")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )

p_fuels
```

### Graph - Merged

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_fuels_merge <- p_fuels +
  theme(plot.title = element_blank())

p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))
```

## Trees

### Prep {.hidden}

```{r}
Trees_graph <- Trees %>% 
  filter(
    AdministrationUnit_Name == target_park,
    MacroPlot.UV1 == target_project,
    Type == target_type
  ) %>% 
  mutate(
    SampleEventDate_Year = as.numeric(SampleEventDate_Year)
    #,SampleEventDate = as.factor(SampleEventDate)
    ) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year, Genus, Status) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot),
    
    Seedling_Count  = sum(Seedling_Count),
    Seedling_Density_ac = round(mean(Seedling_Dens_ac, na.rm = TRUE)),
    #Seedling_Density_ha = round(mean(Seedling_Dens_ha, na.rm = TRUE)),
    
    Sapling_Count = sum(Sapling_Count),
    Sapling_Density_ac = round(mean(Sapling_Dens_ac, na.rm = TRUE)),
    #Sapling_Density_ha = round(mean(Sapling_Dens_ha, na.rm = TRUE)),
    
    Pole_Count = sum(Pole_Count),
    Pole_Density_ac = round(mean(Pole_Dens_ac, na.rm = TRUE)),
    #Pole_Density_ha = round(mean(Pole_Dens_ha, na.rm = TRUE)),
    
    Overstory_Count = sum(Overstory_Count),
    Overstory_Density_ac = round(mean(Overstory_Dens_ac, na.rm = TRUE)),
    #Overstory_Density_ha = round(mean(Overstory_Dens_ha, na.rm = TRUE)),
    
    .groups = "drop"
  ) %>% 
  pivot_longer(
    cols = matches("Seedling|Sapling|Pole|Overstory"),
    names_to = c("SizeClass", ".value"),
    names_pattern = "(Seedling|Sapling|Pole|Overstory)_(Count|Density)"
  ) %>% 
  mutate(
    SizeClass = factor(
      SizeClass,
      levels = c(
        "Overstory",
        "Pole",
        "Sapling",
        "Seedling"
      )
    ))
```

### Select Treatment Units

```{r}
    Trees_graph %>% 
      select(SampleEvent_TreatmentUnit) %>% 
      unique()

target_TreatmentUnits <- c("Cold Harbor I")
```

### Graph - 2025 Report Replicate

```{r}
p_trees_classic <- Trees_graph %>% 
  filter(
    !Status %in% c("X","D"),
    SampleEvent_TreatmentUnit %in% c(target_TreatmentUnits)
    ) %>% 
  filter(SizeClass %in% c(
    #"Seedling",
    #"Sapling",
    "Pole"
    #"Overstory"
    )) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year) %>% 
    mutate(Density = sum(Density)) %>% 
    
  ggplot(aes(x = SampleEventDate_Year, y = Density)) +
  geom_line() +
  geom_point() +
  facet_wrap(~ SampleEvent_TreatmentUnit, ncol = 1) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )

p_trees_classic
```

### Graph - Poles Merged

```{r}
p_trees_poles <- Trees_graph %>% 
  filter(
    !Status %in% c("X", "D"),
    SampleEvent_TreatmentUnit %in% c(target_TreatmentUnits)
    ) %>% 
  filter(SizeClass %in% c(
    #"Seedling",
    #"Sapling",
    "Pole"
    #"Overstory"
    )) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year, Genus, Status) %>% 
  mutate(Density = sum(Density)) %>% 
  filter(Density != 0) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEventDate_Year, 
      y = Density, 
      fill = Genus
      ),
    position = "stack", stat = "identity") +
  facet_wrap(~ SampleEvent_TreatmentUnit, ncol = 1) +
  #facet_grid(Status ~ SampleEvent_TreatmentUnit) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )

#p_trees_poles
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Tree Density"),
    fill = "Disturbance"
       )

p_trees_merge <- p_trees_poles +
  theme(plot.title = element_blank())

p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Graph - Seedlings

```{r}
p_trees_seedlings <- Trees_graph %>% 
  filter(
    !Status %in% c("X", "D"),
    SampleEvent_TreatmentUnit %in% c(target_TreatmentUnits)
    ) %>% 
  filter(SizeClass %in% c(
    "Seedling"
    #"Sapling",
    #"Pole",
    #"Overstory"
    )) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year, Genus, Status) %>% 
  mutate(Density = sum(Density)) %>% 
  filter(Density != 0) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEventDate_Year, 
      y = Density, 
      fill = Genus
      ),
    position = "stack", stat = "identity") +
  facet_wrap(~ SampleEvent_TreatmentUnit, ncol = 1) +
  #facet_grid(Status ~ SampleEvent_TreatmentUnit) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )

p_trees_seedlings
```

### Graph - Saplings

```{r}
p_trees_saplings <- Trees_graph %>% 
  filter(
    !Status %in% c("X", "D"),
    SampleEvent_TreatmentUnit %in% c(target_TreatmentUnits)
    ) %>% 
  filter(SizeClass %in% c(
    #"Seedling",
    "Sapling"
    #"Pole",
    #"Overstory"
    )) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year, Genus, Status) %>% 
  mutate(Density = sum(Density)) %>% 
  filter(Density != 0) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEventDate_Year, 
      y = Density, 
      fill = Genus
      ),
    position = "stack", stat = "identity") +
  facet_wrap(~ SampleEvent_TreatmentUnit, ncol = 1) +
  #facet_grid(Status ~ SampleEvent_TreatmentUnit) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )

p_trees_saplings
```

### Graph - Overstory

```{r}
p_trees_overstory <- Trees_graph %>% 
  filter(
    !Status %in% c("X", "D"),
    SampleEvent_TreatmentUnit %in% c(target_TreatmentUnits)
    ) %>% 
  filter(SizeClass %in% c(
    #"Seedling",
    #"Sapling",
    #"Pole",
    "Overstory"
    )) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year, Genus, Status) %>% 
  mutate(Density = sum(Density)) %>% 
  filter(Density != 0) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEventDate_Year, 
      y = Density, 
      fill = Genus
      ),
    position = "stack", stat = "identity") +
  facet_wrap(~ SampleEvent_TreatmentUnit, ncol = 1) +
  #facet_grid(Status ~ SampleEvent_TreatmentUnit) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )

p_trees_overstory
```

### Graph - All

```{r}
p_trees_all <- Trees_graph %>% 
  filter(
    !Status %in% c("X", "D"),
    SampleEvent_TreatmentUnit %in% c(target_TreatmentUnits)
    ) %>% 
  filter(SizeClass %in% c(
    "Seedling",
    "Sapling",
    "Pole",
    "Overstory"
    )) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year, Genus, Status, SizeClass) %>% 
  mutate(Density = sum(Density)) %>% 
  filter(Density != 0) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEventDate_Year, 
      y = Density, 
      fill = SizeClass
      ),
    position = "stack", stat = "identity") +
  facet_wrap(~ SampleEvent_TreatmentUnit, ncol = 1) +
  #facet_grid(Status ~ SampleEvent_TreatmentUnit) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )

p_trees_all
```

## Herbaceous

### Prep

```{r}
Cover_graph <- Cover %>%
  filter(
    AdministrationUnit_Name == target_park,
    MacroPlot.UV1 == target_project,
    Type == target_type
  ) %>% 
  mutate(
    SampleEventDate_Year = as.numeric(SampleEventDate_Year)
    #,SampleEventDate = as.factor(SampleEventDate)
    ) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, Macroplot, MonStatus, Preferred_Lifeform, Genus, Species.Symbol, Nativity) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot),
    #.groups = "drop"
  )
```

```{r}
Trees_graph <- Trees %>% 
  filter(
    AdministrationUnit_Name == target_park,
    MacroPlot.UV1 == target_project,
    Type == target_type
  ) %>% 
  mutate(
    SampleEventDate_Year = as.numeric(SampleEventDate_Year)
    #,SampleEventDate = as.factor(SampleEventDate)
    ) %>% 
  group_by(AdministrationUnit_Name, Purpose, Type, SampleEvent_TreatmentUnit, MonStatus, SampleEventDate_Year, Genus, Status) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot),
    
    Seedling_Count  = sum(Seedling_Count),
    Seedling_Density_ac = round(mean(Seedling_Dens_ac, na.rm = TRUE)),
    #Seedling_Density_ha = round(mean(Seedling_Dens_ha, na.rm = TRUE)),
    
    Sapling_Count = sum(Sapling_Count),
    Sapling_Density_ac = round(mean(Sapling_Dens_ac, na.rm = TRUE)),
    #Sapling_Density_ha = round(mean(Sapling_Dens_ha, na.rm = TRUE)),
    
    Pole_Count = sum(Pole_Count),
    Pole_Density_ac = round(mean(Pole_Dens_ac, na.rm = TRUE)),
    #Pole_Density_ha = round(mean(Pole_Dens_ha, na.rm = TRUE)),
    
    Overstory_Count = sum(Overstory_Count),
    Overstory_Density_ac = round(mean(Overstory_Dens_ac, na.rm = TRUE)),
    #Overstory_Density_ha = round(mean(Overstory_Dens_ha, na.rm = TRUE)),
    
    .groups = "drop"
  ) %>% 
  pivot_longer(
    cols = matches("Seedling|Sapling|Pole|Overstory"),
    names_to = c("SizeClass", ".value"),
    names_pattern = "(Seedling|Sapling|Pole|Overstory)_(Count|Density)"
  ) %>% 
  mutate(
    SizeClass = factor(
      SizeClass,
      levels = c(
        "Overstory",
        "Pole",
        "Sapling",
        "Seedling"
      )
    ))
```

### Herbs Species Comp

```{r}
# HerbsSpComp_graph <- HerbsSpComp %>%
#   filter(AdministrationUnit_Name == target_park,
#          Type == target_type) %>%
#   # group_by(AdministrationUnit_Name, Purpose, Type, MacroPlot.UV1, MonStatus, SampleEventDate_Year, Nativity) %>%
#   dplyr::summarise(n_species_ByNativity = mean(n_species_ByNativity),
#                    .groups = "drop")
```

```{r}
# HerbsSpComp_graph %>%
#   ggplot(aes(x = SampleEventDate_Year, y = n_species_ByNativity, fill = Nativity)) +
#   geom_bar(position = "stack", stat = "identity")
```

# Discussion
