---
title: "Annual Park Report"
author: "NPS Northeast Region Fire Effects Monitoring Program"
output:
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: false
link-citations: true
bibliography: zotero_refs.bib
csl: "chicago-author-date-17th-edition.csl"
---

# Before Starting {.hidden .unlisted .unnumbered}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
# install.packages("RefManageR")
# install.packages("leaflet")
```

```{r load packages, include=FALSE}
# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
library(stringr)
library(DT)
library(fs)
# ggplot2 is used for graphing. gganimate creates graph animations patchwork stitches graphs together
library(ggplot2)
#library(gganimate)
library(patchwork)
library(RColorBrewer)
# zotero reference manager
library(RefManageR)
# shannon diversity index
library(vegan)
library(here)
# download button
library(downloadthis)
# for maps
library(leaflet)
```

### References {.hidden}

```{r references, include=FALSE}
# ZoteroUserID <- "3306456"
# ZoteroAPIkey <- "F7k8Rp07XhH9rIqiKP1ob0uB"
# ZoteroFolderKey <- "DGJVBG7G"
# 
# bib <- ReadZotero(
#   user = ZoteroUserID,
#   .params = list(
#     collection = ZoteroFolderKey,
#     key = ZoteroAPIkey,
#     limit = 100),
#   temp.file = "zotero_refs.bib",
#   delete.file = FALSE)
```

### Adjust File Paths {.hidden}

```{r file paths, include=FALSE}
path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Reporting/FFI/")
path_save <- paste0(here(), "/output/graphs/")
## Source Code for Gingrich Stocking Chart
source(paste0(here(), "/scripts/4_Reports/Gingrich Stocking Chart.R"))
```

### Load Data {.hidden}

```{r load data, include=FALSE}
MetadataReport <- read.csv(paste0(path_data, "all_metadata.csv"))
SpeciesReport <- read.csv(paste0(path_data, "all_species_info.csv"))
Fuels <- read.csv(paste0(path_data, "fuels.csv"))
Trees <- read.csv(paste0(path_data, "trees.csv"))
Cover <- read.csv(paste0(path_data, "cover.csv"))
# Cover_Points <- read.csv(paste0(path_data, "cover_points.csv"))
# Cover_SpComp <- read.csv(paste0(path_data, "cover_comp.csv"))
# PostBurn <- read.csv(paste0(path_data, "post.csv"))
# Shrubs <- read.csv(paste0(path_data, "shrubs.csv"))
```

### Target Values {.hidden}

```{r}
target_park <- c("RICH")
target_type <- c("Grassland")
target_purpose <- c("Fire Monitoring Handbook")

    
    MetadataReport %>%
      filter(
        Macroplot_Purpose == target_purpose,
        AdminUnit_Name == target_park,
        Macroplot_Type == target_type
        ) %>% 
      rename(ProjectUnit = Macroplot_UV1) %>% 
      rename(MonitoringType = Macroplot_UV2) %>% 
      select(ProjectUnit, MonitoringType) %>% 
      unique()
```

```{r, include=FALSE}
target_ProjectUnit <- c("Malvern Hill")
target_MonitoringType <- c("Warm Season")


    MetadataReport_SampleEvents <- MetadataReport %>%
      filter(
        AdminUnit_Name == target_park,
        Macroplot_Type == target_type,
        Macroplot_Purpose == target_purpose,
        Macroplot_UV1 %in% target_ProjectUnit,
        Macroplot_UV2 %in% target_MonitoringType,
        !MonitoringStatus_Name %in% c("Burn", "Herbicide", "Mechanical", "Mow")
        )

    MetadataReport_Disturbances <- MetadataReport %>%
      filter(
        AdminUnit_Name == target_park,
        Macroplot_Type == target_type,
        Macroplot_Purpose == target_purpose,
        Macroplot_UV1 %in% target_ProjectUnit,
        Macroplot_UV2 %in% target_MonitoringType,
        MonitoringStatus_Name %in% c("Burn", "Herbicide", "Mechanical", "Mow")
        )

year_max <- as.numeric(format(Sys.Date(), "%Y"))
date_max <- as.Date(paste0(year_max, "-12-31"))
year_min <- as.numeric((min(MetadataReport_SampleEvents$SampleEvent_Date_Year)) - 2)
date_min <- as.Date(paste0(year_min, "-12-31"))
```

### Add Species Info {.hidden}

```{r species, include=FALSE}
# Isolate all species which are in the plots analyzed
Species_trees_protocol <- Trees %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 %in% target_ProjectUnit,
    Macroplot_UV2 %in% target_MonitoringType
    ) %>% 
  select(Species_ScientificName) %>% 
  drop_na() %>% 
  unique()

Species_cover_protocol <- Cover %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 %in% target_ProjectUnit,
    Macroplot_UV2 %in% target_MonitoringType
    ) %>% 
  select(Species_ScientificName) %>% 
  drop_na() %>% 
  unique()

# combine all species
Species <- rbind(Species_trees_protocol, Species_cover_protocol) %>% 
  unique()

# target species object
target_Species <- Species$Species_ScientificName
target_TreeSpecies <- Species_trees_protocol$Species_ScientificName

remove(Species_trees_protocol, Species_cover_protocol, Species)

###################################################################################

# filter target species from master list
Species_all <- SpeciesReport %>%
  filter(
    AdminUnit_Name == target_park,
    ) %>%
  filter(Species_ScientificName %in% target_Species) %>% 
  mutate(
    "Genus" = Species_Genus,
    "Scientific Name" = Species_ScientificName,
    "Lifeform" = Species_LifeFormNameLocal,
    "Nativity" = Species_Nativity
  ) %>%
  separate(Species_CommonNameLocal, into = "Common Name", sep = ";") %>%
  select("Genus", "Scientific Name", "Common Name", "Nativity", "Lifeform") %>% 
  arrange(`Scientific Name`)


# filter target species from master list
Species_trees <- SpeciesReport %>%
  filter(
    AdminUnit_Name == target_park,
    ) %>%
  filter(Species_ScientificName %in% target_TreeSpecies) %>% 
  mutate(
    "Genus" = Species_Genus,
    "Scientific Name" = Species_ScientificName,
    "Fire Adaptedness" = Species_UV1,
    "Strategy" = Species_UV2
  ) %>%
  separate(Species_CommonNameLocal, into = "Common Name", sep = ";") %>%
  select("Genus", "Scientific Name", "Common Name", "Fire Adaptedness", "Strategy") %>% 
  arrange(`Scientific Name`)

###################################################################################

# vector of tree genera
colors_genera <- Species_trees$Genus
colors_species <- Species_trees$`Scientific Name`

palette <- c(
  brewer.pal(12,"Set3"),
  brewer.pal(12,"Paired"),
  brewer.pal(8,"Dark2"),
  brewer.pal(9,"Set1"),
  brewer.pal(8,"Set2")
)

cols_genera <- palette[1:length(colors_genera)]
cols_genera <- colorspace::darken(cols_genera, 0.15)
genus_colors <- setNames(cols_genera, colors_genera)
cols_species <- palette[1:length(colors_species)]
cols_species <- colorspace::darken(cols_species, 0.15)
species_colors <- setNames(cols_species, colors_species)

# color for NA
na_color <- "grey70"
```

# `r target_park` `r target_type` Plots: `r target_ProjectUnit` (`r target_MonitoringType`)

# Monitoring Objectives

```{r objectives}
source(paste0(here(), "/scripts/4_Reports/monitoring_objectives.R"))

if(length(target_MonitoringType) > 1) {
  target_FineFuelLoading <- NA
  target_Duff <-  NA
  target_Sapling <- NA
  target_OverstoryLow <- NA
  target_OverstoryHigh <- NA
  target_Native <- NA
  target_Invasive <- NA
  target_Woody <- NA
}


Objectives_Forest <- data.frame(
  "Num" = c(1,2,3,4,5,6),
  "Objective" = c(
    paste0("1. Maintain fine fuel loading (litter, 1-100hr fuels) at < ", target_FineFuelLoading, " tons/acre"),
    paste0("2. Maintain duff depth to ≤ ", target_Duff, " inches"),
    paste0("3. Increase sapling density to ≥ ", target_Sapling, " stems/acre"),
    paste0("4. Reduce pole-sized tree density of mesic fire-intolerant species relative to xeric fire-adapted species"),
    paste0("5. Maintain a stocking density of overstory trees between ", target_OverstoryLow, "-", target_OverstoryHigh, "%"),
    paste0("6. Maintain or increase native grass and forb cover to ≥ ", target_Native, "%")
  ))

Objectives_Grassland <- data.frame(
  "Num" = c(1,2,3),
  "Objective" = c(
    paste0("1. Reduce woody cover to < ", target_Woody, "%"),
    paste0("2. Reduce non-native invasive grass and forb cover to <", target_Invasive, "%"),
    paste0("3. Increase native grass and forb cover to > ", target_Native, "%")
  ))



if (!is.na(target_Native)) {
  
  if (target_type == "Forest") {
    kable(Objectives_Forest %>% select(Objective))
  } else {
    kable(Objectives_Grassland %>% select(Objective))
  }
  
}
```

\newpage

# Background

## Map

```{r}
leaflet(data = MetadataReport_SampleEvents %>%
          select(c(AdminUnit_Name, Macroplot_Type, Macroplot_Name, Macroplot_Lat_dd, Macroplot_Long_dd)) %>%
          distinct()) %>%
  addTiles() %>%
  addMarkers(
    lng = ~Macroplot_Long_dd,
    lat = ~Macroplot_Lat_dd,
    popup = ~Macroplot_Name
  )
```

\newpage

## Disturbance History

### Prep {.hidden}

```{r}
Disturbances_graph <- MetadataReport_Disturbances %>%
  group_by(
    AdminUnit_Region, AdminUnit_Zone, AdminUnit_Unit, AdminUnit_Name, Macroplot_PurposeType, Macroplot_UV1, Macroplot_UV2, Disturbance_Date, Disturbance_Date_Year, SampleEvent_Date_Year, MonitoringStatus_Name
    ) %>%
  filter(
    Disturbance_Date_Year == SampleEvent_Date_Year
    ) %>%
  dplyr::summarize(
    n_Macroplot = n()
    ) %>%
  mutate(
    Disturbance_Date = as.Date(Disturbance_Date),
    Macroplot_Num = Macroplot_UV1
    ) %>%
  arrange(desc(MonitoringStatus_Name))
```

### Timeline

```{r}
if(nrow(MetadataReport_Disturbances) == 0) {
  p_disturbance <- ggplot()
} else {
  p_disturbance <- MetadataReport_Disturbances %>%
    ggplot(aes(x = Disturbance_Date, y = Macroplot_Num)) +
    geom_line(aes(group = Macroplot_Num),
              data = Disturbances_graph) +
    geom_point(aes(x = Disturbance_Date, y = Macroplot_Num, fill = MonitoringStatus_Name),
               data = Disturbances_graph, shape = 21) +
    geom_line(aes(X = Disturbance_Date, y = Macroplot_Num, fill = MonitoringStatus_Name),
              data = Disturbances_graph) +
    geom_point(aes(X = Disturbance_Date, y = Macroplot_Num, fill = MonitoringStatus_Name),
               data = Disturbances_graph, shape = 21, size = 2.5) +
    facet_grid( ~ Macroplot_UV2) +
    labs(title = "Disturbance History",
         y = "",
         x = "Year",
         fill = ""
    ) +
    scale_y_discrete(
      limits = rev(sort(unique(Disturbances_graph$Macroplot_Num)))
    ) + 
    scale_x_date(
      limits = c(date_min, date_max),
      date_breaks = "1 year",
      date_labels = "%Y",
      expand = expansion(mult = c(0, 0))
    ) +
    theme_light() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          plot.title = element_text(size = 15, face="bold", hjust = 0.5),
          axis.title = element_text(size = 12, face="bold"),
          axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
          axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
          #axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
          legend.position = "top")
}

p_disturbance
```

\newpage

# Methods

# Results

## Fuels

### Prep {.hidden}

```{r}
FuelLoad_graph <- Fuels %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 %in% target_ProjectUnit,
    Macroplot_UV2 %in% target_MonitoringType
    ) %>% 
  mutate(
    SampleEvent_Date_Year = as.numeric(SampleEvent_Date_Year)
    ) %>%
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ) %>% 
  dplyr::summarise(
    n_plots = n_distinct(Macroplot_Name),
    ThousHr_FuelLoad = mean(ThousHr_FuelLoad, na.rm = TRUE),
    ThousHrRott_FuelLoad = mean(ThousHrRott_FuelLoad, na.rm = TRUE),
    ThousHrSound_FuelLoad = mean(ThousHrSound_FuelLoad, na.rm = TRUE),
    Fine_FuelLoad = mean(Fine_FuelLoad, na.rm = TRUE),
    HunHr_FuelLoad = mean(HunHr_FuelLoad, na.rm = TRUE),
    TenHr_FuelLoad = mean(TenHr_FuelLoad, na.rm = TRUE),
    OneHr_FuelLoad = mean(OneHr_FuelLoad, na.rm = TRUE),
    Avg_LittDuff_FuelLoad = mean(Avg_LittDuff_FuelLoad, na.rm = TRUE),
    Avg_Litt_FuelLoad  = mean(Avg_Litt_FuelLoad, na.rm = TRUE),
    Avg_Duff_FuelLoad = mean(Avg_Duff_FuelLoad, na.rm = TRUE),
    .groups = "drop"
    ) %>% 
  pivot_longer(
    cols = c(
      ThousHr_FuelLoad,
      ThousHrRott_FuelLoad,
      ThousHrSound_FuelLoad,
      Fine_FuelLoad,
      HunHr_FuelLoad,
      TenHr_FuelLoad,
      OneHr_FuelLoad,
      Avg_LittDuff_FuelLoad,
      Avg_Litt_FuelLoad,
      Avg_Duff_FuelLoad
    ),
    names_to  = "FuelClass",
    values_to = "FuelLoad"
  ) %>% 
    mutate(
    FuelClass = factor(
      FuelClass,
      levels = c(
        "ThousHr_FuelLoad",
        "ThousHrRott_FuelLoad",
        "ThousHrSound_FuelLoad",
        "Fine_FuelLoad",
        "HunHr_FuelLoad",
        "TenHr_FuelLoad",
        "OneHr_FuelLoad",
        "Avg_LittDuff_FuelLoad",
        "Avg_Litt_FuelLoad",
        "Avg_Duff_FuelLoad"
      )
    )
  ) %>%
    mutate(
    FuelClass = recode(
      FuelClass,
      ThousHr_FuelLoad        = "1000-hr",
      ThousHrRott_FuelLoad    = "1000-hr Rotten",
      ThousHrSound_FuelLoad   = "1000-hr Sound",
      Fine_FuelLoad           = "1-100hr",
      HunHr_FuelLoad          = "100-hr",
      TenHr_FuelLoad          = "10-hr",
      OneHr_FuelLoad          = "1-hr",
      Avg_LittDuff_FuelLoad   = "Litter/Duff",
      Avg_Litt_FuelLoad       = "Litter",
      Avg_Duff_FuelLoad       = "Duff"
    )
  )
```

```{r}
FuelDepth_graph <- Fuels %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 %in% target_ProjectUnit,
    Macroplot_UV2 %in% target_MonitoringType
    ) %>% 
  mutate(
    SampleEvent_Date_Year = as.numeric(SampleEvent_Date_Year)
    ) %>%
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ) %>% 
  dplyr::summarise(
    n_plots = n_distinct(Macroplot_Name),
    Avg_LittDep = mean(Avg_LittDep, na.rm = TRUE),
    Avg_DuffDep = mean(Avg_DuffDep, na.rm = TRUE),
    .groups = "drop"
    ) %>% 
  pivot_longer(
    cols = c(
      Avg_LittDep,
      Avg_DuffDep
    ),
    names_to  = "FuelClass",
    values_to = "FuelDepth"
  ) %>% 
    mutate(
    FuelClass = factor(
      FuelClass,
      levels = c(
        "Avg_LittDep",
        "Avg_DuffDep"
      )
    )
  ) %>%
    mutate(
    FuelClass = recode(
      FuelClass,
      Avg_LittDep       = "Litter",
      Avg_DuffDep       = "Duff"
    )
  )
```

\newpage

### Fine Fuels

```{r}
if(target_type == "Forest" & !(is.na(target_FineFuelLoading))) {
  kable(Objectives_Forest %>% 
          filter(Num == 1) %>% 
          select(Objective)
        )
}
```

```{r, include=FALSE}
if(nrow(FuelLoad_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
  p_data <- FuelLoad_graph %>% 
  filter(
    FuelClass %in% c(
      #"1000-hr",
      #"1000-hr Rotten",
      #"1000-hr Sound",
      "1-100hr",
      #"100-hr",
      #"10-hr",
      #"1-hr",
      #"Litter/Duff",
      "Litter"
      #"Duff"
  )) %>% 
  mutate(
    FuelClass = factor(
      FuelClass,
      levels = c(
        "Litter",
        "1-100hr"
      ))) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    ) %>% 
  mutate(
    Total_FuelLoad = sum(FuelLoad)
    ) %>% 
  
  ggplot(aes(x = SampleEvent_Date_Year, y = FuelLoad, color = FuelClass)) +
  geom_line(position = "stack") +
  geom_point(position = "stack") +
  geom_text(
    data = FuelLoad_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Tons / Acre",
    color = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Loading")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  ylim(0, NA) +
  scale_color_manual(values = c("Litter" = "#619CFF", "1-100hr" = "#E69F00")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    ) +
  geom_hline(
    yintercept = target_FineFuelLoading, 
    linetype = "dashed", 
    color = "forestgreen"
    )
}

p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Fuels Fine.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)

download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Fuels Fine"))
}
```

\newpage

### Duff Depth

```{r}
if(target_type == "Forest" & !(is.na(target_Duff))) {
  kable(Objectives_Forest %>% 
          filter(Num == 2) %>% 
          select(Objective)
        )
}
```

```{r, include=FALSE}
if(nrow(FuelDepth_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- FuelDepth_graph %>% 
  filter(
    FuelClass %in% c(
      "Litter",
      "Duff"
  )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    ) %>% 
  mutate(
    Total_FuelDepth = sum(FuelDepth)
    ) %>% 
  
  ggplot() +
  geom_bar(aes(x = SampleEvent_Date_Year, y = FuelDepth, fill = FuelClass),
           position = "stack", stat = "identity") + 
  geom_text(
    data = FuelDepth_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Average Depth (inches)",
    fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Depth")
  ) +
  scale_x_continuous(
    limits = c((year_min), year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = c("Litter" = "#BFEFFF", "Duff" = "#619CFF")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    ) +
  geom_hline(
    yintercept = target_Duff, 
    linetype = "dashed", 
    color = "#619CFF",
    size = 0.7
    )
}

#p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Depth"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Fuels Duff.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)

download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Fuels Duff"))
}
```

\newpage

### All Fuels {.hidden}

```{r, include=FALSE}
if(nrow(FuelLoad_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- FuelLoad_graph %>% 
  filter(
    FuelClass %in% c(
      #"1000-hr",
      "1000-hr Rotten",
      "1000-hr Sound",
      #"1-100hr"
      "100-hr",
      "10-hr",
      "1-hr"
      #"Litter/Duff",
      #"Litter",
      #"Duff"
  )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    ) %>% 
  mutate(
    Total_FuelLoad = sum(FuelLoad)
    ) %>% 
  
  ggplot() +
  geom_bar(aes(x = SampleEvent_Date_Year, y = FuelLoad, fill = FuelClass),
           position = "stack", stat = "identity") + 
  geom_text(
    data = FuelLoad_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Tons / Acre",
    fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Loading")
  ) +
  scale_x_continuous(
    limits = c((year_min), year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    )
}

#p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Fuels All.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)

download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Fuels All"))
}
```

\newpage

## Trees

### Prep {.hidden}

```{r}
Trees_graph <- Trees %>%
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 %in% target_ProjectUnit,
    Macroplot_UV2 %in% target_MonitoringType
    ) %>% 
  mutate(
    SampleEvent_Date_Year = as.numeric(SampleEvent_Date_Year)
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Species_Genus
    ,Species_ScientificName
    ,MethodData_Status
    ) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot_Name),
    
    Seedling_Count  = sum(Seedling_Count),
    Seedling_Density_ac = round((mean(Seedling_Dens_ac, na.rm = TRUE)),1),
    Seedling_Density_ha = round((mean(Seedling_Dens_ha, na.rm = TRUE)),1),
    
    Sapling_Count = sum(Sapling_Count),
    Sapling_Density_ac = round((mean(Sapling_Dens_ac, na.rm = TRUE)),1),
    Sapling_Density_ha = round((mean(Sapling_Dens_ha, na.rm = TRUE)),1),
    
    Pole_Count = sum(Pole_Count),
    Pole_Density_ac = round((mean(Pole_Dens_ac, na.rm = TRUE)),0),
    Pole_Density_ha = round((mean(Pole_Dens_ha, na.rm = TRUE)),0),
    Pole_BA_ft2 = round((mean(Pole_BA_ft2, na.rm = TRUE)), 2),
    Pole_BA_m2 = round((mean(Pole_BA_m2, na.rm = TRUE)), 2),
    
    Overstory_Count = sum(Overstory_Count),
    Overstory_Density_ac = round((mean(Overstory_Dens_ac, na.rm = TRUE)),0),
    Overstory_Density_ha = round((mean(Overstory_Dens_ha, na.rm = TRUE)),0),
    Overstory_BA_ft2 = round((mean(Overstory_BA_ft2, na.rm = TRUE)), 2),
    Overstory_BA_m2 = round((mean(Overstory_BA_m2, na.rm = TRUE)), 2),
    
    .groups = "drop"
  ) %>% 
  pivot_longer(
    cols = matches("Seedling|Sapling|Pole|Overstory"),
    names_to = c("SizeClass", ".value"),
    names_pattern = "(Seedling|Sapling|Pole|Overstory)_(Species|Count|Density_[a-z]+|BA_[a-z0-9]+)"
  ) %>% 
  mutate(
    SizeClass = factor(
      SizeClass,
      levels = c(
        "Overstory",
        "Pole",
        "Sapling",
        "Seedling"
      )
    ))
```

\newpage

### Seedlings

```{r, include=FALSE}
if(nrow(Trees_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Trees_graph %>% 
  filter(
    MethodData_Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      "Seedling"
      #"Sapling"
      #"Pole"
      #"Overstory"
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2
    ,Species_Genus
    #,Species_ScientificName
  ) %>% 
  filter(
    sum(Density_ac) != 0
  ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    ,Species_Genus
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha)
    ) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEvent_Date_Year, 
      y = Total_Density_ac, 
      fill = Species_Genus
      ),
    position = "stack", stat = "identity") +
  geom_text(
    data = Trees_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    fill = "Genus",
    title = paste(target_park, target_type, "Seedling Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = genus_colors, na.value = na_color, drop = FALSE) +
  guides(fill = guide_legend(ncol = 2)) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    )
}

p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Seedling Tree Density"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Seedlings.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Seedlings"))
}
```

\newpage

### Saplings

```{r}
if(target_type == "Forest" & !(is.na(target_Sapling))) {
  kable(Objectives_Forest %>% 
          filter(Num == 3) %>% 
          select(Objective)
        )
}
```

```{r, include=FALSE}
if(nrow(Trees_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Trees_graph %>% 
  filter(
    MethodData_Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      #"Seedling"
      "Sapling"
      #"Pole"
      #"Overstory"
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2
    ,Species_Genus
    #,Species_ScientificName
  ) %>% 
  mutate(
    Genus_Total = sum(Density_ac, na.rm = TRUE)
  ) %>% 
  ungroup() %>% 
  filter(
    Genus_Total != 0 | sum(Genus_Total) == 0
  ) %>% 
  # filter(
  #   sum(Density_ac) != 0
  # ) %>%
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    ,Species_Genus
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha)
    ) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEvent_Date_Year,
      y = Total_Density_ac,
      fill = Species_Genus
      ),
    # position_dodge means the bars will display side by side
    position = "stack", stat = "identity"
    #,position = position_dodge2(preserve = "single"), stat = "identity"
    ) +
  geom_text(
    data = Trees_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    fill = "Genus",
    title = paste(target_park, target_type, "Sapling Tree Density"),
    caption = expression("*80 stems/ac (200 stems/ha) is equivalent to 1 sapling found in a sample area of 50m"^2)
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = genus_colors, na.value = na_color, drop = FALSE) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    ) +
  geom_hline(
    yintercept = target_Sapling, 
    linetype = "dashed", 
    color = "forestgreen"
    )
}

p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Sapling Tree Density"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Saplings.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)

download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Saplings"))
}
```

\newpage

### Pole-Sized

```{r}
if(target_type == "Forest") {
  kable(Objectives_Forest %>% 
          filter(Num == 4) %>% 
          select(Objective)
        )
}
```

```{r, include=FALSE}
if(nrow(Trees_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Trees_graph %>% 
  filter(
    MethodData_Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      #"Seedling"
      #"Sapling"
      "Pole"
      #"Overstory"
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2
    ,Species_Genus
    #,Species_ScientificName
  ) %>% 
  filter(
    sum(Density_ac) != 0
  ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    ,Species_Genus
    #,Species_ScientificName
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha)
    ) %>% 

  ggplot(
    aes(
      x = SampleEvent_Date_Year,
      y = Total_Density_ac,
      color = Species_Genus,
      )
  ) +
  geom_line() +
  geom_point() +
  geom_text(
    data = Trees_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    color = "Genus",
    title = paste(target_park, target_type, "Pole Tree Density"),
    caption = expression("*16 stems/ac (40 stems/ha) is equivalent to 1 tree found in a sample area of 500m"^2)
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  scale_color_manual(values = genus_colors, na.value = na_color, drop = FALSE) +
  ylim(0, NA) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    )
}

#p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Pole Tree Density"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Poles.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Poles"))
}
```

\newpage

### Overstory

```{r, include=FALSE}
if(nrow(Trees_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Trees_graph %>% 
  filter(
    MethodData_Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      #"Seedling"
      #"Sapling"
      #"Pole"
      "Overstory"
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2
    #,Species_Genus
    ,Species_ScientificName
  ) %>% 
  filter(
    sum(Density_ac) != 0
  ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    #,Species_Genus
    ,Species_ScientificName
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha)
    ) %>% 

  ggplot(
    aes(
      x = SampleEvent_Date_Year,
      y = Total_Density_ac,
      color = Species_ScientificName,
      )
  ) +
  geom_line() +
  geom_point() +
  geom_text(
    data = Trees_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    color = "Species",
    title = paste(target_park, target_type, "Overstory Tree Density"),
    caption = expression("*16 stems/ac (40 stems/ha) is equivalent to 1 tree found in a sample area of 500m"^2)
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  scale_color_manual(values = species_colors, na.value = na_color, drop = FALSE) +
  ylim(0, NA) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    )
}

#p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Overstory Tree Density"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Overstory.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Overstory"))
}
```

\newpage

### Overstory - Live vs Dead

```{r, include=FALSE}
if(nrow(Trees_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Trees_graph %>% 
  filter(MethodData_Status %in% c(
    "L",
    "D"
    )) %>%
  filter(SizeClass %in% c(
    #"Seedling"
    #"Sapling"
    #"Pole"
    "Overstory"
    )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    #,Species_Genus
    ,MethodData_Status
    #,SizeClass
    ) %>% 
  summarise(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha),
    .groups = "drop"
    ) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEvent_Date_Year, 
      y = Total_Density_ac, 
      fill = MethodData_Status
      ),
    position = "stack", stat = "identity") +
  geom_text(
    data = Trees_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    fill = "Status",
    title = paste(target_park, target_type, "Overstory Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = c("L" = "#009E73", "D" = "#D55E00")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    )
}

#p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Overstory Tree Density"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Live Dead.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Live Dead"))
}
```

\newpage

### Overstory - Gingrich Stocking Graph

```{r}
if(target_type == "Forest" & !(is.na(target_OverstoryLow))) {
  kable(Objectives_Forest %>% 
          filter(Num == 5) %>% 
          select(Objective)
        )
}
```

```{r gingrich-plot, fig.width=10, fig.height=8}
if(nrow(Trees_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Trees_graph %>% 
  filter(
    MethodData_Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      #"Seedling"
      #"Sapling"
      #"Pole"
      "Overstory"
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    #,Species_Genus, MethodData_Status
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha),
    Total_BA_ft2 = sum(BA_ft2),
    Total_BA_m2 = sum(BA_m2)
    ) %>% 
  filter(
    Total_Density_ac != 0) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type,
    Macroplot_UV1, Macroplot_UV2
  ) %>%
  filter(
    SampleEvent_Date_Year == max(SampleEvent_Date_Year)
  )

plot.gingrich.imperial(
  tpa = p_data$Total_Density_ac,
  ba = p_data$Total_BA_ft2,
  label = p_data$Macroplot_UV1,
  color = TRUE,
  type = "p",
  main = paste(target_park, "\nOverstory Stand Structure")
)
}
```

```{r include=FALSE}
# save when ready
if(is.character(p_data)) {
  p_data
} else {
jpeg(
  filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees Overstory.jpg"),
  width = 10, height = 8, units = "in", res = 300
)

plot.gingrich.imperial(
  tpa = p_data$Total_Density_ac,
  ba = p_data$Total_BA_ft2,
  label = p_data$SampleEvent_Date_Year,
  color = TRUE,
  type = "p",
  main = paste(target_park, target_ProjectUnit, "\nOverstory Stand Structure")
)

dev.off()
}
```

\newpage

### All Size Classes

```{r, include=FALSE}
if(nrow(Trees_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Trees_graph %>% 
  filter(
    MethodData_Status %in% c(
      "L",
      "D"
      ),
    SizeClass %in% c(
      "Seedling",
      "Sapling",
      "Pole",
      "Overstory"
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    ,Species_Genus, MethodData_Status, SizeClass
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha)
    ) %>% 
  filter(
    Total_Density_ac != 0
    ) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEvent_Date_Year, 
      y = Total_Density_ac, 
      fill = SizeClass
      ),
    position = "stack", stat = "identity") +
  geom_text(
    data = Trees_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    fill = "Size Class",
    title = paste(target_park, target_type, "Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    )
}

#p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Tree Density"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees All Sizes.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Trees All Sizes"))
}
```

\newpage

## Cover

### Prep {.hidden}

```{r}
Cover_graph <- Cover %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 %in% target_ProjectUnit,
    Macroplot_UV2 %in% target_MonitoringType
    ) %>% 
  mutate(
    SampleEvent_Date_Year = as.numeric(SampleEvent_Date_Year)
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type,
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Species_LifeFormNameLocal, Species_Genus, Species_Nativity
    ,Species_ScientificName
    ) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot_Name),
    Avg_Ht_m = round(mean(Avg_Ht_m, na.rm = TRUE), 1),
    Avg_Ht_ft = round(mean(Avg_Ht_ft, na.rm = TRUE), 1),
    Abundance = sum(Hits, na.rm = TRUE),
    PctCover = round(mean(PctCover, na.rm = TRUE), 1),
    .groups = "drop"
    ) %>% 
  mutate(
    Species_LifeFormNameLocal = ifelse(Species_LifeFormNameLocal == "Undefined", "Substrate", Species_LifeFormNameLocal),
    Species_LifeFormNameLocal = ifelse(Species_LifeFormNameLocal == "Subshrub", "Shrub", Species_LifeFormNameLocal),
    Species_LifeFormNameLocal = factor(
      Species_LifeFormNameLocal,
      levels = c(
        "Tree",
        "Shrub",
        "Forb/herb",
        "Fern",
        "Vine",
        "Graminoid",
        "Grass-like",
        "Nonvascular", 
        "Lichenous", 
        "Substrate"
      ))) %>% 
  filter(Species_Nativity == "Native")
```

\newpage

### Native Grasses and Forbs

```{r}
if(target_type == "Forest" & !(is.na(target_Native))) {
  kable(Objectives_Forest %>% 
          filter(Num == 6) %>% 
          select(Objective)
        )
}

if(target_type == "Grassland" & !(is.na(target_Native))) {
  kable(Objectives_Grassland %>% 
          filter(Num == 3) %>% 
          select(Objective))
}
```

```{r, include=FALSE}
if(nrow(Cover_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Cover_graph %>% 
  filter(
    Species_LifeFormNameLocal %in% c(
      #"Nonvascular", "Lichenous", 
      "Graminoid", "Grass-like",
      "Forb/herb", "Fern"
      ,"Vine"
      #,"Shrub", "Subshrub",
      #"Tree",
      #"Substrate"
      ),
    Species_Nativity %in% c(
      "Native"
      #"Nonnative",
      #"Invasive",
      #"Unknown"
      )
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    # ,Species_LifeFormNameLocal
    # ,Species_Genus
    # ,Species_ScientificName
    # ,Species_Nativity
    ) %>% 
  dplyr::summarise(
    Status_Cover = sum(PctCover),
    .groups = "drop"
    ) %>%
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    # ,Species_LifeFormNameLocal
    # ,Species_Genus
    # ,Species_ScientificName
    # ,Species_Nativity
    ) %>% 
  dplyr::summarise(
    Total_Cover = round(mean(Status_Cover), 1),
    .groups = "drop"
    ) %>% 

  
  ggplot(aes(x = SampleEvent_Date_Year, y = Total_Cover)) +
  geom_line() +
  geom_point() +
  geom_text(
    data = Cover_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "% Cover",
    title = paste(target_park, target_type, "Native Grass and Forb Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  ylim(0, NA) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )  +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    ) +
  geom_hline(
    yintercept = target_Native, 
    linetype = "dashed", 
    color = "forestgreen"
    )
}

p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Native Grass and Forb Cover"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Native.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Native Herbs"))
}
```

\newpage

### Cover Lifeform

```{r, include=FALSE}
if(nrow(Cover_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Cover_graph %>% 
  filter(
    Species_LifeFormNameLocal %in% c(
      #"Nonvascular", "Lichenous"
      "Graminoid", "Grass-like"
      ,"Forb/herb", "Fern", "Vine"
      ,"Shrub" ,"Subshrub"
      ,"Tree"
      #,"Substrate"
      ),
    Species_Nativity %in% c(
      "Native",
      "Nonnative",
      "Invasive",
      "Unknown"
      )
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Species_LifeFormNameLocal
    # ,Species_Genus
    # ,Species_ScientificName
    # ,Species_Nativity
    ) %>% 
  dplyr::summarise(
    Status_Cover = sum(PctCover),
    .groups = "drop"
    ) %>%
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    ,Species_LifeFormNameLocal
    # ,Species_Genus
    # ,Species_ScientificName
    # ,Species_Nativity
    ) %>% 
  dplyr::summarise(
    Total_Cover = round(mean(Status_Cover), 1),
    .groups = "drop"
    ) %>% 

  ggplot() +
  geom_col(
    aes(
      x = SampleEvent_Date_Year,
      y = Total_Cover,
      fill = Species_LifeFormNameLocal
      ),
    # position_dodge means the bars will display side by side
    position = "stack", stat = "identity"
    #position = position_dodge2(preserve = "single"), stat = "identity"
  ) +
  geom_text(
    data = Cover_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "% Cover",
    fill = "Lifeform",
    title = paste(target_park, target_type, "Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    )
}

p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Cover"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Lifeform.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Lifeform"))
}
```

\newpage

### Cover Nonnative Invasive

```{r}
if(target_type == "Grassland" & !(is.na(target_Invasive))) {
  kable(Objectives_Grassland %>% 
          filter(Num == 2) %>% 
          select(Objective))
}
```

```{r, include=FALSE}
if(nrow(Cover_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Cover_graph %>% 
  filter(
    Species_LifeFormNameLocal %in% c(
      #"Nonvascular", "Lichenous", 
      "Graminoid", "Grass-like",
      "Forb/herb", "Fern"
      ,"Vine"
      #,"Shrub", "Subshrub",
      #"Tree",
      #"Substrate"
      ),
    Species_Nativity %in% c(
      #"Native"
      "Nonnative",
      "Invasive"
      #"Unknown"
      )
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    # ,Species_LifeFormNameLocal
    # ,Species_Genus
    # ,Species_ScientificName
    # ,Species_Nativity
    ) %>% 
  dplyr::summarise(
    Status_Cover = sum(PctCover),
    .groups = "drop"
    ) %>%
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    # ,Species_LifeFormNameLocal
    # ,Species_Genus
    # ,Species_ScientificName
    # ,Species_Nativity
    ) %>% 
  dplyr::summarise(
    Total_Cover = round(mean(Status_Cover), 1),
    .groups = "drop"
    ) %>% 

  
  ggplot(aes(x = SampleEvent_Date_Year, y = Total_Cover)) +
  geom_line() +
  geom_point() +
  geom_text(
    data = Cover_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "% Cover",
    title = paste(target_park, target_type, "Non-Native Invasive Grass and Forb Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  ylim(0, NA) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )  +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    ) +
  geom_hline(
    yintercept = target_Invasive, 
    linetype = "dashed", 
    color = "darkorange"
    )
}

p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Non-Native Invasive Grass and Forb Cover"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Invasive.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Invasive"))
}
```

\newpage

### Cover Woody

```{r}
if(target_type == "Grassland" & !(is.na(target_Woody))) {
  kable(Objectives_Grassland %>% 
          filter(Num == 1) %>% 
          select(Objective))
}
```

```{r, include=FALSE}
if(nrow(Cover_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Cover_graph %>% 
  filter(
    Species_LifeFormNameLocal %in% c(
      #"Nonvascular", "Lichenous", 
      #"Graminoid", "Grass-like",
      #"Forb/herb", "Fern"
      #,"Vine"
      "Shrub", "Subshrub",
      "Tree"
      #"Substrate"
      ),
    Species_Nativity %in% c(
      "Native",
      "Nonnative",
      "Invasive",
      "Unknown"
      )
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    # ,Species_LifeFormNameLocal
    # ,Species_Genus
    # ,Species_ScientificName
    # ,Species_Nativity
    ) %>% 
  dplyr::summarise(
    Status_Cover = sum(PctCover),
    .groups = "drop"
    ) %>%
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    # ,Species_LifeFormNameLocal
    # ,Species_Genus
    # ,Species_ScientificName
    # ,Species_Nativity
    ) %>% 
  dplyr::summarise(
    Total_Cover = round(mean(Status_Cover), 1),
    .groups = "drop"
    ) %>% 

  
  ggplot(aes(x = SampleEvent_Date_Year, y = Total_Cover)) +
  geom_line() +
  geom_point() +
  geom_text(
    data = Cover_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "% Cover",
    title = paste(target_park, target_type, "Woody Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  ylim(0, NA) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )  +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    ) +
  geom_hline(
    yintercept = target_Woody, 
    linetype = "dashed", 
    color = "darkorange"
    )
}

p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Woody Cover"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Woody.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Woody"))
}
```

\newpage

### Cover Height

```{r, include=FALSE}
if(nrow(Cover_graph) == 0) {
  p_data <- "No data available for this selection."
} else {
p_data <- Cover_graph %>% 
  filter(
    Species_LifeFormNameLocal %in% c(
      #"Nonvascular", "Lichenous"
      "Graminoid", "Grass-like"
      ,"Forb/herb", "Fern", "Vine"
      ,"Shrub" ,"Subshrub"
      ,"Tree"
      #,"Substrate"
      ),
    Species_Nativity %in% c(
      "Native",
      "Nonnative",
      "Invasive"
      #"Unknown"
      )
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, SampleEvent_Date_Year
    ,Species_LifeFormNameLocal
    # ,Species_Genus
    # ,Species_ScientificName
    # ,Species_Nativity
    ) %>% 
  dplyr::summarise(
    Total_Cover = sum(PctCover, na.rm = TRUE),
    Avg_Ht_m = mean(Avg_Ht_m),
    Avg_Ht_ft = mean(Avg_Ht_ft),
    .groups = "drop"
    ) %>%  
  
  ggplot() +
  geom_col(
    aes(
      x = SampleEvent_Date_Year,
      y = Avg_Ht_ft,
      fill = Species_LifeFormNameLocal
      ),
    # position_dodge means the bars will display side by side
    #position = "stack", stat = "identity"
    position = position_dodge2(preserve = "single"), stat = "identity"
  ) +
  geom_text(
    data = Cover_graph %>%
      group_by(Macroplot_UV1,Macroplot_UV2,SampleEvent_Date_Year) %>% 
      summarize(n_plots = max(n_plots), .groups = "drop"),
    aes(
      x = SampleEvent_Date_Year,
      y = 0,
      label = n_plots
      ),
    vjust = 0.3, size = 3, color = "grey40"
  ) +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  facet_grid(Macroplot_UV1 ~ Macroplot_UV2) +
  labs(
    x = "Year",
    y = "Height (ft)",
    fill = "Lifeform",
    title = paste(target_park, target_type, "Understory Height")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  ylim(0, 6) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    data = MetadataReport_Disturbances,
    aes(xintercept = Disturbance_Date_Year - 0.5),
    linetype = "dashed",
    color = "red"
    )
}

#p_data
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Understory Height"),
    fill = "Disturbance"
       )

p_data_merge <- p_data +
  theme(plot.title = element_blank(),
        strip.text.x = element_blank())

if(is.character(p_data)) {
  p <- p_data
} else {
  p <-
    p_disturbance_merge / p_data_merge +
    plot_layout(heights = c(0.2, 1.4))
}


# save when ready
if(is.character(p)) {
  print(p)
} else {
  print(p)
  
ggsave(filename = paste0(path_save, target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Height.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
  
download_this(p, icon = NULL,
  output_name = paste0(target_park, "_", target_ProjectUnit, "_", target_MonitoringType, "_Cover Height"))
}
```

\newpage

# Discussion

\newpage

# References

## Tree List

```{r}
Species_trees_table <- Species_trees %>% 
  select(!c(Genus, Strategy)) %>% 
  kbl() %>% 
  kable_styling("striped", full_width = FALSE)

# Apply colors only where needed
Species_trees_table %>%
  row_spec(which(Species_trees$`Fire Adaptedness` == "fire adapted"), 
           background = "coral2") %>% 
  row_spec(which(Species_trees$`Fire Adaptedness` == "fire tolerant"), 
           background = "bisque") %>% 
  row_spec(which(Species_trees$`Fire Adaptedness` == "fire intolerant"), 
           background = "skyblue3")

# # Apply colors only where needed
# Species_trees_table %>%
#   row_spec(which(Species_trees$`Fire Adaptedness` == "fire adapted" & Species_trees$`Strategy` == "Pyrophyte"), 
#            background = "coral2") %>% 
#   row_spec(which(Species_trees$`Fire Adaptedness` == "fire adapted" & is.na(Species_trees$`Strategy`)), 
#            background = "lightsalmon1") %>% 
#   row_spec(which(Species_trees$`Fire Adaptedness` == "fire tolerant" & Species_trees$`Strategy` == "Pyrophyte"), 
#            background = "lightsalmon1") %>% 
#   row_spec(which(Species_trees$`Fire Adaptedness` == "fire tolerant" & Species_trees$`Strategy` == "Intermediate"), 
#            background = "bisque") %>% 
#   row_spec(which(Species_trees$`Fire Adaptedness` == "fire tolerant" & is.na(Species_trees$`Strategy`)), 
#            background = "bisque") %>% 
#   row_spec(which(Species_trees$`Fire Adaptedness` == "fire tolerant" & Species_trees$`Strategy` == "Mesophyte"), 
#            background = "lightskyblue1") %>% 
#   row_spec(which(Species_trees$`Fire Adaptedness` == "fire intolerant" & Species_trees$`Strategy` == "Mesophyte"), 
#            background = "skyblue3")
```

\newpage

## Species List

```{r}
Species_all_table <- Species_all %>% 
  select(!Genus) %>% 
  kbl() %>% 
  kable_styling("striped", full_width = FALSE)

Species_all_table
```

\newpage

## Literature Cited

```{r}
WriteBib(bib, file = "zotero_refs.bib")
```
