---
title: Clean FFI Data
author: Alexandra Lalor
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 1
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: 1
---

# PURPOSE

This code is intended to combine FFI files into flat files to be used with subsequent R scripts.

The Sample Event Report and Macroplot Report can be downloaded via the Utilities menu on the Project Management tab on the FFI Remote App Server.

-   MacroplotReport.csv

-   SampleEventReport.csv

The Local Species Report can be downloaded via the Species menu on the Species Management tab on the FFI Remote App Server.

-   LocalSpeciesReport.csv

The Protocol data can be downloaded via Query tab on the FFI Remote App Server by using the saved queries from the drop down options.

-   Surface Fuels - 1000Hr_XPT.csv

-   Surface Fuels - Duff_Litter_XPT.csv

-   Surface Fuels - Fine_XPT.csv

-   Post Burn Severity (metric)\_XPT.csv

-   Trees - Individuals (metric)\_XPT.csv

-   Density - Quadrats (metric)\_XPT.csv

-   Density - Belts (metric)\_XPT.csv

-   Cover - Species Composition (metric)\_XPT.csv

-   Cover - Points (metric)\_XPT.csv

## BEFORE STARTING {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
# install.packages("tidyverse")
# install.packages("knitr")
# install.packages("here")
```

```{r}
# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
# knitr is used to create output files from R Markdown
library(knitr)
```

### Adjust File Paths {.hidden}

```{r}
# adjust file paths
path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
#path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_main_data <- paste0(path_main, "Exports/")
path_save <- paste0(path_main, "R Outputs/")
```

### Parks {.hidden}

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
```

# METADATA

## Sample Event & Macroplot Report

```{r warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  MacroplotReport <- read.csv(paste0(path_data, "MacroplotReport.csv"), na.strings = c("","NA","N/A"))
  SampleEventReport <- read.csv(paste0(path_data, "SampleEventReport.csv"), na.strings = c("","NA","N/A"))
  
  
  # clean & filter data
  #### Macroplot Report
  # The Macroplot Report contains information on both plot metadata and sample event history. Separate these into 2 tables.
  MacroplotReport_MetaData <- MacroplotReport %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate tables
    filter(is.na(SampleEventDate)) %>%
    # separate Date column
    separate(DateIn, sep = " ", 
             into = c("Macroplot_DateIn", "DateInTime")) %>%
    separate(FutureVisit, sep = " ", 
             into = c("Macroplot_FutureVisit", "FutureVisitTime")) %>%
    separate(DateOut, sep = " ", 
             into = c("Macroplot_DateOut", "DateOutTime")) %>%
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    # make column names consistent
    dplyr::rename(Macroplot_Name = Macroplot) %>% 
    # remove unnecessary columns
    select(!c(DateInTime, FutureVisitTime, DateOutTime)) %>% 
    select(!c(SampleEventDate, SampleEventTeam, SampleEventComment, 
              MonStatusOrd, LegacyMonStatus, MonStatus))

  MacroplotReport_SampleEvents <- MacroplotReport %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate tables
    filter(!is.na(SampleEventDate)) %>%
    # separate Date column
    separate(SampleEventDate, sep = " ", 
             into = c("SampleEvent_Date", "SampleEvent_Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    # make column names consistent
    dplyr::rename(Macroplot_Name = Macroplot,
                  SampleEvent_LegacyMonStatus = LegacyMonStatus,
                  SampleEvent_Who = SampleEventTeam,
                  SampleEvent_Comment = SampleEventComment,
                  MonStatus_Name = MonStatus,
                  MonStatus_Order = MonStatusOrd) %>% 
    # remove unnecessary columns
    select(!c(SampleEvent_Time)) %>%
    select(c(Macroplot_Name, SampleEvent_Date, SampleEvent_Date_Year, 
             SampleEvent_Who, SampleEvent_Comment, MonStatus_Order, 
             SampleEvent_LegacyMonStatus, MonStatus_Name))
  
  #### Sample Event Report
  # The Sample Event Report has different column names as the Macroplot Report, but contains the same information. Make column names consistent.
  SampleEventReport_clean <- SampleEventReport %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(SampleEvent_Date, sep = " ", 
             into = c("SampleEvent_Date", "SampleEvent_Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    # make column names consistent
    dplyr::rename(AdminUnit_Name = AdministrationUnit_Name,
                  Macroplot_Name = MacroPlot_Name,
                  SampleEvent_Protocols = Protocols,
                  SampleEvent_Visited = Visited,
                  MonStatus_Name = MonitoringStatus_Name) %>% 
    # remove unnecessary columns
    select(!c(SampleEvent_Time, SampleEvent_LegacyMonitoringStatus))
  
  
  # merge data
  #### Merge MacroplotReport_Metadata and MacroplotReport_SampleEvents
  MacroplotReport_merge <- merge(MacroplotReport_MetaData, MacroplotReport_SampleEvents, by = c("Macroplot_Name")) %>%
    select(!MonStatus_Order)
  
  #### Filter Sample Event Report for merging
  SampleEventReport_merge <- SampleEventReport_clean %>%
    filter(ProjectUnit_Name != "ALL") %>% 
    select(!c(Multi_PU))
  
  #### Merge Macroplot Report and Sample Event Report
  MetadataReport <- merge(MacroplotReport_merge, SampleEventReport_merge, by = c("Macroplot_Name", "SampleEvent_Date", "SampleEvent_Date_Year", "MonStatus_Name")) %>%
    relocate(AdminUnit_Name, .before = Macroplot_Name) %>%
    relocate(ProjectUnit_Name, .after = Purpose) %>%
    relocate(Type, .after = Purpose) %>% 
    relocate(Macroplot_Name, .after = Type) %>%
    relocate(SampleEvent_Date, .after = SampleEvent_Visited) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(MonStatus_Name, .after = SampleEvent_LegacyMonStatus) %>%
    relocate(LocatedBy, .before = StartPoint)
  
  # replace commas with semicolons
  MetadataReport[] <- lapply(MetadataReport, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  MetadataReport[] <- lapply(MetadataReport, function(x) gsub('"', "'", x))
  
  # add data to master list
  final_df <- rbind(final_df, MetadataReport)
}

# final column renaming to match protocol exports
    final_df <- final_df %>%  
      dplyr::rename(
        Macroplot_Purpose = Purpose,
        Macroplot_Type = Type,
        Macroplot_Lat_dd = Latitude,
        Macroplot_Long_dd = Longitude,
        Macroplot_UtmX_m = UTM_X,
        Macroplot_UtmY_m = UTM_Y,
        Macroplot_UtmZone = UTM_Zone,
        Macroplot_Datum = Datum,
        Macroplot_Pdop = PDOP,
        Macroplot_Precision = Precision,
        Macroplot_Elevation = Elevation,
        Macroplot_ElevationUnits = ElevationUnits,
        Macroplot_Azimuth = Azimuth,
        Macroplot_Aspect = Aspect,
        Macroplot_SlopeHill_pct = SlopeHill,
        Macroplot_SlopeTransect_pct = SlopeTransect,
        Macroplot_LocatedBy = LocatedBy,
        Macroplot_StartPoint = StartPoint,
        Macroplot_Directions = Directions,
        Macroplot_Comment = Comments,
        Macroplot_Metadata = MetaData,
        Macroplot_UV1 = UV1,
        Macroplot_UV2 = UV2,
        Macroplot_UV3 = UV3,
        Macroplot_UV4 = UV4,
        Macroplot_UV5 = UV5,
        Macroplot_UV6 = UV6,
        Macroplot_UV7 = UV7,
        Macroplot_UV8 = UV8
        )
    
  # save file
write.csv(final_df, paste0(path_save, "MetadataReport.csv"), quote = FALSE, row.names = FALSE) 
```

# SPECIES

## Species Report

```{r warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  SpeciesReport <- read.csv(paste0(path_data, "LocalSpeciesReport.csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  SpeciesReport <- SpeciesReport %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  SpeciesReport[] <- lapply(SpeciesReport, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  SpeciesReport[] <- lapply(SpeciesReport, function(x) gsub('"', "'", x))
    
    
  # add data to master list
  final_df <- rbind(final_df, SpeciesReport)
}

  # final column renaming to match protocol exports
    final_df <- final_df %>% 
      dplyr::rename(
        #Species_Id = # not on species report
        #AdminUnitId = # not on species report
        #Species_MasterSpeciesId = # not on species report
        #Species_AuxSpeciesId = # not on species report
        #Species_LocalSpeciesId = # not on species report
        Species_AdminUnitName = ReportType,
        #Species_OrganizationName = # not on species report
        #Species_MasterOrUserLocal = # not on species report
        Species_ITIS_TSN = MasterSpecies_ITIS_TSN,
        Species_LocalSpeciesSymbol = LocalSpecies_Symbol,
        #Species_Symbol = # not on species report
        Species_ScientificName = MasterSpecies_ScientificName,
        #Species_CommonName = # not on species report
        Species_CommonNameLocal = LocalSpecies_CommonName,
        Species_Genus = MasterSpecies_Genus,
        Species_Family = MasterSpecies_Family,
        Species_NotBiological = MasterSpecies_NotBiolgoical,
        #Species_Nativity = # not on species report
        Species_NativityLocal = LocalSpecies_Nativity,
        #Species_LifeFormName = # not on species report
        Species_LifeFormNameLocal = LocalSpecies_PreferedLifeForm,
        Species_Description = LocalSpecies_Description,
        Species_LifeCycleLocal = LocalSpecies_LifeCycle,
        #Species_LifeCycle = # not on species report
        Species_UV1 = LocalSpecies_UV1,
        Species_UV2 = LocalSpecies_UV2,
        Species_UV3 = LocalSpecies_UV3,
        Species_UserAdded = LocalSpecies_UserAdded,
        Species_Cultural = LocalSpecies_Cultural,
        Species_Invasive = LocalSpecies_Invasive,
        Species_Concern = LocalSpecies_Concern,
        Species_Retired = LocalSpecies_Retired,
        Species_Comment = LocalSpecies_Comment
        #MethodData_sppGuid = LocalSpecies_GUID,
        #Species_SourceEntityId = LocalSpecies_GUID
        )
    
  # save file
  write.csv(final_df, paste0(path_save, "SpeciesReport.csv"), quote = FALSE, row.names = FALSE)
```

# PROTOCOLS

## Cover

### cover_frequency

### cover_line_intercept

### cover_points

```{r cover_points, warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  HerbsPoints_all <- read.csv(paste0(path_data, "Cover - Points (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  HerbsPoints_all <- HerbsPoints_all[, -ncol(HerbsPoints_all)]
  ## replace commas with semicolons
  HerbsPoints_all[] <- lapply(HerbsPoints_all, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  HerbsPoints_all[] <- lapply(HerbsPoints_all, function(x) gsub('"', "'", x))
  
  
  # clean data
  HerbsPoints_all <- HerbsPoints_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## HerbsPoints headers
  HerbsPoints_header <- HerbsPoints_all %>%
    filter(!is.na(Visited)) %>% 
    select(c(1:19,
             NumTran, TranLen, NumPtsTran, Offset, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## HerbsPoints data
  HerbsPoints_data <- HerbsPoints_all %>%
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, TranLen, NumPtsTran, Offset, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  HerbsPoints <- merge(HerbsPoints_header, HerbsPoints_data, by = c(1:19))
  
  
  # add column for park name
  HerbsPoints <- HerbsPoints %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # add data to master list
  final_df <- rbind(final_df, HerbsPoints)
}

  # final column renaming to match metadata
  final_df <- final_df %>% 
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonStatus_Name = Monitoring.Status,
      MonStatus_Prefix = Status.Prefix,
      MonStatus_Base = Status.Base,
      MonStatus_Suffix = Status.Suffix,
      MonStatus_Order = Status.Order,
      Species_LifeCycleLocal = Lifecycle,
      Species_NotBiological = NotBiological,
      Species_LifeFormNameLocal = Preferred_Lifeform,
      Species_Family = Family,
      Species_Genus = Genus,
      Species_ScientificName = ScientificName,
      Species_NativityLocal = Native.Species,
      Species_Invasive = Invasive.Species,
      MethodData_LocalSpeciesSymbol = Species.Symbol,
      MethodData_NumTran = NumTran,
      MethodData_TranLen_m = TranLen,
      MethodData_NumPtsTran = NumPtsTran,
      MethodData_Offset_m = Offset,
      MethodData_FieldTeam = FieldTeam,
      MethodData_EntryTeam = EntryTeam,
      MethodData_UV1Desc = UV1Desc,
      MethodData_UV2Desc = UV2Desc,
      MethodData_UV3Desc = UV3Desc,
      MethodData_SAComment = SaComment,
      MethodData_Visited = Visited,
      MethodData_Index = Index,
      MethodData_Transect = Transect,
      MethodData_Point = Point,
      MethodData_Tape = Tape,
      MethodData_Order = Order,
      MethodData_Height_m = Height,
      MethodData_CanopyLayer = CanopyLayer,
      MethodData_Status = Status,
      MethodData_Comment = Comment,
      MethodData_UV1 = UV1,
      MethodData_UV2 = UV2,
      MethodData_UV3 = UV3
      )
  
  # save file
  write.csv(final_df, paste0(path_save, "Data_Cover - Points (metric).csv"), quote = FALSE, row.names = FALSE)
```

### cover_species_composition

```{r cover_species_composition, warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  HerbsSpComp_all <- read.csv(paste0(path_data, "Cover - Species Composition (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  HerbsSpComp_all <- HerbsSpComp_all[, -ncol(HerbsSpComp_all)]
  ## replace commas with semicolons
  HerbsSpComp_all[] <- lapply(HerbsSpComp_all, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  HerbsSpComp_all[] <- lapply(HerbsSpComp_all, function(x) gsub('"', "'", x))
  
  
  # clean data
  HerbsSpComp_all <- HerbsSpComp_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## HerbsSpComp headers
  HerbsSpComp_header <- HerbsSpComp_all %>%
    filter(!is.na(Visited)) %>% 
    select(c(1:19,
             MinCovLevel, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## HerbsSpComp data
  HerbsSpComp_data <- HerbsSpComp_all %>%
    filter(is.na(Visited)) %>% 
    select(!c(MinCovLevel, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  HerbsSpComp <- merge(HerbsSpComp_header, HerbsSpComp_data, by = c(1:19))
  
  
  # add column for park name
  HerbsSpComp <- HerbsSpComp %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # add data to master list
  final_df <- rbind(final_df, HerbsSpComp)
}

# final column renaming to match metadata
  final_df <- final_df %>%  
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonStatus_Name = Monitoring.Status,
      MonStatus_Prefix = Status.Prefix,
      MonStatus_Base = Status.Base,
      MonStatus_Suffix = Status.Suffix,
      MonStatus_Order = Status.Order,
      Species_LifeCycleLocal = Lifecycle,
      Species_NotBiological = NotBiological,
      Species_LifeFormNameLocal = Preferred_Lifeform,
      Species_Family = Family,
      Species_Genus = Genus,
      Species_ScientificName = ScientificName,
      Species_NativityLocal = Native.Species,
      Species_Invasive = Invasive.Species,
      MethodData_LocalSpeciesSymbol = Species.Symbol,
      MethodData_MinCovLevel_pct = MinCovLevel,
      MethodData_Area_ha = Area,
      MethodData_FieldTeam = FieldTeam,
      MethodData_EntryTeam = EntryTeam,
      MethodData_UV1Desc = UV1Desc,
      MethodData_UV2Desc = UV2Desc,
      MethodData_UV3Desc = UV3Desc,
      MethodData_SAComment = SaComment,
      MethodData_Visited = Visited,
      MethodData_Index = Index,
      MethodData_Status = Status,
      MethodData_SizeCl = SizeCl,
      MethodData_AgeCl = AgeCl,
      MethodData_Cover = Cover,
      MethodData_Height_m = Height,
      MethodData_Comment = Comment,
      MethodData_UV1 = UV1,
      MethodData_UV2 = UV2,
      MethodData_UV3 = UV3
      )
  
  # save file
  write.csv(final_df, paste0(path_save, "Data_Cover - Species Composition (metric).csv"), quote = FALSE, row.names = FALSE) 
```

## Surface Fuels

### surface_fuels_alaska_duff_litter

### surface_fuels_duff_litter

```{r surface_fuels_duff_litter, warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  FuelsDuffLitt_all <- read.csv(paste0(path_data, "Surface Fuels - Duff_Litter_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  FuelsDuffLitt_all <- FuelsDuffLitt_all[, -ncol(FuelsDuffLitt_all)]
  ## replace commas with semicolons
  FuelsDuffLitt_all[] <- lapply(FuelsDuffLitt_all, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  FuelsDuffLitt_all[] <- lapply(FuelsDuffLitt_all, function(x) gsub('"', "'", x))
  
  
  # clean data
  FuelsDuffLitt_all <- FuelsDuffLitt_all %>% 
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## FuelsDuffLitt headers
  FuelsDuffLitt_header <- FuelsDuffLitt_all %>%   
    filter(!is.na(Visited)) %>% 
    select(c(1:19,
             NumTran, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## FuelsDuffLitt data
  FuelsDuffLitt_data <- FuelsDuffLitt_all %>%   
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  FuelsDuffLitt <- merge(FuelsDuffLitt_header, FuelsDuffLitt_data, by = c(1:19))
  
  
  # add column for park name
  FuelsDuffLitt <- FuelsDuffLitt %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # add data to master list
  final_df <- rbind(final_df, FuelsDuffLitt)
}

# final column renaming to match metadata
  final_df <- final_df %>%  
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonStatus_Name = Monitoring.Status,
      MonStatus_Prefix = Status.Prefix,
      MonStatus_Base = Status.Base,
      MonStatus_Suffix = Status.Suffix,
      MonStatus_Order = Status.Order,
      MethodData_NumTran = NumTran,
      MethodData_FieldTeam = FieldTeam,
      MethodData_EntryTeam = EntryTeam,
      MethodData_UV1Desc = UV1Desc,
      MethodData_UV2Desc = UV2Desc,
      MethodData_UV3Desc = UV3Desc,
      MethodData_SAComment = SaComment,
      MethodData_Visited = Visited, # not in data depot
      MethodData_Index = Index,
      MethodData_Transect = Transect,
      MethodData_SampLoc_ft = SampLoc,
      MethodData_OffSet = OffSet,
      MethodData_LittDep_in = LittDep,
      MethodData_DuffDep_in = DuffDep,
      MethodData_FuelbedDep_in = FuelbedDep,
      MethodData_DLFuConSt = DLFuConSt,
      MethodData_Comment = Comment,
      MethodData_UV1 = UV1,
      MethodData_UV2 = UV2,
      MethodData_UV3 = UV3
      )
  
  # save file
  write.csv(final_df, paste0(path_save, "Data_Surface Fuels - Duff_Litter.csv"), quote = FALSE, row.names = FALSE) 
```

### surface_fuels_fine

```{r surface_fuels_fine, warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  FuelsFine_all <- read.csv(paste0(path_data, "Surface Fuels - Fine_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  FuelsFine_all <- FuelsFine_all[, -ncol(FuelsFine_all)]
  ## replace commas with semicolons
  FuelsFine_all[] <- lapply(FuelsFine_all, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  FuelsFine_all[] <- lapply(FuelsFine_all, function(x) gsub('"', "'", x))
  
  
  # clean data
  FuelsFine_all <- FuelsFine_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## FuelsFine headers 
  FuelsFine_header <- FuelsFine_all %>%   
    filter(!is.na(Visited)) %>% 
    select(c(1:19,
             NumTran, OneHrTranLen, TenHrTranLen, HunHrTranLen, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
## FuelsFine data
  FuelsFine_data <- FuelsFine_all %>%   
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, OneHrTranLen, TenHrTranLen, HunHrTranLen, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  FuelsFine <- merge(FuelsFine_header, FuelsFine_data, by = c(1:19))
  
  
  # add column for park name
  FuelsFine <- FuelsFine %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # add data to master list
  final_df <- rbind(final_df, FuelsFine)
}

# final column renaming to match metadata
  final_df <- final_df %>%  
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonStatus_Name = Monitoring.Status,
      MonStatus_Prefix = Status.Prefix,
      MonStatus_Base = Status.Base,
      MonStatus_Suffix = Status.Suffix,
      MonStatus_Order = Status.Order,
      MethodData_NumTran = NumTran,
      MethodData_OneHrTranLen_ft = OneHrTranLen,
      MethodData_TenHrTranLen_ft = TenHrTranLen,
      MethodData_HunHrTranLen_ft = HunHrTranLen,
      MethodData_FieldTeam = FieldTeam,
      MethodData_EntryTeam = EntryTeam,
      MethodData_UV1Desc = UV1Desc,
      MethodData_UV2Desc = UV2Desc,
      MethodData_UV3Desc = UV3Desc,
      MethodData_SAComment = SaComment,
      MethodData_Visited = Visited,
      MethodData_Index = Index,
      MethodData_Transect = Transect,
      MethodData_Azimuth_deg = Azimuth,
      MethodData_Slope_pct = Slope,
      MethodData_OneHr = OneHr,
      MethodData_TenHr = TenHr,
      MethodData_HunHr = HunHr,
      MethodData_FWDFuConSt = FWDFuConSt,
      MethodData_Comment = Comment,
      MethodData_UV1 = UV1,
      MethodData_UV2 = UV2,
      MethodData_UV3 = UV3
      )
  
  # save file
  write.csv(final_df, paste0(path_save, "Data_Surface Fuels - Fine.csv"), quote = FALSE, row.names = FALSE) 
```

### surface_fuels_piles

### surface_fuels_thousand_hr

```{r surface_fuels_thousand_hr, warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  Fuels1000_all <- read.csv(paste0(path_data, "Surface Fuels - 1000Hr_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  Fuels1000_all <- Fuels1000_all[, -ncol(Fuels1000_all)]
  ## replace commas with semicolons
  Fuels1000_all[] <- lapply(Fuels1000_all, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  Fuels1000_all[] <- lapply(Fuels1000_all, function(x) gsub('"', "'", x))
  
  
  # clean data
  Fuels1000_all <- Fuels1000_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## Fuels1000 headers
  Fuels1000_header <- Fuels1000_all %>%
    filter(!is.na(Visited)) %>% 
    select(c(1:19, 
             NumTran, TranLen, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## Fuels1000 data
  Fuels1000_data <- Fuels1000_all %>%
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, TranLen, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))


  # merge data
  Fuels1000 <- merge(Fuels1000_header, Fuels1000_data, by = c(1:19))
  
  
  # add column for park name
  Fuels1000 <- Fuels1000 %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # add data to master list
  final_df <- rbind(final_df, Fuels1000)
}

  # final column renaming to match metadata
  final_df <- final_df %>% 
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonStatus_Name = Monitoring.Status,
      MonStatus_Prefix = Status.Prefix,
      MonStatus_Base = Status.Base,
      MonStatus_Suffix = Status.Suffix,
      MonStatus_Order = Status.Order,
      MethodData_NumTran = NumTran,
      MethodData_TranLen_ft = TranLen,
      MethodData_FieldTeam = FieldTeam,
      MethodData_EntryTeam = EntryTeam,
      MethodData_UV1Desc = UV1Desc,
      MethodData_UV2Desc = UV2Desc,
      MethodData_UV3Desc = UV3Desc,
      MethodData_SAComment = SaComment,
      MethodData_Visited = Visited,
      MethodData_Index = Index,
      MethodData_Transect = Transect,
      MethodData_Slope_pct = Slope,
      MethodData_LogNum = LogNum,
      MethodData_Dia_in = Dia,
      MethodData_DecayCl = DecayCl,
      MethodData_CWDFuConSt = CWDFuConSt,
      MethodData_Comment = Comment,
      MethodData_UV1 = UV1,
      MethodData_UV2 = UV2,
      MethodData_UV3 = UV3
      )
  
  # save file
  write.csv(final_df, paste0(path_save, "Data_Surface Fuels - 1000Hr.csv"), quote = FALSE, row.names = FALSE)
```

### surface_fuels_vegetation

## Trees

### trees_individuals

```{r trees_individuals, warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  Trees_all <- read.csv(paste0(path_data, "Trees - Individuals (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  Trees_all <- Trees_all[, -ncol(Trees_all)]
  ## replace commas with semicolons
  Trees_all[] <- lapply(Trees_all, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  Trees_all[] <- lapply(Trees_all, function(x) gsub('"', "'", x))
  
  
  # clean data
  Trees_all <- Trees_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## Trees headers
  Trees_header <- Trees_all %>%   
    filter(!is.na(Visited)) %>% 
    select(c(1:19,
             MacroPlotSize, SnagPlotSize, BrkPntDia, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## Trees data
  Trees_data <- Trees_all %>%   
    filter(is.na(Visited)) %>% 
    select(!c(MacroPlotSize, SnagPlotSize, BrkPntDia, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  Trees <- merge(Trees_header, Trees_data, by = c(1:19))
  
  
  # add column for park name
  Trees <- Trees %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # add data to master list
  final_df <- rbind(final_df, Trees)
}

# final column renaming to match metadata
  final_df <- final_df %>%  
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonStatus_Name = Monitoring.Status,
      MonStatus_Prefix = Status.Prefix,
      MonStatus_Base = Status.Base,
      MonStatus_Suffix = Status.Suffix,
      MonStatus_Order = Status.Order,
      Species_LifeCycleLocal = Lifecycle,
      Species_NotBiological = NotBiological,
      Species_LifeFormNameLocal = Preferred_Lifeform,
      Species_Family = Family,
      Species_Genus = Genus,
      Species_ScientificName = ScientificName,
      Species_NativityLocal = Native.Species,
      Species_Invasive = Invasive.Species,
      MethodData_LocalSpeciesSymbol = Species.Symbol,
      MethodData_MacroPlotSize_ha = MacroPlotSize,
      MethodData_SnagPlotSize_ha = SnagPlotSize,
      MethodData_BrkPntDia_cm = BrkPntDia,
      MethodData_FieldTeam = FieldTeam,
      MethodData_EntryTeam = EntryTeam,
      MethodData_UV1Desc = UV1Desc,
      MethodData_UV2Desc = UV2Desc,
      MethodData_UV3Desc = UV3Desc,
      MethodData_SAComment = SaComment,
      MethodData_Visited = Visited,
      MethodData_Index = Index,
      MethodData_IsVerified = IsVerified,
      MethodData_QTR = QTR,
      MethodData_SubFrac = SubFrac,
      MethodData_TagNo = TagNo,
      MethodData_Status = Status,
      MethodData_DBH_cm = DBH,
      MethodData_Ht_m = Ht,
      MethodData_CrwnRto_pct = CrwnRto,
      MethodData_CrwnCl = CrwnCl,
      MethodData_LiCrBHt_m = LiCrBHt,
      MethodData_CrFuBHt_m = CrFuBHt,
      MethodData_CrwnRad_m = CrwnRad,
      MethodData_Age = Age,
      MethodData_GrwthRt_cm = GrwthRt,
      MethodData_Mort = Mort,
      MethodData_DecayCl = DecayCl,
      MethodData_LaddBaseHt_m = LaddBaseHt,
      MethodData_LaddMaxHt_m = LaddMaxHt,
      MethodData_DRC_cm = DRC,
      MethodData_NuLiStems = NuLiStems,
      MethodData_NuDeStems = NuDeStems,
      MethodData_EqDia_cm = EqDia,
      MethodData_XCoord_m = XCoord,
      MethodData_YCoord_m = YCoord,
      MethodData_CKR = CKR,
      MethodData_CharHt_m = CharHt,
      MethodData_ScorchHt_m = ScorchHt,
      MethodData_CrScPct_pct = CrScPct,
      MethodData_DamCd1 = DamCd1,
      MethodData_DamCd2 = DamCd2,
      MethodData_DamCd3 = DamCd3,
      MethodData_DamCd4 = DamCd4,
      MethodData_DamCd5 = DamCd5,
      MethodData_DamSev1 = DamSev1,
      MethodData_DamSev2 = DamSev2,
      MethodData_DamSev3 = DamSev3,
      MethodData_DamSev4 = DamSev4,
      MethodData_DamSev5 = DamSev5,
      MethodData_Comment = Comment,
      MethodData_UV1 = UV1,
      MethodData_UV2 = UV2,
      MethodData_UV3 = UV3
      )
  
  # save file
  write.csv(final_df, paste0(path_save, "Data_Trees - Individuals (metric).csv"), quote = FALSE, row.names = FALSE)
```

### trees_saplings

### trees_seedlings

## Density

### density_quadrats (seedlings)

```{r density_quadrats, warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  Seedlings_all <- read.csv(paste0(path_data, "Density - Quadrats (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  Seedlings_all <- Seedlings_all[, -ncol(Seedlings_all)]
  ## replace commas with semicolons
  Seedlings_all[] <- lapply(Seedlings_all, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  Seedlings_all[] <- lapply(Seedlings_all, function(x) gsub('"', "'", x))
  
  
  # clean data
  Seedlings_all <- Seedlings_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## Seedlings headers
  Seedlings_header <- Seedlings_all %>%
    filter(!is.na(Visited)) %>% 
    select(c(1:19,
             NumTran, NumQuadTran, QuadLen, QuadWid, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## Seedlings data
  Seedlings_data <- Seedlings_all %>%
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, NumQuadTran, QuadLen, QuadWid, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  Seedlings <- merge(Seedlings_header, Seedlings_data, by = c(1:19))
  
  
  # add column for park name
  Seedlings <- Seedlings %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # add data to master list
  final_df <- rbind(final_df, Seedlings)
}

# final column renaming to match metadata
  final_df <- final_df %>%  
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonStatus_Name = Monitoring.Status,
      MonStatus_Prefix = Status.Prefix,
      MonStatus_Base = Status.Base,
      MonStatus_Suffix = Status.Suffix,
      MonStatus_Order = Status.Order,
      Species_LifeCycleLocal = Lifecycle,
      Species_NotBiological = NotBiological,
      Species_LifeFormNameLocal = Preferred_Lifeform,
      Species_Family = Family,
      Species_Genus = Genus,
      Species_ScientificName = ScientificName,
      Species_NativityLocal = Native.Species,
      Species_Invasive = Invasive.Species,
      MethodData_LocalSpeciesSymbol = Species.Symbol,
      MethodData_NumTran = NumTran,
      MethodData_NumQuadTran = NumQuadTran,
      MethodData_QuadLen = QuadLen,
      MethodData_QuadWid = QuadWid,
      MethodData_Area_ha = Area,
      MethodData_FieldTeam = FieldTeam,
      MethodData_EntryTeam = EntryTeam,
      MethodData_UV1Desc = UV1Desc,
      MethodData_UV2Desc = UV2Desc,
      MethodData_UV3Desc = UV3Desc,
      MethodData_SAComment = SaComment,
      MethodData_Visited = Visited,
      MethodData_Index = Index,
      MethodData_Transect = Transect,
      MethodData_Quadrat = Quadrat,
      MethodData_Status = Status,
      MethodData_SizeCl = SizeCl,
      MethodData_AgeCl = AgeCl,
      MethodData_Count = Count,
      MethodData_Height_m = Height,
      MethodData_SubFrac = SubFrac,
      MethodData_Comment = Comment,
      MethodData_UV1 = UV1,
      MethodData_UV2 = UV2,
      MethodData_UV3 = UV3
      )
  
  # save file
  write.csv(final_df, paste0(path_save, "Data_Density - Quadrats (metric).csv"), quote = FALSE, row.names = FALSE)
```

### density_belts (shrubs)

```{r warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  Shrubs_all <- read.csv(paste0(path_data, "Density - Belts (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  Shrubs_all <- Shrubs_all[, -ncol(Shrubs_all)]
  ## replace commas with semicolons
  Shrubs_all[] <- lapply(Shrubs_all, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  Shrubs_all[] <- lapply(Shrubs_all, function(x) gsub('"', "'", x))
  
  
  # clean data
  Shrubs_all <- Shrubs_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## Shrubs headers
  Shrubs_header <- Shrubs_all %>%
    filter(!is.na(Visited)) %>% 
    select(c(1:19,
             NumTran, NumSubbelt, TranLen, TranWid, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## Shrubs data
  Shrubs_data <- Shrubs_all %>%
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, NumSubbelt, TranLen, TranWid, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  Shrubs <- merge(Shrubs_header, Shrubs_data, by = c(1:19))
  
  
  # add column for park name
  Shrubs <- Shrubs %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # add data to master list
  final_df <- rbind(final_df, Shrubs)
}

# final column renaming to match metadata
  final_df <- final_df %>%  
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonStatus_Name = Monitoring.Status,
      MonStatus_Prefix = Status.Prefix,
      MonStatus_Base = Status.Base,
      MonStatus_Suffix = Status.Suffix,
      MonStatus_Order = Status.Order,
      Species_LifeCycleLocal = Lifecycle,
      Species_NotBiological = NotBiological,
      Species_LifeFormNameLocal = Preferred_Lifeform,
      Species_Family = Family,
      Species_Genus = Genus,
      Species_ScientificName = ScientificName,
      Species_NativityLocal = Native.Species,
      Species_Invasive = Invasive.Species,
      MethodData_LocalSpeciesSymbol = Species.Symbol,
      MethodData_NumTran = NumTran,
      MethodData_NumSubbelt = NumSubbelt,
      MethodData_TranLen = TranLen,
      MethodData_TranWid = TranWid,
      MethodData_Area_ha = Area,
      MethodData_FieldTeam = FieldTeam,
      MethodData_EntryTeam = EntryTeam,
      MethodData_UV1Desc = UV1Desc,
      MethodData_UV2Desc = UV2Desc,
      MethodData_UV3Desc = UV3Desc,
      MethodData_SAComment = SaComment,
      MethodData_Visited = Visited,
      MethodData_Index = Index,
      MethodData_Transect = Transect,
      MethodData_Subbelt = Subbelt,
      MethodData_Status = Status,
      MethodData_SizeCl = SizeCl,
      MethodData_AgeCl = AgeCl,
      MethodData_Count = Count,
      MethodData_Height_m = Height,
      MethodData_SubFrac = SubFrac,
      MethodData_Comment = Comment,
      MethodData_UV1 = UV1,
      MethodData_UV2 = UV2,
      MethodData_UV3 = UV3
      )
  
  # save file
  write.csv(final_df, paste0(path_save, "Data_Density - Belts (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Post Burn

### post_burn_severity

```{r warning=FALSE}
final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/", target_park, "_")
  
  
  # load data
  PostBurn_all <- read.csv(paste0(path_data, "Post Burn Severity (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  PostBurn_all <- PostBurn_all[, -ncol(PostBurn_all)]
  ## replace commas with semicolons
  PostBurn_all[] <- lapply(PostBurn_all, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  PostBurn_all[] <- lapply(PostBurn_all, function(x) gsub('"', "'", x))
  
  
  # clean data
  PostBurn_all <- PostBurn_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # reformate Date column
    mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>%
    # add Year column
    mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate Year column
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## PostBurn headers
  PostBurn_header <- PostBurn_all %>%
    filter(!is.na(Visited)) %>% 
    select(c(1:19,
             NumTran, TranLen, NumPtsTran, PlotType, PtArea, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## PostBurn data
  PostBurn_data <- PostBurn_all %>%
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, TranLen, NumPtsTran, PlotType, PtArea, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  PostBurn <- merge(PostBurn_header, PostBurn_data, by = c(1:19))
  
  
  # add column for park name
  PostBurn <- PostBurn %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # add data to master list
  final_df <- rbind(final_df, PostBurn)
}

# final column renaming to match metadata
  final_df <- final_df %>% 
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonStatus_Name = Monitoring.Status,
      MonStatus_Prefix = Status.Prefix,
      MonStatus_Base = Status.Base,
      MonStatus_Suffix = Status.Suffix,
      MonStatus_Order = Status.Order,
      MethodData_NumTran = NumTran,
      MethodData_TranLen_ft = TranLen,
      MethodData_NumPtsTran = NumPtsTran,
      MethodData_PlotType = PlotType,
      MethodData_PtArea = PtArea,
      MethodData_FieldTeam = FieldTeam,
      MethodData_EntryTeam = EntryTeam,
      MethodData_UV1Desc = UV1Desc,
      MethodData_UV2Desc = UV2Desc,
      MethodData_UV3Desc = UV3Desc,
      MethodData_SAComment = SaComment,
      MethodData_Visited = Visited,
      MethodData_Index = Index,
      MethodData_Transect = Transect,
      MethodData_Point = Point,
      MethodData_TapeDist = TapeDist,
      MethodData_Veg = Veg,
      MethodData_Sub = Sub,
      MethodData_Comment = Comment,
      MethodData_UV1 = UV1,
      MethodData_UV2 = UV2,
      MethodData_UV3 = UV3
      )
  
  # save file
  write.csv(final_df, paste0(path_save, "Data_Post Burn Severity (metric).csv"), quote = FALSE, row.names = FALSE) 
```
