---
title: Sharing Data
author: NPS Northeast Region Fire Effects Monitoring Program
output:
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# PURPOSE

This code is intended to combine data depot exports from multiple parks into a single file.

## Before Starting {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)

# install.packages("tidyverse")
```

```{r load packages, include=FALSE}
library(tidyverse)
```

### Adjust File Paths {.hidden}

```{r file paths, include=FALSE}
path_main <- "E:/Allie/FireFX_NER/FFI_DATA_MANAGEMENT/"
#path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Clean/DataDepot/")
path_save <- paste0(path_main, "Exports_Clean/")
```

### Load Data

```{r load data, include=FALSE}
ProjectUnits_all <- read.csv(paste0(path_data, "all_project_units.csv"))

Fuels1000_all <- read.csv(paste0(path_data, "english_surface_fuels_thousand_hr.csv"))
# FuelsDuffLitt_all <- read.csv(paste0(path_data, "english_surface_fuels_duff_litter.csv"))
# FuelsFine_all <- read.csv(paste0(path_data, "english_surface_fuels_fine.csv"))
# PostBurn_all <- read.csv(paste0(path_data, "metric_post_burn_severity.csv"))
# Trees_all <- read.csv(paste0(path_data, "metric_trees_individuals.csv"))
# Seedlings_all <- read.csv(paste0(path_data, "metric_density_quadrats.csv"))
Shrubs_all <- read.csv(paste0(path_data, "metric_density_belts.csv"))
HerbsSpComp_all <- read.csv(paste0(path_data, "metric_cover_species_composition.csv"))
HerbsPoints_all <- read.csv(paste0(path_data, "metric_cover_points.csv"))
# HerbsFreq_all <- read.csv(paste0(path_data, "metric_cover_frequency.csv"))
```

# METADATA

## Project Units

```{r}
ProjectUnits_merge <- ProjectUnits_all %>%
  filter(
    ProjectUnit_Name != "ALL",
    AdminUnit_Name != "ANTI"
    ) %>%
  select(AdminUnitId, SampleEventId, ProjectUnit_Name, MonitoringStatus_Name, MonitoringStatus_Prefix, MonitoringStatus_Base, MonitoringStatus_Suffix, MonitoringStatus_Order) %>%
  #filter(SampleEventId != "91f3d9d4-3f2b-4bb8-95d4-09f88e45e9c2" | MonitoringStatus_Name != "Measure") %>%
  distinct()
```

# PROTOCOLS

## CBI

### cbi_info

```{r cbi_info, warning=FALSE}

```

### cbi_summation

```{r cbi_summation, warning=FALSE}

```

### cbi_substrates

```{r cbi_substrates, warning=FALSE}

```

### cbi_herbs

```{r cbi_herbs, warning=FALSE}

```

### cbi_tall_shrubs

```{r cbi_tall_shrubs, warning=FALSE}

```

### cbi_intermediate_trees

```{r cbi_intermediate_trees, warning=FALSE}

```

### cbi_big_trees

```{r cbi_big_trees, warning=FALSE}

```

## Cover

### cover_frequency

```{r cover_frequency, warning=FALSE}
# merge monitoring status
HerbsFreq_merge <- merge(ProjectUnits_merge, HerbsFreq_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix)

# save file
write.csv(HerbsFreq_merge, paste0(path_save, "metric_cover_frequency.csv"), row.names = FALSE)
```

### cover_points

```{r cover_points, warning=FALSE}
# merge monitoring status
HerbsPoints_merge <- merge(ProjectUnits_merge, HerbsPoints_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix)

# save file
write.csv(HerbsPoints_merge, paste0(path_save, "metric_cover_points.csv"), row.names = FALSE)
```

### cover_species_composition

```{r cover_species_composition, warning=FALSE}
# merge monitoring status
HerbsSpComp_merge <- merge(ProjectUnits_merge, HerbsSpComp_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix)

# save file
write.csv(HerbsSpComp_merge, paste0(path_save, "metric_cover_species_composition.csv"), row.names = FALSE)
```

## Density

### density_belts

```{r density_belts, warning=FALSE}
Shrubs_all <- Shrubs_all |> 
  arrange(AdminUnitId, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, SampleEvent_Date, MethodData_Index)


# merge monitoring status
Shrubs_merge <- merge(ProjectUnits_merge, Shrubs_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix) |> 
  arrange(AdminUnitId, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, SampleEvent_Date, MethodData_Index)

# save file
write.csv(Shrubs_merge, paste0(path_save, "metric_density_belts.csv"), row.names = FALSE)
```

### density_quadrats

```{r density_quadrats, warning=FALSE}
# merge monitoring status
Seedlings_merge <- merge(ProjectUnits_merge, Seedlings_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix)

# save file
write.csv(Seedlings_merge, paste0(path_save, "metric_density_quadrats.csv"), row.names = FALSE)
```

## Post Burn Severity

### post_burn_severity

```{r post_burn_severity, warning=FALSE}
# merge monitoring status
PostBurn_merge <- merge(ProjectUnits_merge, PostBurn_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix)

# save file
write.csv(PostBurn_merge, paste0(path_save, "metric_post_burn_severity.csv"), row.names = FALSE)
```

## Surface Fuels

### surface_fuels_duff_litter

```{r surface_fuels_duff_litter, warning=FALSE}
# merge monitoring status
FuelsDuffLitt_merge <- merge(ProjectUnits_merge, FuelsDuffLitt_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix)

# save file
write.csv(FuelsDuffLitt_merge, paste0(path_save, "english_surface_fuels_duff_litter.csv"), row.names = FALSE)
```

### surface_fuels_fine

```{r surface_fuels_fine, warning=FALSE}
# merge monitoring status
FuelsFine_merge <- merge(ProjectUnits_merge, FuelsFine_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix)

# save file
write.csv(FuelsFine_merge, paste0(path_save, "english_surface_fuels_fine.csv"), row.names = FALSE)
```

### surface_fuels_thousand_hr

```{r surface_fuels_thousand_hr, warning=FALSE}
# merge monitoring status
Fuels1000_merge <- merge(ProjectUnits_merge, Fuels1000_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix)

# save file
write.csv(Fuels1000_merge, paste0(path_save, "english_surface_fuels_thousand_hr.csv"), row.names = FALSE)
```

## Trees

### trees_individuals

```{r trees_individuals, warning=FALSE}
# merge monitoring status
Trees_merge <- merge(ProjectUnits_merge, Trees_all, by = c("AdminUnitId","SampleEventId"), all.y = TRUE) %>%
  relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
  relocate(MonitoringStatus_Prefix, .after = MonitoringStatus_Name) %>%
  relocate(MonitoringStatus_Base, .after = MonitoringStatus_Prefix) %>%
  relocate(MonitoringStatus_Suffix, .after = MonitoringStatus_Base) %>%
  relocate(MonitoringStatus_Order, .after = MonitoringStatus_Suffix)

# save file
write.csv(Trees_merge, paste0(path_save, "metric_trees_individuals.csv"), row.names = FALSE)
```
