---
title: Sharing Data
author: NPS Northeast Region Fire Effects Monitoring Program
output:
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# Purpose

This code is intended to combine data depot exports from multiple parks into a single file.

## Before Starting {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)

# install.packages("tidyverse")
```

```{r load packages, include=FALSE}
library(tidyverse)
```

### Adjust File Paths {.hidden}

```{r file paths, include=FALSE}
path_main <- "E:/Allie/FireFX_NER/FFI_DATA_MANAGEMENT/"
#path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Clean/DataDepot/")
path_save <- paste0(path_main, "Exports_Clean/Exports_Share/")
```

# Column Names List

columns_MethodData \<- c("MethodData_Visited","MethodData_FieldTeam","MethodData_EntryTeam","MethodData_UV1Desc","MethodData_UV2Desc","MethodData_UV3Desc","MethodData_SAComment","MethodData_CreatedDate","MethodData_UpdatedDate","MethodData_DeletedDate","MethodData_Comment","MethodData_UV1","MethodData_UV2","MethodData_UV3","MethodData_Index")

```{r}
columns_ProjectUnit_keep <- c("AdminUnit_Name","ProjectUnit_Name","ProjectUnit_Agency","ProjectUnit_Area","ProjectUnit_AreaUnits","ProjectUnit_DateIn","ProjectUnit_DateOut","ProjectUnit_Objective","ProjectUnit_Description","ProjectUnit_Comment","MonitoringStatus_Name","MonitoringStatus_Prefix","MonitoringStatus_Base","MonitoringStatus_Suffix","MonitoringStatus_Order")
columns_ProjectUnit_drop <- c("AdminUnitId","ProjectUnitId","MonitoringStatusId","SampleEventId","ProjectUnit_Grid","ProjectUnit_CreateCode","ProjectUnit_UserVariables","MonitoringStatus_Comment")

columns_SpeciesReport_keep <- c("Species_OrganizationName","AdminUnit_Name","Species_LocalSpeciesSymbol","Species_Family","Species_Genus","Species_ScientificName","Species_CommonName","Species_LifeFormNameLocal","Species_LifeCycleLocal","Species_NativityLocal","Species_Invasive","Species_Cultural","Species_Concern","Species_Description","Species_Comment","Species_UV1","Species_UV2","Species_UV3")
columns_SpeciesReport_drop <- c("AdminUnitId","Species_Id","Species_MasterSpeciesId","Species_LocalSpeciesId","Species_AuxSpeciesId", "Species_AdminUnitName","Species_MasterOrUserLocal","Species_ITISTaxonomicSerialNumber","Species_Symbol","Species_CommonNameLocal","Species_LifeFormName","Species_LifeCycle","Species_Nativity","Species_Retired","Species_NotBiological","Species_UserAdded")




columns_ID_drop <- c("OrganizationId","AdminUnitId","MacroplotId","SampleEventId","MethodId")

columns_Macroplot_keep <- c("Organization_Name","AdminUnit_Name","Macroplot_Purpose","Macroplot_Type","Macroplot_Name","Macroplot_Lat_dd","Macroplot_Long_dd","Macroplot_LocatedBy","Macroplot_DateIn","Macroplot_DateOut","Macroplot_Elevation","Macroplot_ElevationUnits","Macroplot_Azimuth","Macroplot_Aspect","Macroplot_SlopeHill_pct","Macroplot_SlopeTransect_pct","Macroplot_UV1","Macroplot_UV2","Macroplot_UV3")
columns_Macroplot_drop <- c("AdminUnit_Comment","Macroplot_UtmX_m","Macroplot_UtmY_m","Macroplot_UtmZone","Macroplot_Datum","Macroplot_Pdop","Macroplot_Precision","Macroplot_FutureVisit","Macroplot_StartPoint","Macroplot_Directions","Macroplot_Comment","Macroplot_Metadata","Macroplot_UV4","Macroplot_UV5","Macroplot_UV6","Macroplot_UV7","Macroplot_UV8")

columns_SampleEvent_keep <- c("SampleEvent_LegacyMonitoringStatus","SampleEvent_Who","SampleEvent_TreatmentUnit","SampleEvent_Date")
columns_SampleEvent_drop <- c("SampleEvent_Comment","SampleEvent_UserVariables","SampleData_Executed")

columns_MethodData_keep <- c("MethodData_FieldTeam","MethodData_EntryTeam","MethodData_UV1Desc","MethodData_UV2Desc","MethodData_UV3Desc","MethodData_UV1","MethodData_UV2","MethodData_UV3","MethodData_Index")
columns_MethodData_drop <- c("MethodData_Visited","MethodData_CreatedDate","MethodData_UpdatedDate","MethodData_DeletedDate","MethodData_SAComment","MethodData_Comment")

columns_Species_keep <- c("Species_SymbolLocal","Species_Family","Species_Genus","Species_ScientificName","Species_CommonName","Species_LifeFormNameLocal","Species_LifeCycleLocal","Species_NativityLocal","Species_Invasive","Species_UV1","Species_UV2","Species_UV3")
columns_Species_drop <- c("Species_SourceEntityId","Species_LocalSpeciesId","Species_MasterSpeciesId","Species_AuxSpeciesId","Species_ITISTaxonomicSerialNumber","MethodData_RemoteApp_LocalSpeciesSymbol","Species_SymbolMaster","Species_CommonNameLocal","Species_LifeFormName","Species_LifeCycle","Species_Nativity","Species_Cultural","Species_Concern","Species_Retired","Species_NotBiological","Species_Description","Species_Comment","MethodData_SppGuid")



columns_CoverFrequency <- c("MethodData_NumTran","MethodData_TranLen", "MethodData_NumQuadLen","MethodData_QuadLen","MethodData_QuadWid","MethodData_NFRatio", "MethodData_NFNum","MethodData_Transect","MethodData_Quadrat","MethodData_Status", "MethodData_NRF","MethodData_TypeCov","MethodData_Cover","MethodData_Height","MethodData_QuadCover","MethodData_Frequency")

columns_CoverPoints <- c("MethodData_NumTran","MethodData_TranLen","MethodData_NumPtsTran","MethodData_Offset","MethodData_Transect","MethodData_Point","MethodData_Tape","MethodData_Order","MethodData_Height","MethodData_Status","MethodData_Cover","MethodData_CanopyLayer")

columns_CoverSpComp <- c("MethodData_MinCovLevel","MethodData_Area","MethodData_Status","MethodData_SizeCl","MethodData_AgeCl","MethodData_Cover","MethodData_Height")

columns_DensityBelts <- c("MethodData_NumTran","MethodData_NumSubbelt","MethodData_TranLen","MethodData_TranWid","MethodData_Area","MethodData_Transect","MethodData_Subbelt","MethodData_Status","MethodData_SizeCl","MethodData_AgeCl","MethodData_Count","MethodData_Height","MethodData_SubFrac","MethodData_Density")

columns_DensityQuads <- c("MethodData_NumTran","MethodData_NumQuadTran","MethodData_QuadLen","MethodData_QuadWid","MethodData_Area","MethodData_Transect","MethodData_Quadrat","MethodData_Status","MethodData_SizeCl","MethodData_AgeCl","MethodData_Count","MethodData_Height","MethodData_SubFrac","MethodData_Density")

columns_PostBurn <- c("MethodData_NumTran","MethodData_tranLen","MethodData_NumPtsTran","MethodData_PlotType","MethodData_PtArea","MethodData_Transect","MethodData_Point","MethodData_TapeDist",'MethodData_Veg',"MethodData_Sub")

columns_FuelsDuffLitt <- c("MethodData_NumTran","MethodData_Transect","MethodData_SampLoc","MethodData_OffSet","MethodData_LittDep","MethodData_DuffDep","MethodData_FuelbedDep","MethodData_DLFuConSt")

columns_FuelsFine <- c("MethodData_NumTran","MethodData_OneHrTranLen","MethodData_TenHrTranLen","MethodData_HunHrTranLen","MethodData_Transect","MethodData_Azimuth","MethodData_Slope","MethodData_OneHr","MethodData_TenHr","MethodData_HunHr","MethodData_FWDFuConSt")

columns_Fuels1000 <- c("MethodData_NumTran","MethodData_TranLen","MethodData_Transect","MethodData_Slope","MethodData_LogNum","MethodData_Dia","MethodData_DecayCl","MethodData_CWDFuConSt")

columns_Trees <- c("MethodData_MacroPlotSize","MethodData_SnagPlotSize","MethodData_BrkPntDia","MethodData_IsVerified","MethodData_QTR","MethodData_SubFrac","MethodData_TagNo","MethodData_Status","MethodData_DBH","MethodData_Ht","MethodData_CrwnRto","MethodData_CrwnCl","MethodData_CrFuBHt","MethodData_LiCrBHt","MethodData_CrwnRad","MethodData_Age","MethodData_GrwthRt","MethodData_Mort","MethodData_DecayCl","MethodData_LaddBaseHt","MethodData_LaddMaxHt","MethodData_DRC","MethodData_NuLiStems","MethodData_NuDeStems","MethodData_EqDia","MethodData_XCoord","MethodData_YCoord","MethodData_CKR","MethodData_CharHt","MethodData_ScorchHt","MethodData_CrScPct","MethodData_DamCd1","MethodData_DamSev1","MethodData_DamCd2","MethodData_DamSev2","MethodData_DamCd3","MethodData_DamSev3","MethodData_DamCd4","MethodData_DamSev4","MethodData_DamCd5","MethodData_DamSev5","MethodData_Density","MethodData_BasalArea")
```

# Metadata

## Macroplots

```{r metadata, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "all_metadata.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    AdminUnit_Name, ProjectUnit_Name, Macroplot_Purpose, Macroplot_Type, Macroplot_Name, Macroplot_Lat_dd, Macroplot_Long_dd, Macroplot_LocatedBy, Macroplot_DateIn, Macroplot_DateOut, Macroplot_Elevation, Macroplot_ElevationUnits, Macroplot_Azimuth, Macroplot_Aspect, Macroplot_SlopeHill_pct, Macroplot_SlopeTransect_pct, Macroplot_UV1, Macroplot_UV2, Macroplot_UV3, MonitoringStatus_Name, SampleEvent_LegacyMonitoringStatus, SampleEvent_Who, SampleEvent_Protocols, SampleEvent_Visited, SampleEvent_Date
    ))
  
drop_df <- temp_df %>%
  select(c(
    Macroplot_UtmX_m, Macroplot_UtmY_m, Macroplot_UtmZone, Macroplot_Datum, Macroplot_Pdop, Macroplot_Precision, Macroplot_FutureVisit, Macroplot_StartPoint, Macroplot_Directions, Macroplot_Comment, Macroplot_Metadata, Macroplot_UV4, Macroplot_UV5, Macroplot_UV6, Macroplot_UV7, Macroplot_UV8, SampleEvent_Comment
    ))

# save file
write.csv(keep_df, paste0(path_save, "all_metadata.csv"), row.names = FALSE)
```

## Project Units

```{r project units, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "all_project_units.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    AdminUnit_Name, ProjectUnit_Name, ProjectUnit_Agency, ProjectUnit_Area, ProjectUnit_AreaUnits, ProjectUnit_DateIn, ProjectUnit_DateOut, ProjectUnit_Objective, ProjectUnit_Description, ProjectUnit_Comment, MonitoringStatus_Name, MonitoringStatus_Prefix, MonitoringStatus_Base, MonitoringStatus_Suffix, MonitoringStatus_Order
  )) %>% 
  filter(ProjectUnit_Name != "ALL")

drop_df <- temp_df %>%
  select(c(
    AdminUnitId, ProjectUnitId, MonitoringStatusId, SampleEventId, ProjectUnit_Grid, ProjectUnit_CreateCode, ProjectUnit_UserVariables, MonitoringStatus_Comment
  ))

# save file
write.csv(keep_df, paste0(path_save, "all_project_units.csv"), row.names = FALSE)
```

## Species

```{r species, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "all_species_info.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    Species_OrganizationName, AdminUnit_Name, Species_LocalSpeciesSymbol, Species_Family, Species_Genus, Species_ScientificName, Species_CommonName, Species_LifeFormNameLocal, Species_LifeCycleLocal, Species_UV1, Species_UV2, Species_UV3, Species_NativityLocal, Species_Invasive, Species_Cultural, Species_Concern, Species_Description, Species_Comment
  ))

drop_df <- temp_df %>%
  select(c(
    AdminUnitId, Species_Id, Species_MasterSpeciesId, Species_LocalSpeciesId, Species_AuxSpeciesId, Species_AdminUnitName, Species_MasterOrUserLocal, Species_ITISTaxonomicSerialNumber, Species_Symbol, Species_CommonNameLocal, Species_LifeFormName, Species_LifeCycle, Species_Nativity, Species_UserAdded, Species_NotBiological, Species_Retired
  ))

# save file
write.csv(keep_df, paste0(path_save, "all_species_info.csv"), row.names = FALSE)
```

# Protocols

## CBI

### cbi_info

```{r cbi_info, warning=FALSE}

```

### cbi_summation

```{r cbi_summation, warning=FALSE}

```

### cbi_substrates

```{r cbi_substrates, warning=FALSE}

```

### cbi_herbs

```{r cbi_herbs, warning=FALSE}

```

### cbi_tall_shrubs

```{r cbi_tall_shrubs, warning=FALSE}

```

### cbi_intermediate_trees

```{r cbi_intermediate_trees, warning=FALSE}

```

### cbi_big_trees

```{r cbi_big_trees, warning=FALSE}

```

## Cover

### cover_frequency

```{r cover_frequency, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "metric_cover_frequency.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_CoverFrequency,
    columns_Species_keep, 
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id, 
    MethodData_SpeciesId,
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop,
    columns_Species_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "metric_cover_frequency.csv"), row.names = FALSE)
```

### cover_points

```{r cover_points, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "metric_cover_points.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_CoverPoints,
    columns_Species_keep
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id,
    MethodData_SpeciesId,
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop,
    columns_Species_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "metric_cover_points.csv"), row.names = FALSE)
```

### cover_species_composition

```{r cover_species_composition, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "metric_cover_species_composition.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_CoverSpComp,
    columns_Species_keep
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id,
    MethodData_SpeciesId,
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop,
    columns_Species_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "metric_cover_species_composition.csv"), row.names = FALSE)
```

## Density

### density_belts

```{r density_belts, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "metric_density_belts.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_DensityBelts,
    columns_Species_keep
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id, MacroPlotId,
    MethodData_SpeciesId,
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop,
    columns_Species_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "metric_density_belts.csv"), row.names = FALSE)
```

### density_quadrats

```{r density_quadrats, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "metric_density_quadrats.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_DensityQuads,
    columns_Species_keep
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id, MacroPlotId,
    MethodData_SpeciesId,
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop,
    columns_Species_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "metric_density_quadrats.csv"), row.names = FALSE)
```

## Post Burn Severity

### post_burn_severity

```{r post_burn_severity, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "metric_post_burn_severity.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_PostBurn
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id, MacroPlotId,
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "metric_post_burn_severity.csv"), row.names = FALSE)
```

## Surface Fuels

### surface_fuels_duff_litter

```{r surface_fuels_duff_litter, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "english_surface_fuels_duff_litter.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_FuelsDuffLitt
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id, 
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "english_surface_fuels_duff_litter.csv"), row.names = FALSE)
```

### surface_fuels_fine

```{r surface_fuels_fine, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "english_surface_fuels_fine.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_FuelsFine
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id, 
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "english_surface_fuels_fine.csv"), row.names = FALSE)
```

### surface_fuels_thousand_hr

```{r surface_fuels_thousand_hr, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "english_surface_fuels_thousand_hr.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_Fuels1000
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id, 
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "english_surface_fuels_thousand_hr.csv"), row.names = FALSE)
```

## Trees

### trees_individuals

```{r trees_individuals, warning=FALSE}
# load data
temp_df <- read.csv(paste0(path_data, "metric_trees_individuals.csv"))

# select columns
keep_df <- temp_df %>%
  select(c(
    columns_Macroplot_keep,
    columns_SampleEvent_keep,
    columns_MethodData_keep,
    columns_Trees,
    columns_Species_keep
  ))

drop_df <- temp_df %>%
  select(c(
    MethodDataId, MethodData_Id, 
    columns_ID_drop,
    columns_Macroplot_drop,
    columns_SampleEvent_drop,
    columns_MethodData_drop,
    columns_Species_drop
  ))

# save file
write.csv(keep_df, paste0(path_save, "metric_trees_individuals.csv"), row.names = FALSE)
```
