---
title: "QAQC MetaData"
author: "Alexandra Lalor"
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 3
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: '3'
---

# Before Starting

This code is intended to quality check species metadata, including the Local Species Report. This report can be downloaded via the Species menu on the Species Management tab on the FFI Remote App Server.

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r install packages, include=FALSE}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("Rtools")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
## Load Packages

# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
library(plyr)
# janitor has functions to find duplicates
library(janitor)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr is used to create output files from R Markdown
library(knitr)
# "here" helps you easily find and reference your working directory
library(here)
```

### Create Function {.hidden}

```{r}
# Blank data frame
errors_blank <- data.frame("SavedQuery" = "", "LocalSpecies_Symbol" = "", "Error" = "", "Fixed" = "", "Explanation" = "", "Queryers" = "")

# QAQC function
qaqc_species <- function(data, query, query_message, values_check) {
  
  # Check if there is data to QAQC
  if(nrow(data) == 0) {
  # If there is no data, default to "No Error" data frame
  errors <- errors_blank %>%
    mutate(SavedQuery = query,
           Error = "No Error")
  # If there is data, perform error check
} else {
  
  # Use relevant dataset to look for errors
  errors <- data %>%  
    # Add columns relevant to error checking
           # Populate the "SavedQuery" column with the query name
    mutate("SavedQuery" = query, 
           # Populate the "Error" column with the query message and relevant data
           "Error" = paste(query_message, "=", values_data),
           # Create a blank "Fixed" column
           "Fixed" = "",
           # Create a blank "Explanation" column
           "Explanation" = "",
           # Create a blank "Queryers" column
           "Queryers" = "") %>%   
    # Filter for data which is "false" (data does not match valid conditions)
    # NA values are treated as "false" (missing data is not valid)
    filter(!(values_check %>% replace_na(FALSE))) %>%   
    # Select relevant columns to view errors
    select(colnames(errors_blank))
  
  # Next, check if there are duplicate errors
  errors_temp <- errors %>% 
    get_dupes(SavedQuery, LocalSpecies_Symbol, Error)
  # Merge duplicate errors
  errors <- unique(merge(errors, errors_temp, all = T))
  # If duplicate errors exist, add number of duplicates to error message
  errors <- errors %>% 
    mutate(Error = ifelse(is.na(dupe_count), Error, paste0("(x", dupe_count, ") ", Error))) %>% 
    select(!"dupe_count")
}
  
  # Check if there are no errors
  if (nrow(errors) == 0) {  
    # If there are no errors, default to "No Error" data frame
    errors <- errors_blank %>%
      mutate(SavedQuery = query,
             Error = "No Error")
    # If there are errors, keep error log you just created
  } else {   
    errors <- errors
  }
}
```

### Target Park

```{r}
# designate target park(s)
target_park <- "SHEN"
```

### Adjust File Paths {.hidden}

```{r import data, include=FALSE}
# adjust file paths
path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_data <- paste0(path_main, "Exports/", target_park, "/")
path_errors <- paste0(path_main, "QAQC/", target_park, "/")
path_errors_name <- paste0(target_park, " Species QAQC Errors")
```

### Load Data {.hidden}

```{r load data, include=FALSE}
## Load Data
SpeciesReport <- read.csv(paste0(path_data, target_park, "_", "SpeciesReport.csv"), na.strings = c("","NA","N/A"))
```

### Clean Data {.hidden}

```{r}
SpeciesReport <- SpeciesReport %>%
  # remove trailing/leading whitespace
  mutate(across(where(is.character), str_trim))

# replace commas with semicolons
SpeciesReport[] <- lapply(SpeciesReport, function(x) gsub(",", ";", x))
```

### Define Codes {.hidden}

```{r}
substrate <- c("BARE", "BOLE", "DUFF", "HAY", "LICHEN", "LITT", "LITTER", "MOSS", "ROCK", "ROOT", "SOIL", "WATER", "WOOD")

unknown <- c("ASTER", "FERN", "FUNGI", "GRASS", "UNKSPP", "UNKSNAG", "UNK_002")
```

# Park: [`r target_park`]{style="color:red"}

## Species Report

### Local Species

[Problem:]{.underline} Species Report is missing information related to Local Species columns (excluding substrates and unknowns)

[Procedure:]{.underline}

-   Check that LocalSpecies_CommonName is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "LocalSpecies_CommonName"
query_message <- paste0("Common Name")
values_data <- data$LocalSpecies_CommonName
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_CommonName <- qaqc_species(data, query, query_message, values_check)
```

-   Check that LocalSpecies_LifeCycle = Perennial, Biennial, or Annual

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "LocalSpecies_LifeCycle"
query_message <- paste0("Life Cycle")
values_data <- data$LocalSpecies_LifeCycle
values_valid <- c("Perennial", "Biennial", "Annual")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_LifeCycle <- qaqc_species(data, query, query_message, values_check)
```

-   Check that LocalSpecies_Nativity = True or False

```{r}
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "LocalSpecies_Nativity"
query_message <- paste0("Nativity")
values_data <- data$LocalSpecies_Nativity
values_valid <- c("True", "False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Nativity <- qaqc_species(data, query, query_message, values_check)
```

-   Check that LocalSpecies_Invasive = True or False

```{r}
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "LocalSpecies_Invasive"
query_message <- paste0("Invasive")
values_data <- data$LocalSpecies_Invasive
values_valid <- c("True", "False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Invasive <- qaqc_species(data, query, query_message, values_check)
```

-   Check that LocalSpecies_Cultural = True or False

```{r}
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "LocalSpecies_Cultural"
query_message <- paste0("Cultural")
values_data <- data$LocalSpecies_Cultural
values_valid <- c("True", "False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Cultural <- qaqc_species(data, query, query_message, values_check)
```

-   Check that LocalSpecies_Concern = True or False

```{r}
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "LocalSpecies_Concern"
query_message <- paste0("Concern")
values_data <- data$LocalSpecies_Concern
values_valid <- c("True", "False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Concern <- qaqc_species(data, query, query_message, values_check)
```

-   Check that LocalSpecies_Retired = True or False

```{r}
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "LocalSpecies_Retired"
query_message <- paste0("Retired")
values_data <- data$LocalSpecies_Retired
values_valid <- c("True", "False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Retired <- qaqc_species(data, query, query_message, values_check)
```

-   Filter for Graminoids. Check that LocalSpecies_UV1 = cool or warm

```{r}
data <- SpeciesReport %>% 
  filter(LocalSpecies_PreferedLifeForm == "Graminoid",
         !LocalSpecies_Symbol %in% unknown)
query <- "LocalSpecies_UV1"
query_message <- paste0("UV1")
values_data <- data$LocalSpecies_UV1
values_valid <- c("cool", "warm")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_UV1 <- qaqc_species(data, query, query_message, values_check)
```

-   Check that LocalSpecies_PreferedLifeForm = Nonvascular, Graminoid, Grass-like, Forb/herb, Vine, Shrub, Subshrub, or Tree.

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "LocalSpecies_PreferedLifeForm"
query_message <- paste0("Life Form")
values_data <- data$LocalSpecies_PreferedLifeForm
values_valid <- c("Nonvascular", "Graminoid", "Grass-like", "Forb/herb", "Vine", "Shrub", "Subshrub", "Tree")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_LifeForm <- qaqc_species(data, query, query_message, values_check)
```

### Master Species

[Problem:]{.underline} Species Report is missing information related to Master Species columns (excluding substrates and unknowns)

[Procedure:]{.underline}

-   Check that MasterSpecies_ScientificName is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "MasterSpecies_ScientificName"
query_message <- paste0("Scientific Name") 
values_data <- data$MasterSpecies_ScientificName
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_ScientificName <- qaqc_species(data, query, query_message, values_check)
```

-   Check that MasterSpecies_ITIS_TSN is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "MasterSpecies_ITIS_TSN"
query_message <- paste0("TSN") 
values_data <- data$MasterSpecies_ITIS_TSN
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_TSN <- qaqc_species(data, query, query_message, values_check)
```

-   Check that MasterSpecies_Genus is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "MasterSpecies_Genus"
query_message <- paste0("Genus") 
values_data <- data$MasterSpecies_Genus
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_Genus <- qaqc_species(data, query, query_message, values_check)
```

-   Check that MasterSpecies_Family is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate,
         !LocalSpecies_Symbol %in% unknown)
query <- "MasterSpecies_Family"
query_message <- paste0("Family") 
values_data <- data$MasterSpecies_Family
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_Family <- qaqc_species(data, query, query_message, values_check)
```

-   Check that MasterSpecies_NotBiological = False

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!LocalSpecies_Symbol %in% substrate)
query <- "MasterSpecies_NotBiological"
query_message <- paste0("Not Biological") 
values_data <- data$MasterSpecies_NotBiolgoical
values_valid <- "False"
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_NotBiological_F <- qaqc_species(data, query, query_message, values_check)
```

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(LocalSpecies_Symbol %in% substrate)
query <- "MasterSpecies_NotBiological"
query_message <- paste0("Substrate. Not Biological") 
values_data <- data$MasterSpecies_NotBiolgoical
values_valid <- "True"
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_NotBiological_T <- qaqc_species(data, query, query_message, values_check)
```

# ALL ERRORS

```{r}
errors_SpeciesReport <- rbind(errors_SpeciesReport_ScientificName, errors_SpeciesReport_Genus, errors_SpeciesReport_Family, errors_SpeciesReport_TSN, errors_SpeciesReport_NotBiological_T, errors_SpeciesReport_NotBiological_F, errors_SpeciesReport_CommonName, errors_SpeciesReport_LifeForm, errors_SpeciesReport_LifeCycle, errors_SpeciesReport_UV1, errors_SpeciesReport_Nativity, errors_SpeciesReport_Invasive, errors_SpeciesReport_Cultural, errors_SpeciesReport_Concern, errors_SpeciesReport_Retired) %>% 
  arrange(LocalSpecies_Symbol)

remove(errors_SpeciesReport_ScientificName, errors_SpeciesReport_Genus, errors_SpeciesReport_Family, errors_SpeciesReport_TSN, errors_SpeciesReport_NotBiological_T, errors_SpeciesReport_NotBiological_F, errors_SpeciesReport_CommonName, errors_SpeciesReport_LifeForm, errors_SpeciesReport_LifeCycle, errors_SpeciesReport_UV1, errors_SpeciesReport_Nativity, errors_SpeciesReport_Invasive, errors_SpeciesReport_Cultural, errors_SpeciesReport_Concern, errors_SpeciesReport_Retired)

if(nrow(errors_SpeciesReport) > 1) {
  errors_SpeciesReport <- errors_SpeciesReport %>%
    filter(Error != "No Error")
} else {
  errors_SpeciesReport <- errors_SpeciesReport}
```

```{r}
# Formatting

# Add blank rows between each tag number
errors_SpeciesReport_blanks <- errors_SpeciesReport[1, ]
for (i in 2:nrow(errors_SpeciesReport)) {
  if (errors_SpeciesReport[i, "LocalSpecies_Symbol"] != errors_SpeciesReport[i - 1, "LocalSpecies_Symbol"]) {
    errors_SpeciesReport_blanks <- rbind(errors_SpeciesReport_blanks, errors_blank, errors_SpeciesReport[i, ])
  } else {
    errors_SpeciesReport_blanks <- rbind(errors_SpeciesReport_blanks, errors_SpeciesReport[i, ])
  }
}

# Add conditional formating to ouput
errors_all <- condformat(errors_SpeciesReport_blanks[1:(nrow(errors_SpeciesReport_blanks)), 1:6]) %>%
  rule_fill_discrete(columns = 1:6,
                     expression = SavedQuery != "",
                     colours = c("TRUE" = "#C6E0B4"),
                     na.value = "#FFFFFF")
```

```{r}
# Table of results for quick check
kable(errors_all, "pipe")

# Save as CSV or XLSX
condformat2excel(errors_all, paste0(path_errors, paste0(target_park, "_errors_species.xlsx")), sheet_name = path_errors_name, overwrite_wb = TRUE)
```
