---
title: "FFI Database Summary"
subtitle: "Grand Canyon"
output: 
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 3
    toc_float:
      smooth_scroll: yes
    code_download: true
date: "`r Sys.Date()`"
---

# Purpose

### Setup

```{r}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
# install.packages("readxl")
```

```{r}
## Load Packages

# "here" helps you easily find and reference your working directory
library(here)
# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
library(readxl)
```

### Target Values {.hidden}

```{r}
# designate target values

# parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
target_park <- "NERI"
```

### Adjust File Paths

```{r}
# Adjust File Paths
#path_data <- "X:/FFI Data Management/Exports from FFI/GRCA_FMH/2025-01-23/"
path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Clean/FFI/")
path_errors <- paste0(here(), "/output/errors/")
```

### Load Data

```{r}
# Load in data
Trees_all <- read.csv(paste0(path_data, "metric_trees_individuals.csv"))
errors_Trees_CrossYear <- read_excel(paste0(path_errors, target_park,  "_Errors_DataEntry_CrossYear.xlsx"))
```

### Clean Data

```{r}
Trees_all <- Trees_all %>%
  # Reformat Date column
  mutate(SampleEvent_Date = as.Date(SampleEvent_Date)) %>%
  mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>%
  relocate(SampleEvent_Date_Year, .after = SampleEvent_Date)
```

### Filter Data

```{r}
Trees_data <- Trees_all %>%
  # Filter for target park
  filter(AdminUnit_Name == target_park)
```

# Data Viz - Trees

#### Mutate Data for Graphing

```{r}
graph_Trees_data <- Trees_data %>% 
  mutate(MethodData_Status = ifelse(MethodData_CrwnCl == "DD", "DD", MethodData_Status)) %>% 
  mutate(MethodData_SubFrac = factor(MethodData_SubFrac),
         MethodData_TagNo = factor(MethodData_TagNo),
         MethodData_Status = factor(MethodData_Status, levels = c("L", "D", "DD")),
         MethodData_CrwnCl = factor(MethodData_CrwnCl, levels = c("X", "",
                                            "SC", "I", "C", "D",
                                            "RS", "LBS", "CS", "BAD", 
                                            "BBD", "CUS", "DD")))
```

#### Define Target Plot & Isolate Problematic Tree Tags

```{r}
##################################################################################
unique(errors_Trees_CrossYear$Macroplot_Name)
target_plot <- "Plot 03"
##################################################################################

badtags_DBH <- errors_Trees_CrossYear %>% 
  filter(grepl("DBH", errors_Trees_CrossYear$SavedQuery)) %>% 
  filter(Macroplot_Name == target_plot)
badtags_DBH <- unique(badtags_DBH$MethodData_TagNo)

badtags_Height <- errors_Trees_CrossYear %>% 
  filter(grepl("Height", errors_Trees_CrossYear$SavedQuery)) %>% 
  filter(Macroplot_Name == target_plot)
badtags_Height <- unique(badtags_Height$MethodData_TagNo)

badtags_Species <- errors_Trees_CrossYear %>% 
  filter(grepl("Species", errors_Trees_CrossYear$SavedQuery)) %>% 
  filter(Macroplot_Name == target_plot)
badtags_Species <- unique(badtags_Species$MethodData_TagNo)

badtags_Status <- errors_Trees_CrossYear %>% 
  filter(grepl("Status", errors_Trees_CrossYear$SavedQuery)) %>% 
  filter(Macroplot_Name == target_plot)
badtags_Status <- unique(badtags_Status$MethodData_TagNo)
```

## [`r target_plot`]{style="color:red"}

### Status

```{r}
graph_Trees_data %>% 
  filter(Macroplot_Name == target_plot,
         MethodData_TagNo %in% c(badtags_Status)) %>% 
  arrange(SampleEvent_Date) %>% 
  ggplot(aes(x = SampleEvent_Date_Year, y = MethodData_TagNo)) +
  geom_line(aes(group = MethodData_TagNo, color = MethodData_Status), size = 1) +
  geom_point(aes(fill = MethodData_Status), shape = 21, size = 3) +
  scale_fill_manual(values = c("L" = "forestgreen", "D" = "darkorange", "DD" = "red")) +
  scale_color_manual(values=c("L" = "forestgreen", "D" = "darkorange", "DD" = "red")) +
  labs(title = target_plot) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))
```

### Species

```{r}
graph_Trees_data %>% 
  filter(Macroplot_Name == target_plot,
         MethodData_TagNo %in% c(badtags_Species)) %>% 
  arrange(SampleEvent_Date) %>% 
  ggplot(aes(x = SampleEvent_Date_Year, y = MethodData_TagNo)) +
  geom_line(aes(group = MethodData_TagNo, color = MethodData_LocalSpeciesSymbol), size = 1) +
  geom_point(aes(fill = MethodData_Status), shape = 21, size = 3) +
  scale_fill_manual(values = c("L" = "forestgreen", "D" = "darkorange", "DD" = "red")) +
  labs(title = target_plot) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))
```

### DBH

Live trees should only increase DBH. Dead trees should only decrease DBH.

```{r}
graph_Trees_data %>% 
  filter(Macroplot_Name == target_plot,
         MethodData_TagNo %in% c(badtags_DBH)
         # !is.na(MethodData_DBH_cm),
         # MethodData_Status != "DD") 
         ) %>% 
  arrange(SampleEvent_Date) %>% 
  ggplot(aes(x = SampleEvent_Date_Year, y = MethodData_DBH_cm)) +
  geom_line(aes(group = MethodData_TagNo, color = MethodData_TagNo), size = 1) +
  geom_point(aes(fill = MethodData_Status), shape = 21, size = 3) +
  scale_fill_manual(values=c("L" = "forestgreen", "D" = "darkorange")) +
  labs(title = target_plot) +
  #facet_wrap(~MethodData_Status) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))
```

### Height

Live trees should only increase in height. Dead trees should only decrease in height.

```{r}
graph_Trees_data %>% 
  filter(Macroplot_Name == target_plot,
         MethodData_TagNo %in% c(badtags_Height),
         !is.na(MethodData_Ht_m),
         MethodData_Status != "DD") %>% 
  arrange(SampleEvent_Date) %>% 
  ggplot(aes(x = SampleEvent_Date_Year, y = MethodData_Ht_m)) +
  geom_line(aes(group = MethodData_TagNo, color = MethodData_TagNo), size = 1) +
  geom_point(aes(fill = MethodData_Status), shape = 21, size = 3) +
  scale_fill_manual(values=c("L" = "forestgreen", "D" = "darkorange")) +
  labs(title = target_plot) +
  #facet_wrap(~MethodData_Status) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))
```
