---
title: "FFI Database Summary"
subtitle: "Northeast Region"
output: 
  html_document:
    toc: true
    toc-float: true
    code_download: true
date: "`r Sys.Date()`"
---

# Purpose

This report summarizes plot work by the NPS Fire Ecology Program. The included tables and graphs allow a user to quickly view the overall status of program, park, project, or protocol activities in an FFI admin unit.

The code summarizes records in the Macroplot Report and Sample Event Report that can be downloaded via the Utilities menu on the Project Management tab on the FFI Remote App Server. You can recreate this Metadata Report by running code found in the file "QAQC_MetadataReport.R", under the scripts folder for this R project.

### Setup

```{r}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
```

```{r}
## Load Packages

# "here" helps you easily find and reference your working directory
library(here)
# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
```

```{r}
## Adjust File Paths

# Identify working directory
here()

# Adjust File Paths
path_data <- paste0("E:/Allie/R/NER/data/")
path_graphs <- paste0(here(), "/output/graphs/")
```

### Load Data

Load in the Metadata Report. This Metadata Report was created by combining Macroplot Reports and Sample Event Reports from each Admin Unit, which can be downloaded via the Utilities menu on the Project Management tab on the FFI Remote App Server.

```{r}
# Load in data
MetadataReport_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_MetadataReport.csv"))
MetadataReport_APCO <- read.csv(paste0(path_data, "APCO/APCO_MetadataReport.csv"))
#MetadataReport_CATO <- read.csv(paste0(path_data, "CATO/CATO_MetadataReport.csv"))
#MetadataReport_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_MetadataReport.csv"))
#MetadataReport_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_MetadataReport.csv"))
#MetadataReport_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_MetadataReport.csv"))
#MetadataReport_GATE <- read.csv(paste0(path_data, "GATE/GATE_MetadataReport.csv"))
MetadataReport_GETT <- read.csv(paste0(path_data, "GETT/GETT_MetadataReport.csv"))
#MetadataReport_MONO <- read.csv(paste0(path_data, "MONO/MONO_MetadataReport.csv"))
#MetadataReport_NERI <- read.csv(paste0(path_data, "NERI/NERI_MetadataReport.csv"))
#MetadataReport_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_MetadataReport.csv"))
MetadataReport_RICH <- read.csv(paste0(path_data, "RICH/RICH_MetadataReport.csv"))
#MetadataReport_SARA <- read.csv(paste0(path_data, "SARA/SARA_MetadataReport.csv"))
#MetadataReport_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_MetadataReport.csv"))
#MetadataReport_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_MetadataReport.csv"))
```

### Merge Data

```{r}
MetadataReport <- rbind(MetadataReport_ANTI, MetadataReport_APCO, MetadataReport_GETT, MetadataReport_RICH)

# MetadataReport <- rbind(MetadataReport_ANTI, MetadataReport_APCO, MetadataReport_CATO, MetadataReport_CUVA, MetadataReport_DEWA, MetadataReport_FRSP, MetadataReport_GATE, MetadataReport_GETT, MetadataReport_MONO, MetadataReport_NERI, MetadataReport_PRWI, MetadataReport_RICH, MetadataReport_SARA, MetadataReport_SHEN, MetadataReport_VAFO)
```

# Add Columns

### Region

-   Region (NER)

-   Zone (e.g. South)

-   Unit (e.g. MTTS)

```{r}
zone_NewEngland <- c("ACAD", "CACO")
zone_MidAtlantic <- c("DEWA", "GATE", "GETT", "SARA", "VAFO")
zone_NCA <- c("ANTI", "CATO", "MONO", "PRWI")
zone_Allegheny <- c("CUVA", "NERI")
zone_MTTS <- c("APCO", "FRSP", "RICH", "SHEN")

MetadataReport <- MetadataReport %>% 
  mutate(Region = ifelse(AdministrationUnit_Name %in% c(zone_NCA), "NCR", "NER")) %>% 
  mutate(Zone = ifelse(AdministrationUnit_Name %in% c(zone_NewEngland, zone_MidAtlantic), "North",
                       ifelse(AdministrationUnit_Name %in% c(zone_Allegheny, zone_MTTS), "South", "NCA"))) %>% 
  mutate(Unit = ifelse(AdministrationUnit_Name %in% zone_NewEngland, "NewEngland",
                       ifelse(AdministrationUnit_Name %in% zone_MidAtlantic, "MidAtlantic", 
                              ifelse(AdministrationUnit_Name %in% zone_Allegheny, "Allegheny",
                                    ifelse(AdministrationUnit_Name %in% zone_MTTS, "MTTS", "NCA"))))) %>%
  relocate(Region, .before = AdministrationUnit_Name) %>% 
  relocate(Zone, .before = AdministrationUnit_Name) %>%
  relocate(Unit, .before = AdministrationUnit_Name)
```

### Macroplot

-   Macroplot_Num (01, 02...)

-   Purpose or PlotType (FMH, RAP...)

-   DateIn_Year

-   SampleEventDate_Year

```{r}
MetadataReport <- MetadataReport %>% 
  extract(Macroplot, regex = "([0-9]+)", into = c("Macroplot_Num"), remove = F) %>% 
  separate(Macroplot, sep = "(?=[0-9])", into = c("Macroplot_Code"), remove = F) %>%
  mutate(Macroplot_Num = ifelse(is.na(Macroplot_Num), 0, Macroplot_Num)) %>% 
  mutate(Macroplot_Num = as.numeric(Macroplot_Num)) %>% 
  #mutate(PlotType = ifelse(grepl("(RA)", Macroplot), "RA", "FMH")) %>%
  separate(DateIn, sep = "-", into = c("DateIn_Year", "Month", "Day"), remove = F) %>%
  separate(SampleEventDate, sep = "-", into = c("SampleEventDate_Year", "Month", "Day"), remove = F) %>%
  #relocate(PlotType, .after = Purpose) %>% 
  select(!c(Month, Day))
```

### Disturbance

-   Disturbance_Type (Burn, Herbicide, Mechanical, Mow)

-   Disturbance_Year (actual year)

```{r}
Disturbances <- MetadataReport %>%    
  select(c(AdministrationUnit_Name, Macroplot, MonStatus, SampleEventDate)) %>%   
  filter(MonStatus %in% c("Burn", "Herbicide", "Mechanical", "Mow")) %>%    
  mutate(Disturbance_Type = MonStatus) %>%    
  relocate(Disturbance_Type, .after = MonStatus) %>%  
  mutate(DisturbanceDate = SampleEventDate) %>% 
  separate(DisturbanceDate, sep = "-", into = c("DisturbanceDate_Year", "Month", "Day"), remove = F) %>%    
  select(!c(Month, Day))
```

### MonStatus

-   Entry / Prefix (0, 1, 2, 3 , 4...)

-   Status (pre, post)

-   TimeSince / Suffix (0, 1, 2, 5, 10, 20)

```{r}
MonStatus <- MetadataReport %>% 
  select(MonStatus) %>% 
  filter(!MonStatus %in% c("", "Burn", "Herbicide", "Mechanical", "Mow"))
MonStatus <- unique(MonStatus)

# Create column with consistent naming
MonStatus <- MonStatus %>%
  mutate(MonStatus_new = ifelse(MonStatus == "Pre", "00 Pre 00", 
                                ifelse(MonStatus == "Pre 2", "00 PR1 00",
                                       ifelse(MonStatus == "Measure", "00 Pre 00", MonStatus))))

order <- seq(1, nrow(MonStatus))

# Extract info
MonStatus <- MonStatus %>%
  arrange(MonStatus_new) %>%
  mutate(MonStatusOrd = order) %>%
  separate(MonStatus_new, sep = " ", into = c("Entry","Status","TimeSince"), remove = F) %>%
  # fix up classifications
  mutate(Status = ifelse(Status == "Yr", "Post", Status)) %>%
  mutate(Status = ifelse(Status == "PR1", "Pre", Status)) %>%
  mutate(TimeSince = ifelse(Status %in% c("Pre", "PR1"), NA, TimeSince)) %>%
  # make columns numeric
  mutate(Entry = as.numeric(Entry),
         TimeSince = as.numeric(TimeSince))
```

### Other

-   Disturbance_Entry (to match with MonStatus)

-   Disturbance_Desc (RX, WF-SUPP, WFU, WF)

-   Disturbance_Name (e.g. Cape Final)

-   Disturbance_Severity (Unaltered, Low, Low/Moderate, Moderate, Moderate/High, High)

-   FuelType (PIPO, PIED, etc.)

### Merge

```{r}
MetadataReport <- merge(MetadataReport, MonStatus, by = c("MonStatus"), all = T) %>% 
  relocate(MonStatus, .after = SampleEventDate_Year) %>%
  relocate(LegacyMonStatus, .before = MonStatus)
MetadataReport <- merge(MetadataReport, Disturbances, by = c("AdministrationUnit_Name", "Macroplot", "MonStatus", "SampleEventDate"), all = T) %>% 
  relocate(AdministrationUnit_Name, .before = ProjectUnit) %>% 
  relocate(Macroplot, .after = Purpose) %>%
  relocate(Type, .after = Purpose) %>% 
  relocate(MonStatus, .after = LegacyMonStatus) %>% 
  relocate(SampleEventDate, .before = SampleEventDate_Year)
```

# Tables

### Overall Program Summary

```{r program summary}
## Summarise projects and events by park
program_summ <- MetadataReport %>%
  summarise(`Parks` = n_distinct(AdministrationUnit_Name),
            `Projects` = n_distinct(ProjectUnit),
            `Number of Plots` = n_distinct(Macroplot),
            `Monitoring Statuses` = n_distinct(MonStatus),
            `Visit Dates` = n_distinct(SampleEventDate),
            `Protocols Used` = n_distinct(Protocols))

program_summ %>% 
  kbl(align = "lcccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T,
                row_label_position = "c") %>% 
  row_spec(0, font_size = 14, bold = TRUE) %>% 
  row_spec(nrow(program_summ), font_size = 14, bold = TRUE)
```

```{r}
## Summarise projects by park
target_park_summ <- MetadataReport %>%
  group_by(`Park` = AdministrationUnit_Name) %>%
  summarise(`Project Name` = unique(ProjectUnit),
            `First Visit` = min(as.numeric(SampleEventDate_Year)),
            `Latest Visit` = max(as.numeric(SampleEventDate_Year)),
            `Number of Plots` = n_distinct(Macroplot),
            `Monitoring Statuses` = n_distinct(MonStatus),
            `Protocols Used` = n_distinct(Protocols)) %>% 
  arrange(`Park`) %>% 
  ungroup() %>% 
  mutate_all(as.character)

# Calculate totals
target_park_summ_totals <- target_park_summ %>%
  summarise(`Number of Plots` = sum(as.numeric(`Number of Plots`))) %>% 
  mutate(`Project Name` = "",
         `First Visit` = "",
         `Latest Visit` = "Total",
         `Monitoring Statuses` = "",
         `Protocols Used` = "") %>% 
  mutate_all(as.character)

# Bind the totals row to the original data frame
target_park_summ_w_totals <- bind_rows(target_park_summ, target_park_summ_totals)
  
target_park_summ_w_totals %>% 
  kbl(align = "lccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T) %>% 
  row_spec(nrow(target_park_summ_w_totals), font_size = 14, bold = TRUE)
```

### Protocol Use Summary

The table below summarizes the frequency of use of protocols occurring in the FFI database, as utilized by the NPS Fire Ecology program. Protocols are arranged in descending order by number of plots such that the most frequently used protocols are listed first.

```{r protocol summ}
## Summarise protocol use by status
protocol_use_summ <- MetadataReport %>%
  filter(Protocols != "") %>% 
  group_by(`Protocol` = Protocols) %>%
  summarise(`First Use` = min(as.numeric(SampleEventDate_Year)),
            `Latest Use` = max(as.numeric(SampleEventDate_Year)),
            `Number of Plots` = n_distinct(Macroplot),
            `Number of Projects` = n_distinct(ProjectUnit),
            `Number of Monitoring Statuses` = n_distinct(MonStatus),
            `Number of Parks` = n_distinct(AdministrationUnit_Name)) %>% 
  arrange(desc(`Number of Plots`))

protocol_use_summ %>% 
  kbl(align = "lcccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T) %>% 
  row_spec(0, font_size = 14, bold = TRUE)
```

### Filtered Summaries

```{r set parameters, include=F}
### Select Data to Summarize
# use commas to build lists of acceptable values for filters

# designate target park(s)
unique(MetadataReport$AdministrationUnit_Name)
target_park <- c("APCO")

# designate target year or years
unique(MetadataReport$SampleEventDate_Year)
target_year <- c(2024)
```

The code underlying this report has been manipulated to display summaries of the following selected park(s) and year(s).\
\
Selected park(s): [`r target_park`]{style="color:red"}\
Selected year(s): [`r target_year`]{style="color:red"}

#### Park Summary: [`r target_park`]{style="color:red"}

The table below summarizes sample events recorded within the `r target_park` project.

```{r project summ}
## Summarise project
# uses 'target park' variable designated above
target_project_summ <- MetadataReport %>%
  filter(AdministrationUnit_Name == target_park) %>%
  group_by(`Monitoring Status` = MonStatus,
           `Order` = MonStatusOrd) %>%
  summarise(`Pre/Post` = unique(Status),
            `First Visit` = min(SampleEventDate_Year),
            `Latest Visit` = max(SampleEventDate_Year),
            `Number of Plots Visited` = n_distinct(Macroplot),
            `Protocols Used` = n_distinct(Protocols)) %>% 
  arrange(`Order`) %>% 
  select(!`Order`)

target_project_summ %>% 
  kbl(align = "lccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T) %>% 
  row_spec(0, font_size = 14, bold = TRUE)
```

#### Plot Activity Summary: [`r target_year`]{style="color:red"}

The table below summarizes all projects with plots sampled within the following year(s): `r target_year`.

```{r year summ}
## Summarise yearly plot activity
# uses 'target year' variable designated above
target_year_summ <- MetadataReport %>%
  filter(SampleEventDate_Year %in% target_year) %>% 
  group_by(`Park` = AdministrationUnit_Name) %>%
  summarise(`Project Name` = unique(ProjectUnit),
            `Start Date` = as.character(min(SampleEventDate)),
            `End Date` = as.character(max(SampleEventDate)),
            `Number of Plots` = n_distinct(Macroplot),
            `Protocols Used` = n_distinct(Protocols)) %>% 
  arrange(`Park`) %>% 
  ungroup()

# Calculate totals
year_summ_totals <- target_year_summ %>%
  summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>%
  mutate(`Park` = "",
         `Project Name` = "",
         `Plot Type` = "",
         `Start Date` = "",
         `End Date` = "Total")

# Bind the totals row to the original data frame
target_year_summ_w_totals <- bind_rows(target_year_summ, year_summ_totals)

target_year_summ_w_totals %>% 
  kbl(align = "lcccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T) %>% 
  row_spec(0, font_size = 14, bold = TRUE) %>% 
  row_spec(nrow(target_year_summ_w_totals), font_size = 14, bold = TRUE)
```

# Graphs

```{r}
graph_MetadataReport <- MetadataReport %>% 
  # remove unnecessary columns
  select(!c(Latitude, Longitude, UTM_X, UTM_Y, UTM_Zone, Datum, PDOP, Precision, )) %>% 
  select(!c(Elevation, ElevationUnits, Azimuth, Aspect, SlopeHill, SlopeTransect)) %>% 
  select(!c(LocatedBy, FutureVisit, DateOut, StartPoint, Directions, Comments, SampleEventTeam, SampleEventComment, LegacyMonStatus)) %>% 
  select(!c(UV1, UV2, UV3, UV4, UV5, UV6, UV7, UV8)) %>% 
  mutate(AdministrationUnit_Name = factor(AdministrationUnit_Name),
         Type = factor(Type),
         ProjectUnit = factor(ProjectUnit),
         Purpose = factor(Purpose),
         Macroplot = factor(Macroplot),
         Protocols = factor(Protocols),
         Visited = factor(Visited),
         MonStatus = factor(MonStatus),
         DateIn = as.Date(DateIn),
         DateIn_Year = as.numeric(DateIn_Year),
         SampleEventDate = as.Date(SampleEventDate),
         SampleEventDate_Year = as.numeric(SampleEventDate_Year),
         DisturbanceDate = as.Date(DisturbanceDate),
         DisturbanceDate_Year = as.numeric(DisturbanceDate_Year),
         Entry = as.factor(Entry),
         Macroplot_Num = as.factor(Macroplot_Num))
```

```{r}
graph_Disturbances <- graph_MetadataReport %>% 
  filter(is.na(Entry),
         !is.na(Disturbance_Type),
         Disturbance_Type == "Burn")

graph_sum_Disturbances <- graph_Disturbances %>% 
  group_by(Region, Zone, Unit, AdministrationUnit_Name, Type, DisturbanceDate, DisturbanceDate_Year, SampleEventDate_Year, MonStatus, Disturbance_Type) %>% 
  filter(DisturbanceDate_Year == SampleEventDate_Year) %>% 
  summarize(n_Macroplot = n()) %>% 
  mutate(DisturbanceDate = as.Date(DisturbanceDate),
         Macroplot_Num = "Disturbances")
```

### All FMH

```{r}
graph_sum_Disturbances %>% 
  filter(AdministrationUnit_Name == "RICH") %>% 
  ggplot(aes(x = DisturbanceDate, y = Disturbance_Type)) +
  geom_line(aes(group = Disturbance_Type)) +
  geom_point(aes(fill = Disturbance_Type), shape = 21) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  #geom_text(size = 4) +
  #geom_label_repel(aes(size = 4)) +
  labs(title = "Disturbance History",
       y = "Park",
       x = "Year",
       fill = "Disturbance Type") +
  #scale_fill_manual(values=c('yellowgreen', "yellow", 'orange', "red", "darkred","grey")) +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

```

```{r}
graph_Disturbances %>% 
  ggplot(aes(x = DisturbanceDate_Year, y = Macroplot_Num)) +
  geom_line(aes(group = DisturbanceDate_Year), color = "grey") +
  geom_point(aes(color = Disturbance_Type)) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Disturbance History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Disturbance Type") +
  #scale_color_manual(values=c("darkred", "blue", "black", "green")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))

```

```{r}
graph_MetadataReport %>% 
  filter(!is.na(Entry),
         AdministrationUnit_Name == "RICH") %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num)) +
  geom_point(aes(color = Entry), size = 2) +
  geom_point(aes(X = DisturbanceDate, y = Macroplot_Num, 
                 fill = Disturbance_Type), 
             data = graph_sum_Disturbances %>% 
               filter(AdministrationUnit_Name == "RICH"),
             shape = 21) +
  geom_line(aes(group = Macroplot_Num, color = Entry)) +
  geom_line(aes(group = Macroplot_Num), 
            data = graph_sum_Disturbances %>% 
              filter(AdministrationUnit_Name == "RICH"), 
            color = "black") +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Sample Event History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry",
       fill = "Disturbance Type") +
  scale_fill_manual(values = c("red", "green", "black", "purple")) +
  #scale_color_manual(values=c('forestgreen',"lightgreen","lightyellow", "yellow", "orange", 'darkorange', "red","red3", "darkred","darkgrey", "black")) +
  theme_light() +
  scale_x_continuous(breaks = seq(1995, 2030, by = 1)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))
```

### South Zone

```{r}
graph_MetadataReport %>% 
  filter(Zone == "South", !is.na(Entry)) %>%
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_line(aes(group = DisturbanceDate_Year), data = graph_Disturbances, color = "red") +
  geom_point(size = 2) +
  geom_line(aes(group = Macroplot)) +
  geom_point(data = graph_Disturbances, color = "red", shape = 1, size = 2) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Sample Event History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  scale_color_manual(values=c('forestgreen',"lightgreen","lightyellow", "yellow", "orange", 'darkorange', "red","red3", "darkred","darkgrey", "black")) +
  theme_light() +
  scale_x_continuous(breaks = seq(1995, 2030, by = 1)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))

#ggsave(path = path_graphs, filename = "Sample Event History_All WACA.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

### National Capital Area

```{r}
graph_MetadataReport %>% 
  filter(Zone == "NCA", !is.na(Entry)) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_point() +
  geom_line(aes(group = Macroplot)) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Sample Event History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  #scale_color_manual(values=c('forestgreen',"lightgreen","lightyellow", "yellow", "orange", 'darkorange', "red","red3", "darkred","darkgrey", "black")) +
  theme_light() +
  scale_x_continuous(breaks = seq(1995, 2030, by = 1)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))

#ggsave(path = path_graphs, filename = "Sample Event History_All WACA.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

### North Zone

```{r}
graph_MetadataReport %>% 
  filter(Zone == "North", !is.na(Entry)) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_point() +
  geom_line(aes(group = Macroplot)) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Sample Event History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  #scale_color_manual(values=c('forestgreen',"lightgreen","lightyellow", "yellow", "orange", 'darkorange', "red","red3", "darkred","darkgrey", "black")) +
  theme_light() +
  scale_x_continuous(breaks = seq(1995, 2030, by = 1)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))

#ggsave(path = path_graphs, filename = "Sample Event History_All WACA.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```
