---
title: "FFI Database Summary"
subtitle: "Grand Canyon"
output: 
  html_document:
    toc: true
    toc-float: true
    code_download: true
date: "`r Sys.Date()`"
---

# Purpose

This report summarizes plot work by the Fire Ecology Program. The included tables and graphs allow a user to quickly view the overall status of program, park, project, or protocol activities in an FFI admin unit.

The code summarizes records in the Macroplot Report and Sample Event Report that can be downloaded via the Utilities menu on the Project Management tab on the FFI Remote App Server. You can recreate this Metadata Report by running code found in the file "Metadata_GRCA.R", under the scripts folder for this R project. This script was made specifically for Grand Canyon, and will combine files (SampleEventReport.csv and MacroplotReport.csv) from all Admin Units (GRCA, I&M, WACA).

### Setup

```{r}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
```

```{r}
## Load Packages

# "here" helps you easily find and reference your working directory
library(here)
# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
```

```{r}
## Adjust File Paths

# Identify working directory
here()

# Adjust File Paths
path_data <- "X:/FFI Data Management/Exports from FFI/metadata/"
path_dataclean <- paste0(here(), "/output/data_clean/")
path_scripts <- paste0(here(), "/scripts/")
path_graphs <- paste0(here(), "/output/graphs/")
# path_data <- "D:/Allie/_FireFX/FFI Data Management/Exports from FFI/metadata/"
```

### Load Data

Load in the Metadata Report. This Metadta Report was created by combining Macroplot Reports and Sample Event Reports from each Admin Unit, which can be downloaded via the Utilities menu on the Project Management tab on the FFI Remote App Server.

```{r}
# Load in data
all_MetadataReport <- read.csv(paste0(path_dataclean, "all_MetadataReport.csv"))
```

```{r}
## reclassify columns

#str(all_MetadataReport)

# reclassify data as correct type
all_MetadataReport <- all_MetadataReport %>% 
  mutate(AdministrationUnit_Name = factor(AdministrationUnit_Name)) %>% 
  mutate(Park = factor(Park)) %>% 
  mutate(PlotType_Name = factor(PlotType_Name)) %>% 
  mutate(Type = factor(Type)) %>% 
  mutate(Park_Unit = factor(Park_Unit)) %>% 
  mutate(ProjectUnit = factor(ProjectUnit)) %>% 
  mutate(Purpose = factor(Purpose)) %>% 
  mutate(Burn_Unit = factor(Burn_Unit)) %>% 
  mutate(MetaData = factor(MetaData)) %>% 
  mutate(Macroplot = factor(Macroplot)) %>% 
  mutate(Macroplot_Code = factor(Macroplot_Code)) %>% 
  mutate(Macroplot_Num = factor(Macroplot_Num)) %>% 
  #mutate(DateIn_Year = as.numeric()) %>%
  mutate(SampleEventDate_Year = as.numeric(SampleEventDate_Year)) %>% 
  mutate(Protocols = factor(Protocols)) %>%
  mutate(Visited = factor(Visited)) %>%
  mutate(LegacyMonStatus = factor(LegacyMonStatus)) %>%
  mutate(MonStatus = factor(MonStatus)) %>%
  mutate(Entry = factor(Entry)) %>% 
  mutate(Status = factor(Status)) %>% 
  #mutate(Disturbance_Type = factor()) %>% 
  #mutate(Disturbance_Name = factor()) %>% 
  #mutate(Disturbance_Desc = factor()) %>% 
  mutate(DisturbanceDate = as.Date(DisturbanceDate)) %>% 
  #mutate(DisturbanceDate_Year = as.numeric()) %>% 
  mutate(Disturbance_Severity = factor(Disturbance_Severity, levels = c("Unburned", "Low", "Low/Mod", "Mod", "Mod/High", "High")))
```

# Tables

```{r manipulate data, include=FALSE}
# check occurrence of unique values in newly created columns, make corrections as needed
all_MetadataReport$PlotType_Name %>% table(exclude = NULL)
all_MetadataReport$Status %>% table(exclude = NULL)
all_MetadataReport$Disturbance_Type %>% table(exclude = NULL)
all_MetadataReport$TimeSince %>% table(exclude = NULL)
```

### Overall Program Summary

```{r program summary}
## Summarise projects and events by park
program_summ <- all_MetadataReport %>%
  summarise(`Parks` = n_distinct(AdministrationUnit_Name),
            `Projects` = n_distinct(ProjectUnit),
            `Number of Plots` = n_distinct(Macroplot),
            `Monitoring Statuses` = n_distinct(MonStatus),
            `Visit Dates` = n_distinct(SampleEventDate),
            `Protocols Used` = n_distinct(Protocols))

program_summ %>% 
  kbl(align = "lcccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T,
                row_label_position = "c") %>% 
  row_spec(0, font_size = 14, bold = TRUE) %>% 
  row_spec(nrow(program_summ), font_size = 14, bold = TRUE)
```

### Filtered Summaries

```{r set parameters, include=F}
### Select Data to Summarize
# use commas to build lists of acceptable values for filters

# designate target park(s)
unique(all_MetadataReport$Park)
target_park <- c("GRCA")

# designate target project(s)
# see all project names
unique(all_MetadataReport$PlotType_Name)
target_project <- c("FMH")

# designate target year or years
unique(all_MetadataReport$SampleEventDate_Year)
target_year <- c(2024)
```

The code underlying this report has been manipulated to display summaries of the following selected park(s), project(s), and year(s).\
\
Selected park(s): [`r target_park`]{style="color:red"}\
Selected project(s): [`r target_project`]{style="color:red"}\
Selected year(s): [`r target_year`]{style="color:red"}\

#### Park Summary: [`r target_park`]{style="color:red"}

The table below summarizes current and past projects in `r target_park`.

```{r park summ}
## Summarise projects by park
# uses 'target park' variable designated above
target_park_summ <- all_MetadataReport %>%
  filter(Park == target_park) %>% 
  group_by(`Project Name` = ProjectUnit) %>%
  summarise(`Plot Type` = unique(PlotType_Name),
            `First Visit` = min(as.numeric(SampleEventDate_Year)),
            `Latest Visit` = max(as.numeric(SampleEventDate_Year)),
            `Number of Plots` = n_distinct(Macroplot),
            `Monitoring Statuses` = n_distinct(MonStatus),
            `Protocols Used` = n_distinct(Protocols)) %>% 
  arrange(`Project Name`) %>% 
  ungroup() %>% 
  mutate_all(as.character)

# Calculate totals
target_park_summ_totals <- target_park_summ %>%
  summarise(`Number of Plots` = sum(as.numeric(`Number of Plots`))) %>% 
  mutate(`Project Name` = "",
         `Plot Type` = "",
         `First Visit` = "",
         `Latest Visit` = "Total",
         `Monitoring Statuses` = "",
         `Protocols Used` = "") %>% 
  mutate_all(as.character)

# Bind the totals row to the original data frame
target_park_summ_w_totals <- bind_rows(target_park_summ, target_park_summ_totals)
  
target_park_summ_w_totals %>% 
  kbl(align = "lccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T) %>% 
  row_spec(nrow(target_park_summ_w_totals), font_size = 14, bold = TRUE)
```

#### Project Summary: [`r target_project`]{style="color:red"}

The table below summarizes sample events recorded within the `r target_project` project.

```{r project summ}
## Summarise project
# uses 'target project' variable designated above
target_project_summ <- all_MetadataReport %>%
  filter(Park == target_park,
         PlotType_Name == target_project) %>%
  group_by(`Monitoring Status` = MonStatus,
           `Order` = MonStatusOrd) %>%
  summarise(`Pre/Post` = unique(Status),
            `First Visit` = min(SampleEventDate_Year),
            `Latest Visit` = max(SampleEventDate_Year),
            `Number of Plots Visited` = n_distinct(Macroplot),
            `Protocols Used` = n_distinct(Protocols)) %>% 
  arrange(`Order`) %>% 
  select(!`Order`)

target_project_summ %>% 
  kbl(align = "lccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T) %>% 
  row_spec(0, font_size = 14, bold = TRUE)
```

#### Plot Activity Summary: [`r target_year`]{style="color:red"}

The table below summarizes all projects with plots sampled within the following year(s): `r target_year`.

```{r year summ}
## Summarise yearly plot activity
# uses 'target year' variable designated above
target_year_summ <- all_MetadataReport %>%
  filter(SampleEventDate_Year %in% target_year) %>% 
  group_by(`Park` = Park,
           `Project Name` = ProjectUnit) %>%
  summarise(`Plot Type` = unique(PlotType_Name),
            `Start Date` = as.character(min(SampleEventDate)),
            `End Date` = as.character(max(SampleEventDate)),
            `Number of Plots` = n_distinct(Macroplot),
            `Protocols Used` = n_distinct(Protocols)) %>% 
  arrange(`Project Name`) %>% 
  ungroup()

# Calculate totals
year_summ_totals <- target_year_summ %>%
  summarise(across(where(is.numeric), \(x) sum(x, na.rm = TRUE))) %>%
  mutate(`Park` = "",
         `Project Name` = "",
         `Plot Type` = "",
         `Start Date` = "",
         `End Date` = "Total")

# Bind the totals row to the original data frame
target_year_summ_w_totals <- bind_rows(target_year_summ, year_summ_totals)

target_year_summ_w_totals %>% 
  kbl(align = "lcccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T) %>% 
  row_spec(0, font_size = 14, bold = TRUE) %>% 
  row_spec(nrow(target_year_summ_w_totals), font_size = 14, bold = TRUE)
```

### Protocol Use Summary

The table below summarizes the frequency of use of protocols occurring in the FFI database, as utilized by the NPS Alaska Fire Ecology program. Protocols are arranged in descending order by number of plots such that the most frequently used protocols are listed first.

```{r protocol summ}
## Summarise protocol use by status
protocol_use_summ <- all_MetadataReport %>%
  group_by(`Protocol` = Protocols) %>%
  summarise(`First Use` = min(as.numeric(SampleEventDate_Year)),
            `Latest Use` = max(as.numeric(SampleEventDate_Year)),
            `Number of Plots` = n_distinct(Macroplot),
            `Number of Projects` = n_distinct(ProjectUnit),
            `Number of Monitoring Statuses` = n_distinct(MonStatus),
            `Number of Parks` = n_distinct(AdministrationUnit_Name)) %>% 
  arrange(desc(`Number of Plots`))

protocol_use_summ %>% 
  kbl(align = "lcccccc") %>%
  kable_styling(bootstrap_options = c("striped","condensed"), 
                full_width = F, position = "left", fixed_thead = T) %>% 
  row_spec(0, font_size = 14, bold = TRUE)
```

# Graphs

```{r}
graph_MetadataReport <- all_MetadataReport %>% 
  filter(!is.na(AdministrationUnit_Name)) %>% 
  # remove unnecessary columns
  select(!c(Latitude, Longitude, UTM_X, UTM_Y, UTM_Zone, Datum, PDOP, Precision, )) %>% 
  select(!c(Elevation, ElevationUnits, Azimuth, Aspect, SlopeHill, SlopeTransect)) %>% 
  select(!c(LocatedBy, FutureVisit, DateOut, StartPoint, Directions, Comments, SampleEventTeam, SampleEventComment, LegacyMonStatus)) %>% 
  select(!c(UV1, UV2, UV3, UV4, UV5, UV6, UV7, UV8))
```

## WACA

### All FMH

```{r}
graph_MetadataReport %>% 
  filter(Park == "WACA",
         PlotType_Name == "FMH") %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_point() +
  geom_line(aes(group = Macroplot)) +
  facet_grid(~Purpose) +
  labs(title = "WACA Sample Event History",
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  scale_color_manual(values=c('forestgreen', "yellow", 'darkorange', "red", "darkred")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Sample Event History_All WACA.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

## GRCA

### All I&M

```{r}
graph_MetadataReport %>% 
  filter(Park == "GRCA",
         PlotType_Name == "I&M") %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_point() +
  geom_line(aes(group = Macroplot)) +
  facet_wrap(~Macroplot_Code) +
  labs(title = "GRCA Sample Event History",
       subtitle = "Inventory and Monitoring (I&M) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  scale_color_manual(values=c('forestgreen', "yellow", 'darkorange', "red", "darkred")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Sample Event History_All I&M.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

### All RAP

```{r}
graph_MetadataReport %>% 
  filter(Park == "GRCA",
         PlotType_Name == "RAP") %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_point() +
  geom_line(aes(group = Macroplot)) +
  facet_wrap(~Macroplot_Code) +
  labs(title = "GRCA Sample Event History",
       subtitle = "Rapid Assessment Protocol (RAP) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  scale_color_manual(values=c('forestgreen', "yellow", 'darkorange', "red", "darkred")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Sample Event History_All RAP.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

### All FMH

```{r}
graph_MetadataReport %>% 
  filter(Park == "GRCA",
         PlotType_Name == "FMH") %>% 
  filter(!Macroplot %in% c("SHOS 01", "SHOS 02")) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_point() +
  geom_line(aes(group = Macroplot)) +
  facet_grid(~Purpose) +
  labs(title = "GRCA Sample Event History",
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  scale_color_manual(values=c('forestgreen', "yellow", 'darkorange', "red", "darkred")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Sample Event History_All FMH.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

#### Summarize

```{r}
# Summarize to one point per (Year, Macroplot, Visited)

summary_points_PIED <- graph_MetadataReport %>%
  filter(Park == "GRCA", Purpose == "PIED") %>%
  group_by(SampleEventDate_Year, Macroplot, Visited) %>%
  summarise(n_protocols = n(), .groups = "drop")  # optional: keep count of protocols

summary_points_PIPO <- graph_MetadataReport %>%
  filter(Park == "GRCA", Purpose == "PIPO") %>%
  group_by(SampleEventDate_Year, Macroplot, Visited) %>%
  summarise(n_protocols = n(), .groups = "drop")

summary_points_PIPN <- graph_MetadataReport %>%
  filter(Park == "GRCA", Purpose == "PIPN") %>%
  group_by(SampleEventDate_Year, Macroplot, Visited) %>%
  summarise(n_protocols = n(), .groups = "drop")

summary_points_PIAB <- graph_MetadataReport %>%
  filter(Park == "GRCA", Purpose == "PIAB") %>%
  group_by(SampleEventDate_Year, Macroplot, Visited) %>%
  summarise(n_protocols = n(), .groups = "drop")

summary_points_PIEN <- graph_MetadataReport %>%
  filter(Park == "GRCA", Purpose == "PIEN") %>%
  group_by(SampleEventDate_Year, Macroplot, Visited) %>%
  summarise(n_protocols = n(), .groups = "drop")
```

#### PIED

```{r}
graph_MetadataReport %>% 
  filter(Park == "GRCA",
         Purpose %in% c("PIED")) %>% 
  group_by(SampleEventDate_Year, Macroplot, Visited) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot)) +
  # Line plot
  geom_line(aes(group = Macroplot, color = Entry)) +
  # Plot green (Visited = Y) points first (background)
  geom_jitter(data = summary_points_PIED %>% filter(Visited == "Y"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  # Plot red (Visited = N) points second (foreground)
  geom_jitter(data = summary_points_PIED %>% filter(Visited == "N"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  #geom_jitter(aes(group = Visited, fill = Visited), shape = 21) +
  labs(title = "GRCA Sample Event History",
       subtitle = "Pinyon Juniper Ecosystem (PIED)",
       y = "Macroplot",
       x = "Year",
       color = "Entry") +
  scale_fill_manual(values = c("Y" = "forestgreen", "N" = "red")) +
  scale_color_manual(values=c('forestgreen', "yellow", 'darkorange', "red", "darkred")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Sample Event History_PIED.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

#### PIPO

```{r}
graph_MetadataReport %>% 
  filter(Park == "GRCA",
         Purpose %in% c("PIPO")) %>% 
  group_by(SampleEventDate_Year, Macroplot, Visited) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot)) +
  # Line plot
  geom_line(aes(group = Macroplot, color = Entry)) +
  # Plot green (Visited = Y) points first (background)
  geom_jitter(data = summary_points_PIPO %>% filter(Visited == "Y"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  # Plot red (Visited = N) points second (foreground)
  geom_jitter(data = summary_points_PIPO %>% filter(Visited == "N"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  #geom_jitter(aes(group = Visited, fill = Visited), shape = 21) +
  labs(title = "GRCA Sample Event History",
       subtitle = "South Rim Ponderosa Pine Ecosystem (PIPO)",
       y = "Macroplot",
       x = "Year",
       color = "Entry",
       fill = "Visited") +
  scale_fill_manual(values = c("Y" = "forestgreen", "N" = "red")) +
  scale_color_manual(values=c('forestgreen', "yellow", 'darkorange', "red", "darkred")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Sample Event History_PIPO.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

#### PIPN

```{r}
graph_MetadataReport %>% 
  filter(Park == "GRCA",
         Purpose %in% c("PIPN")) %>% 
  group_by(SampleEventDate_Year, Macroplot, Visited) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot)) +
  # Line plot
  geom_line(aes(group = Macroplot, color = Entry)) +
  # Plot green (Visited = Y) points first (background)
  geom_jitter(data = summary_points_PIPN %>% filter(Visited == "Y"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  # Plot red (Visited = N) points second (foreground)
  geom_jitter(data = summary_points_PIPN %>% filter(Visited == "N"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  #geom_jitter(aes(group = Visited, fill = Visited), shape = 21) +
  labs(title = "GRCA Sample Event History",
       subtitle = "North Rim Ponderosa Pine Ecosystem (PIPN)",
       y = "Macroplot",
       x = "Year",
       color = "Entry") +
  scale_fill_manual(values = c("Y" = "forestgreen", "N" = "red")) +
  scale_color_manual(values=c('forestgreen', "yellow", 'darkorange', "red", "darkred")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Sample Event History_PIPN.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

#### PIAB

```{r}
graph_MetadataReport %>% 
  filter(Park == "GRCA",
         Purpose %in% c("PIAB")) %>% 
  group_by(SampleEventDate_Year, Macroplot, Visited) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot)) +
  # Line plot
  geom_line(aes(group = Macroplot, color = Entry)) +
  # Plot green (Visited = Y) points first (background)
  geom_jitter(data = summary_points_PIAB %>% filter(Visited == "Y"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  # Plot red (Visited = N) points second (foreground)
  geom_jitter(data = summary_points_PIAB %>% filter(Visited == "N"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  #geom_jitter(aes(group = Visited, fill = Visited), shape = 21) +
  labs(title = "GRCA Sample Event History",
       subtitle = "Pine-Fir Ecosystem (PIAB)",
       y = "Macroplot",
       x = "Year",
       color = "Entry") +
  scale_fill_manual(values = c("Y" = "forestgreen", "N" = "red")) +
  scale_color_manual(values=c('forestgreen', "yellow", 'darkorange', "red", "darkred")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Sample Event History_PIAB.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

#### PIEN

```{r}
graph_MetadataReport %>% 
  filter(Park == "GRCA",
         Purpose %in% c("PIEN")) %>% 
  group_by(SampleEventDate_Year, Macroplot, Visited) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot)) +
  # Line plot
  geom_line(aes(group = Macroplot, color = Entry)) +
  # Plot green (Visited = Y) points first (background)
  geom_jitter(data = summary_points_PIEN %>% filter(Visited == "Y"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  # Plot red (Visited = N) points second (foreground)
  geom_jitter(data = summary_points_PIEN %>% filter(Visited == "N"),
              aes(x = SampleEventDate_Year, y = Macroplot, fill = Visited),
              shape = 21, size = 2, width = 0.1, height = 0.1) +
  #geom_jitter(aes(group = Visited, fill = Visited), shape = 21) +
  labs(title = "GRCA Sample Event History",
       subtitle = "Spruce-Fir Ecosystem (PIEN)",
       y = "Macroplot",
       x = "Year",
       color = "Entry") +
  scale_fill_manual(values = c("Y" = "forestgreen", "N" = "red")) +
  scale_color_manual(values=c('forestgreen', "yellow", 'darkorange', "red", "darkred")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Sample Event History_PIEN.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

### Fires

```{r}
graph_fires_MetadataReport <- graph_MetadataReport %>% 
  filter(Park == "GRCA",
         PlotType_Name == "FMH") %>% 
  filter(!Macroplot %in% c("SHOS 01", "SHOS 02")) %>% 
  filter(Entry != "0") %>% 
  group_by(Burn_Unit, DisturbanceDate, DisturbanceDate_Year, SampleEventDate_Year, Park_Unit, MonStatus, Disturbance_Name, Disturbance_Desc, Disturbance_Severity) %>% 
  filter(DisturbanceDate_Year == SampleEventDate_Year) %>% 
  summarise(n_macroplot = n())
```

```{r}
graph_fires_MetadataReport %>% 
  filter(Park_Unit == "North") %>% 
  mutate(DisturbanceDate = as.Date(DisturbanceDate)) %>% 
  ggplot(aes(x = DisturbanceDate, y = Burn_Unit, label = Disturbance_Desc)) +
  geom_line(aes(group = Burn_Unit)) +
  #geom_point(aes(size  = n_macroplot), shape = "\U1F525") +
  geom_point(aes(fill = Disturbance_Severity, size  = n_macroplot), shape = 21) +
  #geom_text(size = 4) +
  #geom_label_repel(aes(size = 4)) +
  labs(title = "GRCA North Rim Fire History",
       y = "Burn Unit",
       x = "Year",
       fill = "Severity",
       size = "Number of Plots") +
  scale_fill_manual(values=c('yellowgreen', "yellow", 'orange', "red", "darkred","grey")) +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Fire History_North Rim.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

```{r}
graph_fires_MetadataReport %>% 
  filter(Park_Unit == "South") %>% 
  mutate(DisturbanceDate = as.Date(DisturbanceDate)) %>% 
  ggplot(aes(x = DisturbanceDate, y = Burn_Unit, label = Disturbance_Desc)) +
  geom_line(aes(group = Burn_Unit)) +
  #geom_point(aes(size  = n_macroplot), shape = "\U1F525") +
  geom_point(aes(fill = Disturbance_Severity, size  = n_macroplot), shape = 21) +
  #geom_text(size = 4) +
  #geom_label_repel(aes(size = 4)) +
  labs(title = "GRCA South Rim Fire History",
       y = "Burn Unit",
       x = "Year",
       fill = "Severity",
       size = "Number of Plots") +
  scale_fill_manual(values=c('yellowgreen', "yellow", 'orange', "red", "darkred","grey")) +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

ggsave(path = path_graphs, filename = "Fire History_South Rim.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```
