---
title: "FFI Database Summary"
subtitle: "Northeast Region"
output: 
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 2
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: 2
---

# Purpose

This report summarizes plot work by the NPS Fire Ecology Program. The included graphs allow a user to quickly view the overall status of program, park, project, or protocol activities in an FFI admin unit.

The code summarizes records in the Macroplot Report and Sample Event Report that can be downloaded via the Utilities menu on the Project Management tab on the FFI Remote App Server. You can recreate this Metadata Report by running code found in the file "QAQC_MetadataReport.R", under the scripts folder for this R project.

### Setup  {.hidden}

```{r}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
```

```{r}
## Load Packages

# "here" helps you easily find and reference your working directory
library(here)
# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
```

```{r}
## Adjust File Paths

# Identify working directory
here()

# Adjust File Paths
path_data <- "E:/Allie/FireFX_NER/FFI Data Management/Exports/"
#path_data <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/Exports/"
path_graphs <- paste0(here(), "/output/graphs/")
```

### Load Data  {.hidden}

Load in the Metadata Report. This Metadata Report was created by combining Macroplot Reports and Sample Event Reports from each Admin Unit, which can be downloaded via the Utilities menu on the Project Management tab on the FFI Remote App Server.

```{r}
# Load in data
MetadataReport_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_MetadataReport.csv"), quote = "")
MetadataReport_APCO <- read.csv(paste0(path_data, "APCO/APCO_MetadataReport.csv"), quote = "")
MetadataReport_CATO <- read.csv(paste0(path_data, "CATO/CATO_MetadataReport.csv"), quote = "")
MetadataReport_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_MetadataReport.csv"), quote = "")
MetadataReport_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_MetadataReport.csv"), quote = "")
MetadataReport_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_MetadataReport.csv"), quote = "")
MetadataReport_GATE <- read.csv(paste0(path_data, "GATE/GATE_MetadataReport.csv"), quote = "")
MetadataReport_GETT <- read.csv(paste0(path_data, "GETT/GETT_MetadataReport.csv"), quote = "")
MetadataReport_MONO <- read.csv(paste0(path_data, "MONO/MONO_MetadataReport.csv"), quote = "")
MetadataReport_NERI <- read.csv(paste0(path_data, "NERI/NERI_MetadataReport.csv"), quote = "")
MetadataReport_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_MetadataReport.csv"), quote = "")
MetadataReport_RICH <- read.csv(paste0(path_data, "RICH/RICH_MetadataReport.csv"), quote = "")
MetadataReport_SARA <- read.csv(paste0(path_data, "SARA/SARA_MetadataReport.csv"), quote = "")
MetadataReport_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_MetadataReport.csv"), quote = "")
MetadataReport_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_MetadataReport.csv"), quote = "")
```

### Merge Data  {.hidden}

```{r}
MetadataReport <- rbind(MetadataReport_ANTI, MetadataReport_APCO, MetadataReport_CATO, MetadataReport_CUVA, MetadataReport_DEWA, MetadataReport_FRSP, MetadataReport_GATE, MetadataReport_GETT, MetadataReport_MONO, MetadataReport_NERI, MetadataReport_PRWI, MetadataReport_RICH, MetadataReport_SARA, MetadataReport_SHEN, MetadataReport_VAFO)

remove(MetadataReport_ANTI, MetadataReport_APCO, MetadataReport_CATO, MetadataReport_CUVA, MetadataReport_DEWA, MetadataReport_FRSP, MetadataReport_GATE, MetadataReport_GETT, MetadataReport_MONO, MetadataReport_NERI, MetadataReport_PRWI, MetadataReport_RICH, MetadataReport_SARA, MetadataReport_SHEN, MetadataReport_VAFO)
```

# Add Columns  {.hidden}

### Region  {.hidden}

-   Region (NER)

-   Zone (e.g. South)

-   Unit (e.g. MTTS)

```{r}
zone_NewEngland <- c("ACAD", "CACO")
zone_MidAtlantic <- c("DEWA", "GATE", "GETT", "SARA", "VAFO")
zone_NCA <- c("ANTI", "CATO", "MONO", "PRWI")
zone_Allegheny <- c("CUVA", "NERI")
zone_MTTS <- c("APCO", "FRSP", "RICH", "SHEN")

MetadataReport <- MetadataReport %>% 
  mutate(Region = ifelse(AdministrationUnit_Name %in% c(zone_NCA), "NCR", "NER")) %>% 
  mutate(Zone = ifelse(AdministrationUnit_Name %in% c(zone_NewEngland, zone_MidAtlantic), "North",
                       ifelse(AdministrationUnit_Name %in% c(zone_Allegheny, zone_MTTS), "South", "NCA"))) %>% 
  mutate(Unit = ifelse(AdministrationUnit_Name %in% zone_NewEngland, "NewEngland",
                       ifelse(AdministrationUnit_Name %in% zone_MidAtlantic, "MidAtlantic", 
                              ifelse(AdministrationUnit_Name %in% zone_Allegheny, "Allegheny",
                                    ifelse(AdministrationUnit_Name %in% zone_MTTS, "MTTS", "NCA"))))) %>%
  relocate(Region, .before = AdministrationUnit_Name) %>% 
  relocate(Zone, .before = AdministrationUnit_Name) %>%
  relocate(Unit, .before = AdministrationUnit_Name)
```

### Macroplot  {.hidden}

-   Macroplot_Num (01, 02...)

-   Purpose or PlotType (FMH, RAP...)

-   DateIn_Year

-   SampleEventDate_Year

```{r}
MetadataReport <- MetadataReport %>% 
  extract(Macroplot, regex = "([0-9]+)", into = c("Macroplot_Num"), remove = F) %>% 
  separate(Macroplot, sep = "(?=[0-9])", into = c("Macroplot_Code"), remove = F) %>%
  mutate(Macroplot_Num = ifelse(is.na(Macroplot_Num), 0, Macroplot_Num)) %>% 
  mutate(Macroplot_Num = as.numeric(Macroplot_Num))
```

### Disturbance  {.hidden}

-   Disturbance_Type (Burn, Herbicide, Mechanical, Mow)

-   Disturbance_Year (actual year)

```{r}
Disturbances <- MetadataReport %>%    
  select(c(AdministrationUnit_Name, Macroplot, MonStatus, SampleEventDate)) %>%   
  filter(MonStatus %in% c("Burn", "Herbicide", "Mechanical", "Mow")) %>%    
  mutate(Disturbance_Type = MonStatus) %>%    
  relocate(Disturbance_Type, .after = MonStatus) %>%  
  mutate(DisturbanceDate = SampleEventDate) %>% 
  separate(DisturbanceDate, sep = "-", into = c("DisturbanceDate_Year", "Month", "Day"), remove = F) %>%    
  select(!c(Month, Day))
```

### MonStatus  {.hidden}

-   Entry / Prefix (0, 1, 2, 3 , 4...)

-   Status (pre, post)

-   TimeSince / Suffix (0, 1, 2, 5, 10, 20)

```{r}
MonStatus <- MetadataReport %>% 
  select(MonStatus) %>% 
  filter(!MonStatus %in% c("", "Burn", "Herbicide", "Mechanical", "Mow"))
MonStatus <- unique(MonStatus)

# Create column with consistent naming
MonStatus <- MonStatus %>%
  mutate(MonStatus_new = ifelse(MonStatus == "Pre", "00 Pre 00", 
                                ifelse(MonStatus == "Pre 2", "00 PR1 00",
                                       ifelse(MonStatus == "Measure", "00 Pre 00", MonStatus))))

order <- seq(1, nrow(MonStatus))

# Extract info
MonStatus <- MonStatus %>%
  arrange(MonStatus_new) %>%
  mutate(MonStatusOrd = order) %>%
  separate(MonStatus_new, sep = " ", into = c("Entry","Status","TimeSince"), remove = F) %>%
  # fix up classifications
  mutate(Status = ifelse(Status == "Yr", "Post", Status)) %>%
  mutate(Status = ifelse(Status == "PR1", "Pre", Status)) %>%
  mutate(TimeSince = ifelse(Status %in% c("Pre", "PR1"), NA, TimeSince)) %>%
  # make columns numeric
  mutate(Entry = as.numeric(Entry),
         TimeSince = as.numeric(TimeSince))
```

### Other  {.hidden}

-   Disturbance_Entry (to match with MonStatus)

-   Disturbance_Desc (RX, WF-SUPP, WFU, WF)

-   Disturbance_Name (e.g. Cape Final)

-   Disturbance_Severity (Unaltered, Low, Low/Moderate, Moderate, Moderate/High, High)

-   FuelType (PIPO, PIED, etc.)

### Merge  {.hidden}

```{r}
MetadataReport_all <- merge(MetadataReport, MonStatus, by = c("MonStatus"), all = T) %>% 
  relocate(MonStatus, .after = SampleEventDate_Year) %>%
  relocate(LegacyMonStatus, .before = MonStatus)
MetadataReport_all <- merge(MetadataReport_all, Disturbances, by = c("AdministrationUnit_Name", "Macroplot", "MonStatus", "SampleEventDate"), all = T) %>% 
  relocate(AdministrationUnit_Name, .after = Unit) %>% 
  relocate(Macroplot, .after = Purpose) %>%
  relocate(Type, .after = Purpose) %>% 
  relocate(MonStatus, .after = LegacyMonStatus) %>% 
  relocate(SampleEventDate, .before = SampleEventDate_Year)
```

# Graphs

```{r}
graph_MetadataReport <- MetadataReport_all %>% 
  # remove unnecessary columns
  select(!c(Latitude, Longitude, UTM_X, UTM_Y, UTM_Zone, Datum, PDOP, Precision, )) %>% 
  select(!c(Elevation, ElevationUnits, Azimuth, Aspect, SlopeHill, SlopeTransect)) %>% 
  select(!c(LocatedBy, FutureVisit, DateOut, StartPoint, Directions, Comments, SampleEventTeam, SampleEventComment, LegacyMonStatus)) %>% 
  select(!c(UV1, UV2, UV3, UV4, UV5, UV6, UV7, UV8)) %>% 
  mutate(AdministrationUnit_Name = factor(AdministrationUnit_Name),
         Type = factor(Type),
         ProjectUnit = factor(ProjectUnit),
         Purpose = factor(Purpose),
         Macroplot = factor(Macroplot),
         Protocols = factor(Protocols),
         Visited = factor(Visited),
         MonStatus = factor(MonStatus),
         DateIn = as.Date(DateIn),
         DateIn_Year = as.numeric(DateIn_Year),
         SampleEventDate = as.Date(SampleEventDate),
         SampleEventDate_Year = as.numeric(SampleEventDate_Year),
         DisturbanceDate = as.Date(DisturbanceDate),
         DisturbanceDate_Year = as.numeric(DisturbanceDate_Year),
         Entry = as.factor(Entry),
         Macroplot_Num = as.factor(Macroplot_Num))
```

```{r}
graph_Disturbances <- graph_MetadataReport %>% 
  filter(is.na(Entry),
         !is.na(Disturbance_Type),
         Disturbance_Type == "Burn")

graph_sum_Disturbances <- graph_Disturbances %>% 
  group_by(Region, Zone, Unit, AdministrationUnit_Name, Type, DisturbanceDate, DisturbanceDate_Year, SampleEventDate_Year, MonStatus, Disturbance_Type) %>% 
  filter(DisturbanceDate_Year == SampleEventDate_Year) %>% 
  summarize(n_Macroplot = n()) %>% 
  mutate(DisturbanceDate = as.Date(DisturbanceDate),
         Macroplot_Num = "Disturbances")
```

### All FMH

```{r}
graph_sum_Disturbances %>% 
  filter(AdministrationUnit_Name == "RICH") %>% 
  ggplot(aes(x = DisturbanceDate, y = Disturbance_Type)) +
  geom_line(aes(group = Disturbance_Type)) +
  geom_point(aes(fill = Disturbance_Type), shape = 21) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  #geom_text(size = 4) +
  #geom_label_repel(aes(size = 4)) +
  labs(title = "Disturbance History",
       y = "Park",
       x = "Year",
       fill = "Disturbance Type") +
  #scale_fill_manual(values=c('yellowgreen', "yellow", 'orange', "red", "darkred","grey")) +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 8),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))

```

```{r}
graph_Disturbances %>% 
  ggplot(aes(x = DisturbanceDate_Year, y = Macroplot_Num)) +
  geom_line(aes(group = DisturbanceDate_Year), color = "grey") +
  geom_point(aes(color = Disturbance_Type)) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Disturbance History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Disturbance Type") +
  #scale_color_manual(values=c("darkred", "blue", "black", "green")) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))

```

```{r}
graph_MetadataReport %>% 
  filter(!is.na(Entry),
         AdministrationUnit_Name == "RICH") %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num)) +
  geom_point(aes(color = Entry), size = 2) +
  geom_point(aes(X = DisturbanceDate, y = Macroplot_Num, 
                 fill = Disturbance_Type), 
             data = graph_sum_Disturbances %>% 
               filter(AdministrationUnit_Name == "RICH"),
             shape = 21) +
  geom_line(aes(group = Macroplot_Num, color = Entry)) +
  geom_line(aes(group = Macroplot_Num), 
            data = graph_sum_Disturbances %>% 
              filter(AdministrationUnit_Name == "RICH"), 
            color = "black") +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Sample Event History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry",
       fill = "Disturbance Type") +
  scale_fill_manual(values = c("red", "green", "black", "purple")) +
  #scale_color_manual(values=c('forestgreen',"lightgreen","lightyellow", "yellow", "orange", 'darkorange', "red","red3", "darkred","darkgrey", "black")) +
  theme_light() +
  scale_x_continuous(breaks = seq(1995, 2030, by = 1)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))
```

### South Zone

```{r}
graph_MetadataReport %>% 
  filter(Zone == "South", !is.na(Entry)) %>%
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_line(aes(group = DisturbanceDate_Year), data = graph_Disturbances, color = "red") +
  geom_point(size = 2) +
  geom_line(aes(group = Macroplot)) +
  geom_point(data = graph_Disturbances, color = "red", shape = 1, size = 2) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Sample Event History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  scale_color_manual(values=c('forestgreen',"lightgreen","lightyellow", "yellow", "orange", 'darkorange', "red","red3", "darkred","darkgrey", "black")) +
  theme_light() +
  scale_x_continuous(breaks = seq(1995, 2030, by = 1)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))

#ggsave(path = path_graphs, filename = "Sample Event History_All WACA.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

### National Capital Area

```{r}
graph_MetadataReport %>% 
  filter(Zone == "NCA", !is.na(Entry)) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_point() +
  geom_line(aes(group = Macroplot)) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Sample Event History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  #scale_color_manual(values=c('forestgreen',"lightgreen","lightyellow", "yellow", "orange", 'darkorange', "red","red3", "darkred","darkgrey", "black")) +
  theme_light() +
  scale_x_continuous(breaks = seq(1995, 2030, by = 1)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))

#ggsave(path = path_graphs, filename = "Sample Event History_All WACA.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```

### North Zone

```{r}
graph_MetadataReport %>% 
  filter(Zone == "North", !is.na(Entry)) %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Macroplot_Num, color = Entry)) +
  geom_point() +
  geom_line(aes(group = Macroplot)) +
  facet_grid(Type ~ AdministrationUnit_Name) +
  labs(title = paste0("Sample Event History"),
       subtitle = "Fire Monitoring Handbook (FMH) Plots",
       y = "Plot Number",
       x = "Year",
       color = "Entry") +
  #scale_color_manual(values=c('forestgreen',"lightgreen","lightyellow", "yellow", "orange", 'darkorange', "red","red3", "darkred","darkgrey", "black")) +
  theme_light() +
  scale_x_continuous(breaks = seq(1995, 2030, by = 1)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 5),
        axis.text.x = element_text(size = 5, angle = 90, vjust = 0.5, hjust=1))

#ggsave(path = path_graphs, filename = "Sample Event History_All WACA.jpg", width = 8, height = 6, unit = "in", dpi = 300)
```
