---
title: Clean and Merge FFI Data
author: Alexandra Lalor
output:
  word_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# PURPOSE

This code is intended to combine data depot exports from multiple parks into a single file.

## BEFORE STARTING {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
```

```{r}
## Load Packages

# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
library(stringr)
```

### Target Parks

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
```

### Adjust File Paths {.hidden}

```{r}
# adjust file paths
#path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_main_data <- paste0(path_main, "Exports/DataDepot/")
path_main_save <- paste0(path_main, "Exports_Clean/DataDepot/")
```

# Metadata

## project_units

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "project_units"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))
  
  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # add column
    add_column(AdminUnit_Name = target_park, .before = "ProjectUnit_Name")
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%  
    filter(ProjectUnit_Name != "ALL") %>% 
  # final column selections
    select(!c(AdminUnitId, ProjectUnitId, MonitoringStatusId, SampleEventId,
              ProjectUnit_Grid, ProjectUnit_CreateCode))
  
  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # add column
    add_column(AdminUnit_Name = target_park, .before = "ProjectUnit_Name")
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%  
    filter(ProjectUnit_Name != "ALL") %>% 
  # final column selections
    select(!c(AdminUnitId, ProjectUnitId, MonitoringStatusId, SampleEventId,
              ProjectUnit_Grid, ProjectUnit_CreateCode))
  
  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## species_info

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "species_info"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))
  
  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
    ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%  
    dplyr::rename(AdminUnit_Name = Species_AdminUnitName) %>% 
  # final column selections
    select(!c(AdminUnitId, Species_Id, Species_MasterSpeciesId,
              Species_AuxSpeciesId, Species_LocalSpeciesId))
  
  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%  
    dplyr::rename(AdminUnit_Name = Species_AdminUnitName) %>% 
  # final column selections
    select(!c(AdminUnitId, Species_Id, Species_MasterSpeciesId,
              Species_AuxSpeciesId, Species_LocalSpeciesId))
  
  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

# Cover

## cover_frequency

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "cover_frequency"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}
  
  # # final column renaming to match protocol exports
  # final_df <- final_df %>%
  #   # relocate columns
  #     relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
  #     relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
  #     relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
  #   # rename columns
  #   dplyr::rename(
  #     Macroplot_Lat_dd = Macroplot_DdLat,
  #     Macroplot_Long_dd = Macroplot_DdLong,
  #     Macroplot_UtmX_m = Macroplot_UtmX..m.,
  #     Macroplot_UtmY_m = Macroplot_UtmY..m.,
  #     Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
  #     Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
  # 
  #     MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
  # 
  #     MethodData_NumTran = MethodData_NumTran..num..,
  #     MethodData_TranLen_m = MethodData_TranLen..m.,
  #     MethodData_QuadLen_cm = MethodData_QuadLen..cm.,
  #     MethodData_QuadWid_cm = MethodData_QuadWid..cm.,
  #     MethodData_Transect = MethodData_Transect..num..,
  #     MethodData_Quadrat = MethodData_Quadrat..num..,
  #     MethodData_Status = MethodData_Status..num..,
  #     MethodData_NRF = MethodData_NRF..num..,
  #     MethodData_Cover_pct = MethodData_Cover....,
  #     MethodData_Height_m = MethodData_Height..m.
  #   ) %>%
  #   # final column selections
  #   select(!c(OrganizationId, AdminUnitId, MacroplotId,
  #             SampleEventId, MethodId, MethodDataId,
  #             MethodData_Id, MethodData_SpeciesId,
  #             MethodData_SppGuid, MethodData_LocalSpeciesId,
  #             Species_SourceEntityId, Species_LocalSpeciesId,
  #             Species_MasterSpeciesId, Species_AuxSpeciesId
  #             ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## cover_line_intercept

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "cover_line_intercept"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>%
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>%
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>%
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,

      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,

      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_TranLen_m = MethodData_TranLen..m.,
      MethodData_SubFrac = MethodData_SubFrac..num..,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_Status = MethodData_Status..num..,
      MethodData_NRF = MethodData_NRF..num..,
      MethodData_Cover_pct = MethodData_Cover....,
      MethodData_Height_m = MethodData_Height..m.,
      MethodData_Start_m = MethodData_Start..m.,
      MethodData_Stop_m = MethodData_Stop..m.,
      MethodData_SizeCl = MethodData_SizeCl..num..
    ) %>%
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId,
              SampleEventId, MethodId, MethodDataId,
              MethodData_Id, MethodData_SpeciesId,
              MethodData_SppGuid, MethodData_LocalSpeciesId,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## cover_points

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "cover_points"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
      relocate(MethodData_CanopyLayer, .before = MethodData_Cover) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_TranLen_m = MethodData_TranLen..m.,
      MethodData_NumPtsTran = MethodData_NumPtsTran..num..,
      MethodData_Offset_m = MethodData_Offset..m.,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_Point = MethodData_Point..num..,
      MethodData_Tape_m = MethodData_Tape..num..,
      MethodData_Order = MethodData_Order..num..,
      MethodData_Height_m = MethodData_Height..m.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id, MethodData_SpeciesId, 
              MethodData_SppGuid, MethodData_LocalSpeciesId,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
      relocate(MethodData_CanopyLayer, .before = MethodData_Cover) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_TranLen_ft = MethodData_TranLen..ft.,
      MethodData_NumPtsTran = MethodData_NumPtsTran..num..,
      MethodData_Offset_ft = MethodData_Offset..ft.,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_Point = MethodData_Point..num..,
      MethodData_Tape_ft = MethodData_Tape..num..,
      MethodData_Order = MethodData_Order..num..,
      MethodData_Height_ft = MethodData_Height..ft.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id, MethodData_SpeciesId, 
              MethodData_SppGuid, MethodData_LocalSpeciesId,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## cover_species_composition

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "cover_species_composition"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_MinCovLevel_pct = MethodData_MinCovLevel....,
      MethodData_Area_ha = MethodData_Area..ha.,
      MethodData_Status = MethodData_Status..num..,
      MethodData_SizeCl = MethodData_SizeCl..num..,
      MethodData_Height_m = MethodData_Height..m.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id, MethodData_SpeciesId, 
              MethodData_SppGuid, MethodData_LocalSpeciesId,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_MinCovLevel_pct = MethodData_MinCovLevel....,
      MethodData_Area_ac = MethodData_Area..ac..,
      MethodData_Status = MethodData_Status..num..,
      MethodData_SizeCl = MethodData_SizeCl..num..,
      MethodData_Height_ft = MethodData_Height..ft.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id, MethodData_SpeciesId, 
              MethodData_SppGuid, MethodData_LocalSpeciesId,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

# Surface Fuels

## surface_fuels_alaska_duff_litter

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_alaska_duff_litter"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_SampLoc_m = MethodData_SampLoc..m.,
      MethodData_LittDep_cm = MethodData_LittDep..cm.,
      MethodData_LiveMoss_cm = MethodData_LiveMoss..cm.,
      MethodData_DeadMoss_cm = MethodData_DeadMoss..cm.,
      MethodData_UppDuffDep_cm = MethodData_UppDuffDep..cm.,
      MethodData_LowDuffDep_cm = MethodData_LowDuffDep..cm.,
      MethodData_LichDep_cm = MethodData_LichDep..cm.,
      MethodData_FuelBedDep_cm = MethodData_FuelBedDep..cm.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_SampLoc_ft = MethodData_SampLoc..ft.,
      MethodData_LittDep_in = MethodData_LittDep..in.,
      MethodData_LiveMoss_in = MethodData_LiveMoss..in.,
      MethodData_DeadMoss_in = MethodData_DeadMoss..in.,
      MethodData_UppDuffDep_in = MethodData_UppDuffDep..in.,
      MethodData_LowDuffDep_in = MethodData_LowDuffDep..in.,
      MethodData_LichDep_in = MethodData_LichDep..in.,
      MethodData_FuelBedDep_in = MethodData_FuelBedDep..in.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_duff_litter

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_duff_litter"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_SampLoc_m = MethodData_SampLoc..m.,
      MethodData_LittDep_cm = MethodData_LittDep..cm.,
      MethodData_DuffDep_cm = MethodData_DuffDep..cm.,
      MethodData_FuelBedDep_cm = MethodData_FuelbedDep..cm.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_SampLoc_ft = MethodData_SampLoc..ft.,
      MethodData_LittDep_in = MethodData_LittDep..in.,
      MethodData_DuffDep_in = MethodData_DuffDep..in.,
      MethodData_FuelBedDep_in = MethodData_FuelbedDep..in.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_fine

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_fine"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_OneHrTranLen_m = MethodData_OneHrTranLen..m.,
      MethodData_TenHrTranLen_m = MethodData_TenHrTranLen..m.,
      MethodData_HunHrTranLen_m = MethodData_HunHrTranLen..m.,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_Azimuth_deg = MethodData_Azimuth....,
      MethodData_Slope_pct = MethodData_Slope....
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_OneHrTranLen_ft = MethodData_OneHrTranLen..ft.,
      MethodData_TenHrTranLen_ft = MethodData_TenHrTranLen..ft.,
      MethodData_HunHrTranLen_ft = MethodData_HunHrTranLen..ft.,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_Azimuth_deg = MethodData_Azimuth....,
      MethodData_Slope_pct = MethodData_Slope....
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_piles

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_piles"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_PlotDensity_ha = MethodData_plotDensity..ha..,
      MethodData_PileNum = MethodData_PileNum..num..,
      MethodData_Width1_m = MethodData_Width1..m.,
      MethodData_Width2_m = MethodData_Width2..m.,
      MethodData_Length1_m = MethodData_Length1..m.,
      MethodData_Length2_m = MethodData_Length2..m.,
      MethodData_Height1_m = MethodData_Height1..m.,
      MethodData_Height2_m = MethodData_Height2..m.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_PlotDensity_ac = MethodData_plotDensity..ac..,
      MethodData_PileNum = MethodData_PileNum..num..,
      MethodData_Width1_ft = MethodData_Width1..ft.,
      MethodData_Width2_ft = MethodData_Width2..ft.,
      MethodData_Length1_ft = MethodData_Length1..ft.,
      MethodData_Length2_ft = MethodData_Length2..ft.,
      MethodData_Height1_ft = MethodData_Height1..ft.,
      MethodData_Height2_ft = MethodData_Height2..ft.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_thousand_hr

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_thousand_hr"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_TranLen_m = MethodData_TranLen..m.,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_Slope_pct = MethodData_Slope....,
      MethodData_LogNum = MethodData_LogNum..num..,
      MethodData_Dia_cm = MethodData_Dia..cm.,
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_TranLen_ft = MethodData_TranLen..ft.,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_Slope_pct = MethodData_Slope....,
      MethodData_LogNum = MethodData_LogNum..num..,
      MethodData_Dia_in = MethodData_Dia..in.,
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_vegetation

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_vegetation"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) 
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_SampLoc_m = MethodData_SampLoc..m.,
      MethodData_Cover_pct = MethodData_Cover....,
      MethodData_Height_m = MethodData_Height..m.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_SampLoc_ft = MethodData_SampLoc..ft.,
      MethodData_Cover_pct = MethodData_Cover....,
      MethodData_Height_ft = MethodData_Height..ft.
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

# Trees

## trees_individuals

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "trees_individuals"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_MacroPlotSize_ha = MethodData_MacroPlotSize..ha.,
      MethodData_SnagPlotSize_ha = MethodData_SnagPlotSize..ha.,
      MethodData_BrkPntDia_cm = MethodData_BrkPntDia..cm.,
      MethodData_QTR = MethodData_QTR..num..,
      MethodData_SubFrac = MethodData_SubFrac..num..,
      MethodData_TagNo = MethodData_TagNo..num..,
      MethodData_DBH_cm = MethodData_DBH..cm.,
      MethodData_Ht_m = MethodData_Ht..m.,
      MethodData_CrwnRto_pct = MethodData_CrwnRto....,
      MethodData_CrFuBHt_m = MethodData_CrFuBHt..m.,
      MethodData_LiCrBHt_m = MethodData_LiCrBHt..m.,
      MethodData_CrwnRad_m = MethodData_CrwnRad..m.,
      MethodData_Age = MethodData_Age..yrs.,
      MethodData_GrwthRt_cm = MethodData_GrwthRt..cm.,
      MethodData_LaddBaseHt_m = MethodData_LaddBaseHt..m.,
      MethodData_LaddMaxHt_m = MethodData_LaddMaxHt..m.,
      MethodData_DRC_cm = MethodData_DRC..cm.,
      MethodData_EqDia_cm = MethodData_EqDia..cm.,
      MethodData_XCoord_m = MethodData_XCoord..m.,
      MethodData_YCoord_m = MethodData_YCoord..m.,
      MethodData_CharHt_m = MethodData_CharHt..m.,
      MethodData_ScorchHt_m = MethodData_ScorchHt..m.,
      MethodData_CrScPct_pct = MethodData_CrScPct....,
      MethodData_DamSev1 = MethodData_DamSev1..num..,
      MethodData_DamSev2 = MethodData_DamSev2..num..,
      MethodData_DamSev3 = MethodData_DamSev3..num..,
      MethodData_DamSev4 = MethodData_DamSev4..num..,
      MethodData_DamSev5 = MethodData_DamSev5..num..
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id,
              MethodData_SppGuid,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_MacroPlotSize_ac = MethodData_MacroPlotSize..ac..,
      MethodData_SnagPlotSize_ac = MethodData_SnagPlotSize..ac..,
      MethodData_BrkPntDia_in = MethodData_BrkPntDia..in.,
      MethodData_QTR = MethodData_QTR..num..,
      MethodData_SubFrac = MethodData_SubFrac..num..,
      MethodData_TagNo = MethodData_TagNo..num..,
      MethodData_DBH_in = MethodData_DBH..in.,
      MethodData_Ht_ft = MethodData_Ht..ft.,
      MethodData_CrwnRto_pct = MethodData_CrwnRto....,
      MethodData_CrFuBHt_ft = MethodData_CrFuBHt..ft.,
      MethodData_LiCrBHt_ft = MethodData_LiCrBHt..ft.,
      MethodData_CrwnRad_ft = MethodData_CrwnRad..ft.,
      MethodData_Age = MethodData_Age..yrs.,
      MethodData_GrwthRt_in = MethodData_GrwthRt..in.,
      MethodData_LaddBaseHt_ft = MethodData_LaddBaseHt..ft.,
      MethodData_LaddMaxHt_ft = MethodData_LaddMaxHt..ft.,
      MethodData_DRC_in = MethodData_DRC..in.,
      MethodData_EqDia_in = MethodData_EqDia..in.,
      MethodData_XCoord_ft = MethodData_XCoord..ft.,
      MethodData_YCoord_ft = MethodData_YCoord..ft.,
      MethodData_CharHt_ft = MethodData_CharHt..ft.,
      MethodData_ScorchHt_ft = MethodData_ScorchHt..ft.,
      MethodData_CrScPct_pct = MethodData_CrScPct....,
      MethodData_DamSev1 = MethodData_DamSev1..num..,
      MethodData_DamSev2 = MethodData_DamSev2..num..,
      MethodData_DamSev3 = MethodData_DamSev3..num..,
      MethodData_DamSev4 = MethodData_DamSev4..num..,
      MethodData_DamSev5 = MethodData_DamSev5..num..
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id,
              MethodData_SppGuid,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## trees_saplings

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "trees_saplings"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_MacroPlotSize_ha = MethodData_MacroPlotSize..ha..,
      MethodData_SizeClDia_cm = MethodData_SizeClDia..cm.,
      MethodData_AvgHt_m = MethodData_AvgHt..m.,
      MethodData_AvgCrwnRto_pct = MethodData_AvgCrwnRto....,
      MethodData_SubFrac = MethodData_SubFrac..num..,
      
      MethodData_UV1 = MethodData_Record_UV1,
      MethodData_UV2 = MethodData_Record_UV2,
      MethodData_UV3 = MethodData_Record_UV3
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id,
              MethodData_SppGuid,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_MacroPlotSize_ac = MethodData_MacroPlotSize..ac..,
      MethodData_SizeClDia_in = MethodData_SizeClDia..in.,
      MethodData_AvgHt_ft = MethodData_AvgHt..ft.,
      MethodData_AvgCrwnRto_pct = MethodData_AvgCrwnRto....,
      MethodData_SubFrac = MethodData_SubFrac..num..,
      
      MethodData_UV1 = MethodData_Record_UV1,
      MethodData_UV2 = MethodData_Record_UV2,
      MethodData_UV3 = MethodData_Record_UV3
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id,
              MethodData_SppGuid,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## trees_seedlings

```{r warning=FALSE}
#############
## METRIC  ##
#############

protocol <- "trees_seedlings"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_MacroPlotSize_ha = MethodData_MacroPlotSize,
      MethodData_SizeClHt_m = MethodData_SizeClHt..m.,
      MethodData_SubFrac = MethodData_SubFrac..num..,
      MethodData_AvgDia_cm = MethodData_AvgDia..cm.,
      MethodData_AvgCrwnRto_pct = MethodData_AvgCrwnRto....
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id,
              MethodData_SppGuid,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    # relocate columns
      relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
      relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
      relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint) %>% 
    # rename columns
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_MacroPlotSize_ac = MethodData_MacroPlotSize,
      MethodData_SizeClHt_ft = MethodData_SizeClHt..ft.,
      MethodData_SubFrac = MethodData_SubFrac..num..,
      MethodData_AvgDia_in = MethodData_AvgDia..in.,
      MethodData_AvgCrwnRto_pct = MethodData_AvgCrwnRto....
    ) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id,
              MethodData_SppGuid,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```
