---
title: Merge FFI Data
author: Alexandra Lalor
output:
  word_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# PURPOSE

This code is intended to combine data depot exports from multiple parks into a single files.

## BEFORE STARTING {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
```

```{r}
## Load Packages

# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
library(stringr)
```

### Adjust File Paths {.hidden}

```{r}
# adjust file paths
#path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_main_data <- paste0(path_main, "Exports Data Depot/")
path_main_save <- paste0(path_main, "R Outputs Data Depot/Data Depot/")
```

### Parks

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
```

# Metadata

## project_units

```{r}
#############
## METRIC  ##
#############

protocol <- "project_units"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))
  
  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # add column
    add_column(AdminUnit_Name = target_park, .before = "ProjectUnit_Name")
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%  
    dplyr::rename(
      MonStatus_Name = MonitoringStatus_Name,
      MonStatus_Prefix = MonitoringStatus_Prefix,
      MonStatus_Base = MonitoringStatus_Base,
      MonStatus_Suffix = MonitoringStatus_Suffix,
      MonStatus_Order = MonitoringStatus_Order,
      MonStatus_Comment = MonitoringStatus_Comment
    ) %>% 
  # final column selections
    #filter(ProjectUnit_Name != "ALL") %>% 
    select(!c(AdminUnitId, ProjectUnitId, MonitoringStatusId, SampleEventId,
              ProjectUnit_Grid, ProjectUnit_CreateCode))
  
  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # add column
    add_column(AdminUnit_Name = target_park, .before = "ProjectUnit_Name")
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%  
    dplyr::rename(
      MonStatus_Name = MonitoringStatus_Name,
      MonStatus_Prefix = MonitoringStatus_Prefix,
      MonStatus_Base = MonitoringStatus_Base,
      MonStatus_Suffix = MonitoringStatus_Suffix,
      MonStatus_Order = MonitoringStatus_Order,
      MonStatus_Comment = MonitoringStatus_Comment
    ) %>% 
  # final column selections
    #filter(ProjectUnit_Name != "ALL") %>% 
    select(!c(AdminUnitId, ProjectUnitId, MonitoringStatusId, SampleEventId,
              ProjectUnit_Grid, ProjectUnit_CreateCode))
  
  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## species_info

```{r}
#############
## METRIC  ##
#############

protocol <- "species_info"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))
  
  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
    ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%  
    dplyr::rename(
      AdminUnit_Name = Species_AdminUnitName,
      Species_ITIS_TSN = Species_ITISTaxonomicSerialNumber
    )

  # final column selections
  final_df <- final_df %>% 
    select(!c(AdminUnitId, Species_Id, Species_MasterSpeciesId,
              Species_AuxSpeciesId, Species_LocalSpeciesId))
  
  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .)))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%  
    dplyr::rename(
      AdminUnit_Name = Species_AdminUnitName,
      Species_ITIS_TSN = Species_ITISTaxonomicSerialNumber
    )

  # final column selections
  final_df <- final_df %>% 
    select(!c(AdminUnitId, Species_Id, Species_MasterSpeciesId,
              Species_AuxSpeciesId, Species_LocalSpeciesId))
  
  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

# Cover

## cover_frequency

```{r}
#############
## METRIC  ##
#############

protocol <- "cover_frequency"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}
  
  # # final column renaming to match protocol exports
  # final_df <- final_df %>%
  #   dplyr::rename(
  #     Macroplot_Lat_dd = Macroplot_DdLat,
  #     Macroplot_Long_dd = Macroplot_DdLong,
  #     Macroplot_UtmX_m = Macroplot_UtmX..m.,
  #     Macroplot_UtmY_m = Macroplot_UtmY..m.,
  #     Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
  #     Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
  #
  #     SampleEvent_LegacyMonStatus = SampleEvent_LegacyMonitoringStatus,
  #     Species_ITIS_TSN = Species_ITISTaxonomicSerialNumber,
  #     MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
  # 
  #     MethodData_NumTran = MethodData_NumTran..num..,
  #     MethodData_TranLen_m = MethodData_TranLen..m.,
  #     MethodData_QuadLen_cm = MethodData_QuadLen..cm.,
  #     MethodData_QuadWid_cm = MethodData_QuadWid..cm.,
  #     MethodData_Transect = MethodData_Transect..num..,
  #     MethodData_Quadrat = MethodData_Quadrat..num..,
  #     MethodData_Status = MethodData_Status..num..,
  #     MethodData_NRF = MethodData_NRF..num..,
  #     MethodData_Cover_pct = MethodData_Cover....,
  #     MethodData_Height_m = MethodData_Height..m.
  #   ) %>%
  #   # final column selections
  #   select(!c(OrganizationId, AdminUnitId, MacroplotId,
  #             SampleEventId, MethodId, MethodDataId,
  #             MethodData_Id, MethodData_SpeciesId,
  #             MethodData_SppGuid, MethodData_LocalSpeciesId,
  #             Species_SourceEntityId, Species_LocalSpeciesId,
  #             Species_MasterSpeciesId, Species_AuxSpeciesId
  #             ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## cover_line_intercept

```{r}
#############
## METRIC  ##
#############

protocol <- "cover_line_intercept"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # # final column renaming to match protocol exports
  # final_df <- final_df %>%
  #   dplyr::rename(
  #     Macroplot_Lat_dd = Macroplot_DdLat,
  #     Macroplot_Long_dd = Macroplot_DdLong,
  #     Macroplot_UtmX_m = Macroplot_UtmX..m.,
  #     Macroplot_UtmY_m = Macroplot_UtmY..m.,
  #     Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
  #     Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
  #
  #     SampleEvent_LegacyMonStatus = SampleEvent_LegacyMonitoringStatus,
  #     Species_ITIS_TSN = Species_ITISTaxonomicSerialNumber,
  #     MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
  # 
  #     MethodData_NumTran = MethodData_NumTran..num..,
  #     MethodData_TranLen_m = MethodData_TranLen..m.,
  #     MethodData_SubFrac = MethodData_SubFrac..num..,
  #     MethodData_Transect = MethodData_Transect..num..,
  #     MethodData_Status = MethodData_Status..num..,
  #     MethodData_NRF = MethodData_NRF..num..,
  #     MethodData_Cover_pct = MethodData_Cover....,
  #     MethodData_Height_m = MethodData_Height..m.,
  #     MethodData_Start_m = MethodData_Start..m.,
  #     MethodData_Stop_m = MethodData_Stop..m.,
  #     MethodData_SizeCl = MethodData_SizeCl..num..
  #   ) %>%
  #   # final column selections
  #   select(!c(OrganizationId, AdminUnitId, MacroplotId, 
  #             SampleEventId, MethodId, MethodDataId, 
  #             MethodData_Id, MethodData_SpeciesId, 
  #             MethodData_SppGuid, MethodData_LocalSpeciesId,
  #             Species_SourceEntityId, Species_LocalSpeciesId,
  #             Species_MasterSpeciesId, Species_AuxSpeciesId
  #             ))

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## cover_points

```{r}
#############
## METRIC  ##
#############

protocol <- "cover_points"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      SampleEvent_LegacyMonStatus = SampleEvent_LegacyMonitoringStatus,
      Species_ITIS_TSN = Species_ITISTaxonomicSerialNumber,
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_TranLen_m = MethodData_TranLen..m.,
      MethodData_NumPtsTran = MethodData_NumPtsTran..num..,
      MethodData_Offset_m = MethodData_Offset..m.,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_Point = MethodData_Point..num..,
      MethodData_Tape_m = MethodData_Tape..num..,
      MethodData_Order = MethodData_Order..num..,
      MethodData_Height_m = MethodData_Height..m.
    ) %>% 
    relocate(MethodData_CanopyLayer, .before = MethodData_Cover) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id, MethodData_SpeciesId, 
              MethodData_SppGuid, MethodData_LocalSpeciesId,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # final column renaming to match protocol exports
  final_df <- final_df %>%
    dplyr::rename(
      Macroplot_Lat_dd = Macroplot_DdLat,
      Macroplot_Long_dd = Macroplot_DdLong,
      Macroplot_UtmX_m = Macroplot_UtmX..m.,
      Macroplot_UtmY_m = Macroplot_UtmY..m.,
      Macroplot_SlopeHill_pct = Macroplot_SlopeHill....,
      Macroplot_SlopeTransect_pct = Macroplot_SlopeTransect....,
      
      SampleEvent_LegacyMonStatus = SampleEvent_LegacyMonitoringStatus,
      Species_ITIS_TSN = Species_ITISTaxonomicSerialNumber,
      MethodData_LocalSpeciesSymbol = MethodData_RemoteApp_LocalSpeciesSymbol,
      
      MethodData_NumTran = MethodData_NumTran..num..,
      MethodData_TranLen_ft = MethodData_TranLen..ft.,
      MethodData_NumPtsTran = MethodData_NumPtsTran..num..,
      MethodData_Offset_ft = MethodData_Offset..ft.,
      MethodData_Transect = MethodData_Transect..num..,
      MethodData_Point = MethodData_Point..num..,
      MethodData_Tape_ft = MethodData_Tape..num..,
      MethodData_Order = MethodData_Order..num..,
      MethodData_Height_ft = MethodData_Height..ft.
    ) %>% 
    relocate(MethodData_CanopyLayer, .before = MethodData_Cover) %>% 
    # final column selections
    select(!c(OrganizationId, AdminUnitId, MacroplotId, 
              SampleEventId, MethodId, MethodDataId, 
              MethodData_Id, MethodData_SpeciesId, 
              MethodData_SppGuid, MethodData_LocalSpeciesId,
              Species_SourceEntityId, Species_LocalSpeciesId,
              Species_MasterSpeciesId, Species_AuxSpeciesId
              ))
  
  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## cover_species_composition

```{r}
#############
## METRIC  ##
#############

protocol <- "cover_species_composition"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

# Surface Fuels

## surface_fuels_alaska_duff_litter

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_alaska_duff_litter"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_duff_litter

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_duff_litter"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_fine

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_fine"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_piles

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_piles"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_thousand_hr

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_thousand_hr"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_vegetation

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_vegetation"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>%  
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

# Trees

## trees_individuals

```{r}
#############
## METRIC  ##
#############

protocol <- "trees_individuals"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## trees_saplings

```{r}
#############
## METRIC  ##
#############

protocol <- "trees_saplings"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## trees_seedlings

```{r}
#############
## METRIC  ##
#############

protocol <- "trees_seedlings"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"), na.strings = c("","NA","N/A"))

  
  # clean data
  temp_df <- temp_df %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    # remove line breaks
    mutate(across(where(is.character), ~ gsub("[\r\n]+", " ", .))) %>% 
    # relocate columns
    relocate(Macroplot_Datum, .after = Macroplot_UtmZone) %>% 
    relocate(Macroplot_FutureVisit, .after = Macroplot_DateOut) %>% 
    # reformate Date columns
    mutate(
      Macroplot_DateIn = as.Date(Macroplot_DateIn, "%m/%d/%Y"),
      Macroplot_FutureVisit = as.Date(Macroplot_FutureVisit, "%m/%d/%Y"),
      Macroplot_DateOut = as.Date(Macroplot_DateOut, "%m/%d/%Y"),
      SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")
      ) %>%
    # add Year columns
    mutate(
      Macroplot_DateIn_Year = year(Macroplot_DateIn),
      Macroplot_FutureVisit_Year = year(Macroplot_FutureVisit),
      Macroplot_DateOut_Year = year(Macroplot_DateOut),
      SampleEvent_Date_Year = year(SampleEvent_Date)
    ) %>% 
    # relocate Year columns
    relocate(Macroplot_DateIn_Year, .after = Macroplot_DateIn) %>% 
    relocate(Macroplot_FutureVisit_Year, .after = Macroplot_FutureVisit) %>% 
    relocate(Macroplot_DateOut_Year, .after = Macroplot_DateOut) %>%
    relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    relocate(Macroplot_LocatedBy, .before = Macroplot_StartPoint)
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```
