---
title: Merge FFI Data
author: Alexandra Lalor
output:
  word_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# PURPOSE

This code is intended to combine data depot exports from multiple parks into a single files.

## BEFORE STARTING {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
```

```{r}
## Load Packages

# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
library(stringr)
```

### Adjust File Paths {.hidden}

```{r}
# adjust file paths
path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
#path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_main_data <- paste0(path_main, "Exports Data Depot/")
path_main_save <- paste0(path_main, "R Outputs Data Depot/ALL/")
```

### Parks

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
```

# Metadata

## project_units

```{r}
#############
## METRIC  ##
#############

protocol <- "project_units"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))
  
  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    add_column(AdminUnit_Name = target_park, .before = "ProjectUnit_Name")
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>% 
    add_column(AdminUnit_Name = target_park, .before = "ProjectUnit_Name")
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

# Cover

## cover_frequency

```{r}
#############
## METRIC  ##
#############

protocol <- "cover_frequency"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## cover_line_intercept

```{r}
#############
## METRIC  ##
#############

protocol <- "cover_line_intercept"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## cover_points

```{r}
#############
## METRIC  ##
#############

protocol <- "cover_points"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## cover_species_composition

```{r}
#############
## METRIC  ##
#############

protocol <- "cover_species_composition"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

# Surface Fuels

## surface_fuels_alaska_duff_litter

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_alaska_duff_litter"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_duff_litter

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_duff_litter"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_fine

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_fine"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_piles

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_piles"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_thousand_hr

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_thousand_hr"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## surface_fuels_vegetation

```{r}
#############
## METRIC  ##
#############

protocol <- "surface_fuels_vegetation"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

# Trees

## trees_individuals

```{r}
#############
## METRIC  ##
#############

protocol <- "trees_individuals"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## trees_saplings

```{r}
#############
## METRIC  ##
#############

protocol <- "trees_saplings"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```

## trees_seedlings

```{r}
#############
## METRIC  ##
#############

protocol <- "trees_seedlings"

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/Metric_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "Metric/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)

#############################################################################################

#############
## ENGLISH ##
#############

final_df <- NULL
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main_data, target_park, "/English_ffi_", target_park, "_data_export/")
  path_save <- paste0(path_main_save, "English/")
  
  
  # load data
  temp_df <- read.csv(paste0(path_data, "ffi_", target_park, "_data_export_", protocol, ".csv"))

  
  # clean data
  temp_df <- temp_df %>%
  # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim))
  ## replace commas with semicolons
  temp_df[] <- lapply(temp_df, function(x) gsub(",", ";", x))
  ## replace double quotes with single quotes
  temp_df[] <- lapply(temp_df, function(x) gsub('"', "'", x))
  
  
  # add data to master list
  final_df <- rbind(final_df, temp_df)
}

  # save file
write.csv(final_df, paste0(path_save, "data_", protocol, ".csv"), quote = FALSE, row.names = FALSE)
```
