---
title: Complete CSVs
author: Alexandra Lalor
output:
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 1
    toc_float:
      smooth_scroll: true
    code_download: true
  word_document:
    toc: true
    toc_depth: 1
  pdf_document:
    toc: true
    toc_depth: 1
---

# PURPOSE

This code is intended to quality check [all Data Depot CSV exports]{.underline} for fundamental errors.

### Export all CSVs from Data Depot

-   English_ffi_PARK_data_export\_#############.zip

-   Metric_ffi_PARK_data_export\_#############.zip

Populated Data includes:

-   ffi_PARK_data_export_project_units.csv

-   ffi_PARK_data_export_cover_points.csv

-   ffi_PARK_data_export_cover_species_composition.csv

-   ffi_PARK_data_export_surface_fuels_duff_litter.csv

-   ffi_PARK_data_export_surface_fuels_fine.csv

-   ffi_PARK_data_export_surface_fuels_thousand_hr.csv

-   ffi_PARK_data_export_trees_individuals.csv

Excess Data includes:

-   ffi_PARK_data_export_cover_frequency.csv

-   ffi_PARK_data_export_surface_fuels_alaska_duff_litter.csv

-   ffi_PARK_data_export_surface_fuels_piles.csv

-   ffi_PARK_data_export_surface_fuels_vegetation.csv

-   ffi_PARK_data_export_trees_saplings.csv

-   ffi_PARK_data_export_trees_seedlings.csv

Missing Protocols

-   Post Burn Severity (metric)\_XPT.csv

-   Density - Quadrats (metric)\_XPT.csv

-   Density - Belts (metric)\_XPT.csv

## Before Starting {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r install packages, include=FALSE}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
## Load Packages

# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
library(readr)
# janitor has functions to find duplicates
library(janitor)
# diffdf will find differences between databases
library(diffdf)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr and LaTeX is used to create output files from R Markdown
library(knitr)
#library(LaTeX)
```

### Create Function {.hidden}

```{r}
# Create blank data frame as error log template
errors_blank <- data.frame("SavedQuery" = "", "AdminUnit_Name" = "", "Protocol" = "","Error" = "")

# Create error group. Duplicate errors will be grouped by these columns.
errors_group <- c("SavedQuery", "AdminUnit_Name", "Protocol", "Error")

############################################################################################
## Source Code
#Pull in source code that creates QAQC functions and builds an empty error table.
#source("C:/Users/allie/OneDrive/Desktop/R Projects/NER/scripts/1_QAQC/qaqc_function.R")


# QAQC function
qaqc <- function(data, query, query_message, values_check) {

  # Check if there is data to QAQC
  if(nrow(data) == 0) {
  # If there is no data, default to "No Error" data frame
  errors <- errors_blank %>%
    mutate("SavedQuery" = query,
           "Error" = "No Error")
  # If there is data, perform error check
} else {

  # Use relevant dataset to look for errors
  errors <- data %>%
    # Add columns relevant to error checking
           # Populate the "SavedQuery" column with the query name
    mutate("SavedQuery" = query,
           # Populate the "Error" column with the query message and relevant data
           "Error" = paste(query_message, "=", values_data),
           # Create a blank "Fixed" column
           "Fixed" = "",
           # Create a blank "Explanation" column
           "Explanation" = "",
           # Create a blank "Queryers" column
           "Queryers" = "") %>%
    # Filter for data which is "false" (data does not match valid conditions)
    # NA values are treated as "false" (missing data is not valid)
    filter(!(values_check %>% replace_na(FALSE))) %>%
    # Select relevant columns to view errors
    select(colnames(errors_blank))
  
  # Next, check if there are duplicate errors
  errors <- unique(errors)
}

  # Check if there are no errors
  if (nrow(errors) == 0) {
    # If there are no errors, default to "No Error" data frame
    errors <- errors_blank %>%
      mutate(SavedQuery = query,
             Error = "No Error")
    # If there are errors, keep error log you just created
  } else {
    errors <- errors
  }
}
```

### Target Park {.hidden}

```{r}
# designate target park(s)
target_park <- "FRSP"
```

### Adjust File Paths {.hidden}

```{r import data, include=FALSE}
# adjust file paths
#path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_file <- paste0(path_main, "Exports Data Depot/", target_park, "/")
path_data_english <- paste0(path_file, "English_ffi_", target_park, "_data_export/")
path_data_metric <- paste0(path_file, "Metric_ffi_", target_park, "_data_export/")
path_errors <- paste0(path_main, "QAQC/", target_park, "/")
path_errors_name <- paste0(target_park, " Data Depot Errors")
```

### Load Data {.hidden}

```{r}
# load data

# project unit report
ProjectUnitReport <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_project_units.csv"))
SpeciesReport <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_species_info.csv"))

# protocols
Fuels1000_all <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_surface_fuels_thousand_hr.csv"))
FuelsDuffLitt_all <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_surface_fuels_duff_litter.csv"))
FuelsFine_all <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_surface_fuels_fine.csv"))
Trees_all <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_trees_individuals.csv"))
HerbsSpComp_all <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_cover_species_composition.csv"))
HerbsPoints_all <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_cover_points.csv"))
HerbsFrequency_all <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_cover_frequency.csv"))
```

# Column Name List

```{r}
columns_ProjectUnit <- c("AdminUnitId", "ProjectUnitId", "MonitoringStatusId", "SampleEventId", "AdminUnit_Name","Protocol","ProjectUnit_Name", "ProjectUnit_Agency", "ProjectUnit_Area", "ProjectUnit_Grid", "ProjectUnit_AreaUnits", "ProjectUnit_DateIn", "ProjectUnit_DateOut", "ProjectUnit_Objective", "ProjectUnit_Description", "ProjectUnit_CreateCode", "ProjectUnit_Comment", "ProjectUnit_UserVariables", "MonitoringStatus_Name", "MonitoringStatus_Prefix", "MonitoringStatus_Base", "MonitoringStatus_Suffix", "MonitoringStatus_Order", "MonitoringStatus_Comment")

columns_SpeciesReport <- c("Species_Id","AdminUnitId","Species_MasterSpeciesId","Species_AuxSpeciesId","Species_LocalSpeciesId","AdminUnit_Name","Species_OrganizationName","Species_MasterOrUserLocal","Species_ITISTaxonomicSerialNumber","Species_SymbolLocal","Species_SymbolMaster","Species_ScientificName","Species_CommonName","Species_CommonNameLocal","Species_Genus","Species_Family","Species_NotBiological","Species_Nativity","Species_NativityLocal","Species_LifeFormName","Species_LifeFormNameLocal","Species_Description","Species_LifeCycleLocal","Species_LifeCycle","Species_UV1","Species_UV2","Species_UV3","Species_UserAdded","Species_Cultural","Species_Invasive","Species_Concern","Species_Retired","Species_Comment","Protocol")



columns_ID <- c("OrganizationId","AdminUnitId","MacroplotId","SampleEventId","MethodId","MethodDataId","MethodData_Id")

columns_Macroplot <- c("Organization_Name","AdminUnit_Name","Protocol","AdminUnit_Comment","Macroplot_Name","Macroplot_Purpose","Macroplot_LocatedBy","Macroplot_Type","Macroplot_DdLat","Macroplot_DdLong","Macroplot_UtmX (m)","Macroplot_UtmY (m)","Macroplot_UtmZone","Macroplot_Datum","Macroplot_Pdop","Macroplot_Precision","Macroplot_DateIn","Macroplot_DateOut","Macroplot_FutureVisit","Macroplot_Elevation","Macroplot_ElevationUnits","Macroplot_Azimuth","Macroplot_Aspect","Macroplot_SlopeHill (%)","Macroplot_SlopeTransect (%)","Macroplot_StartPoint","Macroplot_Directions","Macroplot_Comment","Macroplot_Metadata","Macroplot_UV1","Macroplot_UV2","Macroplot_UV3","Macroplot_UV4","Macroplot_UV5","Macroplot_UV6","Macroplot_UV7","Macroplot_UV8")

columns_SampleEvent <- c("SampleEvent_Date","SampleEvent_Who","SampleEvent_Comment","SampleEvent_UserVariables","SampleEvent_LegacyMonitoringStatus","SampleEvent_TreatmentUnit","SampleData_Executed")

columns_Species <- c("Species_SourceEntityId","Species_LocalSpeciesId","Species_MasterSpeciesId","Species_AuxSpeciesId","Species_ITISTaxonomicSerialNumber","Species_SymbolLocal","Species_SymbolMaster","Species_ScientificName","Species_CommonNameLocal","Species_CommonName","Species_Genus","Species_Family","Species_NotBiological","Species_Nativity","Species_NativityLocal","Species_Invasive","Species_LifeFormName","Species_LifeFormNameLocal","Species_Description","Species_LifeCycle","Species_LifeCycleLocal","Species_Cultural","Species_Concern","Species_Retired","Species_Comment","Species_UV1","Species_UV2","Species_UV3","MethodData_SpeciesId","MethodData_LocalSpeciesId","MethodData_RemoteApp_LocalSpeciesSymbol","MethodData_SppGuid")

columns_MethodData <- c("MethodData_Visited","MethodData_FieldTeam","MethodData_EntryTeam","MethodData_UV1Desc","MethodData_UV2Desc","MethodData_UV3Desc","MethodData_SAComment","MethodData_CreatedDate","MethodData_UpdatedDate","MethodData_DeletedDate","MethodData_Comment","MethodData_UV1","MethodData_UV2","MethodData_UV3","MethodData_Index")



columns_Fuels1000_M <- c("MethodData_NumTran (num.)","MethodData_TranLen (m)","MethodData_Transect (num.)","MethodData_Slope (%)","MethodData_LogNum (num.)","MethodData_Dia (cm)","MethodData_DecayCl","MethodData_CWDFuConSt")
columns_Fuels1000_E <- c("MethodData_NumTran (num.)","MethodData_TranLen (ft)","MethodData_Transect (num.)","MethodData_Slope (%)","MethodData_LogNum (num.)","MethodData_Dia (in)","MethodData_DecayCl","MethodData_CWDFuConSt")

columns_FuelsDuffLitt_M <- c("MethodData_NumTran (num.)","MethodData_Transect (num.)","MethodData_SampLoc (m)","MethodData_OffSet","MethodData_LittDep (cm)","MethodData_DuffDep (cm)","MethodData_FuelbedDep (cm)","MethodData_DLFuConSt")
columns_FuelsDuffLitt_E <- c("MethodData_NumTran (num.)","MethodData_Transect (num.)","MethodData_SampLoc (ft)","MethodData_OffSet","MethodData_LittDep (in)","MethodData_DuffDep (in)","MethodData_FuelbedDep (in)","MethodData_DLFuConSt")

columns_FuelsFine_M <- c("MethodData_NumTran (num.)","MethodData_OneHrTranLen (m)","MethodData_TenHrTranLen (m)","MethodData_HunHrTranLen (m)","MethodData_Transect (num.)","MethodData_Azimuth (°)","MethodData_Slope (%)","MethodData_OneHr","MethodData_TenHr","MethodData_HunHr","MethodData_FWDFuConSt")
columns_FuelsFine_E <- c("MethodData_NumTran (num.)","MethodData_OneHrTranLen (ft)","MethodData_TenHrTranLen (ft)","MethodData_HunHrTranLen (ft)","MethodData_Transect (num.)","MethodData_Azimuth (°)","MethodData_Slope (%)","MethodData_OneHr","MethodData_TenHr","MethodData_HunHr","MethodData_FWDFuConSt")

columns_Trees_M <- c("MethodData_MacroPlotSize (ha)","MethodData_SnagPlotSize (ha)","MethodData_BrkPntDia (cm)","MethodData_IsVerified","MethodData_QTR (num.)","MethodData_SubFrac (num.)","MethodData_TagNo (num.)","MethodData_Status","MethodData_DBH (cm)","MethodData_Ht (m)","MethodData_CrwnRto (%)","MethodData_CrwnCl","MethodData_CrFuBHt (m)","MethodData_LiCrBHt (m)","MethodData_CrwnRad (m)","MethodData_Age (yrs)","MethodData_GrwthRt (cm)","MethodData_Mort","MethodData_DecayCl","MethodData_LaddBaseHt (m)","MethodData_LaddMaxHt (m)","MethodData_DRC (cm)","MethodData_NuLiStems","MethodData_NuDeStems","MethodData_EqDia (cm)","MethodData_XCoord (m)","MethodData_YCoord (m)","MethodData_CKR","MethodData_CharHt (m)","MethodData_ScorchHt (m)","MethodData_CrScPct (%)","MethodData_DamCd1","MethodData_DamSev1 (num.)","MethodData_DamCd2","MethodData_DamSev2 (num.)","MethodData_DamCd3","MethodData_DamSev3 (num.)","MethodData_DamCd4","MethodData_DamSev4 (num.)","MethodData_DamCd5","MethodData_DamSev5 (num.)","MethodData_Density","MethodData_BasalArea")
columns_Trees_E <- c("MethodData_MacroPlotSize (ac)","MethodData_SnagPlotSize (ac)","MethodData_BrkPntDia (in)","MethodData_IsVerified","MethodData_QTR (num.)","MethodData_SubFrac (num.)","MethodData_TagNo (num.)","MethodData_Status","MethodData_DBH (in)","MethodData_Ht (ft)","MethodData_CrwnRto (%)","MethodData_CrwnCl","MethodData_CrFuBHt (ft)","MethodData_LiCrBHt (ft)","MethodData_CrwnRad (ft)","MethodData_Age (yrs)","MethodData_GrwthRt (cm)","MethodData_Mort","MethodData_DecayCl","MethodData_LaddBaseHt (m)","MethodData_LaddMaxHt (ft)","MethodData_DRC (in)","MethodData_NuLiStems","MethodData_NuDeStems","MethodData_EqDia (in)","MethodData_XCoord (ft)","MethodData_YCoord (ft)","MethodData_CKR","MethodData_CharHt (ft)","MethodData_ScorchHt (ft)","MethodData_CrScPct (%)","MethodData_DamCd1","MethodData_DamSev1 (num.)","MethodData_DamCd2","MethodData_DamSev2 (num.)","MethodData_DamCd3","MethodData_DamSev3 (num.)","MethodData_DamCd4","MethodData_DamSev4 (num.)","MethodData_DamCd5","MethodData_DamSev5 (num.)","MethodData_Density","MethodData_BasalArea")

columns_HerbsSpComp_M <- c("MethodData_MinCovLevel (%)","MethodData_Area (ha)","MethodData_Status (num.)","MethodData_SizeCl (num.)","MethodData_AgeCl","MethodData_Cover","MethodData_Height (m)")
columns_HerbsSpComp_E <- c("MethodData_MinCovLevel (%)","MethodData_Area (ac)","MethodData_Status (num.)","MethodData_SizeCl (num.)","MethodData_AgeCl","MethodData_Cover","MethodData_Height (ft)")

columns_HerbsPoints_M <- c("MethodData_NumTran (num.)","MethodData_TranLen (m)","MethodData_NumPtsTran (num.)","MethodData_Offset (m)","MethodData_Transect (num.)","MethodData_Point (num.)","MethodData_Tape (num.)","MethodData_Order (num.)","MethodData_Height (m)","MethodData_Status","MethodData_Cover","MethodData_CanopyLayer")
columns_HerbsPoints_E <- c("MethodData_NumTran (num.)","MethodData_TranLen (ft)","MethodData_NumPtsTran (num.)","MethodData_Offset (ft)","MethodData_Transect (num.)","MethodData_Point (num.)","MethodData_Tape (num.)","MethodData_Order (num.)","MethodData_Height (ft)","MethodData_Status","MethodData_Cover","MethodData_CanopyLayer")

columns_HerbsFrequency_M <- c("MethodData_NumTran (num.)", "MethodData_TranLen (ft)", "MethodData_NumQuadLen", "MethodData_QuadLen (in)", "MethodData_QuadWid (in)", "MethodData_NFRatio", "MethodData_NFNum", "MethodData_Transect (num.)", "MethodData_Quadrat (num.)", "MethodData_Status (num.)", "MethodData_NRF (num.)", "MethodData_TypeCov", "MethodData_Cover (%)", "MethodData_Height (ft)", "MethodData_QuadCover", "MethodData_Frequency")
columns_HerbsFrequency_E <- c("MethodData_NumTran (num.)", "MethodData_TranLen (ft)", "MethodData_NumQuadLen", "MethodData_QuadLen (in)", "MethodData_QuadWid (in)", "MethodData_NFRatio", "MethodData_NFNum", "MethodData_Transect (num.)", "MethodData_Quadrat (num.)", "MethodData_Status (num.)", "MethodData_NRF (num.)", "MethodData_TypeCov", "MethodData_Cover (%)", "MethodData_Height (ft)", "MethodData_QuadCover", "MethodData_Frequency")
```

# PROJECT UNIT ASSIGNMENT REPORT

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- ProjectUnitReport %>% 
  mutate(AdminUnit_Name = target_park,
         Protocol = "project_units")
values_data <- names(data)
values_valid <- c(columns_ProjectUnit)
MissingColumn1 <- setdiff(values_data, values_valid)
MissingColumn2 <- setdiff(values_valid, values_data)
MissingColumn <- c(MissingColumn1, MissingColumn2)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Column - Names"
query_message <- "Mismatched/Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_ProjectUnitReport_Columns <- qaqc(data, query, query_message, values_check)
errors_ProjectUnitReport_Columns <- unique(errors_ProjectUnitReport_Columns)
```

# SPECIES REPORT

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  mutate(AdminUnit_Name = Species_AdminUnitName,
         Protocol = "species_report")
values_data <- names(data)
values_valid <- c(columns_SpeciesReport)
MissingColumn1 <- setdiff(values_data, values_valid)
MissingColumn2 <- setdiff(values_valid, values_data)
MissingColumn <- c(MissingColumn1, MissingColumn2)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Column - Names"
query_message <- "Mismatched/Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_Columns <- qaqc(data, query, query_message, values_check)
errors_SpeciesReport_Columns <- unique(errors_SpeciesReport_Columns)
```

# PROTOCOL - SURFACE FUELS

## 1000HR (CWD)

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- Fuels1000_all %>% 
  mutate(Protocol = "surface_fuels_thousand_hr")
values_data <- names(data)
values_valid <- c(columns_ID,columns_Macroplot,columns_SampleEvent,columns_MethodData,columns_Fuels1000_E)
MissingColumn1 <- setdiff(values_data, values_valid)
MissingColumn2 <- setdiff(values_valid, values_data)
MissingColumn <- c(MissingColumn1, MissingColumn2)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Column - Names"
query_message <- "Mismatched/Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_Fuels1000_Columns <- qaqc(data, query, query_message, values_check)
errors_Fuels1000_Columns <- unique(errors_Fuels1000_Columns)
```

## DUFF LITTER (DL)

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- FuelsDuffLitt_all %>% 
  mutate(Protocol = "surface_fuels_duff_litter")
values_data <- names(data)
values_valid <- c(columns_ID,columns_Macroplot,columns_SampleEvent,columns_MethodData,
                  columns_FuelsDuffLitt_E)
MissingColumn1 <- setdiff(values_data, values_valid)
MissingColumn2 <- setdiff(values_valid, values_data)
MissingColumn <- c(MissingColumn1, MissingColumn2)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Column - Names"
query_message <- "Mismatched/Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_FuelsDuffLitt_Columns <- qaqc(data, query, query_message, values_check)
errors_FuelsDuffLitt_Columns <- unique(errors_FuelsDuffLitt_Columns)
```

## FINE FUELS (FWD)

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- FuelsFine_all %>% 
  mutate(Protocol = "surface_fuels_fine")
values_data <- names(data)
values_valid <- c(columns_ID,columns_Macroplot,columns_SampleEvent,columns_MethodData,
                  columns_FuelsFine_E)
MissingColumn1 <- setdiff(values_data, values_valid)
MissingColumn2 <- setdiff(values_valid, values_data)
MissingColumn <- c(MissingColumn1, MissingColumn2)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Column - Names"
query_message <- "Mismatched/Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_FuelsFine_Columns <- qaqc(data, query, query_message, values_check)
errors_FuelsFine_Columns <- unique(errors_FuelsFine_Columns)
```

# PROTOCOL - TREES

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- Trees_all %>% 
  mutate(Protocol = "trees_individuals")
values_data <- names(data)
values_valid <- c(columns_ID,columns_Macroplot,columns_SampleEvent,columns_MethodData,
                  columns_Species, columns_Trees_M)
MissingColumn1 <- setdiff(values_data, values_valid)
MissingColumn2 <- setdiff(values_valid, values_data)
MissingColumn <- c(MissingColumn1, MissingColumn2)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Column - Names"
query_message <- "Mismatched/Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_Trees_Columns <- qaqc(data, query, query_message, values_check)
errors_Trees_Columns <- unique(errors_Trees_Columns)
```

# PROTOCOL - HERBS SPECIES COMP

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- HerbsSpComp_all %>% 
  mutate(Protocol = "cover_species_composition")
values_data <- names(data)
values_valid <- c(columns_ID,columns_Macroplot,columns_SampleEvent,columns_MethodData,
                  columns_Species, columns_HerbsSpComp_M)
MissingColumn1 <- setdiff(values_data, values_valid)
MissingColumn2 <- setdiff(values_valid, values_data)
MissingColumn <- c(MissingColumn1, MissingColumn2)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Column - Names"
query_message <- "Mismatched/Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_HerbsSpComp_Columns <- qaqc(data, query, query_message, values_check)
errors_HerbsSpComp_Columns <- unique(errors_HerbsSpComp_Columns)
```

# PROTOCOL - HERBS POINTS

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- HerbsPoints_all %>% 
  mutate(Protocol = "cover_points")
values_data <- names(data)
values_valid <- c(columns_ID,columns_Macroplot,columns_SampleEvent,columns_MethodData,
                  columns_Species, columns_HerbsPoints_M)
MissingColumn1 <- setdiff(values_data, values_valid)
MissingColumn2 <- setdiff(values_valid, values_data)
MissingColumn <- c(MissingColumn1, MissingColumn2)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Column - Names"
query_message <- "Mismatched/Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_HerbsPoints_Columns <- qaqc(data, query, query_message, values_check)
errors_HerbsPoints_Columns <- unique(errors_HerbsPoints_Columns)
```

# PROTOCOL - HERBS FREQUENCY

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- HerbsFrequency_all %>% 
  mutate(Protocol = "cover_frequency")
values_data <- names(data)
values_valid <- c(columns_ID,columns_Macroplot,columns_SampleEvent,columns_MethodData, columns_Species, columns_HerbsFrequency_M)
MissingColumn1 <- setdiff(values_data, values_valid)
MissingColumn2 <- setdiff(values_valid, values_data)
MissingColumn <- c(MissingColumn1, MissingColumn2)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Column - Names"
query_message <- "Mismatched/Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_HerbsFrequency_Columns <- qaqc(data, query, query_message, values_check)
errors_HerbsFrequency_Columns <- unique(errors_HerbsFrequency_Columns)
```

# ALL ERRORS

## Combine Column Errors

```{r}
# Combine
errors_columns <- unique(rbind(errors_ProjectUnitReport_Columns, errors_SpeciesReport_Columns, errors_Fuels1000_Columns, errors_FuelsDuffLitt_Columns, errors_FuelsFine_Columns, errors_Trees_Columns, errors_HerbsSpComp_Columns, errors_HerbsPoints_Columns))

remove(errors_ProjectUnitReport_Columns, errors_SpeciesReport_Columns, errors_Fuels1000_Columns, errors_FuelsDuffLitt_Columns, errors_FuelsFine_Columns, errors_Trees_Columns, errors_HerbsSpComp_Columns, errors_HerbsPoints_Columns)

if(nrow(errors_columns) > 1) {
  errors_columns <- errors_columns %>%
    filter(Error != "No Error")
} else {
  errors_columns <- errors_columns}
```

## Combine All Errors

```{r}
errors_all <- rbind(errors_columns)
```

```{r}
# Save as CSV or XLSX 
write_xlsx(errors_all, paste0(path_errors, target_park, "_errors_DataDepot.xlsx"))
```
