---
title: Clean FFI Data
author: Alexandra Lalor
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 1
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: 1
---

# PURPOSE

This code is intended to combine FFI files into flat files to be used with subsequent R scripts.

The Sample Event Report and Macroplot Report can be downloaded via the Utilities menu on the Project Management tab on the FFI Remote App Server.

-   MacroplotReport.csv

-   SampleEventReport.csv

The Local Species Report can be downloaded via the Species menu on the Species Management tab on the FFI Remote App Server.

-   LocalSpeciesReport.csv

The Protocol data can be downloaded via Query tab on the FFI Remote App Server by using the saved queries from the drop down options.

-   Surface Fuels - 1000Hr_XPT.csv

-   Surface Fuels - Duff_Litter_XPT.csv

-   Surface Fuels - Fine_XPT.csv

-   Post Burn Severity (metric)\_XPT.csv

-   Trees - Individuals (metric)\_XPT.csv

-   Density - Quadrats (metric)\_XPT.csv

-   Density - Belts (metric)\_XPT.csv

-   Cover - Species Composition (metric)\_XPT.csv

-   Cover - Points (metric)\_XPT.csv

## BEFORE STARTING {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
# install.packages("tidyverse")
# install.packages("Rtools")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
# install.packages("EnvStats")
```

```{r}
# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
# knitr is used to create output files from R Markdown
library(knitr)
```

### Adjust File Paths {.hidden}

```{r}
# adjust file paths
path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
#path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
```

### Parks {.hidden}

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
```

# METADATA

## Sample Event & Macroplot Report

```{r}
for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
  path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
  
  # load data
  MacroplotReport <- read.csv(paste0(path_data, "MacroplotReport.csv"), na.strings = c("","NA","N/A"))
  SampleEventReport <- read.csv(paste0(path_data, "SampleEventReport.csv"), na.strings = c("","NA","N/A"))
  
  
  # clean & filter data
  #### Macroplot Report
  # The Macroplot Report contains information on both plot metadata and sample event history. Separate these into 2 tables.
  MacroplotReport_MetaData <- MacroplotReport %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate tables
    filter(is.na(SampleEventDate)) %>%
    # separate Date column
    separate(DateIn, sep = " ", 
             into = c("Macroplot_DateIn", "DateInTime")) %>%
    separate(FutureVisit, sep = " ", 
             into = c("Macroplot_FutureVisit", "FutureVisitTime")) %>%
    separate(DateOut, sep = " ", 
             into = c("Macroplot_DateOut", "DateOutTime")) %>%
    # make column names consistent
    dplyr::rename(Macroplot_Name = Macroplot) %>% 
    # remove unnecessary columns
    select(!c(DateInTime, FutureVisitTime, DateOutTime)) %>% 
    select(!c(SampleEventDate, SampleEventTeam, SampleEventComment, 
              MonStatusOrd, LegacyMonStatus, MonStatus))

  MacroplotReport_SampleEvents <- MacroplotReport %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate tables
    filter(!is.na(SampleEventDate)) %>%
    # separate Date column
    separate(SampleEventDate, sep = " ", 
             into = c("SampleEvent_Date", "SampleEvent_Time")) %>%
    # make column names consistent
    dplyr::rename(Macroplot_Name = Macroplot,
                  SampleEvent_LegacyMonitoringStatus = LegacyMonStatus,
                  SampleEvent_Who = SampleEventTeam,
                  SampleEvent_Comment = SampleEventComment,
                  MonitoringStatus_Name = MonStatus,
                  MonitoringStatus_Order = MonStatusOrd) %>% 
    # remove unnecessary columns
    select(!c(SampleEvent_Time)) %>%
    select(c(Macroplot_Name, SampleEvent_Date,
             SampleEvent_Who, SampleEvent_Comment, MonitoringStatus_Order, 
             SampleEvent_LegacyMonitoringStatus, MonitoringStatus_Name))
  
  #### Sample Event Report
  # The Sample Event Report has different column names as the Macroplot Report, but contains the same information. Make column names consistent.
  SampleEventReport_clean <- SampleEventReport %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(SampleEvent_Date, sep = " ", 
             into = c("SampleEvent_Date", "SampleEvent_Time")) %>%
    # make column names consistent
    dplyr::rename(AdminUnit_Name = AdministrationUnit_Name,
                  Macroplot_Name = MacroPlot_Name,
                  SampleEvent_Protocols = Protocols,
                  SampleEvent_Visited = Visited) %>% 
    # remove unnecessary columns
    select(!c(SampleEvent_Time, SampleEvent_LegacyMonitoringStatus))
  
  
  # merge data
  #### Merge MacroplotReport_Metadata and MacroplotReport_SampleEvents
  MacroplotReport_merge <- merge(MacroplotReport_MetaData, MacroplotReport_SampleEvents, by = c("Macroplot_Name")) %>%
    select(!MonitoringStatus_Order)
  
  #### Filter Sample Event Report for merging
  SampleEventReport_merge <- SampleEventReport_clean %>%
    filter(ProjectUnit_Name != "ALL") %>% 
    select(!c(Multi_PU))
  
  #### Merge Macroplot Report and Sample Event Report
  MetadataReport <- merge(MacroplotReport_merge, SampleEventReport_merge, by = c("Macroplot_Name", "SampleEvent_Date", "MonitoringStatus_Name")) %>%
    relocate(AdminUnit_Name, .before = Macroplot_Name) %>%
    relocate(ProjectUnit_Name, .after = Purpose) %>%
    relocate(Type, .after = Purpose) %>% 
    relocate(Macroplot_Name, .after = Type) %>%
    relocate(SampleEvent_Date, .after = SampleEvent_Visited) %>%
    relocate(MonitoringStatus_Name, .after = SampleEvent_LegacyMonitoringStatus) %>%
    relocate(LocatedBy, .before = StartPoint)
  
  # final column renaming to match protocol exports
    MetadataReport <- MetadataReport %>% 
      dplyr::rename(
        Macroplot_Purpose = Purpose,
        Macroplot_Type = Type,
        Macroplot_DdLat = Latitude,
        Macroplot_DdLong = Longitude,
        "Macroplot_UtmX (m)" = UTM_X,
        "Macroplot_UtmY (m)" = UTM_Y,
        Macroplot_UtmZone = UTM_Zone,
        Macroplot_Datum = Datum,
        Macroplot_Pdop = PDOP,
        Macroplot_Precision = Precision,
        Macroplot_Elevation = Elevation,
        Macroplot_ElevationUnits = ElevationUnits,
        Macroplot_Azimuth = Azimuth,
        Macroplot_Aspect = Aspect,
        "Macroplot_SlopeHill (%)" = SlopeHill,
        "Macroplot_SlopeTransect (%)" = SlopeTransect,
        Macroplot_LocatedBy = LocatedBy,
        Macroplot_StartPoint = StartPoint,
        Macroplot_Directions = Directions,
        Macroplot_Comment = Comments,
        Macroplot_Metadata = MetaData,
        Macroplot_UV1 = UV1,
        Macroplot_UV2 = UV2,
        Macroplot_UV3 = UV3,
        Macroplot_UV4 = UV4,
        Macroplot_UV5 = UV5,
        Macroplot_UV6 = UV6,
        Macroplot_UV7 = UV7,
        Macroplot_UV8 = UV8,
        SampleEvent_DefaultMonitoringStatus = SampleEvent_LegacyMonitoringStatus
        )
  
  # replace commas with semicolons
  MetadataReport[] <- lapply(MetadataReport, function(x) gsub(",", ";", x))
  
  
  # save file
  write.csv(MetadataReport, paste0(path_save, target_park, "_MetadataReport.csv"), quote = FALSE, row.names = FALSE) 
}
```

# SPECIES

## Species Report

```{r}
# for(i in parks) {
#   # select target park
#   target_park <- i
#   
#   
#   # adjust file paths
#   path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
#   path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
#   
#   
#   # load data
#   SpeciesReport <- read.csv(paste0(path_data, "LocalSpeciesReport.csv"), na.strings = c("","NA","N/A"))
# 
#   
#   # clean data
#   SpeciesReport <- SpeciesReport %>%
#   # remove trailing/leading whitespace
#     mutate(across(where(is.character), str_trim))
#   ## replace commas with semicolons
#   SpeciesReport[] <- lapply(SpeciesReport, function(x) gsub(",", ";", x))
#   
#   
#   # final column renaming to match protocol exports
#     SpeciesReport <- SpeciesReport %>%
#       dplyr::rename(
#         MethodData_sppGuid = LocalSpecies_GUID,
#         #Species_SourceEntityId = LocalSpecies_GUID,
#         Species_ITISTaxonomicSerialNumber = MasterSpecies_ITIS_TSN,
#         Species_SymbolLocal = LocalSpecies_Symbol,
#         #Species_Symbol = # not on species report
#         Species_Description = LocalSpecies_Description,
#         Species_CommonNameLocal = LocalSpecies_CommonName,
#         #Species_CommonName = # not on species report
#         Species_LifeCycleLocal = LocalSpecies_LifeCycle,
#         #Species_LifeCycle = # not on species report
#         # = LocalSpecies_UserAdded, # not on data depot outputs
#         Species_NativityLocal = LocalSpecies_Nativity,
#         #Species_Nativity = # not on species report
#         Species_Invasive = LocalSpecies_Invasive,
#         Species_Cultural = LocalSpecies_Cultural,
#         Species_Concern = LocalSpecies_Concern,
#         Species_Retired = LocalSpecies_Retired,
#         Species_Comment = LocalSpecies_Comment,
#         Species_UV1 = LocalSpecies_UV1,
#         Species_UV2 = LocalSpecies_UV2,
#         Species_UV3 = LocalSpecies_UV3,
#         Species_LifeFormNameLocal = LocalSpecies_PreferedLifeForm,
#         #Species_LifeFormName = # not on species report
#         Species_ScientificName = MasterSpecies_ScientificName,
#         Species_Genus = MasterSpecies_Genus,
#         Species_Family = MasterSpecies_Family,
#         Species_NotBiological = MasterSpecies_NotBiolgoical,
#         # = ReportType # not on data depot outputs
#         )
# 
#   
#   # save file
#   write.csv(SpeciesReport, paste0(path_save, target_park, "_SpeciesReport.csv"), quote = FALSE, row.names = FALSE)
# }
```

# PROTOCOLS

## Fuels 1000

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")

for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
  path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
  
  
  # load data
  Fuels1000_all <- read.csv(paste0(path_data, "Surface Fuels - 1000Hr_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  Fuels1000_all <- Fuels1000_all[, -ncol(Fuels1000_all)]
  ## replace commas with semicolons
  Fuels1000_all[] <- lapply(Fuels1000_all, function(x) gsub(",", ";", x))
  
  
  # clean data
  Fuels1000_all <- Fuels1000_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## Fuels1000 headers
  Fuels1000_header <- Fuels1000_all %>%
    filter(!is.na(Visited)) %>% 
    select(c(1:18, 
             NumTran, TranLen, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## Fuels1000 data
  Fuels1000_data <- Fuels1000_all %>%
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, TranLen, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))


  # merge data
  Fuels1000 <- merge(Fuels1000_header, Fuels1000_data, by = c(1:18))
  
  
  # add column for park name
  Fuels1000 <- Fuels1000 %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # final column renaming to match metadata
  Fuels1000 <- Fuels1000 %>% 
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonitoringStatus_Name = Monitoring.Status,
      MonitoringStatus_Prefix = Status.Prefix,
      MonitoringStatus_Base = Status.Base,
      MonitoringStatus_Suffix = Status.Suffix,
      MonitoringStatus_Order = Status.Order,
      "MethodData_numTran (num.)" = NumTran,
      "MethodData_tranLen (ft)" = TranLen,
      MethodData_fieldTeam = FieldTeam,
      MethodData_entryTeam = EntryTeam,
      MethodData_uV1Desc = UV1Desc,
      MethodData_uV2Desc = UV2Desc,
      MethodData_uV3Desc = UV3Desc,
      MethodData_saComment = SaComment,
      MethodData_visited = Visited,
      MethodData_index = Index,
      "MethodData_transect (num.)" = Transect,
      "MethodData_slope (%)" = Slope,
      "MethodData_logNum (num.)" = LogNum,
      "MethodData_dia (in.)" = Dia,
      MethodData_decayCl = DecayCl,
      MethodData_cWDFuConSt = CWDFuConSt,
      MethodData_comment = Comment,
      MethodData_uV1 = UV1,
      MethodData_uV2 = UV2,
      MethodData_uV3 = UV3
      )
  
  
  # save file
  write.csv(Fuels1000, paste0(path_save, target_park, "_Data_Surface Fuels - 1000Hr.csv"), quote = FALSE, row.names = FALSE)
}
```

## Fuels Duff Litt

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")

for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
  path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
  
  
  # load data
  FuelsDuffLitt_all <- read.csv(paste0(path_data, "Surface Fuels - Duff_Litter_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  FuelsDuffLitt_all <- FuelsDuffLitt_all[, -ncol(FuelsDuffLitt_all)]
  ## replace commas with semicolons
  FuelsDuffLitt_all[] <- lapply(FuelsDuffLitt_all, function(x) gsub(",", ";", x))
  
  
  # clean data
  FuelsDuffLitt_all <- FuelsDuffLitt_all %>% 
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## FuelsDuffLitt headers
  FuelsDuffLitt_header <- FuelsDuffLitt_all %>%   
    filter(!is.na(Visited)) %>% 
    select(c(1:18,
             NumTran, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## FuelsDuffLitt data
  FuelsDuffLitt_data <- FuelsDuffLitt_all %>%   
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  FuelsDuffLitt <- merge(FuelsDuffLitt_header, FuelsDuffLitt_data, by = c(1:18))
  
  
  # add column for park name
  FuelsDuffLitt <- FuelsDuffLitt %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose") %>% 
    select(!c(Visited))
  
  
  # final column renaming to match metadata
  FuelsDuffLitt <- FuelsDuffLitt %>% 
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonitoringStatus_Name = Monitoring.Status,
      MonitoringStatus_Prefix = Status.Prefix,
      MonitoringStatus_Base = Status.Base,
      MonitoringStatus_Suffix = Status.Suffix,
      MonitoringStatus_Order = Status.Order,
      "MethodData_numTran (num.)" = NumTran,
      MethodData_fieldTeam = FieldTeam,
      MethodData_entryTeam = EntryTeam,
      MethodData_uV1Desc = UV1Desc,
      MethodData_uV2Desc = UV2Desc,
      MethodData_uV3Desc = UV3Desc,
      MethodData_saComment = SaComment,
      # = Visited, # not in data depot
      MethodData_index = Index,
      "MethodData_transect (num.)" = Transect,
      "MethodData_sampLoc (ft)" = SampLoc,
      MethodData_offSet = OffSet,
      "MethodData_littDep (in.)" = LittDep,
      "MethodData_duffDep (in.)" = DuffDep,
      "MethodData_fuelbedDep (in.)" = FuelbedDep,
      MethodData_dLFuConSt = DLFuConSt,
      MethodData_comment = Comment,
      MethodData_uV1 = UV1,
      MethodData_uV2 = UV2,
      MethodData_uV3 = UV3
      )
  
  
  # save file
  write.csv(FuelsDuffLitt, paste0(path_save, target_park, "_Data_Surface Fuels - Duff_Litter.csv"), quote = FALSE, row.names = FALSE) 
}
```

## Fuels Fine

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")

for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
  path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
  
  
  # load data
  FuelsFine_all <- read.csv(paste0(path_data, "Surface Fuels - Fine_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  FuelsFine_all <- FuelsFine_all[, -ncol(FuelsFine_all)]
  ## replace commas with semicolons
  FuelsFine_all[] <- lapply(FuelsFine_all, function(x) gsub(",", ";", x))
  
  
  # clean data
  FuelsFine_all <- FuelsFine_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## FuelsFine headers 
  FuelsFine_header <- FuelsFine_all %>%   
    filter(!is.na(Visited)) %>% 
    select(c(1:18,
             NumTran, OneHrTranLen, TenHrTranLen, HunHrTranLen, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
## FuelsFine data
  FuelsFine_data <- FuelsFine_all %>%   
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, OneHrTranLen, TenHrTranLen, HunHrTranLen, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  FuelsFine <- merge(FuelsFine_header, FuelsFine_data, by = c(1:18))
  
  
  # add column for park name
  FuelsFine <- FuelsFine %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # final column renaming to match metadata
  FuelsFine <- FuelsFine %>% 
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonitoringStatus_Name = Monitoring.Status,
      MonitoringStatus_Prefix = Status.Prefix,
      MonitoringStatus_Base = Status.Base,
      MonitoringStatus_Suffix = Status.Suffix,
      MonitoringStatus_Order = Status.Order,
      "MethodData_numTran (num.)" = NumTran,
      "MethodData_oneHrTranLen (ft)" = OneHrTranLen,
      "MethodData_tenHrTranLen (ft)" = TenHrTranLen,
      "MethodData_hunHrTranLen (ft)" = HunHrTranLen,
      MethodData_fieldTeam = FieldTeam,
      MethodData_entryTeam = EntryTeam,
      MethodData_uV1Desc = UV1Desc,
      MethodData_uV2Desc = UV2Desc,
      MethodData_uV3Desc = UV3Desc,
      MethodData_saComment = SaComment,
      MethodData_visited = Visited,
      MethodData_index = Index,
      "MethodData_transect (num.)" = Transect,
      "MethodData_azimuth (&#166;)" = Azimuth,
      "MethodData_slope (%)" = Slope,
      MethodData_oneHr = OneHr,
      MethodData_tenHr = TenHr,
      MethodData_hunHr = HunHr,
      MethodData_fWDFuConSt = FWDFuConSt,
      MethodData_comment = Comment,
      MethodData_uV1 = UV1,
      MethodData_uV2 = UV2,
      MethodData_uV3 = UV3
      )
  
  
  # save file
  write.csv(FuelsFine, paste0(path_save, target_park, "_Data_Surface Fuels - Fine.csv"), quote = FALSE, row.names = FALSE) 
}
```

## Post Burn

```{r}
# parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")

# for(i in parks) {
#   # select target park
#   target_park <- i
#   
#   
#   # adjust file paths
#   path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
#   path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
#   
#   
#   # load data
#   PostBurn_all <- read.csv(paste0(path_data, "Post Burn Severity (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
#   ## Drop last column if it's an empty placeholder (common in Excel exports)
#   PostBurn_all <- PostBurn_all[, -ncol(PostBurn_all)]
#   ## replace commas with semicolons
#   PostBurn_all[] <- lapply(PostBurn_all, function(x) gsub(",", ";", x))
#   
#   
#   # clean data
#   PostBurn_all <- PostBurn_all %>%
#     # remove trailing/leading whitespace
#     mutate(across(where(is.character), str_trim)) %>%
#     # separate Date column
#     separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
#     # remove unnecessary columns
#     select(!c("Time"))
#   
#   
#   # filter data
#   ## PostBurn headers
#   PostBurn_header <- PostBurn_all %>%
#     filter(!is.na(Visited)) %>% 
#     select(c(1:18,
#              NumTran, TranLen, NumPtsTran, PlotType, PtArea, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
#   ## PostBurn data
#   PostBurn_data <- PostBurn_all %>%
#     filter(is.na(Visited)) %>% 
#     select(!c(NumTran, TranLen, NumPtsTran, PlotType, PtArea, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
#   
#   
#   # merge data
#   PostBurn <- merge(PostBurn_header, PostBurn_data, by = c(1:18))
#   
#   
#   # add column for park name
#   PostBurn <- PostBurn %>% 
#     add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
#   
#   
#   # final column renaming to match metadata
#   PostBurn <- PostBurn %>% 
#     dplyr::rename(
#       Macroplot_Purpose = MacroPlot.Purpose,
#       Macroplot_Type = MacroPlot.Type,
#       Macroplot_UV1 = MacroPlot.UV1,
#       Macroplot_UV2 = MacroPlot.UV2,
#       Macroplot_UV3 = MacroPlot.UV3,
#       Macroplot_UV4 = MacroPlot.UV4,
#       Macroplot_UV5 = MacroPlot.UV5,
#       Macroplot_UV6 = MacroPlot.UV6,
#       Macroplot_UV7 = MacroPlot.UV7,
#       Macroplot_UV8 = MacroPlot.UV8,
#       Macroplot_Name = MacroPlot.Name,
#       MonitoringStatus_Name = Monitoring.Status,
#       MonitoringStatus_Prefix = Status.Prefix,
#       MonitoringStatus_Base = Status.Base,
#       MonitoringStatus_Suffix = Status.Suffix,
#       MonitoringStatus_Order = Status.Order,
#       "MethodData_numTran (num.)" = NumTran,
#       "MethodData_TranLen (ft)" = TranLen,
#       MethodData_numPtsTran = NumPtsTran,
#       MethodData_plotType = PlotType,
#       MethodData_ptArea = PtArea,
#       MethodData_fieldTeam = FieldTeam,
#       MethodData_entryTeam = EntryTeam,
#       MethodData_uV1Desc = UV1Desc,
#       MethodData_uV2Desc = UV2Desc,
#       MethodData_uV3Desc = UV3Desc,
#       MethodData_saComment = SaComment,
#       MethodData_visited = Visited,
#       MethodData_index = Index,
#       "MethodData_transect (num.)" = Transect,
#       MethodData_point = Point,
#       MethodData_tapeDist = TapeDist,
#       MethodData_veg = Veg,
#       MethodData_sub = Sub,
#       MethodData_comment = Comment,
#       MethodData_uV1 = UV1,
#       MethodData_uV2 = UV2,
#       MethodData_uV3 = UV3
#       )
#   
#   
#   # save file
#   write.csv(PostBurn, paste0(path_save, target_park, "_Data_Post Burn Severity (metric).csv"), quote = FALSE, row.names = FALSE) 
# }
```

## Trees

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "FRSP", "NERI", "RICH", "SHEN")

for(i in parks) {
  
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
  path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
  
  
  # load data
  Trees_all <- read.csv(paste0(path_data, "Trees - Individuals (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  Trees_all <- Trees_all[, -ncol(Trees_all)]
  ## replace commas with semicolons
  Trees_all[] <- lapply(Trees_all, function(x) gsub(",", ";", x))
  
  
  # clean data
  Trees_all <- Trees_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## Trees headers
  Trees_header <- Trees_all %>%   
    filter(!is.na(Visited)) %>% 
    select(c(1:18,
             MacroPlotSize, SnagPlotSize, BrkPntDia, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## Trees data
  Trees_data <- Trees_all %>%   
    filter(is.na(Visited)) %>% 
    select(!c(MacroPlotSize, SnagPlotSize, BrkPntDia, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  Trees <- merge(Trees_header, Trees_data, by = c(1:18))
  
  
  # add column for park name
  Trees <- Trees %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # final column renaming to match metadata
  Trees <- Trees %>% 
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonitoringStatus_Name = Monitoring.Status,
      MonitoringStatus_Prefix = Status.Prefix,
      MonitoringStatus_Base = Status.Base,
      MonitoringStatus_Suffix = Status.Suffix,
      MonitoringStatus_Order = Status.Order,
      #Species_SymbolLocal = Species.Symbol,
      MethodData_symbolLocal = Species.Symbol,
      Species_LifeCycleLocal = Lifecycle,
      Species_NotBiological = NotBiological,
      Species_LifeFormNameLocal = Preferred_Lifeform,
      Species_Family = Family,
      Species_Genus = Genus,
      Species_ScientificName = ScientificName,
      Species_NativityLocal = Native.Species,
      Species_Invasive = Invasive.Species,
      "MethodData_macroPlotSize (ha)" = MacroPlotSize,
      "MethodData_snagPlotSize (ha)" = SnagPlotSize,
      MethodData_breakPntDia = BrkPntDia,
      MethodData_fieldTeam = FieldTeam,
      MethodData_entryTeam = EntryTeam,
      MethodData_uV1Desc = UV1Desc,
      MethodData_uV2Desc = UV2Desc,
      MethodData_uV3Desc = UV3Desc,
      MethodData_saComment = SaComment,
      MethodData_visited = Visited,
      MethodData_index = Index,
      MethodData_isVerified = IsVerified,
      "MethodData_qTR (num.)" = QTR,
      "MethodData_subFrac (num.)" = SubFrac,
      "MethodData_tagNo (num.)" = TagNo,
      MethodData_status = Status,
      "MethodData_dBH (cm)" = DBH,
      "MethodData_ht (m)" = Ht,
      "MethodData_crwnRto (%)" = CrwnRto,
      MethodData_crwnCl = CrwnCl,
      "MethodData_liCrBHt (m)" = LiCrBHt,
      "MethodData_crFuBHt (m)" = CrFuBHt,
      "MethodData_crwnRad (m)" = CrwnRad,
      "MethodData_age (yrs)" = Age,
      "MethodData_grwthRt (cm)" = GrwthRt,
      MethodData_mort = Mort,
      MethodData_decayCl = DecayCl,
      "MethodData_laddBaseHt (m)" = LaddBaseHt,
      "MethodData_laddMaxHt (m)" = LaddMaxHt,
      "MethodData_dRC (cm)" = DRC,
      MethodData_nuLiStems = NuLiStems,
      MethodData_nuDeStems = NuDeStems,
      "MethodData_eqDia (cm)" = EqDia,
      "MethodData_xCoord (m)" = XCoord,
      "MethodData_yCoord (m)" = YCoord,
      MethodData_cKR = CKR,
      "MethodData_charHt (m)" = CharHt,
      "MethodData_scorchHt (m)" = ScorchHt,
      "MethodData_crScPct (%)" = CrScPct,
      MethodData_damCd1 = DamCd1,
      MethodData_damCd2 = DamCd2,
      MethodData_damCd3 = DamCd3,
      MethodData_damCd4 = DamCd4,
      MethodData_damCd5 = DamCd5,
      "MethodData_damSev1 (num.)" = DamSev1,
      "MethodData_damSev2 (num.)" = DamSev2,
      "MethodData_damSev3 (num.)" = DamSev3,
      "MethodData_damSev4 (num.)" = DamSev4,
      "MethodData_damSev5 (num.)" = DamSev5,
      MethodData_comment = Comment,
      MethodData_uV1 = UV1,
      MethodData_uV2 = UV2,
      MethodData_uV3 = UV3
      )
  
  
  # save file
  write.csv(Trees, paste0(path_save, target_park, "_Data_Trees - Individuals (metric).csv"), quote = FALSE, row.names = FALSE) 
}
```

## Seedlings

```{r}
# parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
# excluding park PRWI because of database exporting issues
# excluding park APCO because Density - Quadrats (metric) aka Seedlings protocol does not include Area header...

#for(i in parks) {
#   # select target park
#   target_park <- i
#   
#   
#   # adjust file paths
#   path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
#   path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
#   
#   
#   # load data
#   Seedlings_all <- read.csv(paste0(path_data, "Density - Quadrats (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
#   ## Drop last column if it's an empty placeholder (common in Excel exports)
#   Seedlings_all <- Seedlings_all[, -ncol(Seedlings_all)]
#   ## replace commas with semicolons
#   Seedlings_all[] <- lapply(Seedlings_all, function(x) gsub(",", ";", x))
#   
#   
#   # clean data
#   Seedlings_all <- Seedlings_all %>%
#     # remove trailing/leading whitespace
#     mutate(across(where(is.character), str_trim)) %>%
#     # separate Date column
#     separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
#     # remove unnecessary columns
#     select(!c("Time"))
#   
#   
#   # filter data
#   ## Seedlings headers
#   Seedlings_header <- Seedlings_all %>%
#     filter(!is.na(Visited)) %>% 
#     select(c(1:18,
#              NumTran, NumQuadTran, QuadLen, QuadWid, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
#   ## Seedlings data
#   Seedlings_data <- Seedlings_all %>%
#     filter(is.na(Visited)) %>% 
#     select(!c(NumTran, NumQuadTran, QuadLen, QuadWid, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
#   
#   
#   # merge data
#   Seedlings <- merge(Seedlings_header, Seedlings_data, by = c(1:18))
#   
#   
#   # add column for park name
#   Seedlings <- Seedlings %>% 
#     add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
#   
#   
#   # final column renaming to match metadata
#   Seedlings <- Seedlings %>% 
#     dplyr::rename(
#       Macroplot_Purpose = MacroPlot.Purpose,
#       Macroplot_Type = MacroPlot.Type,
#       Macroplot_UV1 = MacroPlot.UV1,
#       Macroplot_UV2 = MacroPlot.UV2,
#       Macroplot_UV3 = MacroPlot.UV3,
#       Macroplot_UV4 = MacroPlot.UV4,
#       Macroplot_UV5 = MacroPlot.UV5,
#       Macroplot_UV6 = MacroPlot.UV6,
#       Macroplot_UV7 = MacroPlot.UV7,
#       Macroplot_UV8 = MacroPlot.UV8,
#       Macroplot_Name = MacroPlot.Name,
#       MonitoringStatus_Name = Monitoring.Status,
#       MonitoringStatus_Prefix = Status.Prefix,
#       MonitoringStatus_Base = Status.Base,
#       MonitoringStatus_Suffix = Status.Suffix,
#       MonitoringStatus_Order = Status.Order,
#       #Species_SymbolLocal = Species.Symbol,
#       MethodData_symbolLocal = Species.Symbol,
#       Species_LifeCycleLocal = Lifecycle,
#       Species_NotBiological = NotBiological,
#       Species_LifeFormNameLocal = Preferred_Lifeform,
#       Species_Family = Family,
#       Species_Genus = Genus,
#       Species_ScientificName = ScientificName,
#       Species_NativityLocal = Native.Species,
#       Species_Invasive = Invasive.Species,
#       MethodData_numTran = NumTran,
#       MethodData_numQuadTran = NumQuadTran,
#       MethodData_quadLen = QuadLen,
#       MethodData_quadWid = QuadWid,
#       "MethodData_area (ha)" = Area,
#       MethodData_fieldTeam = FieldTeam,
#       MethodData_entryTeam = EntryTeam,
#       MethodData_uV1Desc = UV1Desc,
#       MethodData_uV2Desc = UV2Desc,
#       MethodData_uV3Desc = UV3Desc,
#       MethodData_saComment = SaComment,
#       MethodData_visited = Visited,
#       MethodData_index = Index,
#       MethodData_transect = Transect,
#       MethodData_quadrat = Quadrat,
#       MethodData_status = Status,
#       "MethodData_sizeCl (num.)" = SizeCl,
#       MethodData_ageCl = AgeCl,
#       MethodData_count = Count,
#       "MethodData_height (m)" = Height,
#       MethodData_subFrac = SubFrac,
#       MethodData_comment = Comment,
#       MethodData_uV1 = UV1,
#       MethodData_uV2 = UV2,
#       MethodData_uV3 = UV3
#       )
#   
#   
#   # save file
#   write.csv(Seedlings, paste0(path_save, target_park, "_Data_Density - Quadrats (metric).csv"), quote = FALSE, row.names = FALSE) 
# }
```

## Shrubs

```{r}
# parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
# excluding park PRWI because of database exporting issues
# excluding park APCO because Density - Belts (metric) aka Shrubs protocol does not include Subbelt, NumSubbelt, or Area header...

#for(i in parks) {
#   # select target park
#   target_park <- i
#   
#   
#   # adjust file paths
#   path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
#   path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
#   
#   
#   # load data
#   Shrubs_all <- read.csv(paste0(path_data, "Density - Belts (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
#   ## Drop last column if it's an empty placeholder (common in Excel exports)
#   Shrubs_all <- Shrubs_all[, -ncol(Shrubs_all)]
#   ## replace commas with semicolons
#   Shrubs_all[] <- lapply(Shrubs_all, function(x) gsub(",", ";", x))
#   
#   
#   # clean data
#   Shrubs_all <- Shrubs_all %>%
#     # remove trailing/leading whitespace
#     mutate(across(where(is.character), str_trim)) %>%
#     # separate Date column
#     separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
#     # remove unnecessary columns
#     select(!c("Time"))
#   
#   
#   # filter data
#   ## Shrubs headers
#   Shrubs_header <- Shrubs_all %>%
#     filter(!is.na(Visited)) %>% 
#     select(c(1:18,
#              NumTran, NumSubbelt, TranLen, TranWid, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
#   ## Shrubs data
#   Shrubs_data <- Shrubs_all %>%
#     filter(is.na(Visited)) %>% 
#     select(!c(NumTran, NumSubbelt, TranLen, TranWid, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
#   
#   
#   # merge data
#   Shrubs <- merge(Shrubs_header, Shrubs_data, by = c(1:18))
#   
#   
#   # add column for park name
#   Shrubs <- Shrubs %>% 
#     add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
#   
#   
#   # final column renaming to match metadata
#   Shrubs <- Shrubs %>% 
#     dplyr::rename(
#       Macroplot_Purpose = MacroPlot.Purpose,
#       Macroplot_Type = MacroPlot.Type,
#       Macroplot_UV1 = MacroPlot.UV1,
#       Macroplot_UV2 = MacroPlot.UV2,
#       Macroplot_UV3 = MacroPlot.UV3,
#       Macroplot_UV4 = MacroPlot.UV4,
#       Macroplot_UV5 = MacroPlot.UV5,
#       Macroplot_UV6 = MacroPlot.UV6,
#       Macroplot_UV7 = MacroPlot.UV7,
#       Macroplot_UV8 = MacroPlot.UV8,
#       Macroplot_Name = MacroPlot.Name,
#       MonitoringStatus_Name = Monitoring.Status,
#       MonitoringStatus_Prefix = Status.Prefix,
#       MonitoringStatus_Base = Status.Base,
#       MonitoringStatus_Suffix = Status.Suffix,
#       MonitoringStatus_Order = Status.Order,
#       #Species_SymbolLocal = Species.Symbol,
#       MethodData_symbolLocal = Species.Symbol,
#       Species_LifeCycleLocal = Lifecycle,
#       Species_NotBiological = NotBiological,
#       Species_LifeFormNameLocal = Preferred_Lifeform,
#       Species_Family = Family,
#       Species_Genus = Genus,
#       Species_ScientificName = ScientificName,
#       Species_NativityLocal = Native.Species,
#       Species_Invasive = Invasive.Species,
#       MethodData_numTran = NumTran,
#       MethodData_numSubbelt = NumSubbelt,
#       MethodData_tranLen = TranLen,
#       MethodData_tranWid = TranWid,
#       "MethodData_area (ha)" = Area,
#       MethodData_fieldTeam = FieldTeam,
#       MethodData_entryTeam = EntryTeam,
#       MethodData_uV1Desc = UV1Desc,
#       MethodData_uV2Desc = UV2Desc,
#       MethodData_uV3Desc = UV3Desc,
#       MethodData_saComment = SaComment,
#       MethodData_visited = Visited,
#       MethodData_index = Index,
#       MethodData_transect = Transect,
#       MethodData_subbelt = Subbelt,
#       MethodData_status = Status,
#       "MethodData_sizeCl (num.)" = SizeCl,
#       MethodData_ageCl = AgeCl,
#       MethodData_count = Count,
#       "MethodData_height (m)" = Height,
#       MethodData_subFrac = SubFrac,
#       MethodData_comment = Comment,
#       MethodData_uV1 = UV1,
#       MethodData_uV2 = UV2,
#       MethodData_uV3 = UV3
#       )
#   
#   
#   # save file
#   write.csv(Shrubs, paste0(path_save, target_park, "_Data_Density - Belts (metric).csv"), quote = FALSE, row.names = FALSE) 
# }
```

## Herbs Species Comp

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")

for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
  path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
  
  
  # load data
  HerbsSpComp_all <- read.csv(paste0(path_data, "Cover - Species Composition (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  HerbsSpComp_all <- HerbsSpComp_all[, -ncol(HerbsSpComp_all)]
  ## replace commas with semicolons
  HerbsSpComp_all[] <- lapply(HerbsSpComp_all, function(x) gsub(",", ";", x))
  
  
  # clean data
  HerbsSpComp_all <- HerbsSpComp_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## HerbsSpComp headers
  HerbsSpComp_header <- HerbsSpComp_all %>%
    filter(!is.na(Visited)) %>% 
    select(c(1:18,
             MinCovLevel, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## HerbsSpComp data
  HerbsSpComp_data <- HerbsSpComp_all %>%
    filter(is.na(Visited)) %>% 
    select(!c(MinCovLevel, Area, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  HerbsSpComp <- merge(HerbsSpComp_header, HerbsSpComp_data, by = c(1:18))
  
  
  # add column for park name
  HerbsSpComp <- HerbsSpComp %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # final column renaming to match metadata
  HerbsSpComp <- HerbsSpComp %>% 
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonitoringStatus_Name = Monitoring.Status,
      MonitoringStatus_Prefix = Status.Prefix,
      MonitoringStatus_Base = Status.Base,
      MonitoringStatus_Suffix = Status.Suffix,
      MonitoringStatus_Order = Status.Order,
      #Species_SymbolLocal = Species.Symbol,
      MethodData_symbolLocal = Species.Symbol,
      Species_LifeCycleLocal = Lifecycle,
      Species_NotBiological = NotBiological,
      Species_LifeFormNameLocal = Preferred_Lifeform,
      Species_Family = Family,
      Species_Genus = Genus,
      Species_ScientificName = ScientificName,
      Species_NativityLocal = Native.Species,
      Species_Invasive = Invasive.Species,
      "MethodData_minCovLevel (%)" = MinCovLevel,
      "MethodData_area (ha)" = Area,
      MethodData_fieldTeam = FieldTeam,
      MethodData_entryTeam = EntryTeam,
      MethodData_uV1Desc = UV1Desc,
      MethodData_uV2Desc = UV2Desc,
      MethodData_uV3Desc = UV3Desc,
      MethodData_saComment = SaComment,
      MethodData_visited = Visited,
      MethodData_index = Index,
      "MethodData_status (num.)" = Status, # why is this num?
      "MethodData_sizeCl (num.)" = SizeCl,
      MethodData_ageCl = AgeCl,
      MethodData_cover = Cover,
      "MethodData_height (m)" = Height,
      MethodData_comment = Comment,
      MethodData_uV1 = UV1,
      MethodData_uV2 = UV2,
      MethodData_uV3 = UV3
      )
  
  
  # save file
  write.csv(HerbsSpComp, paste0(path_save, target_park, "_Data_Cover - Species Composition (metric).csv"), quote = FALSE, row.names = FALSE) 
}
```

## Herbs Points

```{r}
parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GETT", "MONO", "NERI", "RICH", "SARA", "SHEN")

for(i in parks) {
  # select target park
  target_park <- i
  
  
  # adjust file paths
  path_data <- paste0(path_main, "Exports/", target_park, "/", target_park, "_")
  path_save <- paste0(path_main, "R Outputs Data Depot/", target_park, "/")
  
  
  # load data
  HerbsPoints_all <- read.csv(paste0(path_data, "Cover - Points (metric)_XPT.csv"), na.strings = c("","NA","N/A"))
  ## Drop last column if it's an empty placeholder (common in Excel exports)
  HerbsPoints_all <- HerbsPoints_all[, -ncol(HerbsPoints_all)]
  ## replace commas with semicolons
  HerbsPoints_all[] <- lapply(HerbsPoints_all, function(x) gsub(",", ";", x))
  
  
  # clean data
  HerbsPoints_all <- HerbsPoints_all %>%
    # remove trailing/leading whitespace
    mutate(across(where(is.character), str_trim)) %>%
    # separate Date column
    separate(Date, sep = " ", into = c("SampleEvent_Date", "Time")) %>%
    # remove unnecessary columns
    select(!c("Time"))
  
  
  # filter data
  ## HerbsPoints headers
  HerbsPoints_header <- HerbsPoints_all %>%
    filter(!is.na(Visited)) %>% 
    select(c(1:18,
             NumTran, TranLen, NumPtsTran, Offset, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  ## HerbsPoints data
  HerbsPoints_data <- HerbsPoints_all %>%
    filter(is.na(Visited)) %>% 
    select(!c(NumTran, TranLen, NumPtsTran, Offset, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV3Desc, SaComment, Visited))
  
  
  # merge data
  HerbsPoints <- merge(HerbsPoints_header, HerbsPoints_data, by = c(1:18))
  
  
  # add column for park name
  HerbsPoints <- HerbsPoints %>% 
    add_column(AdminUnit_Name = target_park, .before = "MacroPlot.Purpose")
  
  
  # final column renaming to match metadata
  HerbsPoints <- HerbsPoints %>% 
    dplyr::rename(
      Macroplot_Purpose = MacroPlot.Purpose,
      Macroplot_Type = MacroPlot.Type,
      Macroplot_UV1 = MacroPlot.UV1,
      Macroplot_UV2 = MacroPlot.UV2,
      Macroplot_UV3 = MacroPlot.UV3,
      Macroplot_UV4 = MacroPlot.UV4,
      Macroplot_UV5 = MacroPlot.UV5,
      Macroplot_UV6 = MacroPlot.UV6,
      Macroplot_UV7 = MacroPlot.UV7,
      Macroplot_UV8 = MacroPlot.UV8,
      Macroplot_Name = MacroPlot.Name,
      MonitoringStatus_Name = Monitoring.Status,
      MonitoringStatus_Prefix = Status.Prefix,
      MonitoringStatus_Base = Status.Base,
      MonitoringStatus_Suffix = Status.Suffix,
      MonitoringStatus_Order = Status.Order,
      #Species_SymbolLocal = Species.Symbol,
      MethodData_symbolLocal = Species.Symbol,
      Species_LifeCycleLocal = Lifecycle,
      Species_NotBiological = NotBiological,
      Species_LifeFormNameLocal = Preferred_Lifeform,
      Species_Family = Family,
      Species_Genus = Genus,
      Species_ScientificName = ScientificName,
      Species_NativityLocal = Native.Species,
      Species_Invasive = Invasive.Species,
      "MethodData_numTran (num.)" = NumTran,
      "MethodData_tranLen (m)" = TranLen,
      "MethodData_numPtsTran (num.)" = NumPtsTran,
      "MethodData_offset (m)" = Offset,
      MethodData_fieldTeam = FieldTeam,
      MethodData_entryTeam = EntryTeam,
      MethodData_uV1Desc = UV1Desc,
      MethodData_uV2Desc = UV2Desc,
      MethodData_uV3Desc = UV3Desc,
      MethodData_saComment = SaComment,
      MethodData_visited = Visited,
      MethodData_index = Index,
      "MethodData_transect (num.)" = Transect,
      "MethodData_point (num.)" = Point,
      "MethodData_tape (num.)" = Tape,
      "MethodData_order (num.)" = Order,
      "MethodData_height (m)" = Height,
      MethodData_canopyLayer = CanopyLayer,
      MethodData_status = Status,
      #MethodData_cover = # not in FFI
      MethodData_comment = Comment,
      MethodData_uV1 = UV1,
      MethodData_uV2 = UV2,
      MethodData_uV3 = UV3
      )
  
  
  # save file
  write.csv(HerbsPoints, paste0(path_save, target_park, "_Data_Cover - Points (metric).csv"), quote = FALSE, row.names = FALSE) 
}
```
