---
title: Complete CSVs
author: Alexandra Lalor
output:
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 1
    toc_float:
      smooth_scroll: true
    code_download: true
  word_document:
    toc: true
    toc_depth: 1
  pdf_document:
    toc: true
    toc_depth: 1
---

# PURPOSE

This code is intended to quality check [all FFI CSV exports]{.underline} for fundamental errors. If these errors are not addressed first, subsequent R scripts may not run properly.

### Export all CSVs from Data Depot

-   English_ffi_PARK_data_export\_#############.zip

-   Metric_ffi_PARK_data_export\_#############.zip

Populated Data includes:

-   ffi_PARK_data_export_project_units.csv

-   ffi_PARK_data_export_cover_points.csv

-   ffi_PARK_data_export_cover_species_composition.csv

-   ffi_PARK_data_export_surface_fuels_duff_litter.csv

-   ffi_PARK_data_export_surface_fuels_fine.csv

-   ffi_PARK_data_export_surface_fuels_thousand_hr.csv

-   ffi_PARK_data_export_trees_individuals.csv

Excess Data includes:

-   ffi_PARK_data_export_cover_frequency.csv

-   ffi_PARK_data_export_surface_fuels_alaska_duff_litter.csv

-   ffi_PARK_data_export_surface_fuels_piles.csv

-   ffi_PARK_data_export_surface_fuels_vegetation.csv

-   ffi_PARK_data_export_trees_saplings.csv

-   ffi_PARK_data_export_trees_seedlings.csv

Missing Protocols

-   Post Burn Severity (metric)\_XPT.csv

-   Density - Quadrats (metric)\_XPT.csv

-   Density - Belts (metric)\_XPT.csv

### Major issues to check across all CSVs

-   Check that protocols exist (manual check). For code to work across all Administration Units, you must export all relevant protocols across all parks. Even if no data exists, a CSV will export with correct protocol headers. If a CSV fails to export, the protocol may be missing or broken in FFI. In this case, take a blank protocol (headers but no data) and use it as a placeholder.

-   Check that columns match expected. If columns do not match across Administration Units, CSVs cannot be combined. Solutions include manually inserting columns with the missing headers (but with no data). If CSVs contains extra columns as empty placeholders (common in CSV exports), you can manually delete these columns or use R to remove them. The script Clean_1_all.Rmd contains this code already.

    For example: Fuels1000_all \<- Fuels1000_all[, -ncol(Fuels1000_all)]

-   Check that fundamental columns are not blank and are consistent between reports (e.g. Macroplot, ProjectUnit, MonStatus)

-   Check that data exists for every protocol which was visited. If data is missing or deviates from protocol, [make sure this is noted in the comment field of the protocol header]{.underline}.

    -   **No data (invalid):** If data should exist but doesn't, data may not have been entered into FFI yet.

    -   **No data (valid):** Certain protocols may not contain data for valid reasons (e.g. no trees, no coarse woody debris, no seedlings, no shrubs, etc...)

    -   **Incomplete data (invalid):** If protocols have fewer data points than expected, select data may be missing (e.g. data exists for 3 fuels transects instead of 4).

    -   **Incomplete data (valid):** Protocols may intentionally have fewer data points than expected (e.g. it was decided that certain plots would only have 1 herb transect instead of 2).

## Before Starting {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r install packages, include=FALSE}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
## Load Packages

# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
library(readr)
# janitor has functions to find duplicates
library(janitor)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr and LaTeX is used to create output files from R Markdown
library(knitr)
#library(LaTeX)
```

### Target Park {.hidden}

```{r}
# designate target park(s)
target_park <- "CATO"
```

### Adjust File Paths {.hidden}

```{r import data, include=FALSE}
# adjust file paths
#path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_file <- paste0(path_main, "Exports Data Depot/", target_park, "/")
path_data_english <- paste0(path_file, "English_ffi_", target_park, "_data_export/")
path_data_metric <- paste0(path_file, "Metric_ffi_", target_park, "_data_export/")
path_data_original <- paste0(path_main, "R Outputs Data Depot/", target_park, "/", target_park, "_")
```

### Zip Data {.hidden}

### Load Data {.hidden}

```{r}
# load data

# # project unit report
# ProjectUnitReport_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_project_units.csv"))
# ProjectUnitReport_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_project_units.csv"))

# protocols
Fuels1000_O <- read_csv(paste0(path_data_original, "Data_Surface Fuels - 1000Hr.csv"))
FuelsDuffLitt_O <- read_csv(paste0(path_data_original, "Data_Surface Fuels - Duff_Litter.csv"))
FuelsFine_O <- read_csv(paste0(path_data_original, "Data_Surface Fuels - Fine.csv"))
Trees_O <- read_csv(paste0(path_data_original, "Data_Trees - Individuals (metric).csv"))
HerbsSpComp_O <- read_csv(paste0(path_data_original, "Data_Cover - Species Composition (metric).csv"))
HerbsPoints_O <- read_csv(paste0(path_data_original, "Data_Cover - Points (metric).csv"))
# protocols
Fuels1000_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_surface_fuels_thousand_hr.csv"))
FuelsDuffLitt_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_surface_fuels_duff_litter.csv"))
FuelsFine_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_surface_fuels_fine.csv"))
Trees_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_trees_individuals.csv"))
HerbsSpComp_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_cover_species_composition.csv"))
HerbsPoints_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_cover_points.csv"))
# protocols
Fuels1000_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_surface_fuels_thousand_hr.csv"))
FuelsDuffLitt_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_surface_fuels_duff_litter.csv"))
FuelsFine_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_surface_fuels_fine.csv"))
Trees_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_trees_individuals.csv"))
HerbsSpComp_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_cover_species_composition.csv"))
HerbsPoints_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_cover_points.csv"))


# # blank protocols
# PostBurn_O <- read.csv(paste0(path_data_original, "Data_Post Burn Severity (metric).csv"))
# Seedlings_O <- read.csv(paste0(path_data_original, "Data_Density - Quadrats (metric).csv"))
# Shrubs_O <- read.csv(paste0(path_data_original, "Data_Density - Belts (metric).csv"))
# # blank protocols
# FuelsDuffLittAK_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_surface_fuels_alaska_duff_litter.csv"))
# FuelsPiles_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_surface_fuels_piles.csv"))
# FuelsVeg_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_surface_fuels_vegetation.csv"))
# TreesSaplings_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_trees_saplings.csv"))
# TreesSeedlings_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_trees_seedlings.csv"))
# HerbsFrequency_E <- read_csv(paste0(path_data_english, "ffi_", target_park, "_data_export_cover_frequency.csv"))
# # blank protocols
# FuelsDuffLittAK_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_surface_fuels_alaska_duff_litter.csv"))
# FuelsPiles_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_surface_fuels_piles.csv"))
# FuelsVeg_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_surface_fuels_vegetation.csv"))
# TreesSaplings_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_trees_saplings.csv"))
# TreesSeedlings_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_trees_seedlings.csv"))
# HerbsFrequency_M <- read_csv(paste0(path_data_metric, "ffi_", target_park, "_data_export_cover_frequency.csv"))
```

```{r}
# remove(PostBurn_O, Seedlings_O, Shrubs_O,
#        FuelsDuffLittAK_E, FuelsDuffLittAK_M,
#        FuelsPiles_E, FuelsPiles_M,
#        FuelsVeg_E, FuelsVeg_M,
#        TreesSaplings_E, TreesSaplings_M,
#        TreesSeedlings_E, TreesSeedlings_M,
#        HerbsFrequency_E, HerbsFrequency_M)
```

# Columns

-   If all successfully load, this means that column names match across all units and protocols

## All Protocols

```{r}
data <- HerbsPoints_M
```

```{r}
data_ID <- data %>% 
  select(c("OrganizationId","AdminUnitId","MacroplotId","MacroPlotId","SampleEventId","sampleEventId","MethodId","MethodDataId","MethodData_id"))

data_Macroplot <- data %>% 
  select(c("Organization_Name","AdminUnit_Name","AdminUnit_Comment","Macroplot_Name","Macroplot_Purpose","Macroplot_LocatedBy","Macroplot_Type","Macroplot_DdLat","Macroplot_DdLong","Macroplot_UtmX (m)","Macroplot_UtmY (m)","Macroplot_UtmZone","Macroplot_Pdop","Macroplot_Precision","Macroplot_DateIn","Macroplot_DateOut","Macroplot_Elevation","Macroplot_ElevationUnits","Macroplot_Azimuth","Macroplot_Aspect","Macroplot_SlopeHill (%)","Macroplot_SlopeTransect (%)","Macroplot_StartPoint","Macroplot_Directions","Macroplot_Comment","Macroplot_Datum","Macroplot_Metadata","Macroplot_FutureVisit","Macroplot_UV1","Macroplot_UV2","Macroplot_UV3","Macroplot_UV4","Macroplot_UV5","Macroplot_UV6","Macroplot_UV7","Macroplot_UV8")) %>% 
  unique()

data_SampleEvent <- data %>% 
  select(c("Macroplot_Name","SampleEvent_Date","SampleEvent_Who","SampleEvent_Comment","SampleEvent_UserVariables","SampleEvent_DefaultMonitoringStatus","SampleEvent_TreatmentUnit","SampleData_Executed","SampleData_SampleData")) %>% 
  unique()

data_MethodData <- data %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_visited","MethodData_fieldTeam","MethodData_entryTeam","MethodData_uV1Desc","MethodData_uV2Desc","MethodData_uV3Desc","MethodData_saComment","MethodData_createdDate","MethodData_updatedDate","MethodData_deletedDate","MethodData_comment","MethodData_uV1","MethodData_uV2","MethodData_uV3")) %>% 
  unique()
```

Species

```{r}
data_SpeciesData <- data %>% 
  select(c("Species_SourceEntityId","Species_LocalSpeciesId","Species_MasterSpeciesId","Species_AuxSpeciesId","Species_ITISTaxonomicSerialNumber","Species_SymbolLocal","Species_Symbol","Species_ScientificName","Species_CommonNameLocal","Species_CommonName","Species_Genus","Species_Family","Species_NotBiological","Species_Nativity","Species_NativityLocal","Species_Invasive","Species_LifeFormName","Species_LifeFormNameLocal","Species_Description","Species_LifeCycle","Species_LifeCycleLocal","Species_Cultural","Species_Concern","Species_Retired","Species_Comment","Species_UV1","Species_UV2","Species_UV3","MethodData_sppGuid"))
```

## PROTOCOL - SURFACE FUELS 1000HR (CWD)

English

```{r}
# select method data
data_MethodData_Data <- Fuels1000_E %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_index","MethodData_numTran (num.)","MethodData_tranLen (ft)","MethodData_transect (num.)","MethodData_slope (%)","MethodData_logNum (num.)","MethodData_dia (in.)","MethodData_decayCl","MethodData_cWDFuConSt")) %>% 
  arrange(MethodData_index)
```

Metric

```{r}
# select method data
data_MethodData_Data <- Fuels1000_M %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_index","MethodData_numTran (num.)","MethodData_tranLen (m)","MethodData_transect (num.)","MethodData_slope (%)","MethodData_logNum (num.)","MethodData_dia (cm)","MethodData_decayCl","MethodData_cWDFuConSt")) %>% 
  arrange(MethodData_index)
```

## PROTOCOL - SURFACE FUELS DUFF LITTER (DL)

English

```{r}
# select method data
data_MethodData_Data <- FuelsDuffLitt_E %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_index","MethodData_numTran (num.)","MethodData_transect (num.)","MethodData_sampLoc (ft)","MethodData_offSet","MethodData_littDep (in.)","MethodData_duffDep (in.)","MethodData_fuelbedDep (in.)","MethodData_dLFuConSt")) %>% 
  arrange(MethodData_index)
```

Metric

```{r}
# select method data
data_MethodData_Data <- FuelsDuffLitt_M %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_index","MethodData_numTran (num.)","MethodData_transect (num.)","MethodData_sampLoc (m)","MethodData_offSet","MethodData_littDep (cm)","MethodData_duffDep (cm)","MethodData_fuelbedDep (cm)","MethodData_dLFuConSt")) %>% 
  arrange(MethodData_index)
```

## PROTOCOL - SURFACE FUELS FINE FUELS (FWD)

English

```{r}
# select method data
data_MethodData_Data <- FuelsFine_E %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_numTran (num.)","MethodData_oneHrTranLen (ft)","MethodData_tenHrTranLen (ft)","MethodData_hunHrTranLen (ft)","MethodData_index","MethodData_transect (num.)","MethodData_azimuth (&#166;)","MethodData_slope (%)","MethodData_oneHr","MethodData_tenHr","MethodData_hunHr","MethodData_fWDFuConSt")) %>% 
  arrange(MethodData_index)
```

Metric

```{r}
# select method data
data_MethodData_Data <- FuelsFine_M %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_numTran (num.)","MethodData_oneHrTranLen (m)","MethodData_tenHrTranLen (m)","MethodData_hunHrTranLen (m)","MethodData_index","MethodData_transect (num.)","MethodData_azimuth (&#166;)","MethodData_slope (%)","MethodData_oneHr","MethodData_tenHr","MethodData_hunHr","MethodData_fWDFuConSt")) %>% 
  arrange(MethodData_index)
```

## PROTOCOL - POST BURN

English

```{r}
#values_data <- names(PostBurn_E)
```

Metric

```{r}
#values_data <- names(PostBurn_M)
```

## PROTOCOL - TREES

English

```{r}
# select method data
data_MethodData_Data <- Trees_E %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_macroPlotSize (ac)","MethodData_snagPlotSize (ac)","MethodData_breakPntDia","MethodData_index","MethodData_isVerified","MethodData_qTR (num.)","MethodData_subFrac (num.)","MethodData_tagNo (num.)","MethodData_symbolLocal","MethodData_status","MethodData_dBH (in.)","MethodData_ht (ft)","MethodData_crwnRto (%)","MethodData_crwnCl","MethodData_crFuBHt (ft)","MethodData_liCrBHt (ft)","MethodData_crwnRad (ft)","MethodData_age (yrs)","MethodData_grwthRt (in.)","MethodData_mort","MethodData_decayCl","MethodData_laddBaseHt (ft)","MethodData_laddMaxHt (ft)","MethodData_dRC (in.)","MethodData_nuLiStems","MethodData_nuDeStems","MethodData_eqDia (in.)","MethodData_xCoord (ft)","MethodData_yCoord (ft)","MethodData_cKR","MethodData_charHt (ft)","MethodData_scorchHt (ft)","MethodData_crScPct (%)","MethodData_damCd1","MethodData_damSev1 (num.)","MethodData_damCd2","MethodData_damSev2 (num.)","MethodData_damCd3","MethodData_damSev3 (num.)","MethodData_damCd4","MethodData_damSev4 (num.)","MethodData_damCd5","MethodData_damSev5 (num.)","MethodData_density","MethodData_basalArea")) %>% 
  arrange(MethodData_index)
```

Metric

```{r}
# select method data
data_MethodData_Data <- Trees_M %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_macroPlotSize (ha)","MethodData_snagPlotSize (ha)","MethodData_breakPntDia","MethodData_index","MethodData_isVerified","MethodData_qTR (num.)","MethodData_subFrac (num.)","MethodData_tagNo (num.)","MethodData_symbolLocal","MethodData_status","MethodData_dBH (cm)","MethodData_ht (m)","MethodData_crwnRto (%)","MethodData_crwnCl","MethodData_crFuBHt (m)","MethodData_liCrBHt (m)","MethodData_crwnRad (m)","MethodData_age (yrs)","MethodData_grwthRt (cm)","MethodData_mort","MethodData_decayCl","MethodData_laddBaseHt (m)","MethodData_laddMaxHt (m)","MethodData_dRC (cm)","MethodData_nuLiStems","MethodData_nuDeStems","MethodData_eqDia (cm)","MethodData_xCoord (m)","MethodData_yCoord (m)","MethodData_cKR","MethodData_charHt (m)","MethodData_scorchHt (m)","MethodData_crScPct (%)","MethodData_damCd1","MethodData_damSev1 (num.)","MethodData_damCd2","MethodData_damSev2 (num.)","MethodData_damCd3","MethodData_damSev3 (num.)","MethodData_damCd4","MethodData_damSev4 (num.)","MethodData_damCd5","MethodData_damSev5 (num.)","MethodData_density","MethodData_basalArea")) %>% 
  arrange(MethodData_index)
```

## PROTOCOL - SEEDLINGS

English

```{r}
#values_data <- names(Seedlings_E)
```

Metric

```{r}
#values_data <- names(Seedlings_M)
```

## PROTOCOL - SHRUBS

English

```{r}
#values_data <- names(Shrubs_E)
```

Metric

```{r}
#values_data <- names(Shrubs_M)
```

## PROTOCOL - HERBS SPECIES COMP

English

```{r}
# select method data
data_MethodData_Data <- HerbsSpComp_E %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_minCovLevel (%)","MethodData_area (ac)","MethodData_index","MethodData_status (num.)","MethodData_sizeCl (num.)","MethodData_ageCl","MethodData_cover","MethodData_height (ft)","MethodData_localSpeciesId","MethodData_localSpeciesSymbol","MethodData_speciesId")) %>% 
  arrange(MethodData_index)
```

Metric

```{r}
# select method data
data_MethodData_Data <- HerbsSpComp_M %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_minCovLevel (%)","MethodData_area (ha)","MethodData_index","MethodData_status (num.)","MethodData_sizeCl (num.)","MethodData_ageCl","MethodData_cover","MethodData_height (m)","MethodData_localSpeciesId","MethodData_localSpeciesSymbol","MethodData_speciesId")) %>% 
  arrange(MethodData_index)
```

## PROTOCOL - HERBS POINTS

English

```{r}
# select method data
data_MethodData_Data <- HerbsPoints_E %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_numTran (num.)","MethodData_tranLen (ft)","MethodData_numPtsTran (num.)","MethodData_offset (ft)","MethodData_index","MethodData_transect (num.)","MethodData_point (num.)","MethodData_tape (num.)","MethodData_order (num.)","MethodData_height (ft)","MethodData_status","MethodData_cover","MethodData_canopyLayer","MethodData_localSpeciesId","MethodData_localSpeciesSymbol","MethodData_speciesId")) %>% 
  arrange(MethodData_index)
```

Metric

```{r}
# select method data
data_MethodData_Data <- HerbsPoints_M %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_numTran (num.)","MethodData_tranLen (m)","MethodData_numPtsTran (num.)","MethodData_offset (m)","MethodData_index","MethodData_transect (num.)","MethodData_point (num.)","MethodData_tape (num.)","MethodData_order (num.)","MethodData_height (m)","MethodData_status","MethodData_cover","MethodData_canopyLayer","MethodData_localSpeciesId","MethodData_localSpeciesSymbol","MethodData_speciesId")) %>% 
  arrange(MethodData_index)
```

## PROTOCOL - HERBS FREQUENCY

English

```{r}
# # select method data
# data_MethodData_Data <- HerbsFrequency_E %>% 
#   select(c("MethodData_numTran (num.)", "MethodData_tranLen (ft)","MethodData_numQuadTran (num.)","MethodData_quadLen (in.)","MethodData_quadWid (in.)","MethodData_nFRatio","MethodData_nFNum","MethodData_index","MethodData_transect (num.)","MethodData_quadrat (num.)","MethodData_status (num.)","MethodData_nRF (num.)","MethodData_typeCov","MethodData_cover (%)","MethodData_height (ft)","MethodData_quadCover","MethodData_frequency","MethodData_localSpeciesId","MethodData_localSpeciesSymbol","MethodData_speciesId")) %>% 
#   arrange(MethodData_index)
```

Metric

```{r}
# # select method data
# data_MethodData_Data <- HerbsFrequency_M %>% 
#   select(c("MethodData_numTran (num.)", "MethodData_tranLen (m)","MethodData_numQuadTran (num.)","MethodData_quadLen (cm)","MethodData_quadWid (cm)","MethodData_nFRatio","MethodData_nFNum","MethodData_index","MethodData_transect (num.)","MethodData_quadrat (num.)","MethodData_status (num.)","MethodData_nRF (num.)","MethodData_typeCov","MethodData_cover (%)","MethodData_height (m)","MethodData_quadCover","MethodData_frequency","MethodData_localSpeciesId","MethodData_localSpeciesSymbol","MethodData_speciesId")) %>% 
#   arrange(MethodData_index)
```

# Metric vs English vs Original

## PROTOCOL - SURFACE FUELS 1000HR (CWD)

Header

```{r}
# select headers
data_MethodData_Header_E <- Fuels1000_E %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_tranLen (ft)")) %>% 
  unique()

data_MethodData_Header_M <- Fuels1000_M %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_tranLen (m)")) %>% 
  unique()

data_MethodData_Header_O <- Fuels1000_O %>% 
  select(c("TranLen")) %>% 
  unique() %>% 
  rename("MethodData_tranLen (org ft)" = TranLen)


data_MethodData_Header_merge <- merge(data_MethodData_Header_E, data_MethodData_Header_O)
data_MethodData_Header_units <- merge(data_MethodData_Header_M, data_MethodData_Header_merge)
remove(data_MethodData_Header_merge, data_MethodData_Header_O, data_MethodData_Header_E, data_MethodData_Header_M)
```

Data

```{r}
# select data
data_MethodData_Data_E <- Fuels1000_E %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_index","MethodData_transect (num.)","MethodData_dia (in.)")) %>% 
  arrange(MethodData_index)

data_MethodData_Data_M <- Fuels1000_M %>% 
  select(c("Macroplot_Name","SampleEvent_Date","MethodData_index","MethodData_transect (num.)","MethodData_dia (cm)")) %>% 
  arrange(MethodData_index)

data_MethodData_Data_O <- Fuels1000_O %>% 
  select(c("Index","Transect","Dia")) %>% 
  rename("MethodData_index" = Index,
         "MethodData_transect (num.)" = Transect,
         "MethodData_dia (org in.)" = Dia) %>% 
  arrange(MethodData_index)

data_MethodData_Data_merge <- merge(data_MethodData_Data_E, data_MethodData_Data_O)
data_MethodData_Data_units <- merge(data_MethodData_Data_M, data_MethodData_Data_merge)
remove(data_MethodData_Data_merge, data_MethodData_Data_O, data_MethodData_Data_E, data_MethodData_Data_M)
```

## PROTOCOL - SURFACE FUELS DUFF LITTER (DL)

Header

Data

## PROTOCOL - SURFACE FUELS FINE FUELS (FWD)

Header

Data

## PROTOCOL - POST BURN

Header

Data

## PROTOCOL - TREES

Header

Data

```{r}
"MethodData_macroPlotSize (ha)","MethodData_snagPlotSize (ha)","MethodData_dBH (cm)","MethodData_ht (m)","MethodData_crFuBHt (m)","MethodData_liCrBHt (m)","MethodData_crwnRad (m)","MethodData_grwthRt (cm)","MethodData_laddBaseHt (m)","MethodData_laddMaxHt (m)","MethodData_dRC (cm)","MethodData_eqDia (cm)","MethodData_xCoord (m)","MethodData_yCoord (m)","MethodData_charHt (m)","MethodData_scorchHt (m)","MethodData_density","MethodData_basalArea"
```

## PROTOCOL - SEEDLINGS

Header

Data

## PROTOCOL - SHRUBS

Header

Data

## PROTOCOL - HERBS SPECIES COMP

Header

Data

## PROTOCOL - HERBS POINTS

Header

Data

# PROJECT UNIT REPORT

[Procedure:]{.underline}

-   Check that columns match expected

```{r}
# Set parameters 
data <- ProjectUnitReport
values_data <- names(data)
values_valid <- c("Macroplot", "ProjectUnit", "Multi_PU")
MissingColumn <- setdiff(values_data, values_valid)
if(length(MissingColumn) == 0) {
  MissingColumn <- "none"
} else {
  MissingColumn <- paste((MissingColumn), collapse = ", ")
}

data$MissingColumn <- MissingColumn
query <- "Project Unit Report"
query_message <- "Missing/Extra Columns"
values_data <- data$MissingColumn
values_valid <- "none"
values_check <- values_data == values_valid

# Identify errors
errors_ProjectUnitReport_Columns <- qaqc(data, query, query_message, values_check)
errors_ProjectUnitReport_Columns <- unique(errors_ProjectUnitReport_Columns)
```

-   Check that Macroplot is not blank

```{r}
# Set parameters 
data <- ProjectUnitReport
query <- "Project Unit Report"
query_message <- "Macroplot" 
values_data <- data$Macroplot
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_ProjectUnitReport_Macroplot <- qaqc(data, query, query_message, values_check)
```

-   Check that ProjectUnit is not blank

```{r}
# Set parameters 
data <- ProjectUnitReport
query <- "Project Unit Report"
query_message <- "Project Unit" 
values_data <- data$ProjectUnit
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_ProjectUnitReport_ProjectUnit <- qaqc(data, query, query_message, values_check)
```

-   Check that Multi_PU = N or Y. If Multi_PU = Y, you will need to isolate which Project Unit contains the primary data for the analysis of interest.

```{r}
# Set parameters 
data <- ProjectUnitReport
query <- "Project Unit Report"
query_message <- "Multi Project Units" 
values_data <- data$Multi_PU
values_valid <- c("N")
values_check <- values_data %in% values_valid

# Identify errors
errors_ProjectUnitReport_MultiPU <- qaqc(data, query, query_message, values_check)
```

### Combine Project Unit Report Errors {.hidden}

```{r}
errors_ProjectUnitReport <- unique(rbind(errors_ProjectUnitReport_Quotes, errors_ProjectUnitReport_Commas, errors_ProjectUnitReport_Columns, errors_ProjectUnitReport_Macroplot, errors_ProjectUnitReport_ProjectUnit, errors_ProjectUnitReport_MultiPU))

remove(errors_ProjectUnitReport_Quotes, errors_ProjectUnitReport_Commas, errors_ProjectUnitReport_Columns, errors_ProjectUnitReport_Macroplot, errors_ProjectUnitReport_ProjectUnit, errors_ProjectUnitReport_MultiPU)

if(nrow(errors_ProjectUnitReport) > 1) {
  errors_ProjectUnitReport <- errors_ProjectUnitReport %>%
    filter(Error != "No Error")
} else {
  errors_ProjectUnitReport <- errors_ProjectUnitReport}
```

# Compare Rows

```{r}
data_depot <- FuelsFine_E
data_ffi <- FuelsFine_O
```

```{r}
data_depot <- data_depot %>% 
  select(!c("OrganizationId","AdminUnitId","MacroplotId","SampleEventId","MethodId","Organization_Name","AdminUnit_Comment","Macroplot_LocatedBy","Macroplot_DdLat","Macroplot_DdLong","Macroplot_UtmX (m)","Macroplot_UtmY (m)","Macroplot_UtmZone","Macroplot_Datum","Macroplot_Pdop","Macroplot_Precision","Macroplot_DateIn","Macroplot_FutureVisit","Macroplot_DateOut","Macroplot_Elevation","Macroplot_ElevationUnits","Macroplot_Azimuth","Macroplot_Aspect","Macroplot_SlopeHill (%)","Macroplot_SlopeTransect (%)","Macroplot_StartPoint","Macroplot_Directions","Macroplot_Comment","Macroplot_Metadata","SampleEvent_Who","SampleEvent_Comment","SampleEvent_UserVariables","SampleEvent_DefaultMonitoringStatus","SampleData_Executed","SampleData_SampleData","sampleEventId","MacroPlotId","MethodDataId","MethodData_id","MethodData_createdDate","MethodData_updatedDate","MethodData_deletedDate")) %>% 
  relocate(Macroplot_Name, .after = Macroplot_UV8) %>% 
  relocate(SampleEvent_TreatmentUnit, .after = Macroplot_Name) %>% 
  relocate(MethodData_visited, .before = MethodData_index) %>% 
  select(!c(Macroplot_Purpose,Macroplot_Type,Macroplot_UV1,Macroplot_UV2,Macroplot_UV3,Macroplot_UV4,Macroplot_UV5,Macroplot_UV6,Macroplot_UV7,Macroplot_UV8,SampleEvent_TreatmentUnit)) %>% 
  mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>% 
  arrange(Macroplot_Name, SampleEvent_Date, MethodData_index) %>% 
  select(!c(Macroplot_Name, MethodData_fieldTeam))


data_ffi <- data_ffi %>% 
  select(!c("MonitoringStatus_Name","MonitoringStatus_Prefix","MonitoringStatus_Base","MonitoringStatus_Suffix","MonitoringStatus_Order")) %>% 
  select(!c(Macroplot_Purpose,Macroplot_Type,Macroplot_UV1,Macroplot_UV2,Macroplot_UV3,Macroplot_UV4,Macroplot_UV5,Macroplot_UV6,Macroplot_UV7,Macroplot_UV8,SampleEvent_TreatmentUnit)) %>% 
  mutate(SampleEvent_Date = as.Date(SampleEvent_Date, "%m/%d/%Y")) %>% 
  arrange(Macroplot_Name, SampleEvent_Date, MethodData_index) %>% 
  select(!c(Macroplot_Name, MethodData_fieldTeam))
```

```{r}
data_depot <- data_depot %>% 
  select(c("Species_SourceEntityId","Species_LocalSpeciesId","Species_MasterSpeciesId","Species_AuxSpeciesId","Species_ITISTaxonomicSerialNumber","Species_SymbolLocal","Species_Symbol","Species_ScientificName","Species_CommonNameLocal","Species_CommonName","Species_Genus","Species_Family","Species_NotBiological","Species_Nativity","Species_NativityLocal","Species_Invasive","Species_LifeFormName","Species_LifeFormNameLocal","Species_Description","Species_LifeCycle","Species_LifeCycleLocal","Species_Cultural","Species_Concern","Species_Retired","Species_Comment","Species_UV1","Species_UV2","Species_UV3","MethodData_sppGuid"))
```

```{r}
all.equal(data_depot, data_ffi)
```
