---
title: Merge FFI Data
author: Alexandra Lalor
output:
  word_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# PURPOSE

This code is intended to combine FFI flat files (created using the Clean_1_All.Rmd script) across all Administration Units.

-   MetadataReport.csv
-   SpeciesReport.csv
-   Data_Surface Fuels - 1000Hr_XPT.csv
-   Data_Surface Fuels - Duff_Litter_XPT.csv
-   Data_Surface Fuels - Fine_XPT.csv
-   Data_Post Burn Severity (metric)\_XPT.csv
-   Data_Trees - Individuals (metric)\_XPT.csv
-   Data_Density - Quadrats (metric)\_XPT.csv
-   Data_Density - Belts (metric)\_XPT.csv
-   Data_Cover - Species Composition (metric)\_XPT.csv
-   Data_Cover - Points (metric)\_XPT.csv

## BEFORE STARTING {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
```

```{r}
## Load Packages

# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
library(stringr)
```

### Adjust File Paths {.hidden}

```{r}
# adjust file paths
path_main <- "E:/Allie/FireFX_NER/FFI Data Management/Exports Data Depot/"
#path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/Exports Data Depot/"
file_version <- "v2"

parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
```

# PROJECT UNITS

```{r}
file_names_df <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(file_names_df) <- c("FilePath", "FileName")

#list file names in each folder and add to date frame
for(i in 1:length(folder_names_list)) {
  target_park <- folder_names_list[1]
  folder_path_M <- paste0(path_main, target_park,"/", file_version ,"/Metric_ffi_", target_park, "_data_export/")
  folder_path_E <- paste0(path_main, target_park,"/", file_version ,"/English_ffi_", target_park, "_data_export/")
  file_names_M <- list.files(folder_path_M)
  file_names_E <- list.files(folder_path_E)
  file_path_M <- paste0(folder_path_M, file_names_M)
  file_path_E <- paste0(folder_path_E, file_names_E)
  
  file_names_M_df_1 <- data.frame(FilePath = file_path_M) %>% 
    separate(FilePath, sep = "_data_export_", 
             into = c("Temp", "CSV"), remove = FALSE) %>% 
    select(!c(Temp)) %>% 
    filter(grepl(".csv", CSV)) %>%
    separate(CSV, sep = ".csv", into = ("FileName"))
  file_names_df <- rbind(file_names_df, file_names_M_df_1)
}



```

```{r}
# Load data

# METRIC
ProjectUnitReport_ANTI_M <- read.csv(paste0(path_main, 
                            "/ANTI/v2/Metric_ffi_ANTI_data_export/ffi_ANTI_data_export_project_units.csv"))
ProjectUnitReport_APCO_M <- read.csv(paste0(path_main, 
                            "/APCO/v2/Metric_ffi_APCO_data_export/ffi_APCO_data_export_project_units.csv"))
ProjectUnitReport_CATO_M <- read.csv(paste0(path_main, 
                            "/CATO/v2/Metric_ffi_CATO_data_export/ffi_CATO_data_export_project_units.csv"))
ProjectUnitReport_CUVA_M <- read.csv(paste0(path_main, 
                            "/CUVA/v2/Metric_ffi_CUVA_data_export/ffi_CUVA_data_export_project_units.csv"))
ProjectUnitReport_DEWA_M <- read.csv(paste0(path_main, 
                            "/DEWA/v2/Metric_ffi_DEWA_data_export/ffi_DEWA_data_export_project_units.csv"))
ProjectUnitReport_FRSP_M <- read.csv(paste0(path_main, 
                            "/FRSP/v2/Metric_ffi_FRSP_data_export/ffi_FRSP_data_export_project_units.csv"))
ProjectUnitReport_GATE_M <- read.csv(paste0(path_main, 
                            "/GATE/v2/Metric_ffi_GATE_data_export/ffi_GATE_data_export_project_units.csv"))
ProjectUnitReport_GETT_M <- read.csv(paste0(path_main, 
                            "/GETT/v2/Metric_ffi_GETT_data_export/ffi_GETT_data_export_project_units.csv"))
ProjectUnitReport_MONO_M <- read.csv(paste0(path_main, 
                            "/MONO/v2/Metric_ffi_MONO_data_export/ffi_MONO_data_export_project_units.csv"))
ProjectUnitReport_NERI_M <- read.csv(paste0(path_main, 
                            "/NERI/v2/Metric_ffi_NERI_data_export/ffi_NERI_data_export_project_units.csv"))
ProjectUnitReport_PRWI_M <- read.csv(paste0(path_main, 
                            "/PRWI/v2/Metric_ffi_PRWI_data_export/ffi_PRWI_data_export_project_units.csv"))
ProjectUnitReport_RICH_M <- read.csv(paste0(path_main, 
                            "/RICH/v2/Metric_ffi_RICH_data_export/ffi_RICH_data_export_project_units.csv"))
ProjectUnitReport_SARA_M <- read.csv(paste0(path_main, 
                            "/SARA/v2/Metric_ffi_SARA_data_export/ffi_SARA_data_export_project_units.csv"))
ProjectUnitReport_SHEN_M <- read.csv(paste0(path_main, 
                            "/SHEN/v2/Metric_ffi_SHEN_data_export/ffi_SHEN_data_export_project_units.csv"))
ProjectUnitReport_VAFO_M <- read.csv(paste0(path_main, 
                            "/VAFO/v2/Metric_ffi_VAFO_data_export/ffi_VAFO_data_export_project_units.csv"))

# ENGLISH
ProjectUnitReport_ANTI_E <- read.csv(paste0(path_main, 
                            "/ANTI/v2/English_ffi_ANTI_data_export/ffi_ANTI_data_export_project_units.csv"))
ProjectUnitReport_APCO_E <- read.csv(paste0(path_main, 
                            "/APCO/v2/English_ffi_APCO_data_export/ffi_APCO_data_export_project_units.csv"))
ProjectUnitReport_CATO_E <- read.csv(paste0(path_main, 
                            "/CATO/v2/English_ffi_CATO_data_export/ffi_CATO_data_export_project_units.csv"))
ProjectUnitReport_CUVA_E <- read.csv(paste0(path_main, 
                            "/CUVA/v2/English_ffi_CUVA_data_export/ffi_CUVA_data_export_project_units.csv"))
ProjectUnitReport_DEWA_E <- read.csv(paste0(path_main, 
                            "/DEWA/v2/English_ffi_DEWA_data_export/ffi_DEWA_data_export_project_units.csv"))
ProjectUnitReport_FRSP_E <- read.csv(paste0(path_main, 
                            "/FRSP/v2/English_ffi_FRSP_data_export/ffi_FRSP_data_export_project_units.csv"))
ProjectUnitReport_GATE_E <- read.csv(paste0(path_main, 
                            "/GATE/v2/English_ffi_GATE_data_export/ffi_GATE_data_export_project_units.csv"))
ProjectUnitReport_GETT_E <- read.csv(paste0(path_main, 
                            "/GETT/v2/English_ffi_GETT_data_export/ffi_GETT_data_export_project_units.csv"))
ProjectUnitReport_MONO_E <- read.csv(paste0(path_main, 
                            "/MONO/v2/English_ffi_MONO_data_export/ffi_MONO_data_export_project_units.csv"))
ProjectUnitReport_NERI_E <- read.csv(paste0(path_main, 
                            "/NERI/v2/English_ffi_NERI_data_export/ffi_NERI_data_export_project_units.csv"))
ProjectUnitReport_PRWI_E <- read.csv(paste0(path_main, 
                            "/PRWI/v2/English_ffi_PRWI_data_export/ffi_PRWI_data_export_project_units.csv"))
ProjectUnitReport_RICH_E <- read.csv(paste0(path_main, 
                            "/RICH/v2/English_ffi_RICH_data_export/ffi_RICH_data_export_project_units.csv"))
ProjectUnitReport_SARA_E <- read.csv(paste0(path_main, 
                            "/SARA/v2/English_ffi_SARA_data_export/ffi_SARA_data_export_project_units.csv"))
ProjectUnitReport_SHEN_E <- read.csv(paste0(path_main, 
                            "/SHEN/v2/English_ffi_SHEN_data_export/ffi_SHEN_data_export_project_units.csv"))
ProjectUnitReport_VAFO_E <- read.csv(paste0(path_main, 
                            "/VAFO/v2/English_ffi_VAFO_data_export/ffi_VAFO_data_export_project_units.csv"))

# Add column for park name
# METRIC
ProjectUnitReport_ANTI_M <- ProjectUnitReport_ANTI_M %>% 
    add_column(AdminUnit_Name = "ANTI", .before = "ProjectUnit_Name")
ProjectUnitReport_APCO_M <- ProjectUnitReport_APCO_M %>% 
    add_column(AdminUnit_Name = "APCO", .before = "ProjectUnit_Name")
ProjectUnitReport_CATO_M <- ProjectUnitReport_CATO_M %>% 
    add_column(AdminUnit_Name = "CATO", .before = "ProjectUnit_Name")
ProjectUnitReport_CUVA_M <- ProjectUnitReport_CUVA_M %>% 
    add_column(AdminUnit_Name = "CUVA", .before = "ProjectUnit_Name")
ProjectUnitReport_DEWA_M <- ProjectUnitReport_DEWA_M %>% 
    add_column(AdminUnit_Name = "DEWA", .before = "ProjectUnit_Name")
ProjectUnitReport_FRSP_M <- ProjectUnitReport_FRSP_M %>% 
    add_column(AdminUnit_Name = "FRSP", .before = "ProjectUnit_Name")
ProjectUnitReport_GATE_M <- ProjectUnitReport_GATE_M %>% 
    add_column(AdminUnit_Name = "GATE", .before = "ProjectUnit_Name")
ProjectUnitReport_GETT_M <- ProjectUnitReport_GETT_M %>% 
    add_column(AdminUnit_Name = "GETT", .before = "ProjectUnit_Name")
ProjectUnitReport_MONO_M <- ProjectUnitReport_MONO_M %>% 
    add_column(AdminUnit_Name = "MONO", .before = "ProjectUnit_Name")
ProjectUnitReport_NERI_M <- ProjectUnitReport_NERI_M %>% 
    add_column(AdminUnit_Name = "NERI", .before = "ProjectUnit_Name")
ProjectUnitReport_PRWI_M <- ProjectUnitReport_PRWI_M %>% 
    add_column(AdminUnit_Name = "PRWI", .before = "ProjectUnit_Name")
ProjectUnitReport_RICH_M <- ProjectUnitReport_RICH_M %>% 
    add_column(AdminUnit_Name = "RICH", .before = "ProjectUnit_Name")
ProjectUnitReport_SARA_M <- ProjectUnitReport_SARA_M %>% 
    add_column(AdminUnit_Name = "SARA", .before = "ProjectUnit_Name")
ProjectUnitReport_SHEN_M <- ProjectUnitReport_SHEN_M %>% 
    add_column(AdminUnit_Name = "SHEN", .before = "ProjectUnit_Name")
ProjectUnitReport_VAFO_M <- ProjectUnitReport_VAFO_M %>% 
    add_column(AdminUnit_Name = "VAFO", .before = "ProjectUnit_Name")
# ENGLISH
ProjectUnitReport_ANTI_E <- ProjectUnitReport_ANTI_E %>% 
    add_column(AdminUnit_Name = "ANTI", .before = "ProjectUnit_Name")
ProjectUnitReport_APCO_E <- ProjectUnitReport_APCO_E %>% 
    add_column(AdminUnit_Name = "APCO", .before = "ProjectUnit_Name")
ProjectUnitReport_CATO_E <- ProjectUnitReport_CATO_E %>% 
    add_column(AdminUnit_Name = "CATO", .before = "ProjectUnit_Name")
ProjectUnitReport_CUVA_E <- ProjectUnitReport_CUVA_E %>% 
    add_column(AdminUnit_Name = "CUVA", .before = "ProjectUnit_Name")
ProjectUnitReport_DEWA_E <- ProjectUnitReport_DEWA_E %>% 
    add_column(AdminUnit_Name = "DEWA", .before = "ProjectUnit_Name")
ProjectUnitReport_FRSP_E <- ProjectUnitReport_FRSP_E %>% 
    add_column(AdminUnit_Name = "FRSP", .before = "ProjectUnit_Name")
ProjectUnitReport_GATE_E <- ProjectUnitReport_GATE_E %>% 
    add_column(AdminUnit_Name = "GATE", .before = "ProjectUnit_Name")
ProjectUnitReport_GETT_E <- ProjectUnitReport_GETT_E %>% 
    add_column(AdminUnit_Name = "GETT", .before = "ProjectUnit_Name")
ProjectUnitReport_MONO_E <- ProjectUnitReport_MONO_E %>% 
    add_column(AdminUnit_Name = "MONO", .before = "ProjectUnit_Name")
ProjectUnitReport_NERI_E <- ProjectUnitReport_NERI_E %>% 
    add_column(AdminUnit_Name = "NERI", .before = "ProjectUnit_Name")
ProjectUnitReport_PRWI_E <- ProjectUnitReport_PRWI_E %>% 
    add_column(AdminUnit_Name = "PRWI", .before = "ProjectUnit_Name")
ProjectUnitReport_RICH_E <- ProjectUnitReport_RICH_E %>% 
    add_column(AdminUnit_Name = "RICH", .before = "ProjectUnit_Name")
ProjectUnitReport_SARA_E <- ProjectUnitReport_SARA_E %>% 
    add_column(AdminUnit_Name = "SARA", .before = "ProjectUnit_Name")
ProjectUnitReport_SHEN_E <- ProjectUnitReport_SHEN_E %>% 
    add_column(AdminUnit_Name = "SHEN", .before = "ProjectUnit_Name")
ProjectUnitReport_VAFO_E <- ProjectUnitReport_VAFO_E %>% 
    add_column(AdminUnit_Name = "VAFO", .before = "ProjectUnit_Name")


# Merge data
# METRIC
ProjectUnitReport_M <- rbind(ProjectUnitReport_ANTI_M, ProjectUnitReport_APCO_M, ProjectUnitReport_CATO_M, ProjectUnitReport_CUVA_M, ProjectUnitReport_DEWA_M, ProjectUnitReport_FRSP_M, ProjectUnitReport_GATE_M, ProjectUnitReport_GETT_M, ProjectUnitReport_MONO_M, ProjectUnitReport_NERI_M, ProjectUnitReport_PRWI_M, ProjectUnitReport_RICH_M, ProjectUnitReport_SARA_M, ProjectUnitReport_SHEN_M, ProjectUnitReport_VAFO_M)
# ENGLISH
ProjectUnitReport_E <- rbind(ProjectUnitReport_ANTI_E, ProjectUnitReport_APCO_E, ProjectUnitReport_CATO_E, ProjectUnitReport_CUVA_E, ProjectUnitReport_DEWA_E, ProjectUnitReport_FRSP_E, ProjectUnitReport_GATE_E, ProjectUnitReport_GETT_E, ProjectUnitReport_MONO_E, ProjectUnitReport_NERI_E, ProjectUnitReport_PRWI_E, ProjectUnitReport_RICH_E, ProjectUnitReport_SARA_E, ProjectUnitReport_SHEN_E, ProjectUnitReport_VAFO_E)

# Remove data
# METRIC
remove(ProjectUnitReport_ANTI_M, ProjectUnitReport_APCO_M, ProjectUnitReport_CATO_M, ProjectUnitReport_CUVA_M, ProjectUnitReport_DEWA_M, ProjectUnitReport_FRSP_M, ProjectUnitReport_GATE_M, ProjectUnitReport_GETT_M, ProjectUnitReport_MONO_M, ProjectUnitReport_NERI_M, ProjectUnitReport_PRWI_M, ProjectUnitReport_RICH_M, ProjectUnitReport_SARA_M, ProjectUnitReport_SHEN_M, ProjectUnitReport_VAFO_M)
# ENGLISH
remove(ProjectUnitReport_ANTI_E, ProjectUnitReport_APCO_E, ProjectUnitReport_CATO_E, ProjectUnitReport_CUVA_E, ProjectUnitReport_DEWA_E, ProjectUnitReport_FRSP_E, ProjectUnitReport_GATE_E, ProjectUnitReport_GETT_E, ProjectUnitReport_MONO_E, ProjectUnitReport_NERI_E, ProjectUnitReport_PRWI_E, ProjectUnitReport_RICH_E, ProjectUnitReport_SARA_E, ProjectUnitReport_SHEN_E, ProjectUnitReport_VAFO_E)

# Save file
# METRIC
write.csv(ProjectUnitReport_M, paste0(path_main, "ALL/Metric/ALL_project_units.csv"), quote = FALSE, row.names = FALSE)
# ENGLISH
write.csv(ProjectUnitReport_E, paste0(path_main, "ALL/English/ALL_project_units.csv"), quote = FALSE, row.names = FALSE)
```

# PROTOCOLS

## Fuels 1000

```{r}
# Load data
Fuels1000_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Surface Fuels - 1000Hr.csv"))

# Merge data
Fuels1000 <- rbind(Fuels1000_ANTI, Fuels1000_APCO, Fuels1000_CATO, Fuels1000_CUVA, Fuels1000_DEWA, Fuels1000_FRSP, Fuels1000_GATE, Fuels1000_GETT, Fuels1000_MONO, Fuels1000_NERI, Fuels1000_PRWI, Fuels1000_RICH, Fuels1000_SARA, Fuels1000_SHEN, Fuels1000_VAFO)

# Remove data
remove(Fuels1000_ANTI, Fuels1000_APCO, Fuels1000_CATO, Fuels1000_CUVA, Fuels1000_DEWA, Fuels1000_FRSP, Fuels1000_GATE, Fuels1000_GETT, Fuels1000_MONO, Fuels1000_NERI, Fuels1000_PRWI, Fuels1000_RICH, Fuels1000_SARA, Fuels1000_SHEN, Fuels1000_VAFO)

# Save file
write.csv(Fuels1000, paste0(path_data, "ALL/ALL_Data_Surface Fuels - 1000Hr.csv"), quote = FALSE, row.names = FALSE)
```

## Fuels Duff Litt

```{r}
FuelsDuffLitt_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Surface Fuels - Duff_Litter.csv"))

# Merge data
FuelsDuffLitt <- rbind(FuelsDuffLitt_ANTI, FuelsDuffLitt_APCO, FuelsDuffLitt_CATO, FuelsDuffLitt_CUVA, FuelsDuffLitt_DEWA, FuelsDuffLitt_FRSP, FuelsDuffLitt_GATE, FuelsDuffLitt_GETT, FuelsDuffLitt_MONO, FuelsDuffLitt_NERI, FuelsDuffLitt_PRWI, FuelsDuffLitt_RICH, FuelsDuffLitt_SARA, FuelsDuffLitt_SHEN, FuelsDuffLitt_VAFO)

# Remove data
remove(FuelsDuffLitt_ANTI, FuelsDuffLitt_APCO, FuelsDuffLitt_CATO, FuelsDuffLitt_CUVA, FuelsDuffLitt_DEWA, FuelsDuffLitt_FRSP, FuelsDuffLitt_GATE, FuelsDuffLitt_GETT, FuelsDuffLitt_MONO, FuelsDuffLitt_NERI, FuelsDuffLitt_PRWI, FuelsDuffLitt_RICH, FuelsDuffLitt_SARA, FuelsDuffLitt_SHEN, FuelsDuffLitt_VAFO)

# Save file
write.csv(FuelsDuffLitt, paste0(path_data, "ALL/ALL_Data_Surface Fuels - Duff_Litter.csv"), quote = FALSE, row.names = FALSE)
```

## Fuels Fine

```{r}
FuelsFine_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Surface Fuels - Fine.csv"))
FuelsFine_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Surface Fuels - Fine.csv"))
FuelsFine_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Surface Fuels - Fine.csv"))
FuelsFine_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Surface Fuels - Fine.csv"))
FuelsFine_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Surface Fuels - Fine.csv"))
FuelsFine_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Surface Fuels - Fine.csv"))
FuelsFine_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Surface Fuels - Fine.csv"))
FuelsFine_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Surface Fuels - Fine.csv"))
FuelsFine_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Surface Fuels - Fine.csv"))
FuelsFine_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Surface Fuels - Fine.csv"))
FuelsFine_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Surface Fuels - Fine.csv"))
FuelsFine_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Surface Fuels - Fine.csv"))
FuelsFine_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Surface Fuels - Fine.csv"))
FuelsFine_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Surface Fuels - Fine.csv"))
FuelsFine_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Surface Fuels - Fine.csv"))

# Merge data
FuelsFine <- rbind(FuelsFine_ANTI, FuelsFine_APCO, FuelsFine_CATO, FuelsFine_CUVA, FuelsFine_DEWA, FuelsFine_FRSP, FuelsFine_GATE, FuelsFine_GETT, FuelsFine_MONO, FuelsFine_NERI, FuelsFine_PRWI, FuelsFine_RICH, FuelsFine_SARA, FuelsFine_SHEN, FuelsFine_VAFO)

# Remove data
remove(FuelsFine_ANTI, FuelsFine_APCO, FuelsFine_CATO, FuelsFine_CUVA, FuelsFine_DEWA, FuelsFine_FRSP, FuelsFine_GATE, FuelsFine_GETT, FuelsFine_MONO, FuelsFine_NERI, FuelsFine_PRWI, FuelsFine_RICH, FuelsFine_SARA, FuelsFine_SHEN, FuelsFine_VAFO)

# Save file
write.csv(FuelsFine, paste0(path_data, "ALL/ALL_Data_Surface Fuels - Fine.csv"), quote = FALSE, row.names = FALSE)
```

## Post Burn

```{r}
PostBurn_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Post Burn Severity (metric).csv"))
PostBurn_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Post Burn Severity (metric).csv"))
PostBurn_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Post Burn Severity (metric).csv"))
PostBurn_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Post Burn Severity (metric).csv"))
PostBurn_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Post Burn Severity (metric).csv"))
PostBurn_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Post Burn Severity (metric).csv"))
PostBurn_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Post Burn Severity (metric).csv"))
PostBurn_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Post Burn Severity (metric).csv"))
PostBurn_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Post Burn Severity (metric).csv"))
PostBurn_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Post Burn Severity (metric).csv"))
PostBurn_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Post Burn Severity (metric).csv"))
PostBurn_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Post Burn Severity (metric).csv"))
PostBurn_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Post Burn Severity (metric).csv"))
PostBurn_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Post Burn Severity (metric).csv"))
PostBurn_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Post Burn Severity (metric).csv"))

# Merge data
PostBurn <- rbind(PostBurn_ANTI, PostBurn_APCO, PostBurn_CATO, PostBurn_CUVA, PostBurn_DEWA, PostBurn_FRSP, PostBurn_GATE, PostBurn_GETT, PostBurn_MONO, PostBurn_NERI, PostBurn_PRWI, PostBurn_RICH, PostBurn_SARA, PostBurn_SHEN, PostBurn_VAFO)

# Remove data
remove(PostBurn_ANTI, PostBurn_APCO, PostBurn_CATO, PostBurn_CUVA, PostBurn_DEWA, PostBurn_FRSP, PostBurn_GATE, PostBurn_GETT, PostBurn_MONO, PostBurn_NERI, PostBurn_PRWI, PostBurn_RICH, PostBurn_SARA, PostBurn_SHEN, PostBurn_VAFO)

# Save file
write.csv(PostBurn, paste0(path_data, "ALL/ALL_Data_Post Burn Severity (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Trees

```{r}
Trees_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Trees - Individuals (metric).csv"))
Trees_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Trees - Individuals (metric).csv"))
Trees_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Trees - Individuals (metric).csv"))
Trees_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Trees - Individuals (metric).csv"))
Trees_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Trees - Individuals (metric).csv"))
Trees_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Trees - Individuals (metric).csv"))
Trees_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Trees - Individuals (metric).csv"))
Trees_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Trees - Individuals (metric).csv"))
Trees_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Trees - Individuals (metric).csv"))
Trees_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Trees - Individuals (metric).csv"))
Trees_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Trees - Individuals (metric).csv"))
Trees_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Trees - Individuals (metric).csv"))
Trees_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Trees - Individuals (metric).csv"))
Trees_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Trees - Individuals (metric).csv"))
Trees_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Trees - Individuals (metric).csv"))

# Merge data
Trees <- rbind(Trees_ANTI, Trees_APCO, Trees_CATO, Trees_CUVA, Trees_DEWA, Trees_FRSP, Trees_GATE, Trees_GETT, Trees_MONO, Trees_NERI, Trees_PRWI, Trees_RICH, Trees_SARA, Trees_SHEN, Trees_VAFO)

# Remove data
remove(Trees_ANTI, Trees_APCO, Trees_CATO, Trees_CUVA, Trees_DEWA, Trees_FRSP, Trees_GATE, Trees_GETT, Trees_MONO, Trees_NERI, Trees_PRWI, Trees_RICH, Trees_SARA, Trees_SHEN, Trees_VAFO)

# Save file
write.csv(Trees, paste0(path_data, "ALL/ALL_Data_Trees - Individuals (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Seedlings

```{r}
Seedlings_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Density - Quadrats (metric).csv"))
Seedlings_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Density - Quadrats (metric).csv"))
Seedlings_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Density - Quadrats (metric).csv"))
Seedlings_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Density - Quadrats (metric).csv"))
Seedlings_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Density - Quadrats (metric).csv"))
Seedlings_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Density - Quadrats (metric).csv"))
Seedlings_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Density - Quadrats (metric).csv"))
Seedlings_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Density - Quadrats (metric).csv"))
Seedlings_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Density - Quadrats (metric).csv"))
Seedlings_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Density - Quadrats (metric).csv"))
Seedlings_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Density - Quadrats (metric).csv"))
Seedlings_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Density - Quadrats (metric).csv"))
Seedlings_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Density - Quadrats (metric).csv"))
Seedlings_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Density - Quadrats (metric).csv"))
Seedlings_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Density - Quadrats (metric).csv"))

# Merge data
Seedlings <- rbind(Seedlings_ANTI, Seedlings_APCO, Seedlings_CATO, Seedlings_CUVA, Seedlings_DEWA, Seedlings_FRSP, Seedlings_GATE, Seedlings_GETT, Seedlings_MONO, Seedlings_NERI, Seedlings_PRWI, Seedlings_RICH, Seedlings_SARA, Seedlings_SHEN, Seedlings_VAFO)

# Remove data
remove(Seedlings_ANTI, Seedlings_APCO, Seedlings_CATO, Seedlings_CUVA, Seedlings_DEWA, Seedlings_FRSP, Seedlings_GATE, Seedlings_GETT, Seedlings_MONO, Seedlings_NERI, Seedlings_PRWI, Seedlings_RICH, Seedlings_SARA, Seedlings_SHEN, Seedlings_VAFO)

# Save file
write.csv(Seedlings, paste0(path_data, "ALL/ALL_Data_Density - Quadrats (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Shrubs

```{r}
Shrubs_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Density - Belts (metric).csv"))
Shrubs_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Density - Belts (metric).csv"))
Shrubs_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Density - Belts (metric).csv"))
Shrubs_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Density - Belts (metric).csv"))
Shrubs_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Density - Belts (metric).csv"))
Shrubs_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Density - Belts (metric).csv"))
Shrubs_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Density - Belts (metric).csv"))
Shrubs_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Density - Belts (metric).csv"))
Shrubs_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Density - Belts (metric).csv"))
Shrubs_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Density - Belts (metric).csv"))
Shrubs_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Density - Belts (metric).csv"))
Shrubs_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Density - Belts (metric).csv"))
Shrubs_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Density - Belts (metric).csv"))
Shrubs_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Density - Belts (metric).csv"))
Shrubs_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Density - Belts (metric).csv"))

# Merge data
Shrubs <- rbind(Shrubs_ANTI, Shrubs_APCO, Shrubs_CATO, Shrubs_CUVA, Shrubs_DEWA, Shrubs_FRSP, Shrubs_GATE, Shrubs_GETT, Shrubs_MONO, Shrubs_NERI, Shrubs_PRWI, Shrubs_RICH, Shrubs_SARA, Shrubs_SHEN, Shrubs_VAFO)

# Remove data
remove(Shrubs_ANTI, Shrubs_APCO, Shrubs_CATO, Shrubs_CUVA, Shrubs_DEWA, Shrubs_FRSP, Shrubs_GATE, Shrubs_GETT, Shrubs_MONO, Shrubs_NERI, Shrubs_PRWI, Shrubs_RICH, Shrubs_SARA, Shrubs_SHEN, Shrubs_VAFO)

# Save file
write.csv(Shrubs, paste0(path_data, "ALL/ALL_Data_Density - Belts (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Herbs Species Comp

```{r}
HerbsSpComp_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Cover - Species Composition (metric).csv"))

# Merge data
HerbsSpComp <- rbind(HerbsSpComp_ANTI, HerbsSpComp_APCO, HerbsSpComp_CATO, HerbsSpComp_CUVA, HerbsSpComp_DEWA, HerbsSpComp_FRSP, HerbsSpComp_GATE, HerbsSpComp_GETT, HerbsSpComp_MONO, HerbsSpComp_NERI, HerbsSpComp_PRWI, HerbsSpComp_RICH, HerbsSpComp_SARA, HerbsSpComp_SHEN, HerbsSpComp_VAFO)

# Remove data
remove(HerbsSpComp_ANTI, HerbsSpComp_APCO, HerbsSpComp_CATO, HerbsSpComp_CUVA, HerbsSpComp_DEWA, HerbsSpComp_FRSP, HerbsSpComp_GATE, HerbsSpComp_GETT, HerbsSpComp_MONO, HerbsSpComp_NERI, HerbsSpComp_PRWI, HerbsSpComp_RICH, HerbsSpComp_SARA, HerbsSpComp_SHEN, HerbsSpComp_VAFO)

# Save file
write.csv(HerbsSpComp, paste0(path_data, "ALL/ALL_Data_Cover - Species Composition (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Herbs Points

```{r}
HerbsPoints_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Cover - Points (metric).csv"))
HerbsPoints_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Cover - Points (metric).csv"))
HerbsPoints_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Cover - Points (metric).csv"))
HerbsPoints_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Cover - Points (metric).csv"))
HerbsPoints_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Cover - Points (metric).csv"))
HerbsPoints_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Cover - Points (metric).csv"))
HerbsPoints_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Cover - Points (metric).csv"))
HerbsPoints_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Cover - Points (metric).csv"))
HerbsPoints_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Cover - Points (metric).csv"))
HerbsPoints_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Cover - Points (metric).csv"))
HerbsPoints_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Cover - Points (metric).csv"))
HerbsPoints_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Cover - Points (metric).csv"))
HerbsPoints_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Cover - Points (metric).csv"))
HerbsPoints_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Cover - Points (metric).csv"))
HerbsPoints_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Cover - Points (metric).csv"))

# Merge data
HerbsPoints <- rbind(HerbsPoints_ANTI, HerbsPoints_APCO, HerbsPoints_CATO, HerbsPoints_CUVA, HerbsPoints_DEWA, HerbsPoints_FRSP, HerbsPoints_GATE, HerbsPoints_GETT, HerbsPoints_MONO, HerbsPoints_NERI, HerbsPoints_PRWI, HerbsPoints_RICH, HerbsPoints_SARA, HerbsPoints_SHEN, HerbsPoints_VAFO)

# Remove data
remove(HerbsPoints_ANTI, HerbsPoints_APCO, HerbsPoints_CATO, HerbsPoints_CUVA, HerbsPoints_DEWA, HerbsPoints_FRSP, HerbsPoints_GATE, HerbsPoints_GETT, HerbsPoints_MONO, HerbsPoints_NERI, HerbsPoints_PRWI, HerbsPoints_RICH, HerbsPoints_SARA, HerbsPoints_SHEN, HerbsPoints_VAFO)

# Save file
write.csv(HerbsPoints, paste0(path_data, "ALL/ALL_Data_Cover - Points (metric).csv"), quote = FALSE, row.names = FALSE)
```
