---
title: Merge FFI Data
author: Alexandra Lalor
output:
  word_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# PURPOSE

This code is intended to combine FFI flat files (created using the Clean_1_All.Rmd script) across all Administration Units.

-   MetadataReport.csv
-   SpeciesReport.csv
-   Data_Surface Fuels - 1000Hr_XPT.csv
-   Data_Surface Fuels - Duff_Litter_XPT.csv
-   Data_Surface Fuels - Fine_XPT.csv
-   Data_Post Burn Severity (metric)\_XPT.csv
-   Data_Trees - Individuals (metric)\_XPT.csv
-   Data_Density - Quadrats (metric)\_XPT.csv
-   Data_Density - Belts (metric)\_XPT.csv
-   Data_Cover - Species Composition (metric)\_XPT.csv
-   Data_Cover - Points (metric)\_XPT.csv

## BEFORE STARTING {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
```

```{r}
## Load Packages

# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
library(stringr)
```

### Adjust File Paths {.hidden}

```{r}
# adjust file paths
#path_main <- "E:/Allie/FireFX_NER/FFI Data Management/Exports Data Depot
path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/Exports Data Depot/"
file_version <- "v2"
path_save <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/R Outputs Data Depot/"
```

## Create list of files that need to be merged

```{r}
folder_names_list <- list.files(path_main)

file_names_df_M <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(file_names_df_M) <- c("FilePath", "FileName")

file_names_df_E <- data.frame(matrix(ncol = 2, nrow = 0))
colnames(file_names_df_E) <- c("FilePath", "FileName")


#list file names in each folder and add to data frame

# METRIC
for(i in 1:length(folder_names_list)) {
  
  target_park <- folder_names_list[i]
  
  folder_path_M <- paste0(path_main, target_park,"/", file_version ,"/Metric_ffi_", target_park, "_data_export/")
  
  file_names_M <- list.files(folder_path_M)
  
  file_path_M <- paste0(folder_path_M, file_names_M)
  
  file_names_df_M_1 <- data.frame(PathData = file_path_M) %>% 
    separate(PathData, sep = "_data_export_", 
             into = c("Temp", "FileName"), remove = FALSE) %>% 
    separate(Temp, sep = "/ffi_", 
             into = c("Temp", "TargetPark"), remove = FALSE) %>% 
    select(!c(Temp)) %>% 
    filter(grepl(".csv", FileName))
  
  file_names_df_M <- rbind(file_names_df_M, file_names_df_M_1)
}


# ENGLISH
for(i in 1:length(folder_names_list)) {
  
  target_park <- folder_names_list[i]
  
  folder_path_E <- paste0(path_main, target_park,"/", file_version ,"/English_ffi_", target_park, "_data_export/")
  file_names_E <- list.files(folder_path_E)
  file_path_E <- paste0(folder_path_E, file_names_E)
  
  file_names_df_E_1 <- data.frame(PathData = file_path_E) %>% 
    separate(PathData, sep = "_data_export_", 
             into = c("Temp", "FileName"), remove = FALSE) %>% 
    separate(Temp, sep = "/ffi_", 
             into = c("Temp", "TargetPark"), remove = FALSE) %>% 
    select(!c(Temp)) %>% 
    filter(grepl(".csv", FileName))
  
  file_names_df_E <- rbind(file_names_df_E, file_names_df_E_1)
}
```

# COLUMNS

```{r}
columns_ProjectUnit <- c("AdminUnitId", "ProjectUnitId", "MonitoringStatusId", "SampleEventId", "AdminUnit_Name", "ProjectUnit_Name", "ProjectUnit_Agency", "ProjectUnit_Area", "ProjectUnit_Grid", "ProjectUnit_AreaUnits", "ProjectUnit_DateIn", "ProjectUnit_DateOut", "ProjectUnit_Objective", "ProjectUnit_Description", "ProjectUnit_CreateCode", "ProjectUnit_Comment", "ProjectUnit_UserVariables", "MonitoringStatus_Name", "MonitoringStatus_Prefix", "MonitoringStatus_Base", "MonitoringStatus_Suffix", "MonitoringStatus_Order", "MonitoringStatus_Comment")


columns_ID <- c("OrganizationId","AdminUnitId","MacroplotId","SampleEventId","MethodId","MethodDataId","MethodData_Id")

columns_Macroplot <- c("Organization_Name","AdminUnit_Name","AdminUnit_Comment","Macroplot_Name","Macroplot_Purpose","Macroplot_LocatedBy","Macroplot_Type","Macroplot_DdLat","Macroplot_DdLong","Macroplot_UtmX (m)","Macroplot_UtmY (m)","Macroplot_UtmZone","Macroplot_Datum","Macroplot_Pdop","Macroplot_Precision","Macroplot_DateIn","Macroplot_DateOut","Macroplot_FutureVisit","Macroplot_Elevation","Macroplot_ElevationUnits","Macroplot_Azimuth","Macroplot_Aspect","Macroplot_SlopeHill (%)","Macroplot_SlopeTransect (%)","Macroplot_StartPoint","Macroplot_Directions","Macroplot_Comment","Macroplot_Metadata","Macroplot_UV1","Macroplot_UV2","Macroplot_UV3","Macroplot_UV4","Macroplot_UV5","Macroplot_UV6","Macroplot_UV7","Macroplot_UV8")

columns_SampleEvent <- c("SampleEvent_Date","SampleEvent_Who","SampleEvent_Comment","SampleEvent_UserVariables","SampleEvent_DefaultMonitoringStatus","SampleEvent_TreatmentUnit","SampleData_Executed")

columns_Species <- c("Species_SourceEntityId","Species_LocalSpeciesId","Species_MasterSpeciesId","Species_AuxSpeciesId","Species_ITISTaxonomicSerialNumber","Species_SymbolLocal","Species_Symbol","Species_ScientificName","Species_CommonNameLocal","Species_CommonName","Species_Genus","Species_Family","Species_NotBiological","Species_Nativity","Species_NativityLocal","Species_Invasive","Species_LifeFormName","Species_LifeFormNameLocal","Species_Description","Species_LifeCycle","Species_LifeCycleLocal","Species_Cultural","Species_Concern","Species_Retired","Species_Comment","Species_UV1","Species_UV2","Species_UV3","MethodData_SpeciesId","MethodData_LocalSpeciesId","MethodData_LocalSpeciesSymbol","MethodData_SymbolLocal","MethodData_SppGuid")

columns_MethodData <- c("MethodData_Visited","MethodData_FieldTeam","MethodData_EntryTeam","MethodData_UV1Desc","MethodData_UV2Desc","MethodData_UV3Desc","MethodData_SAComment","MethodData_CreatedDate","MethodData_UpdatedDate","MethodData_DeletedDate","MethodData_Comment","MethodData_UV1","MethodData_UV2","MethodData_UV3","MethodData_Index")



columns_Fuels1000_M <- c("MethodData_NumTran (num.)","MethodData_TranLen (m)","MethodData_Transect (num.)","MethodData_Slope (%)","MethodData_LogNum (num.)","MethodData_Dia (cm)","MethodData_DecayCl","MethodData_CWDFuConSt")
columns_Fuels1000_E <- c("MethodData_NumTran (num.)","MethodData_TranLen (ft)","MethodData_Transect (num.)","MethodData_Slope (%)","MethodData_LogNum (num.)","MethodData_Dia (in.)","MethodData_DecayCl","MethodData_CWDFuConSt")

columns_FuelsDuffLitt_M <- c("MethodData_NumTran (num.)","MethodData_Transect (num.)","MethodData_SampLoc (m)","MethodData_OffSet","MethodData_LittDep (cm)","MethodData_DuffDep (cm)","MethodData_FuelbedDep (cm)","MethodData_DLFuConSt")
columns_FuelsDuffLitt_E <- c("MethodData_NumTran (num.)","MethodData_Transect (num.)","MethodData_SampLoc (ft)","MethodData_OffSet","MethodData_LittDep (in.)","MethodData_DuffDep (in.)","MethodData_FuelbedDep (in.)","MethodData_DLFuConSt")

columns_FuelsFine_M <- c("MethodData_NumTran (num.)","MethodData_OneHrTranLen (m)","MethodData_TenHrTranLen (m)","MethodData_HunHrTranLen (m)","MethodData_Transect (num.)","MethodData_Azimuth (deg)","MethodData_Slope (%)","MethodData_OneHr","MethodData_TenHr","MethodData_HunHr","MethodData_FWDFuConSt")
columns_FuelsFine_E <- c("MethodData_NumTran (num.)","MethodData_OneHrTranLen (ft)","MethodData_TenHrTranLen (ft)","MethodData_HunHrTranLen (ft)","MethodData_Transect (num.)","MethodData_Azimuth (deg)","MethodData_Slope (%)","MethodData_OneHr","MethodData_TenHr","MethodData_HunHr","MethodData_FWDFuConSt")

columns_Trees_M <- c("MethodData_MacroPlotSize (ha)","MethodData_SnagPlotSize (ha)","MethodData_BrkPntDia (cm)","MethodData_IsVerified","MethodData_QTR (num.)","MethodData_SubFrac (num.)","MethodData_TagNo (num.)","MethodData_Status","MethodData_DBH (cm)","MethodData_Ht (m)","MethodData_CrwnRto (%)","MethodData_CrwnCl","MethodData_CrFuBHt (m)","MethodData_LiCrBHt (m)","MethodData_CrwnRad (m)","MethodData_Age (yrs)","MethodData_GrwthRt (cm)","MethodData_Mort","MethodData_DecayCl","MethodData_LaddBaseHt (m)","MethodData_LaddMaxHt (m)","MethodData_DRC (cm)","MethodData_NuLiStems","MethodData_NuDeStems","MethodData_EqDia (cm)","MethodData_XCoord (m)","MethodData_YCoord (m)","MethodData_CKR","MethodData_CharHt (m)","MethodData_ScorchHt (m)","MethodData_CrScPct (%)","MethodData_DamCd1","MethodData_DamSev1 (num.)","MethodData_DamCd2","MethodData_DamSev2 (num.)","MethodData_DamCd3","MethodData_DamSev3 (num.)","MethodData_DamCd4","MethodData_DamSev4 (num.)","MethodData_DamCd5","MethodData_DamSev5 (num.)","MethodData_Density","MethodData_BasalArea")
columns_Trees_E <- c("MethodData_MacroPlotSize (ac)","MethodData_SnagPlotSize (ac)","MethodData_BrkPntDia (in.)","MethodData_IsVerified","MethodData_QTR (num.)","MethodData_SubFrac (num.)","MethodData_TagNo (num.)","MethodData_Status","MethodData_DBH (in.)","MethodData_Ht (ft)","MethodData_CrwnRto (%)","MethodData_CrwnCl","MethodData_CrFuBHt (ft)","MethodData_LiCrBHt (ft)","MethodData_CrwnRad (ft)","MethodData_Age (yrs)","MethodData_GrwthRt (cm)","MethodData_Mort","MethodData_DecayCl","MethodData_LaddBaseHt (m)","MethodData_LaddMaxHt (ft)","MethodData_DRC (in.)","MethodData_NuLiStems","MethodData_NuDeStems","MethodData_EqDia (in.)","MethodData_XCoord (ft)","MethodData_YCoord (ft)","MethodData_CKR","MethodData_CharHt (ft)","MethodData_ScorchHt (ft)","MethodData_CrScPct (%)","MethodData_DamCd1","MethodData_DamSev1 (num.)","MethodData_DamCd2","MethodData_DamSev2 (num.)","MethodData_DamCd3","MethodData_DamSev3 (num.)","MethodData_DamCd4","MethodData_DamSev4 (num.)","MethodData_DamCd5","MethodData_DamSev5 (num.)","MethodData_Density","MethodData_BasalArea")

columns_HerbsSpComp_M <- c("MethodData_MinCovLevel (%)","MethodData_Area (ha)","MethodData_Status (num.)","MethodData_SizeCl (num.)","MethodData_AgeCl","MethodData_Cover","MethodData_Height (m)")
columns_HerbsSpComp_E <- c("MethodData_MinCovLevel (%)","MethodData_Area (ac)","MethodData_Status (num.)","MethodData_SizeCl (num.)","MethodData_AgeCl","MethodData_Cover","MethodData_Height (ft)")

columns_HerbsPoints_M <- c("MethodData_NumTran (num.)","MethodData_TranLen (m)","MethodData_NumPtsTran (num.)","MethodData_Offset (m)","MethodData_Transect (num.)","MethodData_Point (num.)","MethodData_Tape (num.)","MethodData_Order (num.)","MethodData_Height (m)","MethodData_Status","MethodData_Cover","MethodData_CanopyLayer")
columns_HerbsPoints_E <- c("MethodData_NumTran (num.)","MethodData_TranLen (ft)","MethodData_NumPtsTran (num.)","MethodData_Offset (ft)","MethodData_Transect (num.)","MethodData_Point (num.)","MethodData_Tape (num.)","MethodData_Order (num.)","MethodData_Height (ft)","MethodData_Status","MethodData_Cover","MethodData_CanopyLayer")
```

# PROJECT UNIT REPORT

## Prep

```{r}
file_M <- file_names_df_M %>% 
  filter(FileName == "project_units.csv")

file_E <- file_names_df_E %>% 
  filter(FileName == "project_units.csv")

ProjectUnitReport_M <- data.frame(matrix(ncol = 23, nrow = 0))
colnames(ProjectUnitReport_M) <- c(columns_ProjectUnit)
  
ProjectUnitReport_E <- data.frame(matrix(ncol = 23, nrow = 0))
colnames(ProjectUnitReport_E) <- c(columns_ProjectUnit)
```

## For loop

```{r}
# METRIC

for(i in 1:nrow(file_M)) {
  
  PathData <- file_M[i,1]
  TargetPark <- file_M[i,2]
  Report_M <- read.csv(PathData)
  
  Report_M <- Report_M %>% 
    add_column(AdminUnit_Name = TargetPark, .before = "ProjectUnit_Name")
  
  Report_M <- Report_M[,columns_ProjectUnit]
  
  ProjectUnitReport_M <- rbind(ProjectUnitReport_M, Report_M)
}

write.csv(ProjectUnitReport_M, paste0(path_save, "ALL/Metric/ALL_project_units.csv"), quote = FALSE, row.names = FALSE)
```

```{r}
# ENGLISH

for(i in 1:nrow(file_E)) {
  
  PathData <- file_E[i,1]
  TargetPark <- file_E[i,2]
  Report_E <- read.csv(PathData)
  
  Report_E <- Report_E %>% 
    add_column(AdminUnit_Name = TargetPark, .before = "ProjectUnit_Name")
  
  Report_E <- Report_E[,columns_ProjectUnit]
  
  ProjectUnitReport_E <- rbind(ProjectUnitReport_E, Report_E_1)
}

write.csv(ProjectUnitReport_E, paste0(path_save, "ALL/English/ALL_project_units.csv"), quote = FALSE, row.names = FALSE)
```

## Long form

```{r}
# # Load data
# 
# # METRIC
# ProjectUnitReport_ANTI_M <- read.csv(paste0(path_main, 
#                             "/ANTI/v2/Metric_ffi_ANTI_data_export/ffi_ANTI_data_export_project_units.csv"))
# ProjectUnitReport_APCO_M <- read.csv(paste0(path_main, 
#                             "/APCO/v2/Metric_ffi_APCO_data_export/ffi_APCO_data_export_project_units.csv"))
# ProjectUnitReport_CATO_M <- read.csv(paste0(path_main, 
#                             "/CATO/v2/Metric_ffi_CATO_data_export/ffi_CATO_data_export_project_units.csv"))
# ProjectUnitReport_CUVA_M <- read.csv(paste0(path_main, 
#                             "/CUVA/v2/Metric_ffi_CUVA_data_export/ffi_CUVA_data_export_project_units.csv"))
# ProjectUnitReport_DEWA_M <- read.csv(paste0(path_main, 
#                             "/DEWA/v2/Metric_ffi_DEWA_data_export/ffi_DEWA_data_export_project_units.csv"))
# ProjectUnitReport_FRSP_M <- read.csv(paste0(path_main, 
#                             "/FRSP/v2/Metric_ffi_FRSP_data_export/ffi_FRSP_data_export_project_units.csv"))
# ProjectUnitReport_GATE_M <- read.csv(paste0(path_main, 
#                             "/GATE/v2/Metric_ffi_GATE_data_export/ffi_GATE_data_export_project_units.csv"))
# ProjectUnitReport_GETT_M <- read.csv(paste0(path_main, 
#                             "/GETT/v2/Metric_ffi_GETT_data_export/ffi_GETT_data_export_project_units.csv"))
# ProjectUnitReport_MONO_M <- read.csv(paste0(path_main, 
#                             "/MONO/v2/Metric_ffi_MONO_data_export/ffi_MONO_data_export_project_units.csv"))
# ProjectUnitReport_NERI_M <- read.csv(paste0(path_main, 
#                             "/NERI/v2/Metric_ffi_NERI_data_export/ffi_NERI_data_export_project_units.csv"))
# ProjectUnitReport_PRWI_M <- read.csv(paste0(path_main, 
#                             "/PRWI/v2/Metric_ffi_PRWI_data_export/ffi_PRWI_data_export_project_units.csv"))
# ProjectUnitReport_RICH_M <- read.csv(paste0(path_main, 
#                             "/RICH/v2/Metric_ffi_RICH_data_export/ffi_RICH_data_export_project_units.csv"))
# ProjectUnitReport_SARA_M <- read.csv(paste0(path_main, 
#                             "/SARA/v2/Metric_ffi_SARA_data_export/ffi_SARA_data_export_project_units.csv"))
# ProjectUnitReport_SHEN_M <- read.csv(paste0(path_main, 
#                             "/SHEN/v2/Metric_ffi_SHEN_data_export/ffi_SHEN_data_export_project_units.csv"))
# ProjectUnitReport_VAFO_M <- read.csv(paste0(path_main, 
#                             "/VAFO/v2/Metric_ffi_VAFO_data_export/ffi_VAFO_data_export_project_units.csv"))
# 
# # ENGLISH
# ProjectUnitReport_ANTI_E <- read.csv(paste0(path_main, 
#                             "/ANTI/v2/English_ffi_ANTI_data_export/ffi_ANTI_data_export_project_units.csv"))
# ProjectUnitReport_APCO_E <- read.csv(paste0(path_main, 
#                             "/APCO/v2/English_ffi_APCO_data_export/ffi_APCO_data_export_project_units.csv"))
# ProjectUnitReport_CATO_E <- read.csv(paste0(path_main, 
#                             "/CATO/v2/English_ffi_CATO_data_export/ffi_CATO_data_export_project_units.csv"))
# ProjectUnitReport_CUVA_E <- read.csv(paste0(path_main, 
#                             "/CUVA/v2/English_ffi_CUVA_data_export/ffi_CUVA_data_export_project_units.csv"))
# ProjectUnitReport_DEWA_E <- read.csv(paste0(path_main, 
#                             "/DEWA/v2/English_ffi_DEWA_data_export/ffi_DEWA_data_export_project_units.csv"))
# ProjectUnitReport_FRSP_E <- read.csv(paste0(path_main, 
#                             "/FRSP/v2/English_ffi_FRSP_data_export/ffi_FRSP_data_export_project_units.csv"))
# ProjectUnitReport_GATE_E <- read.csv(paste0(path_main, 
#                             "/GATE/v2/English_ffi_GATE_data_export/ffi_GATE_data_export_project_units.csv"))
# ProjectUnitReport_GETT_E <- read.csv(paste0(path_main, 
#                             "/GETT/v2/English_ffi_GETT_data_export/ffi_GETT_data_export_project_units.csv"))
# ProjectUnitReport_MONO_E <- read.csv(paste0(path_main, 
#                             "/MONO/v2/English_ffi_MONO_data_export/ffi_MONO_data_export_project_units.csv"))
# ProjectUnitReport_NERI_E <- read.csv(paste0(path_main, 
#                             "/NERI/v2/English_ffi_NERI_data_export/ffi_NERI_data_export_project_units.csv"))
# ProjectUnitReport_PRWI_E <- read.csv(paste0(path_main, 
#                             "/PRWI/v2/English_ffi_PRWI_data_export/ffi_PRWI_data_export_project_units.csv"))
# ProjectUnitReport_RICH_E <- read.csv(paste0(path_main, 
#                             "/RICH/v2/English_ffi_RICH_data_export/ffi_RICH_data_export_project_units.csv"))
# ProjectUnitReport_SARA_E <- read.csv(paste0(path_main, 
#                             "/SARA/v2/English_ffi_SARA_data_export/ffi_SARA_data_export_project_units.csv"))
# ProjectUnitReport_SHEN_E <- read.csv(paste0(path_main, 
#                             "/SHEN/v2/English_ffi_SHEN_data_export/ffi_SHEN_data_export_project_units.csv"))
# ProjectUnitReport_VAFO_E <- read.csv(paste0(path_main, 
#                             "/VAFO/v2/English_ffi_VAFO_data_export/ffi_VAFO_data_export_project_units.csv"))
# 
# # Add column for park name
# # METRIC
# ProjectUnitReport_ANTI_M <- ProjectUnitReport_ANTI_M %>% 
#     add_column(AdminUnit_Name = "ANTI", .before = "ProjectUnit_Name")
# ProjectUnitReport_APCO_M <- ProjectUnitReport_APCO_M %>% 
#     add_column(AdminUnit_Name = "APCO", .before = "ProjectUnit_Name")
# ProjectUnitReport_CATO_M <- ProjectUnitReport_CATO_M %>% 
#     add_column(AdminUnit_Name = "CATO", .before = "ProjectUnit_Name")
# ProjectUnitReport_CUVA_M <- ProjectUnitReport_CUVA_M %>% 
#     add_column(AdminUnit_Name = "CUVA", .before = "ProjectUnit_Name")
# ProjectUnitReport_DEWA_M <- ProjectUnitReport_DEWA_M %>% 
#     add_column(AdminUnit_Name = "DEWA", .before = "ProjectUnit_Name")
# ProjectUnitReport_FRSP_M <- ProjectUnitReport_FRSP_M %>% 
#     add_column(AdminUnit_Name = "FRSP", .before = "ProjectUnit_Name")
# ProjectUnitReport_GATE_M <- ProjectUnitReport_GATE_M %>% 
#     add_column(AdminUnit_Name = "GATE", .before = "ProjectUnit_Name")
# ProjectUnitReport_GETT_M <- ProjectUnitReport_GETT_M %>% 
#     add_column(AdminUnit_Name = "GETT", .before = "ProjectUnit_Name")
# ProjectUnitReport_MONO_M <- ProjectUnitReport_MONO_M %>% 
#     add_column(AdminUnit_Name = "MONO", .before = "ProjectUnit_Name")
# ProjectUnitReport_NERI_M <- ProjectUnitReport_NERI_M %>% 
#     add_column(AdminUnit_Name = "NERI", .before = "ProjectUnit_Name")
# ProjectUnitReport_PRWI_M <- ProjectUnitReport_PRWI_M %>% 
#     add_column(AdminUnit_Name = "PRWI", .before = "ProjectUnit_Name")
# ProjectUnitReport_RICH_M <- ProjectUnitReport_RICH_M %>% 
#     add_column(AdminUnit_Name = "RICH", .before = "ProjectUnit_Name")
# ProjectUnitReport_SARA_M <- ProjectUnitReport_SARA_M %>% 
#     add_column(AdminUnit_Name = "SARA", .before = "ProjectUnit_Name")
# ProjectUnitReport_SHEN_M <- ProjectUnitReport_SHEN_M %>% 
#     add_column(AdminUnit_Name = "SHEN", .before = "ProjectUnit_Name")
# ProjectUnitReport_VAFO_M <- ProjectUnitReport_VAFO_M %>% 
#     add_column(AdminUnit_Name = "VAFO", .before = "ProjectUnit_Name")
# # ENGLISH
# ProjectUnitReport_ANTI_E <- ProjectUnitReport_ANTI_E %>% 
#     add_column(AdminUnit_Name = "ANTI", .before = "ProjectUnit_Name")
# ProjectUnitReport_APCO_E <- ProjectUnitReport_APCO_E %>% 
#     add_column(AdminUnit_Name = "APCO", .before = "ProjectUnit_Name")
# ProjectUnitReport_CATO_E <- ProjectUnitReport_CATO_E %>% 
#     add_column(AdminUnit_Name = "CATO", .before = "ProjectUnit_Name")
# ProjectUnitReport_CUVA_E <- ProjectUnitReport_CUVA_E %>% 
#     add_column(AdminUnit_Name = "CUVA", .before = "ProjectUnit_Name")
# ProjectUnitReport_DEWA_E <- ProjectUnitReport_DEWA_E %>% 
#     add_column(AdminUnit_Name = "DEWA", .before = "ProjectUnit_Name")
# ProjectUnitReport_FRSP_E <- ProjectUnitReport_FRSP_E %>% 
#     add_column(AdminUnit_Name = "FRSP", .before = "ProjectUnit_Name")
# ProjectUnitReport_GATE_E <- ProjectUnitReport_GATE_E %>% 
#     add_column(AdminUnit_Name = "GATE", .before = "ProjectUnit_Name")
# ProjectUnitReport_GETT_E <- ProjectUnitReport_GETT_E %>% 
#     add_column(AdminUnit_Name = "GETT", .before = "ProjectUnit_Name")
# ProjectUnitReport_MONO_E <- ProjectUnitReport_MONO_E %>% 
#     add_column(AdminUnit_Name = "MONO", .before = "ProjectUnit_Name")
# ProjectUnitReport_NERI_E <- ProjectUnitReport_NERI_E %>% 
#     add_column(AdminUnit_Name = "NERI", .before = "ProjectUnit_Name")
# ProjectUnitReport_PRWI_E <- ProjectUnitReport_PRWI_E %>% 
#     add_column(AdminUnit_Name = "PRWI", .before = "ProjectUnit_Name")
# ProjectUnitReport_RICH_E <- ProjectUnitReport_RICH_E %>% 
#     add_column(AdminUnit_Name = "RICH", .before = "ProjectUnit_Name")
# ProjectUnitReport_SARA_E <- ProjectUnitReport_SARA_E %>% 
#     add_column(AdminUnit_Name = "SARA", .before = "ProjectUnit_Name")
# ProjectUnitReport_SHEN_E <- ProjectUnitReport_SHEN_E %>% 
#     add_column(AdminUnit_Name = "SHEN", .before = "ProjectUnit_Name")
# ProjectUnitReport_VAFO_E <- ProjectUnitReport_VAFO_E %>% 
#     add_column(AdminUnit_Name = "VAFO", .before = "ProjectUnit_Name")
# 
# 
# # Merge data
# # METRIC
# ProjectUnitReport_M <- rbind(ProjectUnitReport_ANTI_M, ProjectUnitReport_APCO_M, ProjectUnitReport_CATO_M, ProjectUnitReport_CUVA_M, ProjectUnitReport_DEWA_M, ProjectUnitReport_FRSP_M, ProjectUnitReport_GATE_M, ProjectUnitReport_GETT_M, ProjectUnitReport_MONO_M, ProjectUnitReport_NERI_M, ProjectUnitReport_PRWI_M, ProjectUnitReport_RICH_M, ProjectUnitReport_SARA_M, ProjectUnitReport_SHEN_M, ProjectUnitReport_VAFO_M)
# # ENGLISH
# ProjectUnitReport_E <- rbind(ProjectUnitReport_ANTI_E, ProjectUnitReport_APCO_E, ProjectUnitReport_CATO_E, ProjectUnitReport_CUVA_E, ProjectUnitReport_DEWA_E, ProjectUnitReport_FRSP_E, ProjectUnitReport_GATE_E, ProjectUnitReport_GETT_E, ProjectUnitReport_MONO_E, ProjectUnitReport_NERI_E, ProjectUnitReport_PRWI_E, ProjectUnitReport_RICH_E, ProjectUnitReport_SARA_E, ProjectUnitReport_SHEN_E, ProjectUnitReport_VAFO_E)
# 
# # Remove data
# # METRIC
# remove(ProjectUnitReport_ANTI_M, ProjectUnitReport_APCO_M, ProjectUnitReport_CATO_M, ProjectUnitReport_CUVA_M, ProjectUnitReport_DEWA_M, ProjectUnitReport_FRSP_M, ProjectUnitReport_GATE_M, ProjectUnitReport_GETT_M, ProjectUnitReport_MONO_M, ProjectUnitReport_NERI_M, ProjectUnitReport_PRWI_M, ProjectUnitReport_RICH_M, ProjectUnitReport_SARA_M, ProjectUnitReport_SHEN_M, ProjectUnitReport_VAFO_M)
# # ENGLISH
# remove(ProjectUnitReport_ANTI_E, ProjectUnitReport_APCO_E, ProjectUnitReport_CATO_E, ProjectUnitReport_CUVA_E, ProjectUnitReport_DEWA_E, ProjectUnitReport_FRSP_E, ProjectUnitReport_GATE_E, ProjectUnitReport_GETT_E, ProjectUnitReport_MONO_E, ProjectUnitReport_NERI_E, ProjectUnitReport_PRWI_E, ProjectUnitReport_RICH_E, ProjectUnitReport_SARA_E, ProjectUnitReport_SHEN_E, ProjectUnitReport_VAFO_E)
# 
# # Save file
# # METRIC
# write.csv(ProjectUnitReport_M, paste0(path_main, "ALL/Metric/ALL_project_units.csv"), quote = FALSE, row.names = FALSE)
# # ENGLISH
# write.csv(ProjectUnitReport_E, paste0(path_main, "ALL/English/ALL_project_units.csv"), quote = FALSE, row.names = FALSE)
```

# PROTOCOLS

## Fuels 1000

### Prep

```{r}
file_M <- file_names_df_M %>% 
  filter(FileName == "surface_fuels_thousand_hr.csv")

file_E <- file_names_df_E %>% 
  filter(FileName == "surface_fuels_thousand_hr.csv")

Fuels1000_M <- data.frame(matrix(ncol = 23, nrow = 0))
colnames(Fuels1000_M) <- c()
  
Fuels1000_E <- data.frame(matrix(ncol = 23, nrow = 0))
colnames(Fuels1000_E) <- c()
```

### For loop

```{r}
# METRIC

for(i in 1:nrow(file_M)) {
  
  PathData <- file_M[i,1]
  TargetPark <- file_M[i,2]
  Report_M_1 <- read.csv(PathData)
  
  Report_M_1 <- Report_M_1 %>% 
    add_column(AdminUnit_Name = TargetPark, .before = "ProjectUnit_Name")
  
  Report_M_1 <- Report_M_1[,colnames(Report_M)]
  
  Fuels1000_M <- rbind(Fuels1000_M, Report_M_1)
}

write.csv(Fuels1000_M, paste0(path_save, "ALL/Metric/ALL_project_units.csv"), quote = FALSE, row.names = FALSE)
```

```{r}
# Load data
Fuels1000_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Surface Fuels - 1000Hr.csv"))
Fuels1000_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Surface Fuels - 1000Hr.csv"))

# Merge data
Fuels1000 <- rbind(Fuels1000_ANTI, Fuels1000_APCO, Fuels1000_CATO, Fuels1000_CUVA, Fuels1000_DEWA, Fuels1000_FRSP, Fuels1000_GATE, Fuels1000_GETT, Fuels1000_MONO, Fuels1000_NERI, Fuels1000_PRWI, Fuels1000_RICH, Fuels1000_SARA, Fuels1000_SHEN, Fuels1000_VAFO)

# Remove data
remove(Fuels1000_ANTI, Fuels1000_APCO, Fuels1000_CATO, Fuels1000_CUVA, Fuels1000_DEWA, Fuels1000_FRSP, Fuels1000_GATE, Fuels1000_GETT, Fuels1000_MONO, Fuels1000_NERI, Fuels1000_PRWI, Fuels1000_RICH, Fuels1000_SARA, Fuels1000_SHEN, Fuels1000_VAFO)

# Save file
write.csv(Fuels1000, paste0(path_data, "ALL/ALL_Data_Surface Fuels - 1000Hr.csv"), quote = FALSE, row.names = FALSE)
```

## Fuels Duff Litt

```{r}
FuelsDuffLitt_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Surface Fuels - Duff_Litter.csv"))
FuelsDuffLitt_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Surface Fuels - Duff_Litter.csv"))

# Merge data
FuelsDuffLitt <- rbind(FuelsDuffLitt_ANTI, FuelsDuffLitt_APCO, FuelsDuffLitt_CATO, FuelsDuffLitt_CUVA, FuelsDuffLitt_DEWA, FuelsDuffLitt_FRSP, FuelsDuffLitt_GATE, FuelsDuffLitt_GETT, FuelsDuffLitt_MONO, FuelsDuffLitt_NERI, FuelsDuffLitt_PRWI, FuelsDuffLitt_RICH, FuelsDuffLitt_SARA, FuelsDuffLitt_SHEN, FuelsDuffLitt_VAFO)

# Remove data
remove(FuelsDuffLitt_ANTI, FuelsDuffLitt_APCO, FuelsDuffLitt_CATO, FuelsDuffLitt_CUVA, FuelsDuffLitt_DEWA, FuelsDuffLitt_FRSP, FuelsDuffLitt_GATE, FuelsDuffLitt_GETT, FuelsDuffLitt_MONO, FuelsDuffLitt_NERI, FuelsDuffLitt_PRWI, FuelsDuffLitt_RICH, FuelsDuffLitt_SARA, FuelsDuffLitt_SHEN, FuelsDuffLitt_VAFO)

# Save file
write.csv(FuelsDuffLitt, paste0(path_data, "ALL/ALL_Data_Surface Fuels - Duff_Litter.csv"), quote = FALSE, row.names = FALSE)
```

## Fuels Fine

```{r}
FuelsFine_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Surface Fuels - Fine.csv"))
FuelsFine_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Surface Fuels - Fine.csv"))
FuelsFine_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Surface Fuels - Fine.csv"))
FuelsFine_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Surface Fuels - Fine.csv"))
FuelsFine_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Surface Fuels - Fine.csv"))
FuelsFine_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Surface Fuels - Fine.csv"))
FuelsFine_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Surface Fuels - Fine.csv"))
FuelsFine_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Surface Fuels - Fine.csv"))
FuelsFine_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Surface Fuels - Fine.csv"))
FuelsFine_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Surface Fuels - Fine.csv"))
FuelsFine_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Surface Fuels - Fine.csv"))
FuelsFine_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Surface Fuels - Fine.csv"))
FuelsFine_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Surface Fuels - Fine.csv"))
FuelsFine_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Surface Fuels - Fine.csv"))
FuelsFine_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Surface Fuels - Fine.csv"))

# Merge data
FuelsFine <- rbind(FuelsFine_ANTI, FuelsFine_APCO, FuelsFine_CATO, FuelsFine_CUVA, FuelsFine_DEWA, FuelsFine_FRSP, FuelsFine_GATE, FuelsFine_GETT, FuelsFine_MONO, FuelsFine_NERI, FuelsFine_PRWI, FuelsFine_RICH, FuelsFine_SARA, FuelsFine_SHEN, FuelsFine_VAFO)

# Remove data
remove(FuelsFine_ANTI, FuelsFine_APCO, FuelsFine_CATO, FuelsFine_CUVA, FuelsFine_DEWA, FuelsFine_FRSP, FuelsFine_GATE, FuelsFine_GETT, FuelsFine_MONO, FuelsFine_NERI, FuelsFine_PRWI, FuelsFine_RICH, FuelsFine_SARA, FuelsFine_SHEN, FuelsFine_VAFO)

# Save file
write.csv(FuelsFine, paste0(path_data, "ALL/ALL_Data_Surface Fuels - Fine.csv"), quote = FALSE, row.names = FALSE)
```

## Post Burn

```{r}
PostBurn_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Post Burn Severity (metric).csv"))
PostBurn_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Post Burn Severity (metric).csv"))
PostBurn_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Post Burn Severity (metric).csv"))
PostBurn_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Post Burn Severity (metric).csv"))
PostBurn_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Post Burn Severity (metric).csv"))
PostBurn_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Post Burn Severity (metric).csv"))
PostBurn_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Post Burn Severity (metric).csv"))
PostBurn_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Post Burn Severity (metric).csv"))
PostBurn_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Post Burn Severity (metric).csv"))
PostBurn_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Post Burn Severity (metric).csv"))
PostBurn_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Post Burn Severity (metric).csv"))
PostBurn_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Post Burn Severity (metric).csv"))
PostBurn_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Post Burn Severity (metric).csv"))
PostBurn_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Post Burn Severity (metric).csv"))
PostBurn_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Post Burn Severity (metric).csv"))

# Merge data
PostBurn <- rbind(PostBurn_ANTI, PostBurn_APCO, PostBurn_CATO, PostBurn_CUVA, PostBurn_DEWA, PostBurn_FRSP, PostBurn_GATE, PostBurn_GETT, PostBurn_MONO, PostBurn_NERI, PostBurn_PRWI, PostBurn_RICH, PostBurn_SARA, PostBurn_SHEN, PostBurn_VAFO)

# Remove data
remove(PostBurn_ANTI, PostBurn_APCO, PostBurn_CATO, PostBurn_CUVA, PostBurn_DEWA, PostBurn_FRSP, PostBurn_GATE, PostBurn_GETT, PostBurn_MONO, PostBurn_NERI, PostBurn_PRWI, PostBurn_RICH, PostBurn_SARA, PostBurn_SHEN, PostBurn_VAFO)

# Save file
write.csv(PostBurn, paste0(path_data, "ALL/ALL_Data_Post Burn Severity (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Trees

```{r}
Trees_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Trees - Individuals (metric).csv"))
Trees_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Trees - Individuals (metric).csv"))
Trees_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Trees - Individuals (metric).csv"))
Trees_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Trees - Individuals (metric).csv"))
Trees_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Trees - Individuals (metric).csv"))
Trees_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Trees - Individuals (metric).csv"))
Trees_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Trees - Individuals (metric).csv"))
Trees_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Trees - Individuals (metric).csv"))
Trees_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Trees - Individuals (metric).csv"))
Trees_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Trees - Individuals (metric).csv"))
Trees_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Trees - Individuals (metric).csv"))
Trees_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Trees - Individuals (metric).csv"))
Trees_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Trees - Individuals (metric).csv"))
Trees_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Trees - Individuals (metric).csv"))
Trees_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Trees - Individuals (metric).csv"))

# Merge data
Trees <- rbind(Trees_ANTI, Trees_APCO, Trees_CATO, Trees_CUVA, Trees_DEWA, Trees_FRSP, Trees_GATE, Trees_GETT, Trees_MONO, Trees_NERI, Trees_PRWI, Trees_RICH, Trees_SARA, Trees_SHEN, Trees_VAFO)

# Remove data
remove(Trees_ANTI, Trees_APCO, Trees_CATO, Trees_CUVA, Trees_DEWA, Trees_FRSP, Trees_GATE, Trees_GETT, Trees_MONO, Trees_NERI, Trees_PRWI, Trees_RICH, Trees_SARA, Trees_SHEN, Trees_VAFO)

# Save file
write.csv(Trees, paste0(path_data, "ALL/ALL_Data_Trees - Individuals (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Seedlings

```{r}
Seedlings_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Density - Quadrats (metric).csv"))
Seedlings_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Density - Quadrats (metric).csv"))
Seedlings_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Density - Quadrats (metric).csv"))
Seedlings_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Density - Quadrats (metric).csv"))
Seedlings_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Density - Quadrats (metric).csv"))
Seedlings_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Density - Quadrats (metric).csv"))
Seedlings_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Density - Quadrats (metric).csv"))
Seedlings_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Density - Quadrats (metric).csv"))
Seedlings_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Density - Quadrats (metric).csv"))
Seedlings_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Density - Quadrats (metric).csv"))
Seedlings_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Density - Quadrats (metric).csv"))
Seedlings_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Density - Quadrats (metric).csv"))
Seedlings_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Density - Quadrats (metric).csv"))
Seedlings_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Density - Quadrats (metric).csv"))
Seedlings_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Density - Quadrats (metric).csv"))

# Merge data
Seedlings <- rbind(Seedlings_ANTI, Seedlings_APCO, Seedlings_CATO, Seedlings_CUVA, Seedlings_DEWA, Seedlings_FRSP, Seedlings_GATE, Seedlings_GETT, Seedlings_MONO, Seedlings_NERI, Seedlings_PRWI, Seedlings_RICH, Seedlings_SARA, Seedlings_SHEN, Seedlings_VAFO)

# Remove data
remove(Seedlings_ANTI, Seedlings_APCO, Seedlings_CATO, Seedlings_CUVA, Seedlings_DEWA, Seedlings_FRSP, Seedlings_GATE, Seedlings_GETT, Seedlings_MONO, Seedlings_NERI, Seedlings_PRWI, Seedlings_RICH, Seedlings_SARA, Seedlings_SHEN, Seedlings_VAFO)

# Save file
write.csv(Seedlings, paste0(path_data, "ALL/ALL_Data_Density - Quadrats (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Shrubs

```{r}
Shrubs_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Density - Belts (metric).csv"))
Shrubs_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Density - Belts (metric).csv"))
Shrubs_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Density - Belts (metric).csv"))
Shrubs_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Density - Belts (metric).csv"))
Shrubs_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Density - Belts (metric).csv"))
Shrubs_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Density - Belts (metric).csv"))
Shrubs_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Density - Belts (metric).csv"))
Shrubs_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Density - Belts (metric).csv"))
Shrubs_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Density - Belts (metric).csv"))
Shrubs_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Density - Belts (metric).csv"))
Shrubs_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Density - Belts (metric).csv"))
Shrubs_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Density - Belts (metric).csv"))
Shrubs_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Density - Belts (metric).csv"))
Shrubs_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Density - Belts (metric).csv"))
Shrubs_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Density - Belts (metric).csv"))

# Merge data
Shrubs <- rbind(Shrubs_ANTI, Shrubs_APCO, Shrubs_CATO, Shrubs_CUVA, Shrubs_DEWA, Shrubs_FRSP, Shrubs_GATE, Shrubs_GETT, Shrubs_MONO, Shrubs_NERI, Shrubs_PRWI, Shrubs_RICH, Shrubs_SARA, Shrubs_SHEN, Shrubs_VAFO)

# Remove data
remove(Shrubs_ANTI, Shrubs_APCO, Shrubs_CATO, Shrubs_CUVA, Shrubs_DEWA, Shrubs_FRSP, Shrubs_GATE, Shrubs_GETT, Shrubs_MONO, Shrubs_NERI, Shrubs_PRWI, Shrubs_RICH, Shrubs_SARA, Shrubs_SHEN, Shrubs_VAFO)

# Save file
write.csv(Shrubs, paste0(path_data, "ALL/ALL_Data_Density - Belts (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Herbs Species Comp

```{r}
HerbsSpComp_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Cover - Species Composition (metric).csv"))
HerbsSpComp_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Cover - Species Composition (metric).csv"))

# Merge data
HerbsSpComp <- rbind(HerbsSpComp_ANTI, HerbsSpComp_APCO, HerbsSpComp_CATO, HerbsSpComp_CUVA, HerbsSpComp_DEWA, HerbsSpComp_FRSP, HerbsSpComp_GATE, HerbsSpComp_GETT, HerbsSpComp_MONO, HerbsSpComp_NERI, HerbsSpComp_PRWI, HerbsSpComp_RICH, HerbsSpComp_SARA, HerbsSpComp_SHEN, HerbsSpComp_VAFO)

# Remove data
remove(HerbsSpComp_ANTI, HerbsSpComp_APCO, HerbsSpComp_CATO, HerbsSpComp_CUVA, HerbsSpComp_DEWA, HerbsSpComp_FRSP, HerbsSpComp_GATE, HerbsSpComp_GETT, HerbsSpComp_MONO, HerbsSpComp_NERI, HerbsSpComp_PRWI, HerbsSpComp_RICH, HerbsSpComp_SARA, HerbsSpComp_SHEN, HerbsSpComp_VAFO)

# Save file
write.csv(HerbsSpComp, paste0(path_data, "ALL/ALL_Data_Cover - Species Composition (metric).csv"), quote = FALSE, row.names = FALSE)
```

## Herbs Points

```{r}
HerbsPoints_ANTI <- read.csv(paste0(path_data, "ANTI/ANTI_Data_Cover - Points (metric).csv"))
HerbsPoints_APCO <- read.csv(paste0(path_data, "APCO/APCO_Data_Cover - Points (metric).csv"))
HerbsPoints_CATO <- read.csv(paste0(path_data, "CATO/CATO_Data_Cover - Points (metric).csv"))
HerbsPoints_CUVA <- read.csv(paste0(path_data, "CUVA/CUVA_Data_Cover - Points (metric).csv"))
HerbsPoints_DEWA <- read.csv(paste0(path_data, "DEWA/DEWA_Data_Cover - Points (metric).csv"))
HerbsPoints_FRSP <- read.csv(paste0(path_data, "FRSP/FRSP_Data_Cover - Points (metric).csv"))
HerbsPoints_GATE <- read.csv(paste0(path_data, "GATE/GATE_Data_Cover - Points (metric).csv"))
HerbsPoints_GETT <- read.csv(paste0(path_data, "GETT/GETT_Data_Cover - Points (metric).csv"))
HerbsPoints_MONO <- read.csv(paste0(path_data, "MONO/MONO_Data_Cover - Points (metric).csv"))
HerbsPoints_NERI <- read.csv(paste0(path_data, "NERI/NERI_Data_Cover - Points (metric).csv"))
HerbsPoints_PRWI <- read.csv(paste0(path_data, "PRWI/PRWI_Data_Cover - Points (metric).csv"))
HerbsPoints_RICH <- read.csv(paste0(path_data, "RICH/RICH_Data_Cover - Points (metric).csv"))
HerbsPoints_SARA <- read.csv(paste0(path_data, "SARA/SARA_Data_Cover - Points (metric).csv"))
HerbsPoints_SHEN <- read.csv(paste0(path_data, "SHEN/SHEN_Data_Cover - Points (metric).csv"))
HerbsPoints_VAFO <- read.csv(paste0(path_data, "VAFO/VAFO_Data_Cover - Points (metric).csv"))

# Merge data
HerbsPoints <- rbind(HerbsPoints_ANTI, HerbsPoints_APCO, HerbsPoints_CATO, HerbsPoints_CUVA, HerbsPoints_DEWA, HerbsPoints_FRSP, HerbsPoints_GATE, HerbsPoints_GETT, HerbsPoints_MONO, HerbsPoints_NERI, HerbsPoints_PRWI, HerbsPoints_RICH, HerbsPoints_SARA, HerbsPoints_SHEN, HerbsPoints_VAFO)

# Remove data
remove(HerbsPoints_ANTI, HerbsPoints_APCO, HerbsPoints_CATO, HerbsPoints_CUVA, HerbsPoints_DEWA, HerbsPoints_FRSP, HerbsPoints_GATE, HerbsPoints_GETT, HerbsPoints_MONO, HerbsPoints_NERI, HerbsPoints_PRWI, HerbsPoints_RICH, HerbsPoints_SARA, HerbsPoints_SHEN, HerbsPoints_VAFO)

# Save file
write.csv(HerbsPoints, paste0(path_data, "ALL/ALL_Data_Cover - Points (metric).csv"), quote = FALSE, row.names = FALSE)
```
