---
title: "QAQC MetaData"
author: "Alexandra Lalor"
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 3
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: '3'
---

# Before Starting

This code is intended to quality check plot metadata, including the Macroplot Report, Project Unit Assignment Report, and Sample Event Report. These reports can be downloaded via the Utilities menu on the Project Management tab on the FFI Remote App Server. This code also produces a clean Metadata Report, which combines the Macroplot Report, Project Unit Assignment Report, and Sample Event Report into a single flat file, which is used in subsequent R scripts.

### Setup

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r install packages, include=FALSE}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("Rtools")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
## Load Packages

# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
library(plyr)
# janitor has functions to find duplicates
library(janitor)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr is used to create output files from R Markdown
library(knitr)
# "here" helps you easily find and reference your working directory
library(here)
```

### Create Function

```{r}
# Blank data frame
errors_blank_meta <- data.frame("SavedQuery" = "", "Macroplot" = "", "Error" = "", "Fixed" = "", "Explanation" = "", "Queryers" = "")

# QAQC function
qaqc_meta <- function(data, query, query_message, values_check) {
  
  # Check if there is data to QAQC
  if(nrow(data) == 0) {
  # If there is no data, default to "No Error" data frame
  errors <- errors_blank_meta %>%
    mutate(SavedQuery = query,
           Error = "No Error")
  # If there is data, perform error check
} else {
  
  # Use relevant dataset to look for errors
  errors <- data %>%  
    # Add columns relevant to error checking
           # Populate the "SavedQuery" column with the query name
    mutate("SavedQuery" = query, 
           # Populate the "Error" column with the query message and relevant data
           "Error" = paste(query_message, "=", values_data),
           # Create a blank "Fixed" column
           "Fixed" = "",
           # Create a blank "Explanation" column
           "Explanation" = "",
           # Create a blank "Queryers" column
           "Queryers" = "") %>%   
    # Filter for data which is "false" (data does not match valid conditions)
    # NA values are treated as "false" (missing data is not valid)
    filter(!(values_check %>% replace_na(FALSE))) %>%   
    # Select relevant columns to view errors
    select(colnames(errors_blank_meta))
  
  # Next, check if there are duplicate errors
  errors_temp <- errors %>% 
    get_dupes(SavedQuery, Macroplot, Error)
  # Merge duplicate errors
  errors <- unique(merge(errors, errors_temp, all = T))
  # If duplicate errors exist, add number of duplicates to error message
  errors <- errors %>% 
    mutate(Error = ifelse(is.na(dupe_count), Error, paste0("(x", dupe_count, ") ", Error))) %>% 
    select(!"dupe_count")
}
  
  # Check if there are no errors
  if (nrow(errors) == 0) {  
    # If there are no errors, default to "No Error" data frame
    errors <- errors_blank_meta %>%
      mutate(SavedQuery = query,
             Error = "No Error")
    # If there are errors, keep error log you just created
  } else {   
    errors <- errors
  }
}
```

### Adjust File Paths

```{r import data, include=FALSE}
# Identify working directory.
here()

# designate target park(s)
target_park <- "SHEN"

# Load in data.
#path_file <- "E:/Allie/R/NER/data/"
path_file <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/Exports/"
path_data <- paste0(path_file, target_park, "/")
#path_errors <- paste0(here(), "/output/errors/")
path_errors <- "C:/Users/alalor/OneDrive - DOI/R/NER/output/errors/"
path_errors_name <- paste0(target_park, " Metadata QAQC Errors")
```

### Load Data

```{r load data, include=FALSE}
## Load Data
MacroplotReport <- read.csv(paste0(path_data, target_park, "_", "MacroplotReport.csv"))
ProjectUnitReport <- read.csv(paste0(path_data, target_park, "_", "ProjectUnitAssignmentReport.csv"))
SampleEventReport <- read.csv(paste0(path_data, target_park, "_", "SampleEventReport.csv"))
```

### Clean Data

```{r}
#### Macroplot Report
# The Macroplot Report contains information on both plot metadata and sample event history. Separate these into 2 tables.
  
MacroplotReport_MetaData <- MacroplotReport %>%
  # remove trailing/leading whitespace
  mutate(across(where(is.character), str_trim)) %>%
  # separate tables
  mutate(SampleEventDate = ifelse(SampleEventDate == "", NA, SampleEventDate)) %>% 
  filter(is.na(SampleEventDate)) %>%
  # separate Date columns into Date and Time columns
  separate(DateIn, sep = " ", into = c("DateIn", "DateInTime")) %>%
  # reformate Date columns
  mutate(DateIn = as.Date(DateIn, "%m/%d/%Y")) %>%
  # remove unnecessary columns
  select(!c(DateInTime)) %>%
  select(!c(SampleEventDate, SampleEventTeam, SampleEventComment, MonStatusOrd, LegacyMonStatus, MonStatus))

MacroplotReport_SampleEvents <- MacroplotReport %>%
  # remove trailing/leading whitespace
  mutate(across(where(is.character), str_trim)) %>%
  # separate tables
  mutate(SampleEventDate = ifelse(SampleEventDate == "", NA, SampleEventDate)) %>% 
  filter(!is.na(SampleEventDate)) %>%
  # separate Date columns into Date and Time columns
  separate(SampleEventDate, sep = " ", into = c("SampleEventDate", "SampleEventTime")) %>%
  # reformate Date columns
  mutate(SampleEventDate = as.Date(SampleEventDate, "%m/%d/%Y")) %>%
  # remove unnecessary columns
  select(!c(SampleEventTime)) %>%
  select(c(Macroplot, SampleEventDate, SampleEventTeam, SampleEventComment, MonStatusOrd, LegacyMonStatus, MonStatus))


#### Sample Event Report
# The Sample Event Report has different column names as the Macroplot Report, but contains the same information. Make column names consistent.

SampleEventReport <- SampleEventReport %>%
  # remove trailing/leading whitespace
  mutate(across(where(is.character), str_trim)) %>%
  # make column names consistent
  mutate(Macroplot = MacroPlot_Name,
         LegacyMonitoringStatus = SampleEvent_LegacyMonitoringStatus,
         MonStatus = MonitoringStatus_Name,
         ProjectUnit = ProjectUnit_Name,
         SampleEventDate = SampleEvent_Date) %>%
  # separate Date columns into Date and Time columns
  separate(SampleEventDate, sep = " ", into = c("SampleEventDate", "SampleEventTime")) %>%
  # reformate Date columns
  mutate(SampleEventDate = as.Date(SampleEventDate, "%m/%d/%Y")) %>%
  # remove unnecessary columns
  select(!c(SampleEventTime)) %>%
  select(!c(MacroPlot_Name, SampleEvent_LegacyMonitoringStatus, MonitoringStatus_Name, ProjectUnit_Name, SampleEvent_Date))
```

# Park: [`r target_park`]{style="color:red"}

## Macroplot Report

### Installation

[Problem:]{.underline} Macroplot Report is missing information related to plot installation

[Procedure:]{.underline}

-   Check that Macroplot is not blank and has correct naming convention. Plots should have a 2-digit number associated with it (e.g. Plot 01, Plot 02, Plot 03, etc.)

```{r}
# Set parameters 
data <- MacroplotReport_MetaData %>% 
  extract(Macroplot, regex = "([0-9]+[0-9]+)", into = c("Macroplot_Num"), remove = F)
query <- "Macroplot Report - Installation"
query_message <- "Macroplot naming convention is incorrect. Macroplot Number" 
values_data <- data$Macroplot_Num
values_valid <- is.na(data$Macroplot_Num)
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_MacroplotNum <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that Purpose is not blank and is written correctly ("Fire Monitoring Handbook" or "Composite Burn Index").

```{r}
# Set parameters 
data <- MacroplotReport_MetaData
query <- "Macroplot Report - Installation"
query_message <- "Purpose" 
values_data <- data$Purpose
values_valid <- c("Fire Monitoring Handbook", "Composite Burn Index")
values_check <- values_data %in% values_valid

# Identify errors
errors_MacroplotReport_Purpose <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that Type is one of the available options ("Forest", "Grassland", "Brush", "CBI", "Control", "Inventory", "Measured", "Other", or "RA")

```{r}
# Set parameters 
data <- MacroplotReport_MetaData
query <- "Macroplot Report - Installation"
query_message <- "Type" 
values_data <- data$Type
values_valid <- c("Forest", "Grassland", "Brush", "CBI", "Control", "Inventory", "Measured", "Other", "RA", "Shrubland")
values_check <- values_data %in% values_valid

# Identify errors
errors_MacroplotReport_Type <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that DateIn is not blank

```{r}
# Set parameters 
data <- MacroplotReport_MetaData
query <- "Macroplot Report - Installation"
query_message <- "Date In" 
values_data <- data$DateIn
values_valid <- is.na(data$DateIn)
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_DateIn <- qaqc_meta(data, query, query_message, values_check)
```

Combine Installation Errors

```{r}
# Combine
errors_MacroplotReport_Installation <- unique(rbind(errors_MacroplotReport_MacroplotNum, errors_MacroplotReport_Purpose, errors_MacroplotReport_Type, errors_MacroplotReport_DateIn))

remove(errors_MacroplotReport_MacroplotNum, errors_MacroplotReport_Purpose, errors_MacroplotReport_Type, errors_MacroplotReport_DateIn)

if(nrow(errors_MacroplotReport_Installation) > 1) {
  errors_MacroplotReport_Installation <- errors_MacroplotReport_Installation %>%
    filter(Error != "No Error")
} else {
  errors_MacroplotReport_Installation <- errors_MacroplotReport_Installation}
```

### Location

[Problem:]{.underline} Macroplot Report is missing information related to plot geographic location

[Procedure:]{.underline}

-   Check that Latitude is not blank

```{r}
# Set parameters 
data <- MacroplotReport_MetaData
query <- "Macroplot Report - Location"
query_message <- "Latitude" 
values_data <- data$Latitude
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_Latitude <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that Longitude is not blank

```{r}
# Set parameters 
data <- MacroplotReport_MetaData
query <- "Macroplot Report - Location"
query_message <- "Longitude" 
values_data <- data$Longitude
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_Longitude <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that UTM_X (easting) has 6 digits

```{r}
# Set parameters 
data <- MacroplotReport_MetaData %>% 
  mutate(UTM_X_digits = round(UTM_X))
query <- "Macroplot Report - Location"
query_message <- "UTM_X (easting) should have 6 digits. Digits" 
values_data <- nchar(data$UTM_X_digits)
values_valid <- 6
values_check <- values_data == values_valid

# Identify errors
errors_MacroplotReport_UTM_X <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that UTM_Y (northing) has 7 digits

```{r}
# Set parameters 
data <- MacroplotReport_MetaData %>% 
  mutate(UTM_Y_digits = round(UTM_Y))
query <- "Macroplot Report - Location"
query_message <- "UTM_Y (northing) should have 7 digits. Digits" 
values_data <- nchar(data$UTM_Y_digits)
values_valid <- 7
values_check <- values_data == values_valid

# Identify errors
errors_MacroplotReport_UTM_Y <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that UTM_Zone = 17, 18, or 19

```{r}
# Set parameters 
data <- MacroplotReport_MetaData
query <- "Macroplot Report - Location"
query_message <- "UTM_Zone" 
values_data <- data$UTM_Zone
values_valid <- c(17, 18, 19)
values_check <- values_data %in% values_valid

# Identify errors
errors_MacroplotReport_UTM_Zone <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that Datum = NAD83 or NAD27

```{r}
# Set parameters 
data <- MacroplotReport_MetaData
query <- "Macroplot Report - Location"
query_message <- "Datum" 
values_data <- data$Datum
values_valid <- c("NAD83", "NAD27")
values_check <- values_data %in% values_valid

# Identify errors
errors_MacroplotReport_Datum <- qaqc_meta(data, query, query_message, values_check)
```

Combine Location Errors

```{r}
# Combine
errors_MacroplotReport_Location <- unique(rbind(errors_MacroplotReport_Latitude, errors_MacroplotReport_Longitude, errors_MacroplotReport_UTM_X, errors_MacroplotReport_UTM_Y, errors_MacroplotReport_UTM_Zone, errors_MacroplotReport_Datum))

remove(errors_MacroplotReport_Latitude, errors_MacroplotReport_Longitude, errors_MacroplotReport_UTM_X, errors_MacroplotReport_UTM_Y, errors_MacroplotReport_UTM_Zone, errors_MacroplotReport_Datum)

if(nrow(errors_MacroplotReport_Location) > 1) {
  errors_MacroplotReport_Location <- errors_MacroplotReport_Location %>%
    filter(Error != "No Error")
} else {
  errors_MacroplotReport_Location <- errors_MacroplotReport_Location}
```

### Site Characteristics

[Problem:]{.underline} Macroplot Report is missing information related to plot site characteristics

[Procedure:]{.underline}

-   Check that Elevation is not blank

```{r}
# # Set parameters 
# data <- MacroplotReport_MetaData
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Elevation" 
# values_data <- data$Elevation
# values_valid <- ""
# values_check <- values_data != values_valid
# 
# # Identify errors
# errors_MacroplotReport_Elevation <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that ElevationUnits = feet

```{r}
# # Set parameters 
# data <- MacroplotReport_MetaData
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Elevation Units" 
# values_data <- data$ElevationUnits
# values_valid <- c("feet")
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_ElevationUnits <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that Azimuth values are reasonable

```{r}
# # Set parameters 
# data <- MacroplotReport_MetaData
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Azimuth" 
# values_data <- data$Azimuth
# values_valid <- seq(0, 359, by = 1)
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_Azimuth <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that Aspect values are reasonable

```{r}
# # Set parameters 
# data <- MacroplotReport_MetaData
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Aspect" 
# values_data <- data$Aspect
# values_valid <- seq(0, 359, by = 1)
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_Aspect <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that SlopeHill values are reasonable

```{r}
# # Set parameters 
# data <- MacroplotReport_MetaData
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Slope Hill" 
# values_data <- data$SlopeHill
# values_valid <- seq(0, 40, by = 1)
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_SlopeHill <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that SlopeTransect values are reasonable

```{r}
# # Set parameters 
# data <- MacroplotReport_MetaData
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Slope Transect" 
# values_data <- data$SlopeTransect
# values_valid <- seq(0, 40, by = 1)
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_SlopeTransect <- qaqc_meta(data, query, query_message, values_check)
```

Combine Site Characteristics Errors

```{r}
# # Combine
# errors_MacroplotReport_SiteCharacteristics <- unique(rbind(errors_MacroplotReport_Elevation, errors_MacroplotReport_ElevationUnits, errors_MacroplotReport_Azimuth, errors_MacroplotReport_Aspect, errors_MacroplotReport_SlopeHill, errors_MacroplotReport_SlopeTransect))
# 
# remove(errors_MacroplotReport_Elevation, errors_MacroplotReport_ElevationUnits, errors_MacroplotReport_Azimuth, errors_MacroplotReport_Aspect, errors_MacroplotReport_SlopeHill, errors_MacroplotReport_SlopeTransect)
# 
# if(nrow(errors_MacroplotReport_SiteCharacteristics) > 1) {
#   errors_MacroplotReport_SiteCharacteristics <- errors_MacroplotReport_SiteCharacteristics %>%
#     filter(Error != "No Error")
# } else {
#   errors_MacroplotReport_SiteCharacteristics <- errors_MacroplotReport_SiteCharacteristics}
```

### Sample Events

[Problem:]{.underline} Macroplot Report is missing information related to sample events

[Procedure:]{.underline}

-   Check that Macroplot is not blank

```{r}
# Set parameters 
data <- MacroplotReport_SampleEvents
query <- "Macroplot Report - Sample Events"
query_message <- "Macroplot" 
values_data <- data$Macroplot
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_Macroplot <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that SampleEventDate is not blank

```{r}
# Set parameters 
data <- MacroplotReport_SampleEvents
query <- "Macroplot Report - Sample Events"
query_message <- "Sample Event Date" 
values_data <- data$SampleEventDate
values_valid <- is.na(data$SampleEventDate)
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_SampleEventDate <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that MonStatusOrd is not blank

```{r}
# Set parameters 
data <- MacroplotReport_SampleEvents
query <- "Macroplot Report - Sample Events"
query_message <- "Monitoring Status Order" 
values_data <- data$MonStatusOrd
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_MonStatusOrd <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that MonStatus is not blank

```{r}
# Set parameters 
data <- MacroplotReport_SampleEvents
query <- "Macroplot Report - Sample Events"
query_message <- "Monitoring Status" 
values_data <- data$MonStatus
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_MonStatus <- qaqc_meta(data, query, query_message, values_check)
```

Combine Sample Event Errors

```{r}
# Combine
errors_MacroplotReport_SampleEvent <- unique(rbind(errors_MacroplotReport_Macroplot, errors_MacroplotReport_SampleEventDate, errors_MacroplotReport_MonStatusOrd, errors_MacroplotReport_MonStatus))

remove(errors_MacroplotReport_Macroplot, errors_MacroplotReport_SampleEventDate, errors_MacroplotReport_MonStatusOrd, errors_MacroplotReport_MonStatus)

if(nrow(errors_MacroplotReport_SampleEvent) > 1) {
  errors_MacroplotReport_SampleEvent <- errors_MacroplotReport_SampleEvent %>%
    filter(Error != "No Error")
} else {
  errors_MacroplotReport_SampleEvent <- errors_MacroplotReport_SampleEvent}
```

Combine Macroplot Report Errors

```{r}
errors_MacroplotReport <- rbind(errors_MacroplotReport_Installation, errors_MacroplotReport_Location, errors_MacroplotReport_SampleEvent) %>% 
  arrange(Macroplot)

remove(errors_MacroplotReport_Installation, errors_MacroplotReport_Location, errors_MacroplotReport_SampleEvent)
```

## Project Unit Assignment Report

[Problem:]{.underline} Project Unit Assignment Report is missing information

[Procedure:]{.underline}

-   Check that Macroplot is not blank

```{r}
# Set parameters 
data <- ProjectUnitReport
query <- "Project Unit Report"
query_message <- "Macroplot" 
values_data <- data$Macroplot
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_ProjectUnitReport_Macroplot <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that ProjectUnit is not blank

```{r}
# Set parameters 
data <- ProjectUnitReport
query <- "Project Unit Report"
query_message <- "Project Unit" 
values_data <- data$ProjectUnit
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_ProjectUnitReport_ProjectUnit <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that Multi_PU = N or Y. If Multi_PU = Y, you will need to isolate which Project Unit contains the primary data for the analysis of interest.

```{r}
# Set parameters 
data <- ProjectUnitReport
query <- "Project Unit Report"
query_message <- "Multi Project Units" 
values_data <- data$Multi_PU
values_valid <- c("N", "Y")
values_check <- values_data %in% values_valid

# Identify errors
errors_ProjectUnitReport_MultiPU <- qaqc_meta(data, query, query_message, values_check)
```

Combine Project Unit Report Errors

```{r}
errors_ProjectUnitReport <- unique(rbind(errors_ProjectUnitReport_Macroplot, errors_ProjectUnitReport_ProjectUnit, errors_ProjectUnitReport_MultiPU))

remove(errors_ProjectUnitReport_Macroplot, errors_ProjectUnitReport_ProjectUnit, errors_ProjectUnitReport_MultiPU)

if(nrow(errors_ProjectUnitReport) > 1) {
  errors_ProjectUnitReport <- errors_ProjectUnitReport %>%
    filter(Error != "No Error")
} else {
  errors_ProjectUnitReport <- errors_ProjectUnitReport}
```

## Sample Event Report

[Problem:]{.underline} Sample Event Report is missing information or is inconsistent with the Macroplot Report

[Procedure:]{.underline}

-   Check that AdministrationUnit_Name is correct

```{r}
# Set parameters 
data <- SampleEventReport
query <- "Sample Event Report"
query_message <- "Administration Unit Name" 
values_data <- data$AdministrationUnit_Name
values_valid <- target_park
values_check <- values_data == values_valid

# Identify errors
errors_SampleEventReport_AdministrationUnit <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that Protocols contains the correct information

```{r}
# Set parameters 
data <- SampleEventReport %>% 
  filter(!MonStatus %in% c("Burn", "Herbicide", "Mow", "Mechanical"))
query <- "Sample Event Report"
query_message <- paste0("Date = ", data$SampleEventDate, ". Read = ", data$MonStatus, ". Protocol")
values_data <- data$Protocol
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SampleEventReport_Protocols <- qaqc_meta(data, query, query_message, values_check)
```

-   Check that Visited = Y for each relevant monitoring status (excluding disturbance events: Burn, Herbicide, Mow, Mechanical)

```{r}
# Set parameters 
data <- SampleEventReport %>% 
  filter(!MonStatus %in% c("Burn", "Herbicide", "Mow", "Mechanical"))
query <- "Sample Event Report"
query_message <- paste0("Date = ", data$SampleEventDate, ". Read = ", data$MonStatus, ". Visited")
values_data <- data$Visited
values_valid <- "Y"
values_check <- values_data == values_valid

# Identify errors
errors_SampleEventReport_Visited_1 <- qaqc_meta(data, query, query_message, values_check)
```

```{r}
# Set parameters 
data <- SampleEventReport %>% 
  filter(MonStatus %in% c("Burn", "Herbicide", "Mow", "Mechanical"))
query <- "Sample Event Report"
query_message <- paste0("Date = ", data$SampleEventDate, ". Read = ", data$MonStatus, ". Visited")
values_data <- data$Visited
values_valid <- "N"
values_check <- values_data == values_valid

# Identify errors
errors_SampleEventReport_Visited_2 <- qaqc_meta(data, query, query_message, values_check)
```

-   Compare unique MonStatus between both the Sample Event Report and Metadata Report. Isolate differences between reports.

```{r}
# Compare MonStatus between Sample Event Report and Metadata Report, isolate differences
data_temp1 <- SampleEventReport %>% 
  select(Macroplot, SampleEventDate, MonStatus) %>% 
  unique()

data_temp2 <- MacroplotReport_SampleEvents %>% 
  select(Macroplot, SampleEventDate, MonStatus) %>% 
  filter(!is.na(SampleEventDate)) %>% 
  unique()

data_temp <- setdiff(data_temp1, data_temp2) %>% 
  mutate(MonStatusError = MonStatus) %>% 
  filter(MonStatus != "") %>% 
  select(!MonStatus)
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(MacroplotReport_SampleEvents, data_temp, by = c("Macroplot", "SampleEventDate"), all = T)
data$MonStatusError[is.na(data$MonStatusError)] <- ""
data <- data %>% 
  filter(MonStatusError != "")
query <- "MonStatus"
query_message <- paste0("MacroplotReport MonStatus = ", data$MonStatus, ". ", "SampleEventReport MonStatus") 
values_data <- data$MonStatusError
values_valid <- data$MonStatus
values_check <- values_data == values_valid

# Identify errors
errors_SampleEventReport_MonStatus <- qaqc_meta(data, query, query_message, values_check)
```

Combine Sample Event Report Errors

```{r}
errors_SampleEventReport <- unique(rbind(errors_SampleEventReport_AdministrationUnit, errors_SampleEventReport_Protocols, errors_SampleEventReport_Visited_1, errors_SampleEventReport_Visited_2, errors_SampleEventReport_MonStatus))

remove(errors_SampleEventReport_AdministrationUnit, errors_SampleEventReport_Protocols, errors_SampleEventReport_Visited_1, errors_SampleEventReport_Visited_2, errors_SampleEventReport_MonStatus)

if(nrow(errors_SampleEventReport) > 1) {
  errors_SampleEventReport <- errors_SampleEventReport %>%
    filter(Error != "No Error")
} else {
  errors_SampleEventReport <- errors_SampleEventReport}
```

# ALL ERRORS

```{r}
errors_all <- rbind(errors_MacroplotReport, errors_blank_meta, errors_ProjectUnitReport, errors_blank_meta, errors_SampleEventReport)
```

```{r}
# Create conditional formatting rules
errors_all_cf <- errors_all %>% 
  mutate(Color = ifelse(SavedQuery == "", NA, "Color"))

# Add conditional formating to ouput
errors_all <- condformat(errors_all_cf[1:(nrow(errors_all_cf)), 1:7]) %>%
  rule_fill_discrete(columns = 1:6,
                     expression = (errors_all_cf$Color),
                     colours = c("Color"="#C6E0B4"),
                     na.value = "#FFFFFF") %>%
  select(!c("Color"))
```

```{r}
# Table of results for quick check
kable(errors_all, "pipe")

# Save as CSV or XLSX 
condformat2excel(errors_all, paste0(path_errors, paste0(target_park, "_errors_metadata.xlsx")), sheet_name = path_errors_name, overwrite_wb = TRUE)
```

# METADATA REPORT: MERGE AND SAVE

```{r}
#### Merge MacroplotReport_Metadata and MacroplotReport_SampleEvents
MacroplotReport_merge <- merge(MacroplotReport_MetaData, MacroplotReport_SampleEvents, by = c("Macroplot")) %>%
  select(!MonStatusOrd)

#### Filter Sample Event Report for merging
SampleEventReport_merge <- SampleEventReport %>%
  filter(ProjectUnit != "ALL") %>% 
  select(!c(Multi_PU, LegacyMonitoringStatus))

#### Merge Macroplot Report and Sample Event Report
MetadataReport <- merge(MacroplotReport_merge, SampleEventReport_merge, by = c("Macroplot", "SampleEventDate", "MonStatus")) %>%
  relocate(AdministrationUnit_Name, .before = Macroplot) %>%
  relocate(ProjectUnit, .after = Purpose) %>%
  relocate(Type, .after = Purpose) %>% 
  relocate(Macroplot, .after = Type) %>%
  relocate(SampleEventDate, .after = Visited) %>%
  relocate(MonStatus, .after = LegacyMonStatus) %>%
  relocate(LocatedBy, .before = StartPoint)
```

```{r}
MetadataReport[] <- lapply(MetadataReport, function(x) gsub(",", ";", x))

# save metadata file as csv
write.csv(MetadataReport, paste0(path_data, paste0(target_park, "_MetadataReport.csv")), quote=FALSE, row.names = FALSE, na = "") 
```
