---
title: "FFI Database Summary"
subtitle: Northeast Region
output:
  word_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
---

# Metadata Clean

### Setup {.hidden}

```{r}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
```

```{r}
## Load Packages

# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
library(stringr)
library(DT)
library(fs)
```

### Target Park

```{r}
# target_park <- c("RICH")
# target_project <- c("Big Meadows West")
# target_type <- c("Forest")
# target_years <- c(2025)
```

### Adjust File Paths

```{r}
## Adjust File Paths
#path_file <- "E:/Allie/FireFX_NER/FFI Data Management/R Outputs/"
path_file <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/R Outputs/"
path_data <- paste0(path_file, "ALL/ALL_")
```

### Load Data {.hidden}

```{r}
# Load in data
MetadataReport <- read.csv(paste0(path_data, "MetadataReport.csv"))
SpeciesReport <- read.csv(paste0(path_data, "SpeciesReport.csv"))
Fuels1000 <- read.csv(paste0(path_data, "Data_Surface Fuels - 1000Hr.csv"))
FuelsDuffLitt <- read.csv(paste0(path_data, "Data_Surface Fuels - Duff_Litter.csv"))
FuelsFine <- read.csv(paste0(path_data, "Data_Surface Fuels - Fine.csv"))
PostBurn <- read.csv(paste0(path_data, "Data_Post Burn Severity (metric).csv"))
Trees <- read.csv(paste0(path_data, "Data_Trees - Individuals (metric).csv"))
Seedlings <- read.csv(paste0(path_data, "Data_Density - Quadrats (metric).csv"))
Shrubs <- read.csv(paste0(path_data, "Data_Density - Belts (metric).csv"))
HerbsSpComp <- read.csv(paste0(path_data, "Data_Cover - Species Composition (metric).csv"))
HerbsPoints <- read.csv(paste0(path_data, "Data_Cover - Points (metric).csv"))
```

### Define Codes

```{r}
zone_NewEngland <- c("ACAD", "CACO")
zone_MidAtlantic <- c("DEWA", "GATE", "GETT", "SARA", "VAFO")
zone_NCA <- c("ANTI", "CATO", "MONO", "PRWI")
zone_Allegheny <- c("CUVA", "NERI")
zone_MTTS <- c("APCO", "FRSP", "RICH", "SHEN")
zone_North <- c(zone_NewEngland, zone_MidAtlantic)
zone_South <- c(zone_Allegheny, zone_MTTS)
```

# Add Columns

## Metadata Report

### Basic Columns

-   Region (NER)

-   Zone (e.g. South)

-   Unit (e.g. MTTS)

-   Purpose Code (FMH, CBI, RA, ...)

-   Plot Type combines Purpose and Type (FMH - Forest, FMH - Grassland, ...)

-   Macroplot_Num (01, 02...)

```{r}
MetadataReport_all <- MetadataReport %>% 
  # Region
  mutate(Region = ifelse(AdministrationUnit_Name %in% c(zone_NCA), "NCR", "NER")) %>% 
  # Zone
  mutate(Zone = ifelse(AdministrationUnit_Name %in% zone_North, "North",
                       ifelse(AdministrationUnit_Name %in% zone_South, "South", 
                              "NCA"))) %>% 
  # Unit
  mutate(Unit = ifelse(AdministrationUnit_Name %in% zone_NewEngland, "NewEngland",
                       ifelse(AdministrationUnit_Name %in% zone_MidAtlantic, "MidAtlantic",
                              ifelse(AdministrationUnit_Name %in% zone_Allegheny,"Allegheny",
                                    ifelse(AdministrationUnit_Name %in% zone_MTTS, "MTTS", 
                                           "NCA"))))) %>%
  # Purpose Code
  mutate(Purpose_Code = ifelse(Purpose == "Fire Monitoring Handbook", "FMH",
                            ifelse(Purpose == "Inventory & Monitoring", "I&M",
                                   ifelse(Purpose == "Composite Burn Index", "CBI",
                                          ifelse(Purpose=="Rapid Assessment","RA",
                                                 ifelse(Purpose=="Fuels","Fuels",
                                                        "FMH")))))) %>%
  mutate(Purpose_Code = ifelse(is.na(Purpose_Code), "FMH", Purpose_Code)) %>% 
  # Plot Type
  mutate(Plot_Type = paste0(Purpose_Code, " - ", Type)) %>% 
  # Macroplot code and number
  extract(Macroplot, regex = "([0-9]+)", into = c("Macroplot_Num"), remove = F) %>% 
  separate(Macroplot, sep = "(?=[0-9])", into = c("Macroplot_Code"), remove = F) %>%
  mutate(Macroplot_Num = ifelse(is.na(Macroplot_Num), 0, Macroplot_Num)) %>% 
  mutate(Macroplot_Num = as.numeric(Macroplot_Num)) %>% 
  # Reorganize Columns
  relocate(Region, .before = AdministrationUnit_Name) %>% 
  relocate(Zone, .before = AdministrationUnit_Name) %>%
  relocate(Unit, .before = AdministrationUnit_Name) %>% 
  relocate(Purpose_Code, .after = Purpose) %>% 
  relocate(Plot_Type, .after = Type)
```

### Calculations

```{r}
MetadataReport_all <- MetadataReport_all %>% 
  # Calculations
  group_by(AdministrationUnit_Name, Plot_Type) %>%
  dplyr::mutate(n_plots_ByPlotType = n_distinct(Macroplot)) %>% 
  group_by(AdministrationUnit_Name, Plot_Type, MacroPlot.UV1) %>% 
  dplyr::mutate(n_plots_ByProjectUnit = n_distinct(Macroplot)) %>%
  group_by(AdministrationUnit_Name, Plot_Type, MacroPlot.UV2) %>% 
  dplyr::mutate(n_plots_ByMonitoringType = n_distinct(Macroplot)) %>% 
  ungroup()
```

### Merge

```{r}
MetadataReport_merge <- MetadataReport_all %>% 
  select(c(Region, Zone, Unit, AdministrationUnit_Name, 
           Purpose, Purpose_Code, Type, Plot_Type,
           Macroplot, Macroplot_Code, Macroplot_Num,
           MacroPlot.UV1, MacroPlot.UV2, MacroPlot.UV3, MacroPlot.UV4, 
           MacroPlot.UV5, MacroPlot.UV6, MacroPlot.UV7, MacroPlot.UV8,
           MonStatus, 
           SampleEventDate, SampleEventDate_Year,
           n_plots_ByPlotType, n_plots_ByProjectUnit, n_plots_ByMonitoringType)) %>% 
  unique()
```

### Split MetadataReport

```{r}
MetadataReport_Disturbances <- MetadataReport_all %>% 
  filter(MonStatus %in% c("", "Burn", "Herbicide", "Mechanical", "Mow")) %>%  
  mutate(DisturbanceDate = SampleEventDate) %>% 
  mutate(DisturbanceDate_Year = SampleEventDate_Year)

MetadataReport_Reads <- MetadataReport_all %>% 
  filter(!MonStatus %in% c("", "Burn", "Herbicide", "Mechanical", "Mow")) %>% 
  mutate(DisturbanceDate = NA) %>% 
  mutate(DisturbanceDate_Year = NA)
```

#### MonStatus

-   Entry / Prefix (0, 1, 2, 3 , 4...)

-   Status (pre, post)

-   TimeSince / Suffix (0, 1, 2, 5, 10, 20)

```{r}
MonStatus <- MetadataReport_Reads %>% 
  select(MonStatus) %>% 
  filter(!is.na(MonStatus))
MonStatus <- unique(MonStatus)

# Create column with consistent naming
MonStatus <- MonStatus %>%
  mutate(MonStatus_new = ifelse(MonStatus %in%  c("Pre", "PRE", "Preyr00", "Measure", "2001Density", "2001Measure", "2002Density", "2002Measure", "2003Density", "2003Measure", "2004Measure"), "00 Pre", 
                                ifelse(MonStatus %in% c("Pre 2", "Pre 02"), "00 PR1",
                                       ifelse(MonStatus %in% c("Pre 3"), "00 PR2",
                                              ifelse(MonStatus %in% c("Pre 4"), "00 PR3",
                                                     ifelse(MonStatus %in% c("Pre 5"), "00 PR4",
                                                            ifelse(MonStatus %in% c("01Post"), "01 Post 00",
                                                                   ifelse(MonStatus %in% c("01yr01"), "01 Yr 01",
                                                                          ifelse(MonStatus %in% c("01Yr02"), "01 Yr 02",
                                                                                 ifelse(MonStatus %in% c("01Yr03"), "01 Yr 03",
                                                                                        ifelse(MonStatus %in% c("00 Post (Initial CBI)", "01 Post (Extended CBI)", "01 Post (Initial CBI)", "Severity"), "01 Post 00", MonStatus)))))))))))

#order <- seq(1, nrow(MonStatus))

# Extract info
MonStatus <- MonStatus %>%
  arrange(MonStatus_new) %>%
  dplyr::mutate(MonStatusOrd = row_number()) %>%
  separate(MonStatus_new, sep = " ", into = c("Entry","Status","TimeSince"), remove = F) %>%
  # fix up classifications
  mutate(Status = ifelse(Status %in% c("Yr", "yr"), "Year", Status)) %>%
  mutate(Status = ifelse(Status %in%  c("PR1", "PR2", "PR3", "PR4"), "Pre", Status)) %>%
  # make columns numeric
  mutate(Entry = as.numeric(Entry),
         TimeSince = as.numeric(TimeSince)) %>% 
  select(!MonStatus_new)
```

#### Disturbance

-   Disturbance_Type (Burn, Herbicide, Mechanical, Mow)

-   Disturbance_Year (actual year)

```{r}
Disturbances <- MetadataReport_Disturbances %>% 
  filter(MonStatus == "Burn") %>% 
  arrange(AdministrationUnit_Name, Macroplot, SampleEventDate) %>% 
  group_by(AdministrationUnit_Name, Macroplot) %>% 
  dplyr::mutate(Entry = row_number(),
         Status = "Post",
         TimeSince = 0,
         MonStatusOrd = NA)
```

#### Merge

```{r}
# Disturbance
MetadataReport_Disturbances <- merge(MetadataReport_Disturbances, Disturbances, all = T)

# Mon Status
MetadataReport_Reads <- merge(MetadataReport_Reads, MonStatus, by = c("MonStatus"), all = T)

# Merge all
MetadataReport_all <- rbind(MetadataReport_Disturbances, MetadataReport_Reads) %>% 
  arrange(AdministrationUnit_Name, Macroplot, SampleEventDate)
```

### Other

-   Disturbance_Entry (to match with MonStatus)

-   Disturbance_Desc (RX, WF-SUPP, WFU, WF)

-   Disturbance_Name (e.g. Cape Final)

-   Disturbance_Severity (Unaltered, Low, Low/Moderate, Moderate, Moderate/High, High)

-   FuelType (PIPO, PIED, etc.)

## Species Report

## Surface Fuels

```{r}
# Fuels1000_all <- merge(Fuels1000, MetadataReport_merge, by = c("AdministrationUnit_Name", "Purpose", "Type", "Macroplot", "MacroPlot.UV1", "MacroPlot.UV2", "MacroPlot.UV3", "MacroPlot.UV4", "MacroPlot.UV5", "MacroPlot.UV6", "MacroPlot.UV7", "MacroPlot.UV8", "MonStatus", "SampleEventDate", "SampleEventDate_Year"), all.x = T) %>% 
#   # Reorganize Columns
#   relocate(Region, .before = AdministrationUnit_Name) %>% 
#   relocate(Zone, .before = AdministrationUnit_Name) %>%
#   relocate(Unit, .before = AdministrationUnit_Name) %>% 
#   relocate(Purpose_Code, .after = Purpose) %>% 
#   relocate(Plot_Type, .after = Type) %>% 
#   relocate(Macroplot_Num, .after = Macroplot) %>% 
#   relocate(Macroplot_Code, .after = Macroplot)
# 
# FuelsDuffLitt_all <- merge(FuelsDuffLitt, MetadataReport_merge, by = c("AdministrationUnit_Name", "Purpose", "Type", "Macroplot", "MacroPlot.UV1", "MacroPlot.UV2", "MacroPlot.UV3", "MacroPlot.UV4", "MacroPlot.UV5", "MacroPlot.UV6", "MacroPlot.UV7", "MacroPlot.UV8", "MonStatus", "SampleEventDate", "SampleEventDate_Year"), all.x = T) %>% 
#   # Reorganize Columns
#   relocate(Region, .before = AdministrationUnit_Name) %>% 
#   relocate(Zone, .before = AdministrationUnit_Name) %>%
#   relocate(Unit, .before = AdministrationUnit_Name) %>% 
#   relocate(Purpose_Code, .after = Purpose) %>% 
#   relocate(Plot_Type, .after = Type) %>% 
#   relocate(Macroplot_Num, .after = Macroplot) %>% 
#   relocate(Macroplot_Code, .after = Macroplot)
# 
# FuelsFine_all <- merge(FuelsFine, MetadataReport_merge, by = c("AdministrationUnit_Name", "Purpose", "Type", "Macroplot", "MacroPlot.UV1", "MacroPlot.UV2", "MacroPlot.UV3", "MacroPlot.UV4", "MacroPlot.UV5", "MacroPlot.UV6", "MacroPlot.UV7", "MacroPlot.UV8", "MonStatus", "SampleEventDate", "SampleEventDate_Year"), all.x = T) %>% 
#   # Reorganize Columns
#   relocate(Region, .before = AdministrationUnit_Name) %>% 
#   relocate(Zone, .before = AdministrationUnit_Name) %>%
#   relocate(Unit, .before = AdministrationUnit_Name) %>% 
#   relocate(Purpose_Code, .after = Purpose) %>% 
#   relocate(Plot_Type, .after = Type) %>% 
#   relocate(Macroplot_Num, .after = Macroplot) %>% 
#   relocate(Macroplot_Code, .after = Macroplot)

Fuels1000_all <- Fuels1000 %>% 
  select(!c(Purpose, Type, MacroPlot.UV1, MacroPlot.UV2, MacroPlot.UV3, MacroPlot.UV4, MacroPlot.UV5, MacroPlot.UV6, MacroPlot.UV7, MacroPlot.UV8, MonStatus, Status.Prefix, Status.Base, Status.Suffix, MonStatusOrd, SampleEventDate_Year, FieldTeam, EntryTeam, UV1Desc, UV2Desc, UV2Desc, UV3Desc, SaComment, Visited, Index)) %>% 
  mutate(SampleEventDate = ymd(SampleEventDate))

```

### Fuels 1000

```{r calculate fuel loads, include=FALSE}
# -------------------------- #
# ---- 1,000-Hour Fuels ---- #
# -------------------------- #

# ---- Function to calculate 1000-hr fuels for any park dataset ---- #
calculate_coarse_fuels <- function(fuels_df) {


  # ---- Step 1: Ensure Transect is numeric BEFORE calculations ---- #
  fuels_df <- Fuels1000_all %>% 
    mutate(
      SampleEventDate = ymd(SampleEventDate),
      Transect = suppressWarnings(as.numeric(Transect)),
      DecayCl = suppressWarnings(as.numeric(DecayCl)),
      Dia = suppressWarnings(as.numeric(Dia))
      )
  
  # ---- Step 2: Compute per-log contributions ---- #
  #a <- 1.0
  #s_sound <- 0.4
  #s_rotten <- 0.3
  #conversion_factor <- 11.64

  fuels_processed <- fuels_df %>%
    filter(DecayCl %in% c(3, 4)) %>%
    mutate(
      a = 1.0,
      s_sound = 0.4,
      s_rotten = 0.3,
      conversion_factor = 11.64,
      D2 = Dia^2,
      s = if_else(DecayCl == 3, s_sound, s_rotten),
      slope_correction = sqrt(1 + (Slope / 100)^2),
      Load = (conversion_factor * D2 * s * a * slope_correction) / TranLen,
      Load_Adjusted = Load / NumTran
    )

  # ---- Step 3A: Summarise computed loads (only where logs existed) ---- #
  loads_per_transect <- fuels_processed %>% 
   group_by(AdministrationUnit_Name, SampleEvent_TreatmentUnit, Macroplot, SampleEventDate, Transect) %>% 
    summarise(
      ThousHrTranLen      = TranLen,
      ThousHrSound        = sum((DecayCl == 3), na.rm = TRUE),
      ThousHrRott        = sum((DecayCl == 4), na.rm = TRUE),
      ThousHr        = sum((DecayCl %in% c(3,4)), na.rm = TRUE),
      ThousHrSound_FuelLoad     = sum(Load[DecayCl == 3], na.rm = TRUE),
      ThousHrRott_FuelLoad     = sum(Load[DecayCl == 4], na.rm = TRUE),
      ThousHr_FuelLoad = sum(Load, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(Transect = suppressWarnings(as.numeric(Transect)))
  
  
  # ---- Step 3B: Create full grid of expected transects per plot/year ---- #
  all_transects <- fuels_df %>%
    select(AdministrationUnit_Name, SampleEvent_TreatmentUnit, Macroplot, SampleEventDate, NumTran, Transect, TranLen) %>% 
    group_by(AdministrationUnit_Name, SampleEvent_TreatmentUnit, Macroplot, SampleEventDate) %>%
    tidyr::uncount(weights = NumTran, .id = "Transect") %>%
    mutate(Transect = suppressWarnings(as.numeric(Transect))) %>% 
    dplyr::rename(ThousHrTranLen = TranLen) %>% 
    unique()
  
  
  # ---- Step 5C: Bring zeros back in for missing decay classes ---- #
  fuel_by_transect <- all_transects %>%
    left_join(loads_per_transect,
              by = c("AdministrationUnit_Name", "SampleEvent_TreatmentUnit", "Macroplot", "SampleEventDate", "Transect", "ThousHrTranLen")) %>%
    mutate(
      #ThousHrTranLen      = replace_na(ThousHrTranLen),
      ThousHrSound        = replace_na(ThousHrSound, 0),
      ThousHrRott         = replace_na(ThousHrRott, 0),
      ThousHr             = replace_na(ThousHr, 0),
      ThousHrSound_FuelLoad     = replace_na(ThousHrSound_FuelLoad, 0),
      ThousHrRott_FuelLoad     = replace_na(ThousHrRott_FuelLoad, 0),
      ThousHr_FuelLoad = replace_na(ThousHr_FuelLoad, 0)
    ) %>% 
    unique


  return(fuel_by_transect)
}
```

### Fuels Duff Litter Function

```{r calculate fuel loads, include=FALSE}
# -------------------------------------- #  
# ---- Litter and Duff Measurements ---- #
# -------------------------------------- #

# ---- Function to calculate litter and duff fuel loads ---- #
calculate_litterduff <- function(fuels_df) {
 
  
  # ---- Step 1: Ensure Transect is numeric BEFORE calculations ---- #
  
  fuels_df <- fuels_df %>% 
    mutate(
      SampleEventDate = ymd(SampleEventDate),
      Transect = suppressWarnings(as.numeric(Transect))
      )
  
  # ================================ #
  # ==== Bulk density constants ==== #
  # ================================ #

  #litter_bd <- 2.75 * 1.815 # FFI default bulk density for litter (2.75)
  #duff_bd   <- 5.5  * 1.815 # FFI default bulk density for duff (5.5)
  
  # ---- Step 2: Transect-level averages ---- #
  transect_means <- fuels_df %>%
    group_by(AdministrationUnit_Name, SampleEvent_TreatmentUnit, Macroplot, SampleEventDate, Transect, NumTran) %>% 
    summarise(
      Tran_LittDep = mean(LittDep, na.rm = TRUE),
      Tran_DuffDep = mean(DuffDep, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    filter(Transect <= NumTran) %>%   # keep only valid transects
    mutate(
      litter_bd = 2.75 * 1.815, # FFI default bulk density for litter (2.75)
      duff_bd   = 5.5  * 1.815, # FFI default bulk density for duff (5.5)
      Tran_Litt_FuelLoad = Tran_LittDep * litter_bd,
      Tran_Duff_FuelLoad   = Tran_DuffDep * duff_bd,
      Tran_LittDuff_FuelLoad  = Tran_Litt_FuelLoad + Tran_Duff_FuelLoad
    )
  
  # ---- Step 3: Plot-level averages ---- #
  plot_means <- transect_means %>%
    group_by(AdministrationUnit_Name, SampleEvent_TreatmentUnit, Macroplot, SampleEventDate) %>%
    summarise(
      Transect = Transect,
      
      # ---- KEEP TRANSECT FUEL VALUES ---- #
      Tran_LittDep = Tran_LittDep,
      Tran_DuffDep = Tran_DuffDep,
      Tran_Litt_FuelLoad = Tran_Litt_FuelLoad,
      Tran_Duff_FuelLoad   = Tran_Duff_FuelLoad,
      Tran_LittDuff_FuelLoad  = Tran_LittDuff_FuelLoad,
      
      # ---- plot-level depth ---- #
      Avg_LittDep = mean(Tran_LittDep, na.rm = TRUE),
      Avg_DuffDep = mean(Tran_DuffDep, na.rm = TRUE),
  
      # ---- plot-level fuels ---- #
      Avg_Litt_FuelLoad = mean(Tran_Litt_FuelLoad, na.rm = TRUE),
      Avg_Duff_FuelLoad   = mean(Tran_Duff_FuelLoad, na.rm = TRUE),
      Avg_LittDuff_FuelLoad  = mean(Tran_LittDuff_FuelLoad, na.rm = TRUE),
  
      .groups = "drop"
  )
  
  return(plot_means)
}
```

### Fuels Fine

```{r calculate fuel loads, include=FALSE}
# ------------------------------------- #
# ---- Fine Fuels (1,10,100-Hours) ---- #
# ------------------------------------- #

# ---- Function to calculate 1-100-hr fuels for any park dataset ---- #
calculate_fine_fuels <- function(fuels_df) {
  
  # ---- Step 1: Ensure Date is proper datetime format ---- #
  fuels_df <- fuels_df %>%
    mutate(
      SampleEventDate = ymd(SampleEventDate)
    )
  
  # ---- Step 2: Compute per-transect fuel load ---- #
  transect_level <- fuels_df %>%
    mutate(
      d2_1hr = 0.0151,
      d2_10hr = 0.289, 
      d2_100hr = 2.76, 
      s_1hr_10hr = 0.48,
      s_100hr = 0.40,
      a = 1.13,
      c = sqrt(1 + (Slope / 100)^2),
      OneHr_FuelLoad = (11.64 * OneHr * d2_1hr   * s_1hr_10hr * a * c) / OneHrTranLen,
      TenHr_FuelLoad = (11.64 * TenHr * d2_10hr  * s_1hr_10hr * a * c) / TenHrTranLen,
      HunHr_FuelLoad = (11.64 * HunHr * d2_100hr * s_100hr    * a * c) / HunHrTranLen,
      Fine_FuelLoad = OneHr_FuelLoad + TenHr_FuelLoad + HunHr_FuelLoad
    )

  # ---- Step 3: KEEP TRANSECT-LEVEL DATA (do NOT summarise here) ---- #
  plot_level_fine <- transect_level %>%
    mutate(
      Transect_ID = row_number()  # keeps unique transect within plot
    )
}
```

## Combine Fuels

```{r calculate fuel loads, include=FALSE}
Fuels1000_sum <- calculate_coarse_fuels(Fuels1000_all)
FuelsDuffLitt_sum <- calculate_litterduff(FuelsDuffLitt)
FuelsFine_sum <- calculate_fine_fuels(FuelsFine)
```

```{r}





# Fuels1000_all_calcs <- merge(Fuels1000_all, Fuels1000_sum, all = T, by = c("AdministrationUnit_Name", "SampleEvent_TreatmentUnit", "Macroplot", "SampleEventDate", "Transect")) %>% 
#   arrange("AdministrationUnit_Name", "SampleEvent_TreatmentUnit", "Macroplot", "SampleEventDate", "Transect")
```

```{r combine dataframes, include=FALSE}
# ============================================================= #
# ==== Join 1-100-hr, litter-duff, and 1,000-hr dataframes ==== #
# ============================================================= #

fuel_data_combined <- FuelsFine_sum %>%
  full_join(FuelsDuffLitt_sum, by = c("AdministrationUnit_Name", "SampleEvent_TreatmentUnit", "Macroplot", "SampleEventDate", "Transect")) %>% 
  left_join(Fuels1000_sum, by = c("AdministrationUnit_Name", "SampleEvent_TreatmentUnit", "Macroplot", "SampleEventDate", "Transect")) %>% 
  relocate(ThousHrTranLen, .after = HunHrTranLen) %>% 
  relocate(ThousHrSound, .after = HunHr) %>% 
  relocate(ThousHrRott, .after = ThousHrSound) %>% 
  relocate(ThousHr, .after = ThousHrRott) %>% 
  mutate(
    Avg_Litt_FuelLoad = na_if(Avg_Litt_FuelLoad, NaN),
    Avg_Duff_FuelLoad = na_if(Avg_Duff_FuelLoad, NaN),
    across(
      c(ThousHrSound_FuelLoad, ThousHrRott_FuelLoad, ThousHr_FuelLoad),
      ~ replace_na(., 0)
))
```

## Post Burn

## Trees

## Seedlings

## Shrubs

## Herbs Species Comp

```{r}
HerbsSpComp_all <- merge(HerbsSpComp, MetadataReport_merge, by = c("AdministrationUnit_Name", "Purpose", "Type", "Macroplot", "MacroPlot.UV1", "MacroPlot.UV2", "MacroPlot.UV3", "MacroPlot.UV4", "MacroPlot.UV5", "MacroPlot.UV6", "MacroPlot.UV7", "MacroPlot.UV8", "MonStatus", "SampleEventDate", "SampleEventDate_Year"), all.x = T) %>% 
  # Reorganize Columns
  relocate(Region, .before = AdministrationUnit_Name) %>% 
  relocate(Zone, .before = AdministrationUnit_Name) %>%
  relocate(Unit, .before = AdministrationUnit_Name) %>% 
  relocate(Purpose_Code, .after = Purpose) %>% 
  relocate(Plot_Type, .after = Type) %>% 
  relocate(Macroplot_Num, .after = Macroplot) %>% 
  relocate(Macroplot_Code, .after = Macroplot) %>% 
  # Protocol Specific Columns
  mutate(Nativity = ifelse(Native.Species == "True", "Native",
                           ifelse(Invasive.Species == "True", "Invasive", "Unknown"))) 
```

```{r}
HerbsSpComp_all <- HerbsSpComp_all %>% 
  group_by(AdministrationUnit_Name, Plot_Type, Macroplot, SampleEventDate) %>%
  dplyr::mutate(n_species_ByPlotDate = n_distinct(Species.Symbol)) %>% 
  group_by(AdministrationUnit_Name, Plot_Type, MacroPlot.UV1, SampleEventDate) %>% 
  dplyr::mutate(n_species_ByDate = n_distinct(Species.Symbol)) %>% 
  group_by(AdministrationUnit_Name, Plot_Type, MacroPlot.UV1, SampleEventDate, Nativity) %>% 
  dplyr::mutate(n_species_ByNativity = n_distinct(Species.Symbol)) %>% 
  ungroup()
```

## Herbs Points
