---
title: QAQC Species Data
author: NPS Northeast Region Fire Effects Monitoring Program
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 1
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: '3'
---

# PURPOSE

This code is intended to quality check species metadata, including the Local Species Report. This report has been cleaned using the Clean+Merge.Rmd script.

-   SpeciesReport.csv

## Before Starting

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)

# install.packages("tidyverse")
# install.packages("Rtools")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
library(plyr)
# janitor has functions to find duplicates
library(janitor)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr is used to create output files from R Markdown
library(knitr)
library(here)
```

### Create Function {.hidden}

```{r qaqc function, include=FALSE}
## Source Code
#Pull in source code that creates QAQC functions and builds an empty error table.
source(paste0(here(), "/scripts/2_QAQC/qaqc_function.R"))

###################################################################################

# Edit blank data frame for preferred error log template.
errors_blank <- data.frame("SavedQuery" = "", 
                           "AdminUnit_Name" = "", 
                           "Species_LocalSpeciesSymbol" = "", 
                           "Error" = "", 
                           "Fixed" = "", 
                           "Explanation" = "", 
                           "Queryers" = "")

# Edit error group. Duplicate errors will be grouped by these columns.
errors_group <- c("SavedQuery", "AdminUnit_Name", "Species_LocalSpeciesSymbol", "Error")
```

### Target Park {.hidden}

```{r target values, include=FALSE}
# designate target park(s)
# parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
target_park <- "NERI"
```

### Adjust File Paths {.hidden}

```{r file paths, include=FALSE}
# adjust file paths
path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Clean/FFI/")
path_errors <- paste0(here(), "/output/errors/")
path_errors_name <- paste0(target_park, " Species QAQC Errors")
```

### Load Data {.hidden}

```{r load data, include=FALSE}
## Load Data
SpeciesReport_all <- read.csv(paste0(path_data, "all_species_info.csv"))
```

### Filter Data

```{r filter data, include=FALSE}
SpeciesReport <- SpeciesReport_all %>% 
  filter(AdminUnit_Name %in% target_park)
```

### Define Codes {.hidden}

```{r define codes, include=FALSE}
# unknowns_genus <- c("ACALY","ACALYP","ACASPP","ACER","ACHILLEA","AGESPP","AGROS","AGRSPP","ALLIUM","ALLSPP","AMELA","AMESPP","ANDRO","ANDROP","ANDSPP","ANEMO","ANESPP","ANTEN","ANTENN","ANTSPP","APOCY","APOCYNUM","APOSPP", "ARABIS","ARALI","ARISPP","ARIST","ASCLE","ASCLEPIAS","ASCSPP","ASPSPP","ASTER","ASTERACEAE","ASTEspp","BETULA","BIDENS","BOTRY","BOTRYCH","BOTSPP","BRASSICACE","BRASPP","BRASS2","BROMU","bromus","BROMUS","BROSPP","CALAM","CALYSTEGIA","CARDA","CAREX","CAREX2","CARSPP","CARSP1","CARSPP2","CARSP2","CARSP3","CARYA","CASSPP","CENTAUREA","CHIMA","CIRCAE","CIRSI","CIRSPP","CLISPP","CONVO","CONVOL","CONVOLVULU","CONVULVULA","CORNspp","CORSPP","CORNU","CORNUS","CRASPP","CRATA","CRATAEGUS","CUSCU","CUSCUTA","CUSSPP","CYPER","CYPSPP","DANSPP","DATSP","DDTREE","DESMO","DESMODIUM","DESSPP","DICHAN","DICHANTHEL","DICSPP","DICSP1","DICSPP1","DICSP2","DICSPP2","DICSPP3","DICSP5","DIGITA","DIGSPP1","DIGSPP","DIOSC","DIOSPP","ELEOCHARIS","ELESPP","ELYMUS","EPILOBIUM","EPISPP","EPISP1","ERAGR","ERASPP","ERAGROSTIS","ERIGE2","ERIGERON","ERISP","ERISPP","EUPATOR","EUPATORIUM","EUPSPP","EURSPP","EURYB","FABSPP","FABA","FESTUC","FESTUCA","FIMBRI","FRASPP","FRAXINUS","FRAXspp","GALIU","GALIUM","GALSP","GALSPP","GENTI","GEUM","GILLSP", "GLYCERIA","GNASPP","HELIAN","HEPAT","HIERA","HIERAC","HIERACIUM","HIESPP","HOUSTO","HYPER","HYPERICUM","HYPPER","HYPSPP","IMPATIENS","IPOMO","IPOMOE","IPOMOEA","IPOSPP","IRIS","JUNCUS","JUNIspp","JUNSPP","KRIGI","LACSPP","LACTU","LAMSPP","LESPE","LESSPP","LIASPP","LIATR","LINSPP","LINUM","LITHO3","LONIC","LONICE","LONICERA","LONSPP","LOTUS","LYCHN","LYCOPODIUM","LYCOPUS","LYSIM","LYSSSP","MAGNOLIA","MALUS","MEDICAGO","MELILOTUS","MONARDA","MONSPP","MUHLE","MUHLEN","MUHSPP","MYRIO","NABSPP", "OSMOR","OSMSPP","OXALI","OXALIS","OXASPP","PACKER","PACKERA","PACSPP","PANIC","PANICUM","PANSPP","PASPAL","PASSPP","PASSP1","PENSSP","PERSPP","PHLEU","PHYSPP","PINSPP","PINUS","POA","POACEAE","POLYG2","POLYG4","POLYGO","POLYGONUM","POPSPP","POPULUS","POTENT","POTENTILLA","PRESPP","PRUNE","PRUNU","PRUNUS","PRUSPP","PYCNA","PYCNANTHEM","PYRUS","QUERC","QUERCUS","QUESPP","RANSPP","RANUNCULUS","RHAMNUS","RHEXI","RHODO","RIBES","ROSA","ROSSPP","ROSA5","RUBIACEAE","RUBSPP","RUBUS","RUDBECKIA","RUMEX","RUMSPP","SALIX","SAMBU","SANICULA","SANSPP","SCIRP","SCIRPUS","SCLSPP","SCUSPP","SCUTELLARI","SETARIA","SETSPP","SISSPP","SISYR","SMILAX","SMISPP","SOLID","SOLIDAGO","SOLSPP","SOLSP1","SPIRA","SPIRA2","SPIRAE","SPIRAN","STELL","STELLARIA","STIPA","SYMPHY","Symphy2","SYMPHYOTRI","SYMSPP","SYMSP1","SYMSPP1","TARAX","TARSPP","THALICTRUM","TRIFOL","TRIFOLIUM","TRILL","TRILLIUM","TRISPP","ULMSPP","ULMUS","UVUSP","VACCI","VACCIN","VACCINIUM","VACSPP","VERBA","VERBENA","VERON","VERONICA","VIBURN","VIBURNUM","VICIA","VICSPP","VIOLA","VIOSPP","VIOSPP1","VITIS","VITSPP","YPINE")
```

# SPECIES REPORT

## Step 1 - Substrates and Unknowns

Start with unknown species.

```{r}
Substrates_temp <- c("2AB","BARE","BOLE","2BOLE", "DUFF", "FUNG","FUNGI","FUNGUS","2FF","HAY","LICH","LICHEN","2LICH","LITT","LITTER","2LTR","MOSS","ROCK","ROOT","SCAT","SOIL","WATER","WOOD","DDTREE")

Unknowns_MysteryPlants_temp <- c("UNKSPP","UNK_001","UNK_002","UNKN_98","UNKSP1","UNSKP1","UNKSP2","UNKN_WOODY","2PLANT","NOSP","NODATA")

Unknowns_LifeFormOnly_temp <- c(
    "FERN","2FERN",
    "UNKN_FORB","2FORB","2FORBD","2FORBM",
    "GRASS","GRSSPP","GRASSSP","GRASSSP1","GRASP1","GRASSP1","GRSSP1","GRSPP1",
    "GRSPP2","2GL","GRASS_LIG","GRASS_THIN","2GRAM",
    "UNKSNAG","2TREE","2TDBD","UNKN_SHRUB","2SHRUBD","2SHRUB","UNKN_WOODY",
    "2VINEHERB","2VINEWOOD"
    )
```

### Lifeform

-   Substrate. Check that Species_LifeFormNameLocal = Undefined

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(Species_LocalSpeciesSymbol %in% Substrates_temp)
query <- "Species LifeForm"
query_message <- paste0("Substrate. Life Form should be 'Undefined'. Life Form")
values_data <- data$Species_LifeFormNameLocal
values_valid <- "Undefined"
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_LifeForm_Substrate <- qaqc(data, query, query_message, values_check)
```

-   Unknown plant. Check that Species_LifeFormNameLocal = Unknown

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(Species_LocalSpeciesSymbol %in% Unknowns_MysteryPlants_temp)
query <- "Species LifeForm"
query_message <- paste0("Mystery plant. Life Form should be 'Unknown'. Life Form")
values_data <- data$Species_LifeFormNameLocal
values_valid <- "Unknown"
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_LifeForm_Unknown <- qaqc(data, query, query_message, values_check)
```

-   Known plant. Check that Species_LifeFormNameLocal is [not]{.underline} Unknown or Undefined

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% Substrates_temp,
         !Species_LocalSpeciesSymbol %in% Unknowns_MysteryPlants_temp)
query <- "Species LifeForm"
query_message <- paste0("Life Form")
values_data <- data$Species_LifeFormNameLocal
values_valid <- c("Undefined", "Unknown")
values_check <- !values_data %in% values_valid

# Identify errors
errors_SpeciesReport_LifeForm_Known <- qaqc(data, query, query_message, values_check)
```

#### Combine LifeForm Errors {.hidden}

```{r}
errors_SpeciesReport_LifeForm <- unique(rbind(errors_SpeciesReport_LifeForm_Substrate, errors_SpeciesReport_LifeForm_Unknown, errors_SpeciesReport_LifeForm_Known))

remove(errors_SpeciesReport_LifeForm_Substrate, errors_SpeciesReport_LifeForm_Unknown, errors_SpeciesReport_LifeForm_Known)

if(nrow(errors_SpeciesReport_LifeForm) > 1) {
  errors_SpeciesReport_LifeForm <- errors_SpeciesReport_LifeForm %>%
    filter(Error != "No Error")
} else {
  errors_SpeciesReport_LifeForm <- errors_SpeciesReport_LifeForm}
```

### Unknown Taxa

[Problem:]{.underline} Substrate or unknown plant where no taxonomic information is known, but taxonomic fields have data entered.

[Procedure:]{.underline}

-   Filter for unknowns. Make sure that Family, Genus, and Scientific Name columns are blank.

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(Species_LocalSpeciesSymbol %in% c(Substrates_temp, Unknowns_MysteryPlants_temp, Unknowns_LifeFormOnly_temp))
data$Species_Family[is.na(data$Species_Family)] <- ""
query <- "Species Unknown"
query_message <- paste0("Family should be blank. Family")
values_data <- data$Species_Family
values_valid <- ""
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_Unknown_Taxa_Family <- qaqc(data, query, query_message, values_check)
```

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(Species_LocalSpeciesSymbol %in% c(Substrates_temp, Unknowns_MysteryPlants_temp, Unknowns_LifeFormOnly_temp))
data$Species_Genus[is.na(data$Species_Genus)] <- ""
query <- "Species Unknown"
query_message <- paste0("Genus should be blank. Genus")
values_data <- data$Species_Genus
values_valid <- ""
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_Unknown_Taxa_Genus <- qaqc(data, query, query_message, values_check)
```

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(Species_LocalSpeciesSymbol %in% c(Substrates_temp, Unknowns_MysteryPlants_temp, Unknowns_LifeFormOnly_temp))
data$Species_ScientificName[is.na(data$Species_ScientificName)] <- ""
query <- "Species Unknown"
query_message <- paste0("Scientific Name should be blank. Scientific Name")
values_data <- data$Species_ScientificName
values_valid <- ""
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_Unknown_Taxa_ScientificName <- qaqc(data, query, query_message, values_check)
```

#### Combine Unknown Taxa Errors {.hidden}

```{r}
errors_SpeciesReport_Unknown_Taxa <- unique(rbind(errors_SpeciesReport_Unknown_Taxa_Family, errors_SpeciesReport_Unknown_Taxa_Genus, errors_SpeciesReport_Unknown_Taxa_ScientificName))

remove(errors_SpeciesReport_Unknown_Taxa_Family, errors_SpeciesReport_Unknown_Taxa_Genus, errors_SpeciesReport_Unknown_Taxa_ScientificName)

if(nrow(errors_SpeciesReport_Unknown_Taxa) > 1) {
  errors_SpeciesReport_Unknown_Taxa <- errors_SpeciesReport_Unknown_Taxa %>%
    filter(Error != "No Error")
} else {
  errors_SpeciesReport_Unknown_Taxa <- errors_SpeciesReport_Unknown_Taxa}
```

### Family {.hidden}

[Problem:]{.underline} Unknown plant where only the family is known, but other taxonomic fields have data entered.

[Procedure:]{.underline}

-   If Family column has data, make sure that Genus and Scientific Name columns are blank.

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!is.na(Species_Family),
         is.na(Species_ScientificName) | grepl("species|spp", Species_ScientificName))
data$Species_Genus[is.na(data$Species_Genus)] <- ""
query <- "Species Unknown"
query_message <- paste0("Genus should be blank. Genus")
values_data <- data$Species_Genus
values_valid <- ""
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_Unknown_FamilyOnly_Genus <- qaqc(data, query, query_message, values_check)
```

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!is.na(Species_Family),
         is.na(Species_Genus) | grepl("species|spp", Species_Genus))
data$Species_ScientificName[is.na(data$Species_ScientificName)] <- ""
query <- "Species Unknown"
query_message <- paste0("Scientific Name should be blank. Scientific Name")
values_data <- data$Species_ScientificName
values_valid <- ""
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_Unknown_FamilyOnly_ScientificName <- qaqc(data, query, query_message, values_check)
```

#### Combine Family Errors {.hidden}

```{r}
errors_SpeciesReport_Unknown_FamilyOnly <- unique(rbind(errors_SpeciesReport_Unknown_FamilyOnly_Genus, errors_SpeciesReport_Unknown_FamilyOnly_ScientificName))

remove(errors_SpeciesReport_Unknown_FamilyOnly_Genus, errors_SpeciesReport_Unknown_FamilyOnly_ScientificName)

if(nrow(errors_SpeciesReport_Unknown_FamilyOnly) > 1) {
  errors_SpeciesReport_Unknown_FamilyOnly <- errors_SpeciesReport_Unknown_FamilyOnly %>%
    filter(Error != "No Error")
} else {
  errors_SpeciesReport_Unknown_FamilyOnly <- errors_SpeciesReport_Unknown_FamilyOnly}
```

### Genus {.hidden}

[Problem:]{.underline} Genus is spelled incorrectly or genus is unknown.

[Procedure:]{.underline}

-   Check that genus is spelled correctly in both the Genus field and Scientific Name field.
-   If Genus = NA, make sure the Family field is filled out and Scientific Name field is blank
-   If plant is an unknown family, make sure Family/Genus/Scientific Name fields are all blank.

```{r}
data_temp <- SpeciesReport %>% 
  separate(Species_ScientificName, sep = " ", into = c("ScientificGenus"), remove = FALSE)

# Set parameters
data <- data_temp %>% 
  filter(!Species_LocalSpeciesSymbol %in% c(Substrates_temp, Unknowns_MysteryPlants_temp, Unknowns_LifeFormOnly_temp))
query <- "Species Unknown"
query_message <- paste0("Family = ", data$Species_Family, ". Scientific Name = ", data$ScientificGenus, ". Genus")
values_data <- data$Species_Genus
values_valid <- data$ScientificGenus
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_Unknown_GenusOnly <- qaqc(data, query, query_message, values_check)
```

### Combine Unknown Errors {.hidden}

```{r}
errors_SpeciesReport_Unknown <- unique(rbind(errors_SpeciesReport_Unknown_Taxa, errors_SpeciesReport_Unknown_FamilyOnly, errors_SpeciesReport_Unknown_GenusOnly))

remove(errors_SpeciesReport_Unknown_Taxa, errors_SpeciesReport_Unknown_FamilyOnly, errors_SpeciesReport_Unknown_GenusOnly)

if(nrow(errors_SpeciesReport_Unknown) > 1) {
  errors_SpeciesReport_Unknown <- errors_SpeciesReport_Unknown %>%
    filter(Error != "No Error")
} else {
  errors_SpeciesReport_Unknown <- errors_SpeciesReport_Unknown}
```

## Step 2 - Local Species Info

Now that we fixed unknowns, we can use these codes

```{r}
Substrates <- SpeciesReport %>%
  filter(Species_LifeFormNameLocal == "Undefined")
Substrates <- unique(Substrates$Species_LocalSpeciesSymbol)
  
Unknowns_MysteryPlants <- SpeciesReport %>%
  filter(Species_LifeFormNameLocal == "Unknown")
Unknowns_MysteryPlants <- unique(Unknowns_MysteryPlants$Species_LocalSpeciesSymbol)

Unknowns_LifeFormOnly <- SpeciesReport %>%
  filter(!Species_LifeFormNameLocal %in% c("Undefined", "Unknown"),
         is.na(Species_Family) & is.na(Species_Genus))
Unknowns_LifeFormOnly <- unique(Unknowns_LifeFormOnly$Species_LocalSpeciesSymbol)

Unknowns_FamilyOnly <- SpeciesReport %>%
  filter(!Species_LifeFormNameLocal %in% c("Undefined", "Unknown"),
         !is.na(Species_Family) & is.na(Species_Genus) & is.na(Species_ScientificName))
Unknowns_FamilyOnly <- unique(Unknowns_FamilyOnly$Species_LocalSpeciesSymbol)

Unknowns_GenusOnly <- SpeciesReport %>%
  filter(Species_ScientificName == Species_Genus)
Unknowns_GenusOnly <- unique(Unknowns_GenusOnly$Species_LocalSpeciesSymbol)



Unknowns <- c(Unknowns_MysteryPlants, Unknowns_LifeFormOnly, Unknowns_FamilyOnly, Unknowns_GenusOnly)
```

### Taxonomy

[Problem:]{.underline} Species Report is missing taxonomic information

[Procedure:]{.underline}

-   Check that Species_ScientificName is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns)
query <- "Species Taxa"
query_message <- paste0("Scientific Name") 
values_data <- data$Species_ScientificName
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_Taxa_ScientificName <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_Genus is not blank.

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns)
query <- "Species Taxa"
query_message <- paste0("Genus") 
values_data <- data$Species_Genus
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_Taxa_Genus <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_Family is not blank. (Field sometimes cannot be edited in FFI)

```{r}
# Set parameters
data <- SpeciesReport %>%
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns)
query <- "Species Taxa"
query_message <- paste0("Family")
values_data <- data$Species_Family
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_Taxa_Family <- qaqc(data, query, query_message, values_check)
```

#### Combine Taxonomy Errors {.hidden}

```{r}
errors_SpeciesReport_Taxa <- unique(rbind(errors_SpeciesReport_Taxa_Family, errors_SpeciesReport_Taxa_Genus, errors_SpeciesReport_Taxa_ScientificName))

remove(errors_SpeciesReport_Taxa_Family, errors_SpeciesReport_Taxa_Genus, errors_SpeciesReport_Taxa_ScientificName)

if(nrow(errors_SpeciesReport_Taxa) > 1) {
  errors_SpeciesReport_Taxa <- errors_SpeciesReport_Taxa %>%
    filter(Error != "No Error")
} else {
  errors_SpeciesReport_Taxa <- errors_SpeciesReport_Taxa}
```

### Local Characteristics

[Problem:]{.underline} Species Report is missing locally defined information

[Procedure:]{.underline}

-   Check that Species_CommonNameLocal is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns)
query <- "Species Local"
query_message <- paste0("Common Name")
values_data <- data$Species_CommonNameLocal
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_Local_CommonName <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_LifeCycleLocal is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns)
query <- "Species Local"
query_message <- paste0("Life Cycle")
values_data <- data$Species_LifeCycleLocal
values_valid <- "Not Defined"
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_Local_LifeCycle <- qaqc(data, query, query_message, values_check)
```

-   Sort by Native = True. Check that Invasive = False. Native Species should not be invasive.

```{r}
# Set parameters
data <- SpeciesReport %>% 
  filter(Species_NativityLocal == "True")
query <- "Species Local"
query_message <- paste0("Native = True. Invasive")
values_data <- data$Species_Invasive
values_valid <- c("False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Local_Native <- qaqc(data, query, query_message, values_check)
```

-   Sort by Native = False. Check that Invasive = True (Nonnative & noninvasive species ok, but should be double checked)

```{r}
# # Set parameters
# data <- SpeciesReport %>%
#   filter(Species_NativityLocal == "False",
#          !Species_LocalSpeciesSymbol %in% Substrates,
#          !Species_LocalSpeciesSymbol %in% Unknowns)
# query <- "Species_Local"
# query_message <- paste0("Native = False. Invasive")
# values_data <- data$Species_Invasive
# values_valid <- c("True")
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_SpeciesReport_Local_NonNative <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_ScientificName is not duplicated

```{r}
# Check for species duplication and store results in new column
data_temp <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns) %>% 
  get_dupes(AdminUnit_Name, Species_ScientificName)

# Set parameters 
data <- merge(SpeciesReport, data_temp, all.x = T)
data$dupe_count[is.na(data$dupe_count)] <- 0
query <- "Species Local" 
query_message <- paste0("Species = ", data$Species_ScientificName, ". Duplicates")
values_data <- data$dupe_count
values_valid <- 0
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_Local_Duplicate <- qaqc(data, query, query_message, values_check)
```

-   Trees UV fields

```{r}

```

#### Combine Local Characteristics Errors {.hidden}

```{r}
errors_SpeciesReport_Local <- unique(rbind(errors_SpeciesReport_Local_CommonName, errors_SpeciesReport_Local_LifeCycle, errors_SpeciesReport_Local_Native, errors_SpeciesReport_Local_Duplicate))

remove(errors_SpeciesReport_Local_CommonName, errors_SpeciesReport_Local_LifeCycle, errors_SpeciesReport_Local_Native, errors_SpeciesReport_Local_Duplicate)

if(nrow(errors_SpeciesReport_Local) > 1) {
  errors_SpeciesReport_Local <- errors_SpeciesReport_Local %>%
    filter(Error != "No Error")
} else {
  errors_SpeciesReport_Local <- errors_SpeciesReport_Local}
```

### Combine and Save Errors {.hidden}

```{r}
errors_SpeciesReport_Step2 <- rbind(errors_SpeciesReport_LifeForm, errors_blank, errors_SpeciesReport_Unknown, errors_blank, errors_SpeciesReport_Taxa, errors_blank, errors_SpeciesReport_Local)
```

```{r}
# # Formatting
# 
# # Add blank rows between each tag number
# errors_SpeciesReport_Step1_blanks <- errors_SpeciesReport_Step1[1, ]
# for (i in 2:nrow(errors_SpeciesReport_Step1)) {
#   if (errors_SpeciesReport_Step1[i, "AdminUnit_Name"] != errors_SpeciesReport_Step1[i - 1, "AdminUnit_Name"]) {
#     errors_SpeciesReport_Step1_blanks <- rbind(errors_SpeciesReport_Step1_blanks, errors_blank, errors_SpeciesReport_Step1[i, ])
#   } else {
#     errors_SpeciesReport_Step1_blanks <- rbind(errors_SpeciesReport_Step1_blanks, errors_SpeciesReport_Step1[i, ])
#   }
# }
# 
# # Add conditional formating to ouput
# errors_Step1_all <- condformat(errors_SpeciesReport_Step1_blanks[1:(nrow(errors_SpeciesReport_Step1_blanks)), 1:ncol(errors_SpeciesReport_Step1_blanks)]) %>%
#   rule_fill_discrete(columns = 1:(ncol(errors_SpeciesReport_Step1_blanks)),
#                      expression = SavedQuery != "",
#                      colours = c("TRUE" = "#C6E0B4"),
#                      na.value = "#FFFFFF")
# 
# # Save as CSV or XLSX
# condformat2excel(errors_Step1_all, paste0(path_errors, target_park, "_Errors_SpeciesManagement_Step1.xlsx"), sheet_name = path_errors_name, overwrite_wb = TRUE)
```

## Step 3 - Cross Park Inconsistencies

### Inconsistencies

```{r}
# Set parameters 
data <- SpeciesReport %>%
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns) %>% 
  dplyr::group_by(Species_ScientificName) %>%
  dplyr::mutate(n_families = dplyr::n_distinct(Species_Family)) %>%
  dplyr::ungroup()
query <- "Species Cross Park" 
query_message <- paste0("Species = ", data$Species_ScientificName, ". Family = ", data$Species_Family, ". Family count")
values_data <- data$n_families
values_valid <- 1
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_CrossPark_Family <- qaqc(data, query, query_message, values_check)
errors_SpeciesReport_CrossPark_Family <- errors_SpeciesReport_CrossPark_Family %>% 
  arrange(errors_SpeciesReport_CrossPark_Family$Error)
```

```{r}
# Set parameters 
data <- SpeciesReport %>%
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns) %>% 
  dplyr::group_by(Species_ScientificName) %>%
  dplyr::mutate(n_lifeform = dplyr::n_distinct(Species_LifeFormNameLocal)) %>%
  dplyr::ungroup()
query <- "Species Cross Park" 
query_message <- paste0("Species = ", data$Species_ScientificName, ". Lifeform = ", data$Species_LifeFormNameLocal, ". Life form count")
values_data <- data$n_lifeform
values_valid <- 1
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_CrossPark_Lifeform <- qaqc(data, query, query_message, values_check)
errors_SpeciesReport_CrossPark_Lifeform <- errors_SpeciesReport_CrossPark_Lifeform %>% 
  arrange(errors_SpeciesReport_CrossPark_Lifeform$Error)
```

```{r}
# Set parameters
data <- SpeciesReport %>%
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns) %>%
  dplyr::group_by(Species_ScientificName) %>%
  dplyr::mutate(n_invasive = dplyr::n_distinct(Species_Invasive)) %>%
  dplyr::ungroup()
query <- "Species Cross Park"
query_message <- paste0("Species = ", data$Species_ScientificName, ". Native = ", data$Species_NativityLocal, ". Invasive = ", data$Species_Invasive, ". Invasive count")
values_data <- data$n_invasive
values_valid <- 1
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_CrossPark_Invasive <- qaqc(data, query, query_message, values_check)
errors_SpeciesReport_CrossPark_Invasive <- errors_SpeciesReport_CrossPark_Invasive %>%
  arrange(errors_SpeciesReport_CrossPark_Invasive$Error)
```

### Combine Errors {.hidden}

```{r}
errors_SpeciesReport_Step3 <- rbind(errors_SpeciesReport_CrossPark_Family, errors_blank, errors_SpeciesReport_CrossPark_Lifeform, errors_blank, errors_SpeciesReport_CrossPark_Invasive)
```

# ALL ERRORS

```{r}
errors_SpeciesReport <- rbind(errors_SpeciesReport_ScientificName, errors_SpeciesReport_Genus, errors_SpeciesReport_CommonName, errors_SpeciesReport_LifeForm, errors_SpeciesReport_LifeCycle, errors_SpeciesReport_Native, errors_SpeciesReport_Cultural, errors_SpeciesReport_Concern, errors_SpeciesReport_Retired) %>% 
  arrange(Species_LocalSpeciesSymbol)

remove(errors_SpeciesReport_ScientificName, errors_SpeciesReport_Genus, errors_SpeciesReport_CommonName, errors_SpeciesReport_LifeForm, errors_SpeciesReport_LifeCycle, errors_SpeciesReport_Native, errors_SpeciesReport_Cultural, errors_SpeciesReport_Concern, errors_SpeciesReport_Retired)

if(nrow(errors_SpeciesReport) > 1) {
  errors_SpeciesReport <- errors_SpeciesReport %>%
    filter(Error != "No Error")
} else {
  errors_SpeciesReport <- errors_SpeciesReport}
```

```{r}
# Formatting

# Add blank rows between each tag number
errors_SpeciesReport_blanks <- errors_SpeciesReport[1, ]
for (i in 2:nrow(errors_SpeciesReport)) {
  if (errors_SpeciesReport[i, "Species_LocalSpeciesSymbol"] != errors_SpeciesReport[i - 1, "Species_LocalSpeciesSymbol"]) {
    errors_SpeciesReport_blanks <- rbind(errors_SpeciesReport_blanks, errors_blank, errors_SpeciesReport[i, ])
  } else {
    errors_SpeciesReport_blanks <- rbind(errors_SpeciesReport_blanks, errors_SpeciesReport[i, ])
  }
}

# Add conditional formating to ouput
errors_all <- condformat(errors_SpeciesReport_blanks[1:(nrow(errors_SpeciesReport_blanks)), 1:ncol(errors_SpeciesReport_blanks)]) %>%
  rule_fill_discrete(columns = 1:(ncol(errors_SpeciesReport_blanks)),
                     expression = SavedQuery != "",
                     colours = c("TRUE" = "#C6E0B4"),
                     na.value = "#FFFFFF")
```

```{r}
path_errors

# Save as CSV or XLSX
condformat2excel(errors_all, paste0(path_errors, target_park, "_Errors_SpeciesManagement.xlsx"), sheet_name = path_errors_name, overwrite_wb = TRUE)
```
