---
title: Complete CSVs
author: Alexandra Lalor
output:
  html_document:
    theme: readable
    highlight: null
    toc: true
    toc_depth: 1
    toc_float:
      smooth_scroll: true
    code_download: true
  word_document:
    toc: true
    toc_depth: 1
  pdf_document:
    toc: true
    toc_depth: 1
---

# PURPOSE

This code is intended to quality check all FFI CSV exports for missing data. Missing data is especially difficult to catch because it relies on information on how much data there is "supposed to be" vs how much data actually was exported. There is added complexity because certain protocols may not contain data for valid reasons (e.g. no trees, no coarse woody debris, no seedlings, no shrubs, etc...). Each error should be carefully checked and considered as a potential major error. Follow the guide below to determine what action is needed.

# Major issues to check across all CSVs

-   [Procedure:]{.underline}

    -   Code will check that data exists for every protocol which was visited/included in the sample event.
        -   Group by Macroplot_Name and SampleEvent_Date. Calculate number of data points per plot. Check that data_points \> 0
    -   **No data (valid):**
        -   Certain protocols may not contain data for valid reasons (e.g. no trees, no coarse woody debris, no seedlings, no shrubs, etc...). [Make sure this is noted in the comment field of the protocol header in FFI]{.underline}.

        -   Protocols may have been inadvertently added to the sample event with no intention to collect data on that protocol. [Make sure to delete protocol from the sample event in FFI.]{.underline}
    -   **No data (invalid):**
        -   If data should exist but doesn't, data may not have been entered into FFI yet. [Make sure to enter missing data into FFI.]{.underline}

        -   Data may have been added into a non-standard protocol (e.g. "Density - Quadrats" instead of "Density - Quadrats (metric)". [Make sure to transfer data into the correct protocol.]{.underline}

        -   There may be an issue exporting the data out of FFI. [Make sure to troubleshoot data exports, and contact FFI developers if the issue cannot be resolved.]{.underline}

### Export all CSVs

This code uses the Macroplot Report and Sample Event Report from FFI as the reference file for how much data there is "supposed to be". These reports have been combined into a clean "Metadata Report", using the Clean_1_All.Rmd script. The sample event information in this file is then compared to each protocol export, to ensure that all expected macroplots and sample events are included in the export.

-   MetadataReport.csv

These protocols are included in the code and have been cleaned using the Clean_1_All.Rmd script.

-   Surface Fuels - 1000Hr

-   Surface Fuels - Duff_Litter

-   Surface Fuels - Fine

-   Post Burn Severity

-   Trees - Individuals (metric)

-   Density - Quadrats (metric)

-   Density - Belts (metric)

-   Cover - Species Composition (metric)

-   Cover - Points (metric)

## Before Starting {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r install packages, include=FALSE}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
## Load Packages

# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
library(readr)
# janitor has functions to find duplicates
library(janitor)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr and LaTeX is used to create output files from R Markdown
library(knitr)
#library(LaTeX)
```

### Create Function {.hidden}

```{r}
# Create blank data frame as error log template
errors_blank <- data.frame("SavedQuery" = "", "Error" = "", "Fixed" = "", "Explanation" = "", "Queryers" = "")

# Create error group. Duplicate errors will be grouped by these columns.
errors_group <- c("SavedQuery", "Error")

############################################################################################
## Source Code
#Pull in source code that creates QAQC functions and builds an empty error table.
#source("C:/Users/allie/OneDrive/Desktop/R Projects/NER/scripts/1_QAQC/qaqc_function.R")


# QAQC function
qaqc <- function(data, query, query_message, values_check) {

  # Check if there is data to QAQC
  if(nrow(data) == 0) {
  # If there is no data, default to "No Error" data frame
  errors <- errors_blank %>%
    mutate("SavedQuery" = query,
           "Error" = "No Error")
  # If there is data, perform error check
} else {

  # Use relevant dataset to look for errors
  errors <- data %>%
    # Add columns relevant to error checking
           # Populate the "SavedQuery" column with the query name
    mutate("SavedQuery" = query,
           # Populate the "Error" column with the query message and relevant data
           "Error" = paste(query_message, "=", values_data),
           # Create a blank "Fixed" column
           "Fixed" = "",
           # Create a blank "Explanation" column
           "Explanation" = "",
           # Create a blank "Queryers" column
           "Queryers" = "") %>%
    # Filter for data which is "false" (data does not match valid conditions)
    # NA values are treated as "false" (missing data is not valid)
    filter(!(values_check %>% replace_na(FALSE))) %>%
    # Select relevant columns to view errors
    select(colnames(errors_blank))
  
  # Next, check if there are duplicate errors
  errors <- unique(errors)
}

  # Check if there are no errors
  if (nrow(errors) == 0) {
    # If there are no errors, default to "No Error" data frame
    errors <- errors_blank %>%
      mutate(SavedQuery = query,
             Error = "No Error")
    # If there are errors, keep error log you just created
  } else {
    errors <- errors
  }
}
```

### Target Park {.hidden}

```{r}
# designate target park(s)
target_park <- "SHEN"
```

### Adjust File Paths {.hidden}

```{r import data, include=FALSE}
# adjust file paths
path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
#path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_data <- paste0(path_main, "R Outputs/ALL/ALL_")
path_errors <- paste0(path_main, "QAQC/", target_park, "/")
path_errors_name <- paste0(target_park, " CSV Errors")
```

### Load Data {.hidden}

```{r load data, include=FALSE}
# load data
MetadataReport_all <- read.csv(paste0(path_data, "MetadataReport.csv"))

Fuels1000_all <- read.csv(paste0(path_data, "Data_Surface Fuels - 1000Hr.csv"))
FuelsDuffLitt_all <- read.csv(paste0(path_data, "Data_Surface Fuels - Duff_Litter.csv"))
FuelsFine_all <- read.csv(paste0(path_data, "Data_Surface Fuels - Fine.csv"))
PostBurn_all <- read.csv(paste0(path_data, "Data_Post Burn Severity (metric).csv"))
Trees_all <- read.csv(paste0(path_data, "Data_Trees - Individuals (metric).csv"))
Seedlings_all <- read.csv(paste0(path_data, "Data_Density - Quadrats (metric).csv"))
Shrubs_all <- read.csv(paste0(path_data, "Data_Density - Belts (metric).csv"))
HerbsSpComp_all <- read.csv(paste0(path_data, "Data_Cover - Species Composition (metric).csv"))
HerbsPoints_all <- read.csv(paste0(path_data, "Data_Cover - Points (metric).csv"))
```

### Filter Data {.hidden}

```{r}
#####
# Metadata Report
#####
MetadataReport <- MetadataReport_all %>%
  filter(AdminUnit_Name %in% target_park)

#####
# Fuels1000
#####
Fuels1000_data <- Fuels1000_all %>%
  filter(AdminUnit_Name %in% target_park)

#####
# FuelsDuffLitt
#####
FuelsDuffLitt_data <- FuelsDuffLitt_all %>%   
  filter(AdminUnit_Name %in% target_park)

#####
# FuelsFine
#####
FuelsFine_data <- FuelsFine_all %>%   
  filter(AdminUnit_Name %in% target_park)

#####
# PostBurn
#####
PostBurn_data <- PostBurn_all %>%
  filter(AdminUnit_Name %in% target_park)

#####
# Trees
#####
Trees_data <- Trees_all %>%   
  filter(AdminUnit_Name %in% target_park)

#####
# Seedlings
#####
Seedlings_data <- Seedlings_all %>%
  filter(AdminUnit_Name %in% target_park)

#####
# Shrubs
#####
Shrubs_data <- Shrubs_all %>%
  filter(AdminUnit_Name %in% target_park)

#####
# HerbsSpComp
#####
HerbsSpComp_data <- HerbsSpComp_all %>%
  filter(AdminUnit_Name %in% target_park)

#####
# HerbsPoints
#####
HerbsPoints_data <- HerbsPoints_all %>%
  filter(AdminUnit_Name %in% target_park)
```

# PROTOCOL - SURFACE FUELS

## 1000HR (CWD)

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport %>%
  filter(SampleEvent_Protocols == "Surface Fuels") %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- Fuels1000_data %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(Fuels1000_data, data_temp, by = c("Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Fuel 1000" 
query_message <- paste0(data$Macroplot_Name, ". Date = ",data$SampleEvent_Date, ". If applicable, write 'no CWD found' in comments field in FFI. CWD")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_Fuels1000 <- qaqc(data, query, query_message, values_check)
```

## DUFF LITTER (DL)

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport %>%
  filter(SampleEvent_Protocols == "Surface Fuels") %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- FuelsDuffLitt_data %>%
  filter(!is.na(LittDep)) %>%
  filter(!is.na(DuffDep)) %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(FuelsDuffLitt_data, data_temp, by = c("Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Fuel DL" 
query_message <- paste0(data$Macroplot_Name, ". Date = ",data$SampleEvent_Date, ". Complete Sample Locations")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_FuelsDuffLitt <- qaqc(data, query, query_message, values_check)
```

## FINE FUELS (FWD)

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport %>%
  filter(SampleEvent_Protocols == "Surface Fuels") %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- FuelsFine_data %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(FuelsFine_data, data_temp, by = c("Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Fuel Fine"
query_message <- paste0(data$Macroplot_Name, ". Date = ",data$SampleEvent_Date, ". Complete Transects")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_FuelsFine <- qaqc(data, query, query_message, values_check)
```

# PROTOCOL - POST BURN

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport %>%
  filter(SampleEvent_Protocols == "Post Burn Severity (metric)") %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- PostBurn_data %>% 
  filter(!is.na(Veg)) %>%
  filter(!is.na(Sub)) %>%
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(PostBurn_data, data_temp, by = c("Macroplot_Name","SampleEvent_Date"), all = T)
query <- "PBSev" 
query_message <- paste0(data$Macroplot_Name, ". Date = ",data$SampleEvent_Date, ". Complete Sample Locations")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_PostBurn <- qaqc(data, query, query_message, values_check)
```

# PROTOCOL - TREES

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport %>%
  filter(SampleEvent_Protocols == "Trees - Individuals (metric)") %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- Trees_data %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(Trees_data, data_temp, by = c("Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Trees" 
query_message <- paste0(data$Macroplot_Name, ". Date = ",data$SampleEvent_Date, ". If applicable, write 'no trees found' in comments field in FFI. Trees")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_Trees <- qaqc(data, query, query_message, values_check)
```

# PROTOCOL - SEEDLINGS

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport %>%
  filter(SampleEvent_Protocols == "Density - Quadrats (metric)") %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- Seedlings_data %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)


# Set parameters 
data <- merge(Seedlings_data, data_temp, by = c("Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Dens Quad" 
query_message <- paste0(data$Macroplot_Name, ". Date = ",data$SampleEvent_Date, ". If applicable, write 'no seedlings found' in comments field in FFI. Seedlings")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_Seedlings <- qaqc(data, query, query_message, values_check)
```

# PROTOCOL - SHRUBS

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport %>%
  filter(SampleEvent_Protocols == "Density - Belts (metric)") %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- Shrubs_data %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(Shrubs_data, data_temp, by = c("Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Dens Belts" 
query_message <- paste0(data$Macroplot_Name, ". Date = ",data$SampleEvent_Date, ". If applicable, write 'no shrubs found' in comments field in FFI. Shrubs")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_Shrubs <- qaqc(data, query, query_message, values_check)
```

# PROTOCOL - HERBS SPECIES COMP

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport %>%
  filter(SampleEvent_Protocols == "Cover - Species Composition (metric)") %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- HerbsSpComp_data %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)


# Set parameters 
data <- merge(HerbsSpComp_data, data_temp, by = c("Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Cvr SpComp" 
query_message <- paste0(data$Macroplot_Name, ". Date = ",data$SampleEvent_Date, ". If applicable, write 'no species found' in comments field in FFI. Species")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_HerbsSpComp <- qaqc(data, query, query_message, values_check)
```

# PROTOCOL - HERBS POINTS

[Procedure:]{.underline}

-   Group by Macroplot_Name and SampleEvent_Date. Calculate number of data points per plot. Check that data_points \> 0
-   Filter by Order = 1. Group by Macroplot, Date, and Transect. Calculate number of hits per plot. Check that sum_hits = 166

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport %>%
  filter(SampleEvent_Protocols == "Cover - Points (metric)") %>% 
  group_by(Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- HerbsPoints_data %>%
  filter(Order == 1) %>%
  group_by(Macroplot_Name, SampleEvent_Date, Transect) %>% 
  dplyr::summarise("data_points" = n())

data_temp_transects <- as.data.frame(1:2)
colnames(data_temp_transects) <- "Transect"
data_temp1 <- merge(data_temp1, data_temp_transects) %>% 
  dplyr::rename("Transect" = !!names(.)[3]) %>% 
  arrange(Macroplot_Name, SampleEvent_Date, Transect)

data_temp <- merge(data_temp1, data_temp2, by = c("Macroplot_Name","SampleEvent_Date", "Transect"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2, data_temp_transects)

# Set parameters 
data <- merge(HerbsPoints_data, data_temp, by = c("Macroplot_Name","SampleEvent_Date", "Transect"), all = T)
query <- "Cvr Pts" 
query_message <- paste0(data$Macroplot_Name, ". Date = ",data$SampleEvent_Date, ". Transect = ", data$Transect, ". Total Points") 
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_HerbsPoints <- qaqc(data, query, query_message, values_check)
```

# ALL ERRORS

```{r}
# Create protocol separators
errors_blank_Fuels1000 <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - FUEL 1000")

errors_blank_FuelsDuffLitt <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - FUEL DUFF LITTER")

errors_blank_FuelsFine <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - FUEL FINE")

errors_blank_PostBurn <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - POST BURN")

errors_blank_Trees <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - TREES")

errors_blank_Seedlings <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - SEEDLINGS")

errors_blank_Shrubs <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - SHRUBS")

errors_blank_HerbsSpComp <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - HERBS OBSERVED")

errors_blank_HerbsPoints <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - HERBS POINTS")
```

```{r}
# Save to master error list 
errors_all <- rbind(errors_blank_Fuels1000, errors_blank, errors_Fuels1000, errors_blank, errors_blank_FuelsDuffLitt, errors_blank, errors_FuelsDuffLitt, errors_blank, errors_blank_FuelsFine, errors_blank, errors_FuelsFine, errors_blank, errors_blank_PostBurn, errors_blank, errors_PostBurn, errors_blank, errors_blank_Trees, errors_blank, errors_Trees, errors_blank, errors_blank_Seedlings, errors_blank, errors_Seedlings, errors_blank, errors_blank_Shrubs, errors_blank, errors_Shrubs, errors_blank, errors_blank_HerbsSpComp, errors_blank, errors_HerbsSpComp, errors_blank, errors_blank_HerbsPoints, errors_blank, errors_HerbsPoints)
```

```{r}
# # Create conditional formatting rules
errors_all_cf <- errors_all %>%
  mutate(Color = ifelse(SavedQuery == "", NA, "Color")) %>% 
  mutate(Color = ifelse((grepl("PROTOCOL|REPORT", errors_all$SavedQuery) == TRUE), "Protocol", Color)) %>%
  mutate(Color = ifelse(Color == FALSE, "Standard", Color))

# Add conditional formating to ouput
errors_all <- condformat(errors_all_cf[1:(nrow(errors_all_cf)), 1:6]) %>%
  rule_fill_discrete(columns = 1:5,
                     expression = (errors_all_cf$Color),
                     colours = c("Color"="#C6E0B4",
                                 "Protocol" = "#969696"),
                     na.value = "#FFFFFF") %>%
  select(!c("Color"))
```

```{r}
# Save as CSV or XLSX 
condformat2excel(errors_all, paste0(path_errors, paste0(target_park, "_errors_Complete.xlsx")), sheet_name = path_errors_name, overwrite_wb = TRUE)
```
