---
title: "QAQC Cross Year"
author: "Alexandra Lalor"
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 3
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: '3'
---

# Before Starting

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r install packages, include=FALSE}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("Rtools")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
## Load Packages

# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
#library(plyr)
# janitor has functions to find duplicates
library(janitor)
# EnvStats is needed for the rosnerTest() function
library(EnvStats)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr is used to create output files from R Markdown
library(knitr)
# here is useful for easily finding the working directory of any project
library(here)
```

### Create Function

```{r qaqc function, include=FALSE}
## Source Code
#Pull in source code that creates QAQC functions and builds an empty error table.
source(paste0(here(), "/scripts/2_QAQC/qaqc_function.R"))
```

### Target Values {.hidden}

```{r target values, include=FALSE}
# designate target values

# parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
target_park <- "RICH"
```

### Adjust File Paths

```{r file paths, include=FALSE}
# adjust file paths

path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
#path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_data <- paste0(path_main, "Exports_Clean/FFI/")
#path_errors <- paste0(path_main, "QAQC/", target_park, "/")
path_errors <- paste0(here(), "/output/errors/")
path_errors_name <- paste0(target_park, " Cross Year Errors")
```

### Load Data

```{r load data, include=FALSE}
Fuels1000_all <- read.csv(paste0(path_data, "english_surface_fuels_thousand_hr.csv"))
FuelsFine_all <- read.csv(paste0(path_data, "english_surface_fuels_fine.csv"))
Trees_all <- read.csv(paste0(path_data, "metric_trees_individuals.csv"))
```

### Filter Data

```{r filter data, include=FALSE}
# Clean up data frame
df_names <- c("Fuels1000_all", "FuelsFine_all", "Trees_all")

for (name in df_names) {
  # load data
  current_df <- get(name)
  
  # filter data for target park
  filtered_df <- current_df %>% 
    # mutate(SampleEvent_Date = as.Date(SampleEvent_Date)) %>% 
    # mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>% 
    # relocate(SampleEvent_Date_Year, .after = SampleEvent_Date) %>% 
    filter(
      AdminUnit_Name == target_park
      )
  
  # rename and save
  new_name <- sub("_all$", "_data_CrossYear", name)
  assign(new_name, filtered_df)
}
```

### Set Thresholds

This QAQC check isolates *incorrect* changes in the following values. Setting thresholds allows us to decide what degree of inaccuracy is acceptable in the data. Larger changes may indicate clear errors, while smaller errors may simply reflect variation in data collection instruments and data collector interpretations. For instance, a live tree could decrease in height by 1 meter or by 10 meters; are both of these changes acceptable or unacceptable? Setting thresholds should consider imperfections in data collection methods and potential impacts to data analysis.

```{r}
# Azimuth (degrees)
max_Azimuth <- 30

# DBH (centimeters)
max_DBH <- 5

# Height (meters)
max_Ht <- 5
```

## Add Columns

### Slope Columns

-   Slope_Count = How many unique slopes have been recorded for each transect?

-   Slope_Change = Has slope changed over time? if Slope_Count \> 1, Slope_Change = Y.

```{r}
# Find data with multiple slopes
Fuels1000_data_CrossYear_Slope <- Fuels1000_data_CrossYear %>% 
  group_by(Macroplot_Name, MethodData_Transect) %>% 
  mutate(Slope_Count = n_distinct(unique(MethodData_Slope_pct))) %>% 
  ungroup() %>% 
  arrange(Macroplot_Name, SampleEvent_Date, MethodData_Transect)

data_temp_merge_Slope_Fuels1000 <- Fuels1000_data_CrossYear_Slope %>% 
  filter(Slope_Count > 1) %>%
  group_by(Macroplot_Name, MethodData_Transect) %>% 
  mutate(Slope_Change = ifelse(duplicated(MethodData_Slope_pct), "N", "Y")) %>%
  filter(Slope_Change == "Y") %>%
  unique()

remove(Fuels1000_data_CrossYear_Slope)
```

```{r}
# Find data with multiple slopes
FuelsFine_data_CrossYear_Slope <- FuelsFine_data_CrossYear %>% 
  group_by(Macroplot_Name, MethodData_Transect) %>% 
  mutate(Slope_Count = n_distinct(unique(MethodData_Slope_pct))) %>% 
  ungroup() %>% 
  arrange(Macroplot_Name, SampleEvent_Date, MethodData_Transect)

data_temp_merge_Slope_FuelsFine <- FuelsFine_data_CrossYear_Slope %>% 
  filter(Slope_Count > 1) %>%
  group_by(Macroplot_Name, MethodData_Transect) %>% 
  mutate(Slope_Change = ifelse(duplicated(MethodData_Slope_pct), "N", "Y")) %>%
  filter(Slope_Change == "Y") %>%
  unique()

remove(FuelsFine_data_CrossYear_Slope)
```

### Azimuth Columns

-   Azimuth_Count = How many unique azimuths have been recorded for each transect?

-   Azimuth_Change = Has azimuth changed over time? if Azimuth_Count \> 1, Azimuth_Change = Y.

-   AzimuthDiff = What is the difference between azimuth values?

```{r}
# Find data with multiple azimuths
FuelsFine_data_CrossYear_Azimuth <- FuelsFine_data_CrossYear %>% 
  group_by(Macroplot_Name, MethodData_Transect) %>% 
  mutate(Azimuth_Count = n_distinct(unique(MethodData_Azimuth_deg))) %>% 
  ungroup() %>% 
  arrange(Macroplot_Name, SampleEvent_Date, MethodData_Transect)

data_temp_merge_Azimuth <- FuelsFine_data_CrossYear_Azimuth %>% 
  filter(Azimuth_Count > 1) %>%
  group_by(Macroplot_Name, MethodData_Transect) %>% 
  mutate(AzimuthDiff = max(MethodData_Azimuth_deg - min(MethodData_Azimuth_deg)),
         Azimuth_Change = ifelse(duplicated(MethodData_Azimuth_deg), "N", "Y")) %>%
  filter(Azimuth_Change == "Y") %>%
  unique()

remove(FuelsFine_data_CrossYear_Azimuth)
```

### DBH Columns

-   MinDBH = What is the smallest recorded DBH of each individual **dead** tree?

-   MinDBHDate = What date was the smallest DBH recorded?

-   MinDBHDiff = What is the size difference between the smallest recorded DBH, and the sample event DBH?

-   MaxDBH = What is the largest recorded DBH of each individual **live** tree?

-   MaxDBHDate = What date was the largest DBH recorded?

-   MaxDBHDiff = What is the size difference between the largest recorded DBH, and the sample event DBH?

```{r}
data_temp_DBH <- Trees_data_CrossYear %>% 
  filter(MethodData_Status == "D",
         !is.na(MethodData_DBH_cm)) %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MinDBH = min(MethodData_DBH_cm),
         MinDBHDiff = MethodData_DBH_cm - MinDBH) %>% 
  ungroup() %>% 
  arrange(MethodData_TagNo, Macroplot_Name, SampleEvent_Date, MethodData_SubFrac)

data_temp_MinDBHDate <- data_temp_DBH %>% 
  filter(MethodData_DBH_cm == MinDBH) %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MinDBHDate = min(SampleEvent_Date)) %>% 
  select(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac, MinDBHDate) %>% 
  unique()

data_temp_merge_DeadDBH <- merge(data_temp_DBH, data_temp_MinDBHDate, all = T)

############################################################################################

data_temp_DBH <- Trees_data_CrossYear %>% 
  filter(MethodData_Status == "L",
         !is.na(MethodData_DBH_cm)) %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MaxDBH = max(MethodData_DBH_cm),
         MaxDBHDiff = MaxDBH - MethodData_DBH_cm) %>% 
  ungroup() %>% 
  arrange(MethodData_TagNo, Macroplot_Name, SampleEvent_Date, MethodData_SubFrac)

data_temp_MaxDBHDate <- data_temp_DBH %>% 
  filter(MethodData_DBH_cm == MaxDBH) %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MaxDBHDate = max(SampleEvent_Date)) %>% 
  select(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac, MaxDBHDate) %>% 
  unique()

data_temp_merge_LiveDBH <- merge(data_temp_DBH, data_temp_MaxDBHDate, all = T)

############################################################################################

data_temp_merge_DBH <- merge(data_temp_merge_DeadDBH, data_temp_merge_LiveDBH, all = T)
remove(data_temp_merge_DeadDBH, data_temp_merge_LiveDBH, data_temp_DBH, data_temp_MinDBHDate, data_temp_MaxDBHDate)
```

### Height Columns

-   MinHeight= What is the shortest recorded Height of each individual **dead** tree?

-   MinHeightDate = What date was the shortest Height recorded?

-   MinHeightDiff = What is the size difference between the shortest recorded Height, and the sample event Height?

-   MaxHeight = What is the tallest recorded Height of each individual **live** tree?

-   MaxHeightDate = What date was the tallest Height recorded?

-   MaxHeightDiff = What is the size difference between the tallest recorded Height, and the sample event Height?

```{r}
data_temp_Height <- Trees_data_CrossYear %>% 
  filter(MethodData_Status == "D",
         !is.na(MethodData_Ht_m)) %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MinHeight = min(MethodData_Ht_m),
         MinHeightDiff = MethodData_Ht_m - MinHeight) %>% 
  ungroup() %>% 
  arrange(MethodData_TagNo, Macroplot_Name, SampleEvent_Date, MethodData_SubFrac)

data_temp_MinHeightDate <- data_temp_Height %>% 
  filter(MethodData_Ht_m == MinHeight) %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MinHeightDate = min(SampleEvent_Date)) %>% 
  select(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac, MinHeightDate) %>% 
  unique()

data_temp_merge_DeadHeight <- merge(data_temp_Height, data_temp_MinHeightDate, all = T)

############################################################################################

data_temp_Height <- Trees_data_CrossYear %>% 
  filter(MethodData_Status == "L",
         !is.na(MethodData_Ht_m)) %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MaxHeight = max(MethodData_Ht_m),
         MaxHeightDiff = MaxHeight - MethodData_Ht_m) %>% 
  ungroup() %>% 
  arrange(MethodData_TagNo, Macroplot_Name, SampleEvent_Date, MethodData_SubFrac)

data_temp_MaxHeightDate <- data_temp_Height %>% 
  filter(MethodData_Ht_m == MaxHeight) %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MaxHeightDate = max(SampleEvent_Date)) %>% 
  select(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac, MaxHeightDate) %>% 
  unique()

data_temp_merge_LiveHeight <- merge(data_temp_Height, data_temp_MaxHeightDate, all = T)

############################################################################################

data_temp_merge_Height <- merge(data_temp_merge_DeadHeight, data_temp_merge_LiveHeight, all = T)
remove(data_temp_merge_DeadHeight, data_temp_merge_LiveHeight, data_temp_Height, data_temp_MinHeightDate, data_temp_MaxHeightDate)
```

### Species Columns

-   Species_Count = How many unique species have been recorded for each individual tree? Count \> 1 means that the tree has changed species.

```{r}
Trees_data_CrossYear_Species <- Trees_data_CrossYear %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(Species_Count = n_distinct(unique(MethodData_LocalSpeciesSymbol))) %>% 
  ungroup() %>% 
  arrange(MethodData_TagNo, Macroplot_Name, SampleEvent_Date, MethodData_SubFrac)

data_temp_Species <- Trees_data_CrossYear_Species %>% 
  filter(Species_Count > 1) %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(Species_Change = ifelse(duplicated(MethodData_LocalSpeciesSymbol), "N", "Y")) %>% 
  filter(Species_Change == "Y") %>% 
  unique()

data_temp_merge_Species <- data_temp_Species
remove(Trees_data_CrossYear_Species, data_temp_Species)
```

### Status Columns

-   Status_Count = How many unique statuses have been recorded for each individual tree? Count of 1 means that the tree has been alive or dead for the entirety of data collection. Count of 2 means that the tree has been both alive and dead.

-   MinDeadDate = What date was the tree first recorded as Dead?

-   MinLiveDate = What date was the tree first recorded as Live?

```{r}
Trees_data_CrossYear_Status <- Trees_data_CrossYear %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(Status_Count = n_distinct(unique(MethodData_Status))) %>% 
  ungroup() %>% 
  arrange(MethodData_TagNo, Macroplot_Name, SampleEvent_Date, MethodData_SubFrac)

# add min death date to data_temp
data_temp_Status_AllDead <- Trees_data_CrossYear_Status %>% 
  filter(Status_Count == 1 & MethodData_Status == "D")
data_temp_Status_SomeDead <- Trees_data_CrossYear_Status %>% 
  filter(Status_Count > 1)
data_temp_Status_Dead <- rbind(data_temp_Status_AllDead, data_temp_Status_SomeDead)

data_temp_MinDeadDate <- data_temp_Status_Dead %>% 
  filter(MethodData_Status == "D") %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MinDeadDate = min(SampleEvent_Date)) %>% 
  select(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac, MinDeadDate) %>% 
  unique()

data_temp_merge_Status_Dead <- merge(data_temp_Status_Dead, data_temp_MinDeadDate, all = T)

# add min live date to data_temp
data_temp_Status_AllLive <- Trees_data_CrossYear_Status %>% 
  filter(Status_Count == 1 & MethodData_Status == "L")
data_temp_Status_SomeLive <- Trees_data_CrossYear_Status %>% 
  filter(Status_Count > 1)
data_temp_Status_Live <- rbind(data_temp_Status_AllLive, data_temp_Status_SomeLive)

data_temp_MinLiveDate <- data_temp_Status_Live %>% 
  filter(MethodData_Status == "L") %>% 
  group_by(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac) %>% 
  mutate(MinLiveDate = min(SampleEvent_Date)) %>% 
  select(MethodData_TagNo, Macroplot_Name, MethodData_SubFrac, MinLiveDate) %>% 
  unique()

data_temp_merge_Status_Live <- merge(data_temp_Status_Live, data_temp_MinLiveDate, all = T)

# merge
data_temp_merge_Status <- merge(data_temp_merge_Status_Dead, data_temp_merge_Status_Live, all = T)

remove(Trees_data_CrossYear_Status, data_temp_Status_AllDead, data_temp_Status_SomeDead, data_temp_Status_Dead, data_temp_MinDeadDate, data_temp_merge_Status_Dead, data_temp_Status_AllLive, data_temp_Status_SomeLive, data_temp_Status_Live, data_temp_MinLiveDate, data_temp_merge_Status_Live)
```

# PROTOCOL - SURFACE FUELS

## 1000HR (CWD) & FINE FUELS (FWD)

This code conducts cross-year quality control checks on 2 surface fuels datasets

-   coarse woody debris (CWD) surface fuels data within the "Surface Fuels - 1000Hr" data set

-   fine woody debris (FWD) surface fuels data within the "Surface Fuels - Fine" data set.

It checks for errors in: Fuel Slope consistency across years, Fuel Azimuth consistency across years

### Adjust Function

```{r}
# Edit blank data frame for preferred error log template.
errors_blank <- data.frame("SavedQuery" = "", 
                           "AdminUnit_Name" = "", 
                           "SampleEvent_TreatmentUnit" = "", 
                           "Macroplot_Name" = "", 
                           "MethodData_Transect" = as.integer(NA), 
                           "Error" = "", 
                           "Fixed" = "", 
                           "Explanation" = "", 
                           "Queryers" = "")

# Edit error group. Duplicate errors will be grouped by these columns.
errors_group <- c("SavedQuery", "AdminUnit_Name", "Macroplot_Name", "MethodData_Transect", "Error")
```

### Fuel Slope

#### Fuels 1000

```{r}
# Set parameters 
data <- merge(Fuels1000_data_CrossYear, data_temp_merge_Slope_Fuels1000, all = T)
query <- "Fuel 1000 Slope" 
query_message <- paste0("Slope = ", data$MethodData_Slope_pct, ". ", "Earliest date = ", data$SampleEvent_Date, ". ", "Conflicting slopes")
values_data <- data$Slope_Change
values_valid <- "Y"
values_check <- (values_data != values_valid) %>% replace_na(TRUE)

# Identify errors
errors_Fuels1000_CrossYear_Slope <- qaqc(data, query, query_message, values_check)

# Consolidate duplicate slope errors into one row
errors_Fuels1000_CrossYear_Slope <- errors_Fuels1000_CrossYear_Slope %>%
  separate(Error, sep = ". Conflicting slopes = Y", into = c("Error")) %>% 
  separate(Error, sep = "date = ", into = c("Test", "Date"), remove = F) %>% 
  arrange(Macroplot_Name, MethodData_Transect, Date) %>% 
  group_by(SavedQuery, AdminUnit_Name, SampleEvent_TreatmentUnit, Macroplot_Name, MethodData_Transect) %>% 
  summarize(
    Error = paste(Error, collapse = "; "),
    Fixed = "",
    Explanation = "",
    Queryers = "")
```

#### Fuels Fine

```{r}
# Set parameters 
data <- merge(FuelsFine_data_CrossYear, data_temp_merge_Slope_FuelsFine, all = T)
query <- "Fuel Fine Slope" 
query_message <- paste0("Slope = ", data$MethodData_Slope_pct, ". ", "Earliest date = ", data$SampleEvent_Date, ". ", "Conflicting slopes")
values_data <- data$Slope_Change
values_valid <- "Y"
values_check <- (values_data != values_valid) %>% replace_na(TRUE)

# Identify errors
errors_FuelsFine_CrossYear_Slope <- qaqc(data, query, query_message, values_check)

# Consolidate duplicate species errors into one row
errors_FuelsFine_CrossYear_Slope <- errors_FuelsFine_CrossYear_Slope %>%
  separate(Error, sep = ". Conflicting slopes = Y", into = c("Error")) %>% 
  separate(Error, sep = "date = ", into = c("Test", "Date"), remove = F) %>% 
  arrange(Macroplot_Name, MethodData_Transect, Date) %>% 
  group_by(SavedQuery, AdminUnit_Name, SampleEvent_TreatmentUnit, Macroplot_Name, MethodData_Transect) %>% 
  summarize(
    Error = paste(Error, collapse = "; "),
    Fixed = "",
    Explanation = "",
    Queryers = "")
```

### Fuel Azimuth

```{r}
# Set parameters 
data <- merge(FuelsFine_data_CrossYear, data_temp_merge_Azimuth, all = T) %>% 
  filter(AzimuthDiff >= max_Azimuth)
query <- "Fuel Fine Azimuth" 
query_message <- paste0("Azimuth = ", data$MethodData_Azimuth_deg, ". ", "Earliest date = ", data$SampleEvent_Date, ". ", "Conflicting azimuths")
values_data <- data$Azimuth_Change
values_valid <- "Y"
values_check <- (values_data != values_valid) %>% replace_na(TRUE)

# Identify errors
errors_FuelsFine_CrossYear_Azimuth <- qaqc(data, query, query_message, values_check)

# Consolidate duplicate species errors into one row
errors_FuelsFine_CrossYear_Azimuth <- errors_FuelsFine_CrossYear_Azimuth %>%
  separate(Error, sep = ". Conflicting azimuths = Y", into = c("Error")) %>% 
  separate(Error, sep = "date = ", into = c("Test", "Date"), remove = F) %>% 
  arrange(Macroplot_Name, MethodData_Transect, Date) %>% 
  group_by(SavedQuery, AdminUnit_Name, SampleEvent_TreatmentUnit, Macroplot_Name, MethodData_Transect) %>% 
  summarize(
    Error = paste(Error, collapse = "; "),
    Fixed = "",
    Explanation = "",
    Queryers = "")
```

### Fuel Constant

## ALL FUEL ERRORS

```{r}
errors_Fuels_CrossYear <- rbind(errors_Fuels1000_CrossYear_Slope, errors_FuelsFine_CrossYear_Slope, errors_FuelsFine_CrossYear_Azimuth) %>% 
  arrange(Macroplot_Name, MethodData_Transect)

remove(errors_Fuels1000_CrossYear_Slope, errors_FuelsFine_CrossYear_Slope, errors_FuelsFine_CrossYear_Azimuth)
```

```{r}
# Formatting

# Add blank rows between each tag number
errors_Fuels_CrossYear_blanks <- errors_Fuels_CrossYear[1, ]
for (i in 2:nrow(errors_Fuels_CrossYear)) {
  if (errors_Fuels_CrossYear[i, "Macroplot_Name"] != errors_Fuels_CrossYear[i - 1, "Macroplot_Name"]) {
    errors_Fuels_CrossYear_blanks <- rbind(errors_Fuels_CrossYear_blanks, errors_blank, errors_Fuels_CrossYear[i, ])
  } else {
    errors_Fuels_CrossYear_blanks <- rbind(errors_Fuels_CrossYear_blanks, errors_Fuels_CrossYear[i, ])
  }
}

# Add conditional formating to ouput
errors_Fuels_CrossYear_blanks <- condformat(errors_Fuels_CrossYear_blanks[1:(nrow(errors_Fuels_CrossYear_blanks)), 1:ncol(errors_Fuels_CrossYear)]) %>%
  rule_fill_discrete(columns = 1:ncol(errors_Fuels_CrossYear),
                     expression = SavedQuery != "",
                     colours = c("TRUE" = "#C6E0B4"),
                     na.value = "#FFFFFF")
```

```{r}
# Save as CSV or XLSX 
#path_errors

#write_xlsx(errors_Fuels_CrossYear, paste0(path_errors, "errors_Fuels_CrossYear.xlsx"))
# Formatted
condformat2excel(errors_Fuels_CrossYear_blanks, paste0(path_errors, "errors_CrossYear_Fuels_formatted.xlsx"), sheet_name = path_errors_name, overwrite_wb = TRUE)
```

# PROTOCOL - TREES

This code conducts quality control checks on tree data within the "Trees - Individuals (metric)" data set.

It checks for illogical changes over time in: CBH, DBH, Height, Species, and Status

## Adjust Function

```{r qaqc function, include=FALSE}

# Edit blank data frame for preferred error log template.
errors_blank <- data.frame("SavedQuery" = "", 
                           "AdminUnit_Name" = "", 
                           "SampleEvent_TreatmentUnit" = "", 
                           "Macroplot_Name" = "", 
                           "MethodData_TagNo" = "", 
                           "Error" = "", 
                           "Fixed" = "", 
                           "Explanation" = "", 
                           "Queryers" = "")

# Edit error group. Duplicate errors will be grouped by these columns.
errors_group <- c("SavedQuery", "AdminUnit_Name", "Macroplot_Name", "MethodData_TagNo", "Error")
```

### Trees DBH

#### DBH Live Decrease

[Problem:]{.underline} Live trees have DBH which decreases over time.

[Procedure:]{.underline}

-   Filter for Status = L. Filter to exclude a certain threshold where the difference in DBH is not a concern. Remaining entries should include all DBHs that are smaller than the maximum DBH.

-   We are concerned with live trees which decrease in DBH while they are still alive. Ensure that each sample event date is *earlier* than the date with the largest recorded DBH (**MaxDBHDate**).

```{r}
# Set parameters 
data <- merge(Trees_data_CrossYear, data_temp_merge_DBH, all = T) %>% 
  filter(MethodData_Status == "L", !is.na(MethodData_DBH_cm),
         # set threshold of concern
         MaxDBHDiff >= max_DBH)
query <- "Trees DBH" 
query_message <- paste0("Status = ", data$MethodData_Status, ". ", "DBH decreases over time. ", "Max DBH = ", data$MaxDBH, " on date")
values_data <- data$MaxDBHDate
values_valid <- data$SampleEvent_Date
values_check <- values_data >= values_valid

# Identify errors
errors_Trees_CrossYear_DBH_Live <- qaqc(data, query, query_message, values_check)
```

#### DBH Dead Increase

[Problem:]{.underline} Dead trees have DBH which increases over time.

[Procedure:]{.underline}

-   Filter for Status = D. Filter to exclude a certain threshold where the difference in DBH is not a concern. Remaining entries should include all DBHs that are larger than the minimum DBH.

-   We are concerned with dead trees which increase DBH post-death. Ensure that each sample event date is *earlier* than the date with the smallest recorded DBH (**MinDBHDate**).

```{r}
# Set parameters 
data <- merge(Trees_data_CrossYear, data_temp_merge_DBH, all = T) %>% 
  filter(Status == "D", !is.na(DBH),
         # set threshold of concern
         MinDBHDiff >= max_DBH)
query <- "Trees DBH" 
query_message <- paste0("Status = ", data$Status, ". ", "DBH increases over time. ", "Min DBH = ", data$MinDBH, " on date")
values_data <- data$MinDBHDate
values_valid <- data$Date
values_check <- values_data >= values_valid

# Identify errors
errors_Trees_CrossYear_DBH_Dead <- qaqc(data, query, query_message, values_check)
```

### Trees Height

#### Height Live Decrease

[Problem:]{.underline} Live trees have Height which decreases over time.

[Procedure:]{.underline}

-   Filter for Status = L. Filter to exclude a certain threshold where the difference in Height is not a concern. Remaining entries should include all Heights that are shorter than the maximum Height.

-   We are concerned with live trees which decrease in Height over time. Ensure that each sample event date is *earlier* than the date with the tallest recorded Height (**MaxHeightDate**).

```{r}
# Set parameters 
data <- merge(Trees_data_CrossYear, data_temp_merge_Height, all = T) %>% 
  filter(Status == "L", !is.na(Ht),
         # set threshold of concern
         MaxHeightDiff >= max_Ht)
query <- "Trees Height" 
query_message <- paste0("Status = ", data$Status, ". ", "Height decreases over time. ", "Max Height = ", data$MaxHeight, " on date")
values_data <- data$MaxHeightDate
values_valid <- data$Date
values_check <- values_data >= values_valid

# Identify errors
errors_Trees_CrossYear_Height_Live <- qaqc(data, query, query_message, values_check)
```

#### Height Dead Increase

[Problem:]{.underline} Dead trees have Height which increases over time.

[Procedure:]{.underline}

-   Filter for Status = D. Filter to exclude a certain threshold where the difference in Height is not a concern. Remaining entries should include all Heights that are taller than the minimum Height.

-   We are concerned with dead trees which increase in Height over time. Ensure that each sample event date is *earlier* than the date with the shortest recorded Height (**MinHeightDate**).

```{r}
# Set parameters 
data <- merge(Trees_data_CrossYear, data_temp_merge_Height, all = T) %>% 
  filter(Status == "D", !is.na(Ht),
         # set threshold of concern
         MinHeightDiff >= max_Ht)
query <- "Trees Height" 
query_message <- paste0("Status = ", data$Status, ". ", "Height increases over time. ", "Min Height = ", data$MinHeight, " on date")
values_data <- data$MinHeightDate
values_valid <- data$Date
values_check <- values_data >= values_valid

# Identify errors
errors_Trees_CrossYear_Height_Dead <- qaqc(data, query, query_message, values_check)
```

### Trees Species

#### Species Change

[Problem:]{.underline} Trees change species over time.

[Procedure:]{.underline}

-   Isolate rows which have more than 1 entry for Species.Symbol for each individual tree, and the earliest date when each species was recorded.

```{r}
# Set parameters 
data <- merge(Trees_data_CrossYear, data_temp_merge_Species, all = T)
query <- "Trees Species" 
query_message <- paste0("Species = ", data$Species.Symbol, ". ", "Earliest date = ", data$Date, ". ", "Species change")
values_data <- data$Species_Change
values_valid <- "Y"
values_check <- (values_data != values_valid) %>%  replace_na(TRUE)

# Identify errors
errors_Trees_CrossYear_Species_1 <- qaqc(data, query, query_message, values_check)

# Consolidate duplicate species errors into one row
errors_Trees_CrossYear_Species <- errors_Trees_CrossYear_Species_1 %>% 
  separate(Error, sep = ". Species change = Y", into = c("Error")) %>% 
  separate(Error, sep = "date = ", into = c("Test", "Date"), remove = F) %>% 
  arrange(MacroPlot.Name, TagNo, Date) %>% 
  group_by(SavedQuery, MacroPlot.Name, TagNo) %>% 
  summarize(
    Error = paste(Error, collapse = "; "),
    Fixed = "",
    Explanation = "",
    Queryers = "")
```

### Trees Status

#### Status Dead to Live

[Problem:]{.underline} Trees change status from D to L over time.

[Procedure:]{.underline}

-   Filter for Status = L. Check that the sample event date is not later than the death date.

```{r}
# Set parameters 
data <- merge(Trees_data_CrossYear, data_temp_merge_Status, all = T) %>% 
  filter(Status == "L")
query <- "Trees Status" 
query_message <- paste0("Status = ", data$Status, ". ", "Death date")
values_data <- data$MinDeadDate
values_valid <- data$Date
values_check <- (values_data >= values_valid) %>%  replace_na(TRUE)

# Identify errors
errors_Trees_CrossYear_Status <- qaqc(data, query, query_message, values_check)
```

## ALL TREE ERRORS

```{r}
errors_Trees_CrossYear <- rbind(errors_Trees_CrossYear_DBH_Live, errors_Trees_CrossYear_DBH_Dead, errors_Trees_CrossYear_Height_Live, errors_Trees_CrossYear_Height_Dead, errors_Trees_CrossYear_Species, errors_Trees_CrossYear_Status) %>% 
  arrange(Macroplot_Name, TagNo, desc(SavedQuery))

remove(errors_Trees_CrossYear_DBH_Live, errors_Trees_CrossYear_DBH_Dead, errors_Trees_CrossYear_Height_Live, errors_Trees_CrossYear_Height_Dead, errors_Trees_CrossYear_Species, errors_Trees_CrossYear_Species_1, errors_Trees_CrossYear_Status)
```

```{r}
# Formatting

# Add blank rows between each tag number
errors_Trees_CrossYear_blanks <- errors_Trees_CrossYear[1, ]
for (i in 2:nrow(errors_Trees_CrossYear)) {
  if (errors_Trees_CrossYear[i, "TagNo"] != errors_Trees_CrossYear[i - 1, "TagNo"]) {
    errors_Trees_CrossYear_blanks <- rbind(errors_Trees_CrossYear_blanks, errors_blank_trees, errors_Trees_CrossYear[i, ])
  } else {
    errors_Trees_CrossYear_blanks <- rbind(errors_Trees_CrossYear_blanks, errors_Trees_CrossYear[i, ])
  }
}

# Add conditional formating to ouput
errors_Trees_CrossYear_blanks <- condformat(errors_Trees_CrossYear_blanks[1:(nrow(errors_Trees_CrossYear_blanks)), 1:7]) %>%
  rule_fill_discrete(columns = 1:7,
                     expression = SavedQuery != "",
                     colours = c("TRUE" = "#C6E0B4"),
                     na.value = "#FFFFFF")
```

```{r}
# Save as CSV or XLSX 
path_errors

#write_xlsx(errors_Trees_CrossYear, paste0(path_errors, "errors_CrossYear.xlsx"))
# Formatted
condformat2excel(errors_Trees_CrossYear_blanks, paste0(path_errors, "errors_CrossYear_Trees_formatted.xlsx"), sheet_name = path_errors_name, overwrite_wb = TRUE)
```
