---
title: Complete CSVs
author: Alexandra Lalor
output:
  html_document:
    theme: readable
    highlight: null
    code_download: true
  word_document:
  pdf_document:
---

# Purpose

This code is intended to quality check all FFI CSV exports for missing data. Missing data is especially difficult to catch because it relies on information on how much data there is "supposed to be" vs how much data actually was exported. There is added complexity because certain protocols may not contain data for valid reasons (e.g. no trees, no coarse woody debris, no seedlings, no shrubs, etc...). Each error should be carefully checked and considered as a potential major error. Sample events with errors are [entirely absent]{.underline} from FFI CSV exports. Follow the guide below to determine what action is needed.

-   [Procedure:]{.underline}

    -   Code will check that data exists for every protocol which was visited/included in the sample event.
        -   Group by Macroplot_Name and SampleEvent_Date. Calculate number of data points per plot. Check that data_points \> 0
    -   **No data (valid):**
        -   Certain protocols may not contain data for valid reasons (e.g. no trees, no coarse woody debris, no seedlings, no shrubs, etc...). [Make sure this is noted in the comment field of the protocol header in FFI]{.underline}.

        -   Protocols may have been inadvertently added to the sample event with no intention to collect data on that protocol. [Make sure to delete protocol from the sample event in FFI.]{.underline}
    -   **No data (invalid):**
        -   If data should exist but doesn't, data may not have been entered into FFI yet. [Make sure to enter missing data into FFI.]{.underline}

        -   Data may have been added into a non-standard protocol (e.g. "Density - Quadrats" instead of "Density - Quadrats (metric)". [Make sure to transfer data into the correct protocol.]{.underline}

        -   There may be an issue exporting the data out of FFI. [Make sure to troubleshoot data exports, and contact FFI developers if the issue cannot be resolved.]{.underline}

This code uses the Macroplot Report and Sample Event Report from FFI as the reference file for how much data there is "supposed to be". These reports have been combined into a clean "Metadata Report", using the Clean+Merge.Rmd script.

-   MetadataReport.csv

These protocols are included in the code and have been cleaned using the Clean+Merge.Rmd script.

-   Cover - Points (metric)

-   Cover - Species Composition (metric)

-   Density - Belts (metric)

-   Density - Quadrats (metric)

-   Post Burn Severity (metric)

-   Surface Fuels - 1000Hr

-   Surface Fuels - Duff_Litter

-   Surface Fuels - Fine

-   Trees - Individuals (metric)

**If you are using a protocol that is not listed above, you will need to add code to check this data. See the below table for protocols used by your program.**

## Before Starting {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r install packages, include=FALSE}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
## Load Packages

# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
library(readr)
# here() helps locate file paths
library(here)
# janitor has functions to find duplicates
library(janitor)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr and LaTeX is used to create output files from R Markdown
library(knitr)
#library(LaTeX)
```

### Create Function {.hidden}

```{r qaqc function, include=FALSE}
## Source Code
#Pull in source code that creates QAQC functions and builds an empty error table.
source(paste0(here(), "/scripts/2_QAQC/qaqc_function.R"))

###################################################################################

# Edit blank data frame for preferred error log template.
errors_blank <- data.frame("SavedQuery" = "", 
                           "AdminUnit_Name" = "", 
                           "Macroplot_Type" = "", 
                           "Macroplot_Name" = "", 
                           "SampleEvent_Date" = as.Date(NA), 
                           "Error" = "", 
                           "Fixed" = "", 
                           "Explanation" = "", 
                           "Queryers" = "")

# Edit error group. Duplicate errors will be grouped by these columns.
errors_group <- c("SavedQuery", "AdminUnit_Name", "Macroplot_Type", "Macroplot_Name", "SampleEvent_Date", "Error")
```

### Target Park {.hidden}

```{r target values, include=FALSE}
# designate target park(s)
# write 4-letter code of your park (e.g. "SHEN")
# parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
target_park <- "ANTI"
```

### Adjust File Paths {.hidden}

```{r file paths, include=FALSE}
# adjust file paths
#path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_data <- paste0(path_main, "Exports_Clean/FFI/")
path_errors <- paste0(path_main, "QAQC/", target_park, "/")
path_errors_name <- paste0(target_park, " CSV Errors")
```

### Load Data {.hidden}

```{r load data, include=FALSE}
# load data
MetadataReport_all <- read.csv(paste0(path_data, "all_metadata.csv"))

Fuels1000_all <- read.csv(paste0(path_data, "english_surface_fuels_thousand_hr.csv"))
FuelsDuffLitt_all <- read.csv(paste0(path_data, "english_surface_fuels_duff_litter.csv"))
FuelsFine_all <- read.csv(paste0(path_data, "english_surface_fuels_fine.csv"))
PostBurn_all <- read.csv(paste0(path_data, "metric_post_burn_severity.csv"))
Trees_all <- read.csv(paste0(path_data, "metric_trees_individuals.csv"))
Seedlings_all <- read.csv(paste0(path_data, "metric_density_quadrats.csv"))
Shrubs_all <- read.csv(paste0(path_data, "metric_density_belts.csv"))
HerbsSpComp_all <- read.csv(paste0(path_data, "metric_cover_species_composition.csv"))
HerbsPoints_all <- read.csv(paste0(path_data, "metric_cover_points.csv"))
```

### Filter Data

```{r filter data, include=FALSE}
# Clean up data frame
df_names <- c("MetadataReport_all", "Fuels1000_all", "FuelsDuffLitt_all", "FuelsFine_all",  "PostBurn_all", "Trees_all", "Seedlings_all", "Shrubs_all", "HerbsSpComp_all", "HerbsPoints_all")

for (name in df_names) {
  # load data
  current_df <- get(name)
  
  # filter data for target park
  filtered_df <- current_df %>% 
    filter(
      AdminUnit_Name == target_park
      )
  
  # rename and save
  new_name <- sub("_all$", "_data", name)
  assign(new_name, filtered_df)
}
```

# SUMMARY

```{r}
kable(
  MetadataReport_all %>% 
  group_by(SampleEvent_Protocols) %>% 
  dplyr::summarize("Usage" = n(),
                   "Parks" = paste(na.omit(unique(AdminUnit_Name)), collapse = ", "))
)
```

# PROTOCOLS {.hidden}

## Cover

### cover_frequency

```{r}

```

### cover_line_intercept

```{r}

```

### cover_points

Forest

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Cover - Points", SampleEvent_Protocols),
         Macroplot_Type %in% c("Forest")) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- HerbsPoints_data %>%
  filter(MethodData_Order == 1) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date, MethodData_Transect) %>% 
  dplyr::summarise("data_points" = n())

data_temp_transects <- as.data.frame(1:2)
colnames(data_temp_transects) <- "MethodData_Transect"
data_temp1 <- merge(data_temp1, data_temp_transects) %>% 
  dplyr::rename("MethodData_Transect" = !!names(.)[5]) %>% 
  arrange(Macroplot_Name, SampleEvent_Date, MethodData_Transect)

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name", "SampleEvent_Date", "MethodData_Transect"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2, data_temp_transects)

# Set parameters 
data <- merge(HerbsPoints_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name", "SampleEvent_Date", "MethodData_Transect"), all = T)
query <- "Cvr Pts" 
query_message <- paste0("Transect = ", data$MethodData_Transect, ". Total Points") 
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_HerbsPoints_Forest <- qaqc(data, query, query_message, values_check)
```

Grassland & Shrubland

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Cover - Points", SampleEvent_Protocols),
         Macroplot_Type %in% c("Grassland", "Shrubland")) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- HerbsPoints_data %>%
  filter(MethodData_Order == 1) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date, MethodData_Transect) %>% 
  dplyr::summarise("data_points" = n())

data_temp_transects <- as.data.frame(1)
colnames(data_temp_transects) <- "MethodData_Transect"
data_temp1 <- merge(data_temp1, data_temp_transects) %>% 
  dplyr::rename("MethodData_Transect" = !!names(.)[5]) %>% 
  arrange(Macroplot_Name, SampleEvent_Date, MethodData_Transect)

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name", "SampleEvent_Date", "MethodData_Transect"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2, data_temp_transects)

# Set parameters 
data <- merge(HerbsPoints_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name", "SampleEvent_Date", "MethodData_Transect"), all = T)
query <- "Cvr Pts" 
query_message <- paste0("Transect = ", data$MethodData_Transect, ". Total Points") 
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_HerbsPoints_Grassland <- qaqc(data, query, query_message, values_check)
```

#### combine errors

```{r}
# Combine
errors_HerbsPoints <- unique(rbind(errors_HerbsPoints_Forest, errors_HerbsPoints_Grassland))

remove(errors_HerbsPoints_Forest, errors_HerbsPoints_Grassland)

if(nrow(errors_HerbsPoints) > 1) {
  errors_HerbsPoints <- errors_HerbsPoints %>%
    filter(Error != "No Error")
} else {
  errors_HerbsPoints <- errors_HerbsPoints}
```

### cover_species_composition

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Cover - Species Composition", SampleEvent_Protocols)) %>% 
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- HerbsSpComp_data %>% 
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)


# Set parameters 
data <- merge(HerbsSpComp_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Cvr SpComp" 
query_message <- paste0("If applicable, write 'no species found' in comments field in FFI. Species")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_HerbsSpComp <- qaqc(data, query, query_message, values_check)
```

## Density

### density_belts (shrubs)

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Density - Belts", SampleEvent_Protocols)) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- Shrubs_data %>% 
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(Shrubs_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Dens Belts" 
query_message <- paste0("If applicable, write 'no shrubs found' in comments field in FFI. Shrubs")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_Shrubs <- qaqc(data, query, query_message, values_check)
```

### density_quadrats (seedlings)

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Density - Quadrats", SampleEvent_Protocols)) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- Seedlings_data %>% 
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)


# Set parameters 
data <- merge(Seedlings_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Dens Quad" 
query_message <- paste0("If applicable, write 'no seedlings found' in comments field in FFI. Seedlings")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_Seedlings <- qaqc(data, query, query_message, values_check)
```

## Surface Fuels

### surface_fuels_alaska_duff_litter

```{r}

```

### surface_fuels_duff_litter

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Surface Fuels", SampleEvent_Protocols)) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- FuelsDuffLitt_data %>%
  filter(!is.na(MethodData_LittDep_in)) %>%
  filter(!is.na(MethodData_DuffDep_in)) %>% 
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(FuelsDuffLitt_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Fuel DL" 
query_message <- paste0("Complete Sample Locations")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_FuelsDuffLitt <- qaqc(data, query, query_message, values_check)
```

### surface_fuels_fine

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Surface Fuels", SampleEvent_Protocols)) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- FuelsFine_data %>% 
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(FuelsFine_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Fuel Fine"
query_message <- paste0("Complete Transects")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_FuelsFine <- qaqc(data, query, query_message, values_check)
```

### surface_fuels_piles

```{r}

```

### surface_fuels_thousand_hr

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Surface Fuels", SampleEvent_Protocols)) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- Fuels1000_data %>% 
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(Fuels1000_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Fuel 1000" 
query_message <- paste0("If applicable, write 'no CWD found' in comments field in FFI. CWD")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_Fuels1000 <- qaqc(data, query, query_message, values_check)
```

## Trees

### trees_individuals

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Trees - Individuals", SampleEvent_Protocols)) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- Trees_data %>% 
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(Trees_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = T)
query <- "Trees" 
query_message <- paste0("If applicable, write 'no trees found' in comments field in FFI. Trees")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_Trees <- qaqc(data, query, query_message, values_check)
```

### trees_saplings

```{r}

```

### trees_seedlings

```{r}

```

## Post Burn

### post_burn_severity

```{r}
# Filter NA values. Add number of data points and store in new column
data_temp1 <- MetadataReport_data %>%
  filter(grepl("Post Burn Severity", SampleEvent_Protocols)) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarize()

data_temp2 <- PostBurn_data %>% 
  filter(!is.na(MethodData_Veg)) %>%
  filter(!is.na(MethodData_Sub)) %>%
  group_by(AdminUnit_Name, Macroplot_Type, Macroplot_Name, SampleEvent_Date) %>% 
  dplyr::summarise("data_points" = n())

data_temp <- merge(data_temp1, data_temp2, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = TRUE)
data_temp$data_points[is.na(data_temp$data_points)] <- 0
remove(data_temp1, data_temp2)

# Set parameters 
data <- merge(PostBurn_data, data_temp, by = c("AdminUnit_Name", "Macroplot_Type", "Macroplot_Name","SampleEvent_Date"), all = T)
query <- "PBSev" 
query_message <- paste0("Complete Sample Locations")
values_data <- data$data_points
values_valid <- 0
values_check <- values_data > values_valid

# Identify errors
errors_PostBurn <- qaqc(data, query, query_message, values_check)
```

# ALL ERRORS

```{r}
# Create protocol separators
errors_blank_Fuels1000 <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - FUEL 1000")

errors_blank_FuelsDuffLitt <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - FUEL DUFF LITTER")

errors_blank_FuelsFine <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - FUEL FINE")

errors_blank_PostBurn <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - POST BURN")

errors_blank_Trees <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - TREES")

errors_blank_Seedlings <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - SEEDLINGS")

errors_blank_Shrubs <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - SHRUBS")

errors_blank_HerbsSpComp <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - HERBS SPECIES COMPOSITION")

errors_blank_HerbsPoints <- errors_blank %>%
  mutate(SavedQuery = "PROTOCOL - HERBS POINTS")
```

```{r}
# Save to master error list 
errors_all <- rbind(errors_blank_Fuels1000, errors_blank, errors_Fuels1000, errors_blank, errors_blank_FuelsDuffLitt, errors_blank, errors_FuelsDuffLitt, errors_blank, errors_blank_FuelsFine, errors_blank, errors_FuelsFine, errors_blank, errors_blank_PostBurn, errors_blank, errors_PostBurn, errors_blank, errors_blank_Trees, errors_blank, errors_Trees, errors_blank, errors_blank_Seedlings, errors_blank, errors_Seedlings, errors_blank, errors_blank_Shrubs, errors_blank, errors_Shrubs, errors_blank, errors_blank_HerbsSpComp, errors_blank, errors_HerbsSpComp, errors_blank, errors_blank_HerbsPoints, errors_blank, errors_HerbsPoints)
```

```{r}
# # Create conditional formatting rules
errors_all_cf <- errors_all %>%
  mutate(Color = ifelse(SavedQuery == "", NA, "Color")) %>% 
  mutate(Color = ifelse((grepl("PROTOCOL|REPORT", errors_all$SavedQuery) == TRUE), "Protocol", Color)) %>%
  mutate(Color = ifelse(Color == FALSE, "Standard", Color))

# Add conditional formating to ouput
errors_all <- condformat(errors_all_cf[1:(nrow(errors_all_cf)), 1:ncol(errors_all_cf)]) %>%
  rule_fill_discrete(columns = 1:(ncol(errors_all_cf)-1),
                     expression = (errors_all_cf$Color),
                     colours = c("Color"="#C6E0B4",
                                 "Protocol" = "#969696"),
                     na.value = "#FFFFFF") %>%
  select(!c("Color"))
```

QAQC file saved to:

```{r}
# Save as CSV or XLSX 
path_errors
errors_all <- errors_all %>% 
  mutate(SampleEvent_Date = as.character(SampleEvent_Date))
condformat2excel(errors_all, paste0(path_errors, paste0(target_park, "_errors_complete.xlsx")), sheet_name = path_errors_name, overwrite_wb = TRUE)
```
