---
title: QAQC Species Data
author: NPS Northeast Region Fire Effects Monitoring Program
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 1
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: '3'
---

# PURPOSE

This code is intended to quality check species metadata, including the Local Species Report. This report has been cleaned using the Clean+Merge.Rmd script.

-   SpeciesReport.csv

## Before Starting

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)

# install.packages("tidyverse")
# install.packages("Rtools")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
library(plyr)
library(stringr)
# janitor has functions to find duplicates
library(janitor)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr is used to create output files from R Markdown
library(knitr)
library(here)
```

### Create Function {.hidden}

```{r qaqc function, include=FALSE}
## Source Code
#Pull in source code that creates QAQC functions and builds an empty error table.
source(paste0(here(), "/scripts/2_QAQC/qaqc_function.R"))

###################################################################################

# Edit blank data frame for preferred error log template.
errors_blank <- data.frame("SavedQuery" = "", 
                           "AdminUnit_Name" = "", 
                           "Species_LocalSpeciesSymbol" = "", 
                           "Error" = "", 
                           "Fixed" = "", 
                           "Explanation" = "", 
                           "Queryers" = "")

# Edit error group. Duplicate errors will be grouped by these columns.
errors_group <- c("SavedQuery", "AdminUnit_Name", "Species_LocalSpeciesSymbol", "Error")
```

### Adjust File Paths {.hidden}

```{r file paths, include=FALSE}
# adjust file paths
path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Clean/FFI/")
path_errors <- paste0(here(), "/output/errors/")
path_errors_name <- paste0("Cross Park Species QAQC Errors")
```

### Load Data {.hidden}

```{r load data, include=FALSE}
## Load Data
SpeciesReport_all <- read.csv(paste0(path_data, "all_species_info.csv"))
```

### Filter Data

```{r filter data, include=FALSE}
SpeciesReport <- SpeciesReport_all
```

### Define Codes

```{r}
#Now that we fixed unknowns, we can use these codes
Substrates <- SpeciesReport %>%
  filter(Species_LifeFormNameLocal == "Undefined")
Substrates <- unique(Substrates$Species_LocalSpeciesSymbol)
  
Unknowns_MysteryPlants <- SpeciesReport %>%
  filter(Species_LifeFormNameLocal == "Unknown")
Unknowns_MysteryPlants <- unique(Unknowns_MysteryPlants$Species_LocalSpeciesSymbol)

Unknowns_LifeFormOnly <- SpeciesReport %>%
  filter(!Species_LifeFormNameLocal %in% c("Undefined", "Unknown"),
         is.na(Species_Family) & is.na(Species_Genus))
Unknowns_LifeFormOnly <- unique(Unknowns_LifeFormOnly$Species_LocalSpeciesSymbol)

Unknowns_FamilyOnly <- SpeciesReport %>%
  filter(!Species_LifeFormNameLocal %in% c("Undefined", "Unknown"),
         !is.na(Species_Family) & is.na(Species_Genus) & is.na(Species_ScientificName))
Unknowns_FamilyOnly <- unique(Unknowns_FamilyOnly$Species_LocalSpeciesSymbol)

Unknowns_GenusOnly <- SpeciesReport %>%
  filter(Species_ScientificName == Species_Genus)
Unknowns_GenusOnly <- unique(Unknowns_GenusOnly$Species_LocalSpeciesSymbol)



Unknowns <- c(Unknowns_MysteryPlants, Unknowns_LifeFormOnly, Unknowns_FamilyOnly, Unknowns_GenusOnly)
```

# SPECIES REPORT

## Step 3 - Cross Park Inconsistencies

```{r}
# Set parameters 
data <- SpeciesReport %>%
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% c(Unknowns_MysteryPlants, Unknowns_LifeFormOnly, Unknowns_FamilyOnly)) %>% 
  dplyr::group_by(Species_ScientificName) %>%
  dplyr::mutate(n_families = dplyr::n_distinct(Species_Family)) %>%
  dplyr::mutate(family_change = ifelse(n_families > 1, "Y", "N")) %>% 
  dplyr::ungroup()
query <- "Species Cross Park Family" 
query_message <- paste0(data$Species_ScientificName, "- Family = ", data$Species_Family, ". Family change")
values_data <- data$family_change
values_valid <- "N"
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_CrossPark_Family_1 <- qaqc(data, query, query_message, values_check)
errors_SpeciesReport_CrossPark_Family_1 <- errors_SpeciesReport_CrossPark_Family_1 %>% 
  arrange(errors_SpeciesReport_CrossPark_Family_1$Error)


# Consolidate species errors into one row
errors_SpeciesReport_CrossPark_Family <- errors_SpeciesReport_CrossPark_Family_1 %>% 
  separate(Error, sep = ". Family change = Y", into = c("Error")) %>% 
  separate(Error, sep = "- ", into = c("Species_LocalSpeciesSymbol", "Error"), remove = F) %>% 
  dplyr::group_by(SavedQuery, Species_LocalSpeciesSymbol) %>% 
  dplyr::summarize(
    AdminUnit_Name = paste(AdminUnit_Name, collapse = "; "),
    Error = paste(Error, collapse = "; "),
    Fixed = "",
    Explanation = "",
    Queryers = "") %>% 
  relocate(AdminUnit_Name, .before = Species_LocalSpeciesSymbol)

remove(errors_SpeciesReport_CrossPark_Family_1)
```

```{r}
# Set parameters 
data <- SpeciesReport %>%
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% c(Unknowns_MysteryPlants, Unknowns_LifeFormOnly, Unknowns_FamilyOnly)) %>% 
  dplyr::group_by(Species_ScientificName) %>%
  dplyr::mutate(n_lifeform = dplyr::n_distinct(Species_LifeFormNameLocal)) %>%
  dplyr::mutate(lifeform_change = ifelse(n_lifeform > 1, "Y", "N")) %>% 
  dplyr::ungroup()
query <- "Species Cross Park Lifeform" 
query_message <- paste0(data$Species_ScientificName, "- Lifeform = ", data$Species_LifeFormNameLocal, ". Lifeform change")
values_data <- data$lifeform_change
values_valid <- "N"
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_CrossPark_Lifeform_1 <- qaqc(data, query, query_message, values_check)
errors_SpeciesReport_CrossPark_Lifeform_1 <- errors_SpeciesReport_CrossPark_Lifeform_1 %>% 
  arrange(errors_SpeciesReport_CrossPark_Lifeform_1$Error)

# Consolidate species errors into one row
errors_SpeciesReport_CrossPark_Lifeform <- errors_SpeciesReport_CrossPark_Lifeform_1 %>% 
  separate(Error, sep = ". Lifeform change = Y", into = c("Error")) %>% 
  separate(Error, sep = "- ", into = c("Species_LocalSpeciesSymbol", "Error"), remove = F) %>% 
  dplyr::group_by(SavedQuery, Species_LocalSpeciesSymbol) %>% 
  dplyr::summarize(
    AdminUnit_Name = paste(AdminUnit_Name, collapse = "; "),
    Error = paste(Error, collapse = "; "),
    Fixed = "",
    Explanation = "",
    Queryers = "") %>% 
  relocate(AdminUnit_Name, .before = Species_LocalSpeciesSymbol)

remove(errors_SpeciesReport_CrossPark_Lifeform_1)
```

```{r}
# Set parameters
data <- SpeciesReport %>%
  filter(!Species_LocalSpeciesSymbol %in% Substrates,
         !Species_LocalSpeciesSymbol %in% Unknowns) %>%
  mutate(Nativity = ifelse(Species_NativityLocal == "True", "Native",
                           ifelse(Species_Invasive == "True", "Invasive", 
                                  "Non-Native"))) %>% 
  dplyr::group_by(Species_ScientificName) %>%
  dplyr::mutate(n_nativity = dplyr::n_distinct(Nativity)) %>%
  dplyr::mutate(nativity_change = ifelse(n_nativity> 1, "Y", "N")) %>% 
  dplyr::ungroup()
query <- "Species Cross Park Nativity"
query_message <- paste0(data$Species_ScientificName, "- Status = ", data$Nativity, ". Nativity change")
values_data <- data$nativity_change
values_valid <- "N"
values_check <- values_data == values_valid

# Identify errors
errors_SpeciesReport_CrossPark_Nativity_1 <- qaqc(data, query, query_message, values_check)
errors_SpeciesReport_CrossPark_Nativity_1 <- errors_SpeciesReport_CrossPark_Nativity_1 %>%
  arrange(errors_SpeciesReport_CrossPark_Nativity_1$Error)

# Consolidate species errors into one row
errors_SpeciesReport_CrossPark_Nativity <- errors_SpeciesReport_CrossPark_Nativity_1 %>% 
  separate(Error, sep = ". Nativity change = Y", into = c("Error")) %>% 
  separate(Error, sep = "- ", into = c("Species_LocalSpeciesSymbol", "Error"), remove = F) %>% 
  dplyr::group_by(SavedQuery, Species_LocalSpeciesSymbol) %>% 
  dplyr::summarize(
    AdminUnit_Name = paste(AdminUnit_Name, collapse = "; "),
    Error = paste(Error, collapse = "; "),
    Fixed = "",
    Explanation = "",
    Queryers = "") %>% 
  relocate(AdminUnit_Name, .before = Species_LocalSpeciesSymbol)

remove(errors_SpeciesReport_CrossPark_Nativity_1)
```

# ALL ERRORS

```{r}
errors_SpeciesReport_CrossPark <- rbind(errors_SpeciesReport_CrossPark_Family, errors_blank, errors_SpeciesReport_CrossPark_Lifeform, errors_blank, errors_SpeciesReport_CrossPark_Nativity)
```

```{r}
# Formatting

# Add conditional formating to ouput
errors_all <- condformat(errors_SpeciesReport_CrossPark[1:(nrow(errors_SpeciesReport_CrossPark)), 1:ncol(errors_SpeciesReport_CrossPark)]) %>%
  rule_fill_discrete(columns = 1:(ncol(errors_SpeciesReport_CrossPark)),
                     expression = SavedQuery != "",
                     colours = c("TRUE" = "#C6E0B4"),
                     na.value = "#FFFFFF")
```

```{r}
path_errors

# Save as CSV or XLSX
condformat2excel(errors_all, paste0(path_errors, "ALL_Errors_SpeciesManagement_CrossPark.xlsx"), sheet_name = path_errors_name, overwrite_wb = TRUE)
```
