---
title: QAQC Species Data
author: NPS Northeast Region Fire Effects Monitoring Program
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 1
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: '3'
---

# PURPOSE

This code is intended to quality check species metadata, including the Local Species Report. This report has been cleaned using the Clean+Merge.Rmd script.

-   SpeciesReport.csv

## Before Starting

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)

# install.packages("tidyverse")
# install.packages("Rtools")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
library(plyr)
# janitor has functions to find duplicates
library(janitor)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr is used to create output files from R Markdown
library(knitr)
library(here)
```

### Create Function {.hidden}

```{r qaqc function, include=FALSE}
## Source Code
#Pull in source code that creates QAQC functions and builds an empty error table.
source(paste0(here(), "/scripts/2_QAQC/qaqc_function.R"))

###################################################################################

# Edit blank data frame for preferred error log template.
errors_blank <- data.frame("SavedQuery" = "", 
                           "AdminUnit_Name" = "", 
                           "Species_LocalSpeciesSymbol" = "", 
                           "Error" = "", 
                           "Fixed" = "", 
                           "Explanation" = "", 
                           "Queryers" = "")

# Edit error group. Duplicate errors will be grouped by these columns.
errors_group <- c("SavedQuery", "AdminUnit_Name", "Species_LocalSpeciesSymbol", "Error")
```

### Target Park {.hidden}

```{r target values, include=FALSE}
# designate target park(s)
# parks <- c("ANTI", "APCO", "CATO", "CUVA", "DEWA", "FRSP", "GATE", "GETT", "MONO", "NERI", "PRWI", "RICH", "SARA", "SHEN", "VAFO")
target_park <- "NERI"
```

### Adjust File Paths {.hidden}

```{r file paths, include=FALSE}
# adjust file paths
path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Clean/FFI/")
path_errors <- paste0(here(), "/output/errors/")
path_errors_name <- paste0(target_park, " Species QAQC Errors")
```

### Load Data {.hidden}

```{r load data, include=FALSE}
## Load Data
SpeciesReport_all <- read.csv(paste0(path_data, "all_species_info.csv"))
```

### Filter Data

```{r filter data, include=FALSE}
SpeciesReport <- SpeciesReport_all %>% 
  filter(AdminUnit_Name %in% target_park)
```

### Define Codes {.hidden}

```{r define codes, include=FALSE}
unknowns_genus <- c("ACALY","ACALYP","ACASPP","ACER","ACHILLEA","AGESPP","AGROS","AGRSPP","ALLIUM","ALLSPP","AMELA","AMESPP","ANDRO","ANDROP","ANDSPP","ANEMO","ANESPP","ANTEN","ANTENN","ANTSPP","APOCY","APOCYNUM","APOSPP", "ARABIS","ARALI","ARISPP","ARIST","ASCLE","ASCLEPIAS","ASCSPP","ASPSPP","ASTER","ASTERACEAE","ASTEspp","BETULA","BIDENS","BOTRY","BOTRYCH","BOTSPP","BRASSICACE","BRASPP","BRASS2","BROMU","bromus","BROMUS","BROSPP","CALAM","CALYSTEGIA","CARDA","CAREX","CAREX2","CARSPP","CARSP1","CARSPP2","CARSP2","CARSP3","CARYA","CASSPP","CENTAUREA","CHIMA","CIRCAE","CIRSI","CIRSPP","CLISPP","CONVO","CONVOL","CONVOLVULU","CONVULVULA","CORNspp","CORSPP","CORNU","CORNUS","CRASPP","CRATA","CRATAEGUS","CUSCU","CUSCUTA","CUSSPP","CYPER","CYPSPP","DANSPP","DATSP","DDTREE","DESMO","DESMODIUM","DESSPP","DICHAN","DICHANTHEL","DICSPP","DICSP1","DICSPP1","DICSP2","DICSPP2","DICSPP3","DICSP5","DIGITA","DIGSPP1","DIGSPP","DIOSC","DIOSPP","ELEOCHARIS","ELESPP","ELYMUS","EPILOBIUM","EPISPP","EPISP1","ERAGR","ERASPP","ERAGROSTIS","ERIGE2","ERIGERON","ERISP","ERISPP","EUPATOR","EUPATORIUM","EUPSPP","EURSPP","EURYB","FABSPP","FABA","FESTUC","FESTUCA","FIMBRI","FRASPP","FRAXINUS","FRAXspp","GALIU","GALIUM","GALSP","GALSPP","GENTI","GEUM","GILLSP", "GLYCERIA","GNASPP","HELIAN","HEPAT","HIERA","HIERAC","HIERACIUM","HIESPP","HOUSTO","HYPER","HYPERICUM","HYPPER","HYPSPP","IMPATIENS","IPOMO","IPOMOE","IPOMOEA","IPOSPP","IRIS","JUNCUS","JUNIspp","JUNSPP","KRIGI","LACSPP","LACTU","LAMSPP","LESPE","LESSPP","LIASPP","LIATR","LINSPP","LINUM","LITHO3","LONIC","LONICE","LONICERA","LONSPP","LOTUS","LYCHN","LYCOPODIUM","LYCOPUS","LYSIM","LYSSSP","MAGNOLIA","MALUS","MEDICAGO","MELILOTUS","MONARDA","MONSPP","MUHLE","MUHLEN","MUHSPP","MYRIO","NABSPP", "OSMOR","OSMSPP","OXALI","OXALIS","OXASPP","PACKER","PACKERA","PACSPP","PANIC","PANICUM","PANSPP","PASPAL","PASSPP","PASSP1","PENSSP","PERSPP","PHLEU","PHYSPP","PINSPP","PINUS","POA","POACEAE","POLYG2","POLYG4","POLYGO","POLYGONUM","POPSPP","POPULUS","POTENT","POTENTILLA","PRESPP","PRUNE","PRUNU","PRUNUS","PRUSPP","PYCNA","PYCNANTHEM","PYRUS","QUERC","QUERCUS","QUESPP","RANSPP","RANUNCULUS","RHAMNUS","RHEXI","RHODO","RIBES","ROSA","ROSSPP","ROSA5","RUBIACEAE","RUBSPP","RUBUS","RUDBECKIA","RUMEX","RUMSPP","SALIX","SAMBU","SANICULA","SANSPP","SCIRP","SCIRPUS","SCLSPP","SCUSPP","SCUTELLARI","SETARIA","SETSPP","SISSPP","SISYR","SMILAX","SMISPP","SOLID","SOLIDAGO","SOLSPP","SOLSP1","SPIRA","SPIRA2","SPIRAE","SPIRAN","STELL","STELLARIA","STIPA","SYMPHY","Symphy2","SYMPHYOTRI","SYMSPP","SYMSP1","SYMSPP1","TARAX","TARSPP","THALICTRUM","TRIFOL","TRIFOLIUM","TRILL","TRILLIUM","TRISPP","ULMSPP","ULMUS","UVUSP","VACCI","VACCIN","VACCINIUM","VACSPP","VERBA","VERBENA","VERON","VERONICA","VIBURN","VIBURNUM","VICIA","VICSPP","VIOLA","VIOSPP","VIOSPP1","VITIS","VITSPP","YPINE")

unknowns_generic <- c("ASTER","FERN","GRASS","GRSSPP","GRASSSP","GRASSSP1","GRASP1","GRASSP1","GRSSP1","GRSPP1","GRSPP2","2GL","GRASS_LIG","GRASS_THIN","UNKSPP","UNKSNAG","UNK_001","UNK_002","UNKN_98","UNKSP1","UNSKP1","UNKSP2","UNKN_FORB","UNKN_SHRUB","UNKN_WOODY","2AB","2FERN","2FORB","2FORBD","2FORBM","2GRAM","2LICH","2PLANT","2SHRUBD","2TDBD","2TREE","2VINEHERB","2VINEWOOD","NOSP","NODATA")

unknowns <- unique(c(unknowns_genus, unknowns_generic))

substrates <- c("BARE","BOLE","2BOLE", "DUFF","2FF","FUNG","FUNGI","FUNGUS","HAY","LICH","LICHEN","LITT","LITTER","2LTR","MOSS","ROCK","ROOT","SCAT","SOIL","WATER","WOOD","DDTREE")
```

# SPECIES REPORT

[Problem:]{.underline} Species Report is missing information

[Procedure:]{.underline}

-   Check that Species_ScientificName is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates,
         !Species_LocalSpeciesSymbol %in% unknowns)
query <- "Species_ScientificName"
query_message <- paste0("Scientific Name") 
values_data <- data$Species_ScientificName
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_ScientificName <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_Genus is not blank.

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates,
         !Species_LocalSpeciesSymbol %in% unknowns)
query <- "Species_Genus"
query_message <- paste0("Genus") 
values_data <- data$Species_Genus
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_Genus <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_Family is not blank. (Field cannot be edited in FFI)

```{r}
# # Set parameters 
# data <- SpeciesReport %>% 
#   filter(!Species_LocalSpeciesSymbol %in% substrates,
#          !Species_LocalSpeciesSymbol %in% unknowns)
# query <- "Species_Family"
# query_message <- paste0("Family") 
# values_data <- data$Species_Family
# values_valid <- ""
# values_check <- values_data != values_valid
# 
# # Identify errors
# errors_SpeciesReport_Family <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_ITIS_TSN is not blank. (Field cannot be edited in FFI)

```{r}
# # Set parameters 
# data <- SpeciesReport %>% 
#   filter(!Species_LocalSpeciesSymbol %in% substrates,
#          !Species_LocalSpeciesSymbol %in% unknowns)
# query <- "Species_ITIS_TSN"
# query_message <- paste0("TSN") 
# values_data <- data$Species_ITISTaxonomicSerialNumber
# values_valid <- ""
# values_check <- values_data != values_valid
# 
# # Identify errors
# errors_SpeciesReport_TSN <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_NotBiological = False. (Field cannot be edited in FFI).

```{r}
# # Set parameters 
# data <- SpeciesReport %>% 
#   filter(!Species_LocalSpeciesSymbol %in% substrates)
# query <- "Species_NotBiological"
# query_message <- paste0("Not Biological") 
# values_data <- data$Species_NotBiological
# values_valid <- "False"
# values_check <- values_data == values_valid
# 
# # Identify errors
# errors_SpeciesReport_NotBiological_F <- qaqc(data, query, query_message, values_check)
```

```{r}
# # Set parameters 
# data <- SpeciesReport %>% 
#   filter(Species_LocalSpeciesSymbol %in% substrates)
# query <- "Species_NotBiological"
# query_message <- paste0("Substrate. Not Biological") 
# values_data <- data$Species_NotBiological
# values_valid <- "True"
# values_check <- values_data == values_valid
# 
# # Identify errors
# errors_SpeciesReport_NotBiological_T <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_CommonNameLocal is not blank

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates,
         !Species_LocalSpeciesSymbol %in% unknowns)
query <- "Species_CommonNameLocal"
query_message <- paste0("Common Name")
values_data <- data$Species_CommonNameLocal
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_CommonName <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_LifeCycleLocal = Perennial, Biennial, or Annual

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates,
         !Species_LocalSpeciesSymbol %in% unknowns)
query <- "Species_LifeCycleLocal"
query_message <- paste0("Life Cycle")
values_data <- data$Species_LifeCycleLocal
values_valid <- c("Perennial", "Biennial", "Annual")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_LifeCycle <- qaqc(data, query, query_message, values_check)
```

-   Sort by Native = True. Check that Invasive = False

```{r}
# Set parameters
data <- SpeciesReport %>% 
  filter(Species_NativityLocal == "True")
query <- "Species_NativityLocal"
query_message <- paste0("Native = True. Invasive")
values_data <- data$Species_Invasive
values_valid <- c("False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Native <- qaqc(data, query, query_message, values_check)
```

-   Sort by Native = False. Check that Invasive = True (Nonnative & noninvasive species ok, but should be double checked)

```{r}
# # Set parameters
# data <- SpeciesReport %>% 
#   filter(Species_NativityLocal == "False",
#          !Species_LocalSpeciesSymbol %in% substrates,
#          !Species_LocalSpeciesSymbol %in% unknowns)
# query <- "Species_Invasive"
# query_message <- paste0("Native = False. Invasive")
# values_data <- data$Species_Invasive
# values_valid <- c("True")
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_SpeciesReport_NonNative <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_Cultural = True or False

```{r}
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates,
         !Species_LocalSpeciesSymbol %in% unknowns)
query <- "Species_Cultural"
query_message <- paste0("Cultural")
values_data <- data$Species_Cultural
values_valid <- c("True", "False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Cultural <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_Concern = True or False

```{r}
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates,
         !Species_LocalSpeciesSymbol %in% unknowns)
query <- "Species_Concern"
query_message <- paste0("Concern")
values_data <- data$Species_Concern
values_valid <- c("True", "False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Concern <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_Retired = True or False

```{r}
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates,
         !Species_LocalSpeciesSymbol %in% unknowns)
query <- "Species_Retired"
query_message <- paste0("Retired")
values_data <- data$Species_Retired
values_valid <- c("True", "False")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Retired <- qaqc(data, query, query_message, values_check)
```

### Lifeform

-   Check that Species_LifeFormNameLocal = Nonvascular, Lichenous, Graminoid, Grass-like, Fern, Forb/herb, Vine, Shrub, Subshrub, or Tree

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates,
         !Species_LocalSpeciesSymbol %in% unknowns)
query <- "Species_LifeFormNameLocal"
query_message <- paste0("Life Form")
values_data <- data$Species_LifeFormNameLocal
values_valid <- c("Nonvascular", "Lichenous", "Graminoid", "Grass-like", "Fern", "Forb/herb", "Vine", "Shrub", "Subshrub", "Tree")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_LifeForm <- qaqc(data, query, query_message, values_check)
```

-   Check that Species_LifeFormNameLocal = Undefined for [substrates]{.underline}

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(Species_LocalSpeciesSymbol %in% substrates)
query <- "Species_LifeFormNameLocal"
query_message <- paste0("Substrate. Life Form")
values_data <- data$Species_LifeFormNameLocal
values_valid <- c("Undefined")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_LifeForm_Substrate <- qaqc(data, query, query_message, values_check)
```

#### Combine LifeForm Errors {.hidden}

```{r}
# errors_SpeciesReport_LifeForm <- unique(rbind())
# 
# remove()
# 
# if(nrow(errors_SpeciesReport_LifeForm ) > 1) {
#   errors_SpeciesReport_LifeForm  <- errors_SpeciesReport_LifeForm  %>%
#     filter(Error != "No Error")
# } else {
#   errors_SpeciesReport_LifeForm  <- errors_SpeciesReport_LifeForm }
```

### Unknowns

[Problem:]{.underline} Unknown species codes should have unique identifiers that allow them to be searchable.

-   Completely unknowns species (UNKSPP)

-   Plants where the lifeform is known (GRASS)

-   Plants where the genus is known but the species is not (CAREX, CARSPP)

[Procedure:]{.underline}

-   Unknown genus. Filter out substrate codes. Filter for Life Form == Undefined. Check that Genus == Scientific Name. If this is true, Life Form should be known (not "Undefined).

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates)
query <- "Species Unknowns"
query_message <- paste0("Life form")
values_data <- data$Species_LifeFormNameLocal
values_valid <- "Undefined"
values_check <- values_data != values_valid

# Identify errors
errors_SpeciesReport_Unknown_Genus <- qaqc(data, query, query_message, values_check)
```

-   If this is false...

```{r}
# Set parameters 
data <- SpeciesReport %>% 
  filter(!Species_LocalSpeciesSymbol %in% substrates,
         Species_LifeFormNameLocal == "Undefined") %>%
  mutate(UnkGenus = ifelse(Species_ScientificName == Species_Genus, "Y", "N"))
query <- "Species Unknowns"
query_message <- paste0("Life form = ", data$Species_LifeFormNameLocal, ". Unknown Genus")
values_data <- data$UnkGenus
values_valid <- c("Y", "N")
values_check <- values_data %in% values_valid

# Identify errors
errors_SpeciesReport_Unknown_Genus <- qaqc(data, query, query_message, values_check)
```

# ALL ERRORS

```{r}
errors_SpeciesReport <- rbind(errors_SpeciesReport_ScientificName, errors_SpeciesReport_Genus, errors_SpeciesReport_CommonName, errors_SpeciesReport_LifeForm, errors_SpeciesReport_LifeCycle, errors_SpeciesReport_Native, errors_SpeciesReport_Cultural, errors_SpeciesReport_Concern, errors_SpeciesReport_Retired) %>% 
  arrange(Species_LocalSpeciesSymbol)

remove(errors_SpeciesReport_ScientificName, errors_SpeciesReport_Genus, errors_SpeciesReport_CommonName, errors_SpeciesReport_LifeForm, errors_SpeciesReport_LifeCycle, errors_SpeciesReport_Native, errors_SpeciesReport_Cultural, errors_SpeciesReport_Concern, errors_SpeciesReport_Retired)

if(nrow(errors_SpeciesReport) > 1) {
  errors_SpeciesReport <- errors_SpeciesReport %>%
    filter(Error != "No Error")
} else {
  errors_SpeciesReport <- errors_SpeciesReport}
```

```{r}
# Formatting

# Add blank rows between each tag number
errors_SpeciesReport_blanks <- errors_SpeciesReport[1, ]
for (i in 2:nrow(errors_SpeciesReport)) {
  if (errors_SpeciesReport[i, "Species_LocalSpeciesSymbol"] != errors_SpeciesReport[i - 1, "Species_LocalSpeciesSymbol"]) {
    errors_SpeciesReport_blanks <- rbind(errors_SpeciesReport_blanks, errors_blank, errors_SpeciesReport[i, ])
  } else {
    errors_SpeciesReport_blanks <- rbind(errors_SpeciesReport_blanks, errors_SpeciesReport[i, ])
  }
}

# Add conditional formating to ouput
errors_all <- condformat(errors_SpeciesReport_blanks[1:(nrow(errors_SpeciesReport_blanks)), 1:ncol(errors_SpeciesReport_blanks)]) %>%
  rule_fill_discrete(columns = 1:(ncol(errors_SpeciesReport_blanks)),
                     expression = SavedQuery != "",
                     colours = c("TRUE" = "#C6E0B4"),
                     na.value = "#FFFFFF")
```

```{r}
path_errors

# Save as CSV or XLSX
condformat2excel(errors_all, paste0(path_errors, target_park, "_Errors_SpeciesManagement.xlsx"), sheet_name = path_errors_name, overwrite_wb = TRUE)
```
