---
title: QAQC MetaData
author: Alexandra Lalor
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 1
    toc_float:
      smooth_scroll: yes
    code_download: true
  pdf_document:
    toc: yes
    toc_depth: '3'
---

# Purpose

This code is intended to quality check plot metadata, including the Macroplot Report and Sample Event Report, which have been combined into a single flat file using the Clean_1_All.Rmd script.

-   MetadataReport.csv

## Before Starting {.hidden}

### Setup {.hidden}

```{r setup, include=FALSE}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r install packages, include=FALSE}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("Rtools")
# install.packages("janitor")
# install.packages("condformat")
# install.packages("knitr")
# install.packages("here")
```

```{r load packages, include=FALSE}
## Load Packages

# tidyverse and dplyr have lots of useful functions for data cleaning
library(tidyverse)
library(dplyr)
#library(plyr)
# janitor has functions to find duplicates
library(janitor)
# writexl is used to create excel output files
library(writexl)
# condformat is used to format excel output files
library(condformat)
# knitr is used to create output files from R Markdown
library(knitr)
# "here" helps you easily find and reference your working directory
library(here)
```

### Create Function {.hidden}

```{r}
# Create blank data frame as error log template
errors_blank <- data.frame("SavedQuery" = "", "Macroplot_Name" = "", "Error" = "", "Fixed" = "", "Explanation" = "", "Queryers" = "")

# Create error group. Duplicate errors will be grouped by these columns.
errors_group <- c("SavedQuery", "Macroplot_Name", "Error")

############################################################################################
## Source Code
#Pull in source code that creates QAQC functions and builds an empty error table.
#source("C:/Users/allie/OneDrive/Desktop/R Projects/NER/scripts/1_QAQC/qaqc_function.R")


# QAQC function
qaqc <- function(data, query, query_message, values_check) {

  # Check if there is data to QAQC
  if(nrow(data) == 0) {
  # If there is no data, default to "No Error" data frame
  errors <- errors_blank %>%
    mutate("SavedQuery" = query,
           "Error" = "No Error")
  # If there is data, perform error check
} else {

  # Use relevant dataset to look for errors
  errors <- data %>%
    # Add columns relevant to error checking
           # Populate the "SavedQuery" column with the query name
    mutate("SavedQuery" = query,
           # Populate the "Error" column with the query message and relevant data
           "Error" = paste(query_message, "=", values_data),
           # Create a blank "Fixed" column
           "Fixed" = "",
           # Create a blank "Explanation" column
           "Explanation" = "",
           # Create a blank "Queryers" column
           "Queryers" = "") %>%
    # Filter for data which is "false" (data does not match valid conditions)
    # NA values are treated as "false" (missing data is not valid)
    filter(!(values_check %>% replace_na(FALSE))) %>%
    # Select relevant columns to view errors
    select(colnames(errors_blank))

  # Next, check if there are duplicate errors
  errors_temp <- errors %>%
    get_dupes(errors_group)
  # Merge duplicate errors
  errors <- unique(merge(errors, errors_temp, all = T))
  # If duplicate errors exist, add number of duplicates to error message
  errors <- errors %>%
    mutate(Error = ifelse(is.na(dupe_count), Error, paste0("(x", dupe_count, ") ", Error))) %>%
    select(!"dupe_count")
}

  # Check if there are no errors
  if (nrow(errors) == 0) {
    # If there are no errors, default to "No Error" data frame
    errors <- errors_blank %>%
      mutate(SavedQuery = query,
             Error = "No Error")
    # If there are errors, keep error log you just created
  } else {
    errors <- errors
  }
}
```

### Target Park {.hidden}

```{r target values, include=FALSE}
# designate target park(s)
target_park <- "APCO"
```

### Adjust File Paths {.hidden}

```{r import data, include=FALSE}
# adjust file paths
path_main <- "E:/Allie/FireFX_NER/FFI Data Management/"
#path_main <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/"
path_data <- paste0(path_main, "R Outputs/", target_park, "/", target_park, "_")
path_errors <- paste0(path_main, "QAQC/", target_park, "/")
path_errors_name <- paste0(target_park, " Metadata QAQC Errors")
```

### Load Data {.hidden}

```{r load data, include=FALSE}
MetadataReport <- read.csv(paste0(path_data, "MetadataReport.csv"))
```

# Park: [`r target_park`]{style="color:red"}

# Macroplot Report

### Installation

[Problem:]{.underline} Macroplot Report is missing information related to plot installation

[Procedure:]{.underline}

-   Check that Macroplot is not blank and has correct naming convention. Plots should have a 2-digit number associated with it (e.g. Plot 01, Plot 02, Plot 03, etc.)

```{r}
# Set parameters 
data <- MetadataReport %>% 
  extract(Macroplot_Name, regex = "([0-9]+[0-9]+)", into = c("Macroplot_Num"), remove = F)
query <- "Macroplot Report - Installation"
query_message <- "Macroplot naming convention is incorrect. Macroplot Number" 
values_data <- data$Macroplot_Num
values_valid <- is.na(data$Macroplot_Num)
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_MacroplotNum <- qaqc(data, query, query_message, values_check)
```

-   Check that Purpose is not blank and is written correctly ("Fire Monitoring Handbook", "Composite Burn Index", "Rapid Assessment", "Fuels", "Inventory & Monitoring").

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Installation"
query_message <- "Purpose" 
values_data <- data$Macroplot_Purpose
values_valid <- c("Fire Monitoring Handbook", "Composite Burn Index", "Rapid Assessment", "Fuels", "Inventory & Monitoring")
values_check <- values_data %in% values_valid

# Identify errors
errors_MacroplotReport_Purpose <- qaqc(data, query, query_message, values_check)
```

-   Check that Type is one of the available options ("Forest", "Grassland", "Shrubland", "CBI", "Control", "Inventory", "Measured", "Other", "RA")

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Installation"
query_message <- "Type" 
values_data <- data$Macroplot_Type
values_valid <- c("Forest", "Grassland", "Shrubland", "CBI", "Control", "Inventory", "Measured", "Other", "RA")
values_check <- values_data %in% values_valid

# Identify errors
errors_MacroplotReport_Type <- qaqc(data, query, query_message, values_check)
```

-   Check that DateIn is not blank

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Installation"
query_message <- "Date In" 
values_data <- data$Macroplot_DateIn
values_valid <- is.na(data$Macroplot_DateIn)
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_DateIn <- qaqc(data, query, query_message, values_check)
```

#### Combine Installation Errors {.hidden}

```{r}
# Combine
errors_MacroplotReport_Installation <- unique(rbind(errors_MacroplotReport_MacroplotNum, errors_MacroplotReport_Purpose, errors_MacroplotReport_Type, errors_MacroplotReport_DateIn))

remove(errors_MacroplotReport_MacroplotNum, errors_MacroplotReport_Purpose, errors_MacroplotReport_Type, errors_MacroplotReport_DateIn)

if(nrow(errors_MacroplotReport_Installation) > 1) {
  errors_MacroplotReport_Installation <- errors_MacroplotReport_Installation %>%
    filter(Error != "No Error")
} else {
  errors_MacroplotReport_Installation <- errors_MacroplotReport_Installation}
```

### Location

[Problem:]{.underline} Macroplot Report is missing information related to plot geographic location

[Procedure:]{.underline}

-   Check that Latitude is not blank

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Location"
query_message <- "Latitude" 
values_data <- data$Latitude
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_Latitude <- qaqc(data, query, query_message, values_check)
```

-   Check that Longitude is not blank

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Location"
query_message <- "Longitude" 
values_data <- data$Longitude
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_Longitude <- qaqc(data, query, query_message, values_check)
```

-   Check that UTM_X (easting) has 6 digits

```{r}
# Set parameters 
data <- MetadataReport %>% 
  mutate(UTM_X_digits = round(UTM_X))
query <- "Macroplot Report - Location"
query_message <- "UTM_X (easting) should have 6 digits. Digits" 
values_data <- nchar(data$UTM_X_digits)
values_valid <- 6
values_check <- values_data == values_valid

# Identify errors
errors_MacroplotReport_UTM_X <- qaqc(data, query, query_message, values_check)
```

-   Check that UTM_Y (northing) has 7 digits

```{r}
# Set parameters 
data <- MetadataReport %>% 
  mutate(UTM_Y_digits = round(UTM_Y))
query <- "Macroplot Report - Location"
query_message <- "UTM_Y (northing) should have 7 digits. Digits" 
values_data <- nchar(data$UTM_Y_digits)
values_valid <- 7
values_check <- values_data == values_valid

# Identify errors
errors_MacroplotReport_UTM_Y <- qaqc(data, query, query_message, values_check)
```

-   Check that UTM_Zone = 17, 18, or 19

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Location"
query_message <- "UTM_Zone" 
values_data <- data$UTM_Zone
values_valid <- c(17, 18, 19)
values_check <- values_data %in% values_valid

# Identify errors
errors_MacroplotReport_UTM_Zone <- qaqc(data, query, query_message, values_check)
```

-   Check that Datum = NAD83 or NAD27

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Location"
query_message <- "Datum" 
values_data <- data$Datum
values_valid <- c("NAD83", "NAD27")
values_check <- values_data %in% values_valid

# Identify errors
errors_MacroplotReport_Datum <- qaqc(data, query, query_message, values_check)
```

#### Combine Location Errors {.hidden}

```{r}
# Combine
errors_MacroplotReport_Location <- unique(rbind(errors_MacroplotReport_Latitude, errors_MacroplotReport_Longitude, errors_MacroplotReport_UTM_X, errors_MacroplotReport_UTM_Y, errors_MacroplotReport_UTM_Zone, errors_MacroplotReport_Datum))

remove(errors_MacroplotReport_Latitude, errors_MacroplotReport_Longitude, errors_MacroplotReport_UTM_X, errors_MacroplotReport_UTM_Y, errors_MacroplotReport_UTM_Zone, errors_MacroplotReport_Datum)

if(nrow(errors_MacroplotReport_Location) > 1) {
  errors_MacroplotReport_Location <- errors_MacroplotReport_Location %>%
    filter(Error != "No Error")
} else {
  errors_MacroplotReport_Location <- errors_MacroplotReport_Location}
```

### Site Characteristics

[Problem:]{.underline} Macroplot Report is missing information related to plot site characteristics

[Procedure:]{.underline}

-   Check that Elevation is not blank

```{r}
# # Set parameters 
# data <- MetadataReport
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Elevation" 
# values_data <- data$Elevation
# values_valid <- ""
# values_check <- values_data != values_valid
# 
# # Identify errors
# errors_MacroplotReport_Elevation <- qaqc(data, query, query_message, values_check)
```

-   Check that ElevationUnits = feet

```{r}
# # Set parameters 
# data <- MetadataReport
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Elevation Units" 
# values_data <- data$ElevationUnits
# values_valid <- c("feet")
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_ElevationUnits <- qaqc(data, query, query_message, values_check)
```

-   Check that Azimuth values are reasonable

```{r}
# # Set parameters 
# data <- MetadataReport
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Azimuth" 
# values_data <- data$Azimuth
# values_valid <- seq(0, 359, by = 1)
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_Azimuth <- qaqc(data, query, query_message, values_check)
```

-   Check that Aspect values are reasonable

```{r}
# # Set parameters 
# data <- MetadataReport
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Aspect" 
# values_data <- data$Aspect
# values_valid <- seq(0, 359, by = 1)
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_Aspect <- qaqc(data, query, query_message, values_check)
```

-   Check that SlopeHill values are reasonable

```{r}
# # Set parameters 
# data <- MetadataReport
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Slope Hill" 
# values_data <- data$SlopeHill
# values_valid <- seq(0, 40, by = 1)
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_SlopeHill <- qaqc(data, query, query_message, values_check)
```

-   Check that SlopeTransect values are reasonable

```{r}
# # Set parameters 
# data <- MetadataReport
# query <- "Macroplot Report - Site Characteristics"
# query_message <- "Slope Transect" 
# values_data <- data$SlopeTransect
# values_valid <- seq(0, 40, by = 1)
# values_check <- values_data %in% values_valid
# 
# # Identify errors
# errors_MacroplotReport_SlopeTransect <- qaqc(data, query, query_message, values_check)
```

#### Combine Site Characteristics Errors {.hidden}

```{r}
# # Combine
# errors_MacroplotReport_SiteCharacteristics <- unique(rbind(errors_MacroplotReport_Elevation, errors_MacroplotReport_ElevationUnits, errors_MacroplotReport_Azimuth, errors_MacroplotReport_Aspect, errors_MacroplotReport_SlopeHill, errors_MacroplotReport_SlopeTransect))
# 
# remove(errors_MacroplotReport_Elevation, errors_MacroplotReport_ElevationUnits, errors_MacroplotReport_Azimuth, errors_MacroplotReport_Aspect, errors_MacroplotReport_SlopeHill, errors_MacroplotReport_SlopeTransect)
# 
# if(nrow(errors_MacroplotReport_SiteCharacteristics) > 1) {
#   errors_MacroplotReport_SiteCharacteristics <- errors_MacroplotReport_SiteCharacteristics %>%
#     filter(Error != "No Error")
# } else {
#   errors_MacroplotReport_SiteCharacteristics <- errors_MacroplotReport_SiteCharacteristics}
```

### Sample Events

[Problem:]{.underline} Macroplot Report is missing information related to sample events

[Procedure:]{.underline}

-   Check that Macroplot is not blank

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Sample Events"
query_message <- "Macroplot" 
values_data <- data$Macroplot_Name
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_Macroplot <- qaqc(data, query, query_message, values_check)
```

-   Check that SampleEventDate is not blank

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Sample Events"
query_message <- "Sample Event Date" 
values_data <- data$SampleEvent_Date
values_valid <- is.na(data$SampleEvent_Date)
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_SampleEventDate <- qaqc(data, query, query_message, values_check)
```

-   Check that MonStatus is not blank

```{r}
# Set parameters 
data <- MetadataReport
query <- "Macroplot Report - Sample Events"
query_message <- "Monitoring Status" 
values_data <- data$MonitoringStatus_Name
values_valid <- ""
values_check <- values_data != values_valid

# Identify errors
errors_MacroplotReport_MonStatus <- qaqc(data, query, query_message, values_check)
```

#### Combine Sample Event Errors {.hidden}

```{r}
# Combine
errors_MacroplotReport_SampleEvent <- unique(rbind(errors_MacroplotReport_Macroplot, errors_MacroplotReport_SampleEventDate, errors_MacroplotReport_MonStatus))

remove(errors_MacroplotReport_Macroplot, errors_MacroplotReport_SampleEventDate, errors_MacroplotReport_MonStatus)

if(nrow(errors_MacroplotReport_SampleEvent) > 1) {
  errors_MacroplotReport_SampleEvent <- errors_MacroplotReport_SampleEvent %>%
    filter(Error != "No Error")
} else {
  errors_MacroplotReport_SampleEvent <- errors_MacroplotReport_SampleEvent}
```

### Combine Macroplot Report Errors {.hidden}

```{r}
errors_MacroplotReport <- rbind(errors_MacroplotReport_Installation, errors_MacroplotReport_Location, errors_MacroplotReport_SampleEvent)
```

# Sample Event Report

[Problem:]{.underline} Sample Event Report is missing information or is inconsistent with the Macroplot Report

[Procedure:]{.underline}

-   Check that AdministrationUnit_Name is correct

```{r}
# Set parameters 
data <- MetadataReport
query <- "Sample Event Report"
query_message <- "Administration Unit Name" 
values_data <- data$AdminUnit_Name
values_valid <- target_park
values_check <- values_data == values_valid

# Identify errors
errors_SampleEventReport_AdministrationUnit <- qaqc(data, query, query_message, values_check)
```

-   Check that Protocols contains the correct information

```{r}
# Set parameters 
data <- MetadataReport %>% 
  filter(!MonitoringStatus_Name %in% c("Burn", "Herbicide", "Mow", "Mechanical"))
query <- "Sample Event Report"
query_message <- paste0("Date = ", data$SampleEvent_Date, ". Read = ", data$MonitoringStatus_Name, ". Protocol")
values_data <- data$SampleEvent_Protocols
values_valid <- c("Surface Fuels", "Surface Fuels - 1000Hr", "Surface Fuels - Duff_Litter", "Surface Fuels - Fine", "Post Burn Severity (metric)", "Trees - Individuals (metric)", "Density - Quadrats (metric)", "Density - Belts (metric)", "Cover - Species Composition (metric)", "Cover - Points (metric)", "CBI")
values_check <- values_data %in% values_valid

# Identify errors
errors_SampleEventReport_Protocols <- qaqc(data, query, query_message, values_check)
```

```{r}
data <- MetadataReport %>% 
  filter(MonitoringStatus_Name %in% c("Burn", "Herbicide", "Mow", "Mechanical"))
query <- "Sample Event Report"
query_message <- paste0("Date = ", data$SampleEvent_Date, ". Read = ", data$MonitoringStatus_Name, ". Protocol")
values_data <- data$SampleEvent_Protocols
values_valid <- c("Disturbance History", NA)
values_check <- values_data %in% values_valid

# Identify errors
errors_SampleEventReport_ProtocolsPost <- qaqc(data, query, query_message, values_check)
```

-   Check that Visited = Y for each relevant monitoring status (excluding disturbance events: Burn, Herbicide, Mow, Mechanical)

```{r}
# Set parameters 
data <- MetadataReport %>% 
  filter(!MonitoringStatus_Name %in% c("Burn", "Herbicide", "Mow", "Mechanical"))
query <- "Sample Event Report"
query_message <- paste0("Date = ", data$SampleEvent_Date, ". Read = ", data$MonitoringStatus_Name, ". Visited")
values_data <- data$SampleEvent_Visited
values_valid <- "Y"
values_check <- values_data == values_valid

# Identify errors
errors_SampleEventReport_Visited_1 <- qaqc(data, query, query_message, values_check)
```

```{r}
# Set parameters 
data <- MetadataReport %>% 
  filter(MonitoringStatus_Name %in% c("Burn", "Herbicide", "Mow", "Mechanical"),
         SampleEvent_Protocols != "Disturbance History")
query <- "Sample Event Report"
query_message <- paste0("Date = ", data$SampleEvent_Date, ". Read = ", data$MonitoringStatus_Name, ". Visited")
values_data <- data$SampleEvent_Visited
values_valid <- "N"
values_check <- values_data == values_valid

# Identify errors
errors_SampleEventReport_Visited_2 <- qaqc(data, query, query_message, values_check)
```

#### Combine Sample Event Report Errors {.hidden}

```{r}
errors_SampleEventReport <- unique(rbind(errors_SampleEventReport_AdministrationUnit, errors_SampleEventReport_Protocols, errors_SampleEventReport_ProtocolsPost, errors_SampleEventReport_Visited_1, errors_SampleEventReport_Visited_2))

remove(errors_SampleEventReport_AdministrationUnit, errors_SampleEventReport_Protocols, errors_SampleEventReport_ProtocolsPost, errors_SampleEventReport_Visited_1, errors_SampleEventReport_Visited_2)

if(nrow(errors_SampleEventReport) > 1) {
  errors_SampleEventReport <- errors_SampleEventReport %>%
    filter(Error != "No Error")
} else {
  errors_SampleEventReport <- errors_SampleEventReport}
```

# ALL ERRORS

```{r}
errors_all <- rbind(errors_MacroplotReport, errors_blank, errors_SampleEventReport)
```

```{r}
# Create conditional formatting rules
errors_all_cf <- errors_all %>% 
  mutate(Color = ifelse(SavedQuery == "", NA, "Color"))

# Add conditional formating to ouput
errors_all <- condformat(errors_all_cf[1:(nrow(errors_all_cf)), 1:7]) %>%
  rule_fill_discrete(columns = 1:6,
                     expression = (errors_all_cf$Color),
                     colours = c("Color"="#C6E0B4"),
                     na.value = "#FFFFFF") %>%
  select(!c("Color"))
```

```{r}
# Table of results for quick check
kable(errors_all, "pipe")

# Save as CSV or XLSX 
condformat2excel(errors_all, paste0(path_errors, paste0(target_park, "_errors_metadata.xlsx")), sheet_name = path_errors_name, overwrite_wb = TRUE)
```
