---
title: QAQC Cross Year Trees Data Viz
subtitle: NPS Northeast Region Fire Effects Monitoring Program
output:
  html_document:
    theme: readable
    highlight: 
    toc: yes
    toc_depth: 1
    toc_float:
      smooth_scroll: yes
    code_download: true
---

# Purpose

This code is to help visualize tree data across years to identify errors. It only shows problem trees which have an error in one or more data point (Status, Species, DBH, Height). If a graph appears blank, it means that there were no tree issues for that particular data point. It uses the error sheet produced from the QAQC_DataEntry_CrossYear.Rmd script.

### Setup {.hidden}

```{r}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
# install.packages("readxl")
```

```{r}
# "here" helps you easily find and reference your working directory
library(here)
# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
library(readxl)
```

### Target Values {.hidden}

```{r}
# designate target values
# parks <- c("ANTI", "APCO", "CATO", "CUVA", "FRSP", "NERI", "RICH", "SHEN")
target_park <- "NERI"
```

### Adjust File Paths {.hidden}

```{r}
# Adjust File Paths
path_main <- "Z:/NER/SHEN/RAD/Fire/Fire Mgmt/FIRE_ECOLOGIST_FILES/FFI_DATA_MANAGEMENT/"
path_data <- paste0(path_main, "Exports_Clean/FFI/")
path_errors <- paste0(path_main, "/QAQC/")
```

### Load Data {.hidden}

```{r}
# Load in data
Trees_all <- read.csv(paste0(path_data, "metric_trees_individuals.csv"))
errors_Trees_CrossYear <- read_excel(paste0(path_errors, target_park, "/", target_park, "_Errors_DataEntry_CrossYear_MasterRecord.xlsx"))
```

### Clean Data {.hidden}

```{r}
Trees_all <- Trees_all %>%
  # Reformat Date column
  mutate(SampleEvent_Date = as.Date(SampleEvent_Date)) %>%
  mutate(SampleEvent_Date_Year = year(SampleEvent_Date)) %>%
  relocate(SampleEvent_Date_Year, .after = SampleEvent_Date)
```

### Filter Data {.hidden}

```{r}
Trees_data <- Trees_all %>%
  # Filter for target park
  filter(AdminUnit_Name == target_park)

year_max <- as.numeric(format(Sys.Date(), "%Y"))
year_min <- as.numeric((min(Trees_data$SampleEvent_Date_Year)) - 1)
```

### Mutate Data for Graphing {.hidden}

```{r}
graph_Trees_data <- Trees_data %>% 
  mutate(MethodData_Status = ifelse(!is.na(MethodData_CrwnCl) & MethodData_CrwnCl == "DD", "DD", MethodData_Status)) %>% 
  mutate(MethodData_SubFrac = factor(MethodData_SubFrac),
         MethodData_TagNo = factor(MethodData_TagNo),
         MethodData_Status = factor(MethodData_Status, levels = c("L", "D", "DD")),
         MethodData_CrwnCl = factor(MethodData_CrwnCl, levels = c("X", "",
                                            "SC", "I", "C", "D",
                                            "RS", "LBS", "CS", "BAD", 
                                            "BBD", "CUS", "DD")))
```

### Define Target Plot & Isolate Problematic Tree Tags

```{r}
##################################################################################
unique(errors_Trees_CrossYear$Macroplot_Name)
target_plot <- "Plot 04"
##################################################################################

badtags_DBH <- errors_Trees_CrossYear %>% 
  filter(grepl("DBH", errors_Trees_CrossYear$SavedQuery)) %>% 
  filter(Macroplot_Name == target_plot)
badtags_DBH <- unique(badtags_DBH$MethodData_TagNo)

badtags_Height <- errors_Trees_CrossYear %>% 
  filter(grepl("Height", errors_Trees_CrossYear$SavedQuery)) %>% 
  filter(Macroplot_Name == target_plot)
badtags_Height <- unique(badtags_Height$MethodData_TagNo)

badtags_Species <- errors_Trees_CrossYear %>% 
  filter(grepl("Species", errors_Trees_CrossYear$SavedQuery)) %>% 
  filter(Macroplot_Name == target_plot)
badtags_Species <- unique(badtags_Species$MethodData_TagNo)

badtags_Status <- errors_Trees_CrossYear %>% 
  filter(grepl("Status", errors_Trees_CrossYear$SavedQuery)) %>% 
  filter(Macroplot_Name == target_plot)
badtags_Status <- unique(badtags_Status$MethodData_TagNo)
```

# Data Viz - Trees

## [`r target_park`]{style="color:red"} [`r target_plot`]{style="color:red"}

### Status

Status changes from dead to live ("zombie trees").

```{r}
graph_Trees_data %>% 
  filter(Macroplot_Name == target_plot,
         MethodData_TagNo %in% c(badtags_Status)) %>% 
  arrange(SampleEvent_Date) %>% 
  ggplot(aes(x = SampleEvent_Date_Year, y = MethodData_TagNo)) +
  geom_line(aes(group = MethodData_TagNo, color = MethodData_Status), size = 2) +
  geom_point(aes(fill = MethodData_Status), shape = 21, size = 4) +
  scale_fill_manual(values = c("L" = "forestgreen", "D" = "darkorange", "DD" = "red")) +
  scale_color_manual(values=c("L" = "forestgreen", "D" = "darkorange", "DD" = "red")) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(title = target_plot) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))
```

### Species

Individual trees species changes over time.

```{r}
graph_Trees_data %>% 
  filter(Macroplot_Name == target_plot,
         MethodData_TagNo %in% c(badtags_Species)) %>% 
  arrange(SampleEvent_Date) %>% 
  ggplot(aes(x = SampleEvent_Date_Year, y = MethodData_TagNo)) +
  geom_line(aes(group = MethodData_TagNo, color = MethodData_LocalSpeciesSymbol), size = 2) +
  geom_point(aes(fill = MethodData_Status), shape = 21, size = 4) +
  scale_fill_manual(values = c("L" = "forestgreen", "D" = "darkorange", "DD" = "red")) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(title = target_plot) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))
```

### DBH

Live trees should only increase DBH. Dead trees should only decrease DBH.

```{r}
graph_Trees_data %>% 
  filter(Macroplot_Name == target_plot,
         MethodData_TagNo %in% c(badtags_DBH)
         # !is.na(MethodData_DBH_cm),
         # MethodData_Status != "DD") 
         ) %>% 
  arrange(SampleEvent_Date) %>% 
  ggplot(aes(x = SampleEvent_Date_Year, y = MethodData_DBH_cm)) +
  geom_line(aes(group = MethodData_TagNo, color = MethodData_TagNo), size = 1) +
  geom_point(aes(fill = MethodData_Status), shape = 21, size = 4) +
  scale_fill_manual(values=c("L" = "forestgreen", "D" = "darkorange")) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(title = target_plot) +
  #facet_wrap(~MethodData_Status) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))
```

### Height

Live trees should only increase in height. Dead trees should only decrease in height.

```{r}
graph_Trees_data %>% 
  filter(Macroplot_Name == target_plot,
         MethodData_TagNo %in% c(badtags_Height),
         !is.na(MethodData_Ht_m),
         MethodData_Status != "DD") %>% 
  arrange(SampleEvent_Date) %>% 
  ggplot(aes(x = SampleEvent_Date_Year, y = MethodData_Ht_m)) +
  geom_line(aes(group = MethodData_TagNo, color = MethodData_TagNo), size = 1) +
  geom_point(aes(fill = MethodData_Status), shape = 21, size = 4) +
  scale_fill_manual(values=c("L" = "forestgreen", "D" = "darkorange")) +
    scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(title = target_plot) +
  #facet_wrap(~MethodData_Status) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 20, face="bold", hjust = 0.5),
        plot.subtitle = element_text(size = 12, face="italic", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1))
```
