---
title: Richmond National Battlefield Park Report - Forest Plots
author: NPS Northeast Region Fire Effects Monitoring Program
output:
  html_document:
    theme: readable
    highlight: null
    toc: false
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
  pdf_document:
    toc: true
    toc_depth: 2
  word_document:
    toc: true
    toc_depth: 2
link-citations: true
bibliography: zotero_refs.bib
csl: chicago-author-date-17th-edition.csl
---

# Annual Report {.hidden}

### Setup {.hidden}

```{r}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
# install.packages("RefManageR")
# install.packages("vegan")
# install.packages("downloadthis")
```

```{r}
## Load Packages

# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
library(stringr)
library(DT)
library(fs)
# ggplot2 is used for graphing. gganimate creates graph animations patchwork stitches graphs together
library(ggplot2)
#library(gganimate)
library(patchwork)
library(RColorBrewer)
# zotero reference manager
library(RefManageR)
# shannon diversity index
library(vegan)
library(here)
# download button
library(downloadthis)
```

### References

```{r}
ZoteroUserID <- "3306456"
ZoteroAPIkey <- "F7k8Rp07XhH9rIqiKP1ob0uB"
ZoteroFolderKey <- "DGJVBG7G"

bib <- ReadZotero(
  user = ZoteroUserID,
  .params = list(
    collection = ZoteroFolderKey,
    key = ZoteroAPIkey,
    limit = 100),
  temp.file = "zotero_refs.bib",
  delete.file = FALSE)
```

### Adjust File Paths {.hidden}

```{r}
## Adjust File Paths
#path_file <- "E:/Allie/FireFX_NER/FFI Data Management/R Outputs/"
path_file <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/R Outputs/"
path_data <- paste0(path_file, "ALL/Calculations/ALL_")
path_save <- "C:/Users/alalor/OneDrive - DOI/R/NER/output/graphs/"
## Source Code for Gingrich Stocking Chart
source(paste0(here(), "/scripts/4_Reports/Gingrich Stocking Chart.R"))
```

### Load Data {.hidden}

```{r}
# Load in data
MetadataReport <- read.csv(paste0(path_data, "MetadataReport.csv"))
SpeciesReport <- read.csv(paste0(path_data, "SpeciesReport.csv"))
Fuels <- read.csv(paste0(path_data, "Data_Fuels.csv"))
Trees <- read.csv(paste0(path_data, "Data_Trees.csv"))
Seedlings <- read.csv(paste0(path_data, "Data_Seedlings.csv"))
Cover <- read.csv(paste0(path_data, "Data_Cover_Points.csv"))
# Cover_SpComp <- read.csv(paste0(path_data, "Data_Cover_SpComp.csv"))
# PostBurn <- read.csv(paste0(path_data, "Data_Post Burn Severity (metric).csv"))
# Shrubs <- read.csv(paste0(path_data, "Data_Density - Belts (metric).csv"))
```

### Target Values {.hidden}

```{r}
target_park <- c("RICH")
target_type <- c("Forest")
target_purpose <- c("Fire Monitoring Handbook")
target_year <- c(2025)

    
    MetadataReport %>%
      filter(
        Macroplot_Purpose == target_purpose,
        AdminUnit_Name == target_park,
        Macroplot_Type == target_type
        ) %>% 
      select(Macroplot_UV1, Macroplot_UV2) %>% 
      unique()

target_ProjectUnit <- c("Cold Harbor I")
target_MonitoringType <- c("Pine Oak")


    MetadataReport_SampleEvents <- MetadataReport %>%
      filter(
        AdminUnit_Name == target_park,
        Macroplot_Type == target_type,
        Macroplot_Purpose == target_purpose,
        Macroplot_UV1 == target_ProjectUnit,
        Macroplot_UV2 == target_MonitoringType,
        !MonitoringStatus_Name %in% c("Burn", "Herbicide", "Mechanical", "Mow")
        )

    MetadataReport_Disturbances <- MetadataReport %>%
      filter(
        AdminUnit_Name == target_park,
        Macroplot_Type == target_type,
        Macroplot_Purpose == target_purpose,
        Macroplot_UV1 == target_ProjectUnit,
        Macroplot_UV2 == target_MonitoringType,
        MonitoringStatus_Name %in% c("Burn", "Herbicide", "Mechanical", "Mow")
        )

year_max <- as.numeric(format(Sys.Date(), "%Y"))
date_max <- as.Date(paste0(year_max, "-12-31"))
year_min <- as.numeric((min(MetadataReport_SampleEvents$SampleEvent_Date_Year)) - 1)
date_min <- as.Date(paste0(year_min, "-12-31"))
```

### Add Species Info

```{r}
# Isolate all trees which are in the plots analyzed
Species_trees_protocol <- Trees %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  select(ScientificName)

Species_seedlings_protocol <- Seedlings %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  select(ScientificName)

Species_trees_filter <- rbind(Species_trees_protocol, 
                              Species_seedlings_protocol) %>% 
  drop_na() %>% 
  unique() %>% 
  filter(ScientificName != "Unknown")

# target species object
target_species <- Species_trees_filter$ScientificName


# filter target species from master list
Species_trees <- SpeciesReport %>%
  filter(
        ReportType == paste0("AdminUnit: ", target_park, " - Full Species Report"),
        LocalSpecies_PreferedLifeForm == "Tree"
      ) %>%
  filter(MasterSpecies_ScientificName %in% target_species) %>% 
  mutate(
    "Genus" = MasterSpecies_Genus,
    "Scientific Name" = MasterSpecies_ScientificName,
    "Fire Adaptedness" = LocalSpecies_UV1
  ) %>%
  separate(LocalSpecies_CommonName, into = "Common Name", sep = ";") %>%
  select("Genus", "Scientific Name", "Common Name", "Fire Adaptedness")


# vector of tree genera
genera <- Species_trees$Genus

palette <- c(
  brewer.pal(12,"Set3"),
  brewer.pal(12,"Paired"),
  brewer.pal(8,"Dark2"),
  brewer.pal(9,"Set1"),
  brewer.pal(8,"Set2")
)

cols <- palette[1:length(genera)]
cols <- colorspace::darken(cols, 0.15)
genus_colors <- setNames(cols, genera)

# color for NA
na_color <- "grey70"
```

# Project Unit: `r target_ProjectUnit`

# Overview

The current vegetation association of Richmond's forest is a Northern Coastal Plain Mixed Oak / Heath Forest [@noauthor_natureserve_nodate]. Recommendations for forest characteristics will be aimed at maintaining this community type.

# Monitoring Objectives

```{r}
Objectives <- data.frame(
  "Num" = c(1,2,3,4,5,6),
  "Objective" = c(
    "1. Maintain fine fuel loading (1-hr, 10-hr, and 100-hr fuels) at < 2.4 tons/acre",
    "2. Maintain duff depth to ≤1.5 inch",
    "3. Increase sapling density to ≥1,000 stems/acre",
    "4. Reduce pole-sized tree density of mesic fire-intolerant/fire-tolerant species relative to xeric fire-adapted species",
    "5. Maintain a stocking density of overstory trees between 30-70%",
    "6. Maintain or increase native grass and forb cover to ≥50%"
    ))

target_FineFuelLoading <- 2.4
target_Duff <- 1.5
target_Sapling <- 1000
target_Cover <- 50

kable(Objectives %>% 
        select(Objective)
      )
```

#### Justifications

1.  The fuel model most representative of this vegetation association is Timber Litter 6 (TL6) [@scott_standard_2005]. Timber Litter fuel models are primarily driven by dead and down woody fuel, and TL6 specifically represents moderate load broadleaf litter. To moderate fire spread potential, fine fuel loading should be at or below what is expected for each fuel model.
2.  To promote oak and pine regeneration, duff depth should be maintained at low levels to allow seedlings with shallow root systems to establish in mineral soil [@jenkins_yellow_2011].
3.  Young trees can be categorized by height class. In this report we define "seedlings" as \<1m tall and "saplings" as \>1m tall but \<2.5cm DBH (DBH = diameter at height of 1.3m). We will focus on sapling tree density metrics because larger size classes are more competitive and better predictors of advanced regeneration [@harris_increasing_2022].
4.  Pole-sized trees are classified as between 2.5cm and 15cm DBH. Species composition of pole-sized trees reflect the trajectory of forest change and can be targeted for thinning treatments. Fire-adapted oak-pine ecosystems contain a higher ratio of xeric species, which are drought tolerant and usually fire-adapted, compared to mesic species, which are tolerant of shadier and moister conditions [@alexander_mesophication_2021].
5.  Overstory trees are classified as \>15cm DBH. These are the mature trees which make up the overall forest structure. To promote open canopy woodlands, tree stocking densities should be maintained within 30-70% [@ginrich_measuring_1967; @kabrick_silvicultural_2014; @hanberry_open_2020; @pile_knapp_managing_2024]
6.  Diversity objective...

## Overview {.hidden}

### Prep {.hidden}

```{r}
Disturbances_graph <- MetadataReport_Disturbances %>%
  group_by(
    Region, Zone, Unit, AdminUnit_Name, Plot_Type, 
    Disturbance_Date, Disturbance_Date_Year, SampleEvent_Date_Year, MonitoringStatus_Name
    ) %>%
  filter(
    Disturbance_Date_Year == SampleEvent_Date_Year
    ) %>%
  dplyr::summarize(
    n_Macroplot = n()
    ) %>%
  mutate(
    Disturbance_Date = as.Date(Disturbance_Date),
    Macroplot_Num = "All"
    ) %>%
  arrange(desc(MonitoringStatus_Name))
```

### Disturbance History

```{r}
if(nrow(MetadataReport_Disturbances) == 0) {
  p_disturbance <- ggplot()
} else {
  p_disturbance <- MetadataReport_Disturbances %>%
    ggplot(aes(x = Disturbance_Date, y = Macroplot_Num)) +
    geom_line(aes(group = Macroplot_Num),
              data = Disturbances_graph) +
    geom_point(aes(X = Disturbance_Date, y = Macroplot_Num, fill = MonitoringStatus_Name),
               data = Disturbances_graph, shape = 21) +
    geom_line(aes(X = Disturbance_Date, y = Macroplot_Num, fill = MonitoringStatus_Name),
              data = Disturbances_graph) +
    geom_point(aes(X = Disturbance_Date, y = Macroplot_Num, fill = MonitoringStatus_Name),
               data = Disturbances_graph, shape = 21, size = 2.5) +
    facet_grid( ~ Macroplot_UV2) +
    labs(title = "Disturbance History",
         y = "",
         x = "Year",
         fill = "") +
    scale_x_date(
      limits = c(date_min, date_max),
      date_breaks = "1 year",
      date_labels = "%Y",
      expand = expansion(mult = c(0, 0))
    ) +
    theme_light() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          plot.title = element_text(size = 15, face="bold", hjust = 0.5),
          axis.title = element_text(size = 12, face="bold"),
          axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
          axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
          legend.position = "top")
}

#p_disturbance
```

## Surface Fuels

### Prep {.hidden}

```{r}
Fuels_graph <- Fuels %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  mutate(
    SampleEvent_Date_Year = as.numeric(SampleEvent_Date_Year)
    ) %>%
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ) %>% 
  dplyr::summarise(
    n_plots = n_distinct(Macroplot_Name),
    ThousHr_FuelLoad = mean(ThousHr_FuelLoad, na.rm = TRUE),
    ThousHrRott_FuelLoad = mean(ThousHrRott_FuelLoad, na.rm = TRUE),
    ThousHrSound_FuelLoad = mean(ThousHrSound_FuelLoad, na.rm = TRUE),
    Fine_FuelLoad = mean(Fine_FuelLoad, na.rm = TRUE),
    HunHr_FuelLoad = mean(HunHr_FuelLoad, na.rm = TRUE),
    TenHr_FuelLoad = mean(TenHr_FuelLoad, na.rm = TRUE),
    OneHr_FuelLoad = mean(OneHr_FuelLoad, na.rm = TRUE),
    Avg_LittDuff_FuelLoad = mean(Avg_LittDuff_FuelLoad, na.rm = TRUE),
    Avg_Litt_FuelLoad  = mean(Avg_Litt_FuelLoad, na.rm = TRUE),
    Avg_Duff_FuelLoad = mean(Avg_Duff_FuelLoad, na.rm = TRUE),
    .groups = "drop"
    ) %>% 
  pivot_longer(
    cols = c(
      ThousHr_FuelLoad,
      ThousHrRott_FuelLoad,
      ThousHrSound_FuelLoad,
      Fine_FuelLoad,
      HunHr_FuelLoad,
      TenHr_FuelLoad,
      OneHr_FuelLoad,
      Avg_LittDuff_FuelLoad,
      Avg_Litt_FuelLoad,
      Avg_Duff_FuelLoad
    ),
    names_to  = "FuelClass",
    values_to = "FuelLoad"
  ) %>% 
    mutate(
    FuelClass = factor(
      FuelClass,
      levels = c(
        "ThousHr_FuelLoad",
        "ThousHrRott_FuelLoad",
        "ThousHrSound_FuelLoad",
        "Fine_FuelLoad",
        "HunHr_FuelLoad",
        "TenHr_FuelLoad",
        "OneHr_FuelLoad",
        "Avg_LittDuff_FuelLoad",
        "Avg_Litt_FuelLoad",
        "Avg_Duff_FuelLoad"
      )
    )
  ) %>%
    mutate(
    FuelClass = recode(
      FuelClass,
      ThousHr_FuelLoad        = "1000-hr",
      ThousHrRott_FuelLoad    = "1000-hr Rotten",
      ThousHrSound_FuelLoad   = "1000-hr Sound",
      Fine_FuelLoad           = "Fine",
      HunHr_FuelLoad          = "100-hr",
      TenHr_FuelLoad          = "10-hr",
      OneHr_FuelLoad          = "1-hr",
      Avg_LittDuff_FuelLoad   = "Litter/Duff",
      Avg_Litt_FuelLoad       = "Litter",
      Avg_Duff_FuelLoad       = "Duff"
    )
  )
```

```{r}
FuelsDuff_graph <- Fuels %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  mutate(
    SampleEvent_Date_Year = as.numeric(SampleEvent_Date_Year)
    ) %>%
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ) %>% 
  dplyr::summarise(
    n_plots = n_distinct(Macroplot_Name),
    Avg_LittDep = mean(Avg_LittDep, na.rm = TRUE),
    Avg_DuffDep = mean(Avg_DuffDep, na.rm = TRUE),
    .groups = "drop"
    ) %>% 
  pivot_longer(
    cols = c(
      Avg_LittDep,
      Avg_DuffDep
    ),
    names_to  = "FuelClass",
    values_to = "FuelDepth"
  ) %>% 
    mutate(
    FuelClass = factor(
      FuelClass,
      levels = c(
        "Avg_LittDep",
        "Avg_DuffDep"
      )
    )
  ) %>%
    mutate(
    FuelClass = recode(
      FuelClass,
      Avg_LittDep       = "Litter",
      Avg_DuffDep       = "Duff"
    )
  )
```

### Fine Fuels

```{r}
kable(Objectives %>% 
      filter(Num == 1) %>% 
      select(Objective)
      )
```

```{r}
if(nrow(Fuels_graph) == 0) {
  p_fuels <- "No data available for this selection."
} else {
  p_fuels <- Fuels_graph %>% 
  filter(
    FuelClass %in% c(
      #"1000-hr",
      #"1000-hr Rotten",
      #"1000-hr Sound",
      "Fine"
      #"100-hr",
      #"10-hr",
      #"1-hr",
      #"Litter/Duff",
      #"Litter",
      #"Duff"
  )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ) %>% 
  mutate(
    Total_FuelLoad = sum(FuelLoad)
    ) %>% 
  
  ggplot(aes(x = SampleEvent_Date_Year, y = Total_FuelLoad, fill = FuelClass)) +
  geom_line() +
  geom_point() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Tons / Acre",
    fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Loading")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  ylim(0, 8) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    ) +
  geom_hline(
    yintercept = target_FineFuelLoading, 
    linetype = "dashed", 
    color = "forestgreen"
    )
}

#p_fuels
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_fuels_merge <- p_fuels +
  theme(plot.title = element_blank())

if(is.character(p_fuels)) {
  p_fuels
} else {
p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))
}
```

```{r}
# save when ready
p <-
  p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))

ggsave(filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Fuels Fine.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
```

### Duff Depth

```{r}
kable(Objectives %>% 
      filter(Num == 2) %>% 
      select(Objective)
      )
```

```{r}
if(nrow(FuelsDuff_graph) == 0) {
  p_fuels <- "No data available for this selection."
} else {
p_fuels <- FuelsDuff_graph %>% 
  filter(
    FuelClass %in% c(
      "Litter",
      "Duff"
  )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ) %>% 
  mutate(
    Total_FuelDepth = sum(FuelDepth)
    ) %>% 
  
  ggplot() +
  geom_bar(aes(x = SampleEvent_Date_Year, y = FuelDepth, fill = FuelClass),
           position = "stack", stat = "identity") + 
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Depth (inches)",
    fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Depth")
  ) +
  scale_x_continuous(
    limits = c((year_min), year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = c("Litter" = "#BFEFFF", "Duff" = "#619CFF")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    ) +
  geom_hline(
    yintercept = target_Duff, 
    linetype = "dashed", 
    color = "#619CFF",
    size = 0.7
    )
}

#p_fuels
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_fuels_merge <- p_fuels +
  theme(plot.title = element_blank())

if(is.character(p_fuels)) {
  p_fuels
} else {
p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))
}
```

```{r}
# save when ready
p <-
  p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))

ggsave(filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Fuels Duff.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
```

### All Fuels {.hidden}

```{r}
if(nrow(Fuels_graph) == 0) {
  p_fuels <- "No data available for this selection."
} else {
p_fuels <- Fuels_graph %>% 
  filter(
    FuelClass %in% c(
      #"1000-hr",
      "1000-hr Rotten",
      "1000-hr Sound",
      #"Fine"
      "100-hr",
      "10-hr",
      "1-hr"
      #"Litter/Duff",
      #"Litter",
      #"Duff"
  )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ) %>% 
  mutate(
    Total_FuelLoad = sum(FuelLoad)
    ) %>% 
  
  ggplot() +
  geom_bar(aes(x = SampleEvent_Date_Year, y = FuelLoad, fill = FuelClass),
           position = "stack", stat = "identity") + 
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Tons / Acre",
    fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Loading")
  ) +
  scale_x_continuous(
    limits = c((year_min), year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )
}

#p_fuels
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_fuels_merge <- p_fuels +
  theme(plot.title = element_blank())

if(is.character(p_fuels)) {
  p_fuels
} else {
p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))
}
```

```{r}
# save when ready
p <-
  p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))

ggsave(filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Fuels All.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
```

## Trees

### Prep {.hidden}

```{r}
Seedlings_graph <- Seedlings %>%
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  mutate(
    SampleEvent_Date_Year = as.numeric(SampleEvent_Date_Year)
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Genus
    ,ScientificName
    ,Status
    ) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot_Name),
    
    Seedling_Count  = sum(Seedling_Count),
    Seedling_Density_ac = round((mean(Seedling_Dens_ac, na.rm = TRUE)),0),
    Seedling_Density_ha = round((mean(Seedling_Dens_ac, na.rm = TRUE)),0),
    
    Sapling_Count = sum(Sapling_Count),
    Sapling_Density_ac = round((mean(Sapling_Dens_ac, na.rm = TRUE)),0),
    Sapling_Density_ha = round((mean(Sapling_Dens_ac, na.rm = TRUE)),0),
    
    .groups = "drop"
  ) %>% 
  pivot_longer(
    cols = matches("Seedling|Sapling"),
    names_to = c("SizeClass", ".value"),
    names_pattern = "(Seedling|Sapling)_(Species|Count|Density_[a-z]+)"
  ) %>% 
  # mutate(Legend  = ifelse(Genus == "Carya",
  #                         "Fire Tolerant",
  #                    ifelse(Genus %in% c("Liriodendron", "Liquidambar"),
  #                           "Fire Intolerant",
  #                                  ifelse(Genus %in% c("Pinus", "Quercus"),
  #                                         "Fire Adapted", "Unknown")))
  #        ) %>%
  mutate(
    SizeClass = factor(
      SizeClass,
      levels = c(
        "Sapling",
        "Seedling"
      ))
    # Genus = factor(
    #   Genus,
    #   levels = c(
    #     "Pinus",
    #     "Quercus",
    #     "Carya",
    #     "Liriodendron",
    #     "Liquidambar",
    #     "Carex"
    #   )),
    # Legend = factor(
    #   Legend,
    #   levels = c(
    #     "Fire Adapted",
    #     "Fire Tolerant",
    #     "Fire Intolerant",
    #     "Unknown"
    #     ))
    )
```

```{r}
Trees_graph <- Trees %>%
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  mutate(
    SampleEvent_Date_Year = as.numeric(SampleEvent_Date_Year)
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Genus
    ,ScientificName
    ,Status
    ) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot_Name),
    
    Pole_Count = sum(Pole_Count),
    Pole_Density_ac = round((mean(Pole_Dens_ac, na.rm = TRUE)),0),
    Pole_Density_ha = round((mean(Pole_Dens_ac, na.rm = TRUE)),0),
    Pole_BA_ft2 = round((mean(Pole_BA_ft2, na.rm = TRUE)), 2),
    Pole_BA_m2 = round((mean(Pole_BA_m2, na.rm = TRUE)), 2),
    
    Overstory_Count = sum(Overstory_Count),
    Overstory_Density_ac = round((mean(Overstory_Dens_ac, na.rm = TRUE)),0),
    Overstory_Density_ha = round((mean(Overstory_Dens_ac, na.rm = TRUE)),0),
    Overstory_BA_ft2 = round((mean(Overstory_BA_ft2, na.rm = TRUE)), 2),
    Overstory_BA_m2 = round((mean(Overstory_BA_m2, na.rm = TRUE)), 2),
    
    .groups = "drop"
  ) %>% 
  pivot_longer(
    cols = matches("Pole|Overstory"),
    names_to = c("SizeClass", ".value"),
    names_pattern = "(|Pole|Overstory)_(Species|Count|Density_[a-z]+|BA_[a-z0-9]+)"
  ) %>% 
  mutate(
    SizeClass = factor(
      SizeClass,
      levels = c(
        "Overstory",
        "Pole"
      ))
    # Genus = factor(
    #   Genus,
    #   levels = c(
    #     "Pinus",
    #     "Quercus",
    #     "Carya",
    #     "Liriodendron",
    #     "Liquidambar",
    #     "Carex"
    #   )),
    # LocalSpecies_UV1 = factor(
    #   LocalSpecies_UV1,
    #   levels = c(
    #     "fire adapted",
    #     "fire tolerant",
    #     "fire intolerant",
    #     "unknown"
    #     ))
  )
```

### Seedlings {.hidden}

```{r}
if(nrow(Seedlings_graph) == 0) {
  p_trees_seedlings <- "No data available for this selection."
} else {
p_trees_seedlings <- Seedlings_graph %>% 
  filter(
    Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      "Seedling"
      #"Sapling",
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Genus
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha)
    ) %>% 
  filter(
    Total_Density_ac != 0
    ) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEvent_Date_Year, 
      y = Total_Density_ac, 
      fill = Genus
      ),
    position = "stack", stat = "identity") +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Seedling Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )
}

#p_trees_seedlings
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Seedling Tree Density"),
    fill = "Disturbance"
       )

p_trees_merge <- p_trees_seedlings +
  theme(plot.title = element_blank())

if(is.character(p_trees_seedlings)) {
  p_trees_seedlings
} else {
p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))
}
```

```{r}
# save when ready
p <-
  p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))

ggsave(filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Trees Seedlings.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
```

### Saplings

```{r}
kable(Objectives %>% 
      filter(Num == 3) %>% 
      select(Objective)
      )
```

```{r}
if(nrow(Seedlings_graph) == 0) {
  p_trees_saplings <- "No data available for this selection."
} else {
p_trees_saplings <- Seedlings_graph %>% 
  filter(
    Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      #"Seedling",
      "Sapling"
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Genus
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha)
    ) %>% 
  filter(
    Total_Density_ac != 0
    ) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEvent_Date_Year,
      y = Total_Density_ac,
      fill = Genus
      ),
    # position_dodge means the bars will display side by side
    position = "stack", stat = "identity"
    #,position = position_dodge2(preserve = "single"), stat = "identity"
    ) +
 facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Sapling Tree Density"),
    caption = expression("*80 stems/ac (200 stems/ha) is equivalent to 1 sapling found in a sample area of 50m"^2)
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = genus_colors, na.value = na_color, drop = FALSE) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    ) +
  geom_hline(
    yintercept = target_Sapling, 
    linetype = "dashed", 
    color = "forestgreen"
    )
}

#p_trees_saplings
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Sapling Tree Density"),
    fill = "Disturbance"
       )

p_trees_merge <- p_trees_saplings +
  theme(plot.title = element_blank())

if(is.character(p_trees_saplings)) {
  p_trees_saplings
} else {
p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))
}
```

```{r}
# save when ready
p <-
  p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))

ggsave(filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Trees Saplings.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
```

### Pole-Sized

```{r}
kable(Objectives %>% 
      filter(Num == 4) %>% 
      select(Objective)
      )
```

```{r}
if(nrow(Trees_graph) == 0) {
  p_trees_poles <- "No data available for this selection."
} else {
p_trees_poles <- Trees_graph %>% 
  filter(
    Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      "Pole"
      #"Overstory"
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Genus
    #,ScientificName
    #,LocalSpecies_UV1
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha)
    #Species = paste(na.omit(unique(Species)), collapse = "; ")
    ) %>% 
  filter(
    Total_Density_ac != 0
    ) %>% 
  
  ggplot(
    aes(
      x = SampleEvent_Date_Year,
      y = Total_Density_ac,
      color = Genus,
      )
  ) +
  geom_line() +
  geom_point() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Pole Tree Density"),
    color = element_blank()
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  scale_color_manual(values = genus_colors, na.value = na_color, drop = FALSE) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )
}

#p_trees_poles
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Pole Tree Density"),
    fill = "Disturbance"
       )

p_trees_merge <- p_trees_poles +
  theme(plot.title = element_blank())

if(is.character(p_trees_poles)) {
  p_trees_poles
} else {
p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))
}
```

```{r}
# save when ready
p <-
  p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))

ggsave(filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Trees Poles.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
```

### Overstory - Gingrich Stocking Graph

```{r}
kable(Objectives %>% 
      filter(Num == 5) %>% 
      select(Objective)
      )
```

```{r gingrich-plot, fig.width=10, fig.height=8}
if(nrow(Trees_graph) == 0) {
  p_trees_overstory_BA <- "No data available for this selection."
} else {
p_trees_overstory_BA <- Trees_graph %>% 
  filter(
    Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      #"Pole",
      "Overstory"
      )) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    #,Genus, Status
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha),
    Total_BA_ft2 = sum(BA_ft2),
    Total_BA_m2 = sum(BA_m2)
    ) %>% 
  filter(
    Total_Density_ac != 0,
    SampleEvent_Date_Year %in% max(Trees_graph$SampleEvent_Date_Year)
    )

plot.gingrich.imperial(
  tpa = p_trees_overstory_BA$Total_Density_ac,
  ba = p_trees_overstory_BA$Total_BA_ft2,
  label = p_trees_overstory_BA$SampleEvent_Date_Year,
  color = TRUE,
  type = "p",
  main = paste(target_park, target_ProjectUnit, "\nOverstory Stand Structure")
)
}
```

```{r include=FALSE}
# save when ready
if(is.character(p_trees_overstory_BA)) {
  p_trees_overstory_BA
} else {
jpeg(
  filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Trees Overstory.jpg"),
  width = 10, height = 8, units = "in", res = 300
)

plot.gingrich.imperial(
  tpa = p_trees_overstory_BA$Total_Density_ac,
  ba = p_trees_overstory_BA$Total_BA_ft2,
  label = p_trees_overstory_BA$SampleEvent_Date_Year,
  color = TRUE,
  type = "p",
  main = paste(target_park, target_ProjectUnit, "\nOverstory Stand Structure")
)

dev.off()
}
```

## Cover

### Prep {.hidden}

```{r}
Cover_graph <- Cover %>% 
  filter(
    AdminUnit_Name == target_park,
    Macroplot_Type == target_type,
    Macroplot_Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  mutate(
    SampleEvent_Date_Year = as.numeric(SampleEvent_Date_Year)
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type,
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Preferred_Lifeform, Genus, ScientificName, Nativity
    ) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot_Name),
    Avg_Ht_m = round(mean(Avg_Ht_m, na.rm = TRUE), 1),
    Avg_Ht_ft = round(mean(Avg_Ht_ft, na.rm = TRUE), 1),
    Abundance = sum(Hits, na.rm = TRUE),
    PctCover = round(mean(PctCover, na.rm = TRUE), 2),
    .groups = "drop"
    ) %>% 
  mutate(
    Preferred_Lifeform = ifelse(Preferred_Lifeform == "Undefined", "Substrate", Preferred_Lifeform),
    Preferred_Lifeform = factor(
      Preferred_Lifeform,
      levels = c(
        "Tree",
        "Shrub",
        "Subshrub",
        "Forb/herb",
        "Fern",
        "Vine",
        "Graminoid",
        "Grass-like",
        "Nonvascular", 
        "Lichenous", 
        "Substrate"
      )))
```

### Diversity {.hidden}

```{r}
# wide_diversity <- Cover_graph %>%
#   filter(
#     Preferred_Lifeform %in% c(
#       #"Nonvascular", "Lichenous", 
#       "Graminoid", "Grass-like",
#       "Forb/herb", "Fern", "Vine"
#       #"Shrub", "Subshrub",
#       #"Tree"
#       #"Substrate"
#       ),
#     Nativity %in% c(
#       "Native",
#       "Non-Native",
#       "Invasive"
#       #"Unknown"
#       )
#     ) %>% 
#   select(SampleEvent_Date_Year, Species.Symbol, Abundance) %>%
#   tidyr::pivot_wider(
#     names_from = Species.Symbol,
#     values_from = Abundance,
#     values_fill = 0
#   )
# 
# shannon <- wide_diversity %>%
#   mutate(
#     Shannon_Index = diversity(select(., -SampleEvent_Date_Year),
#                         index = "shannon")
#   ) %>%
#   select(SampleEvent_Date_Year, Shannon_Index)
# 
# 
# p_diversity <- shannon %>% 
#   ggplot(aes(x = SampleEvent_Date_Year, y = Shannon_Index)) +
#   geom_line() +
#   geom_point() +
#   #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
#   labs(
#     x = "Year",
#     y = "Shannon-Wiener Diversity Index",
#     title = paste(target_park, target_type, "Native Grass Cover")
#     ) +
#   scale_x_continuous(
#     limits = c(year_min, year_max),
#     breaks = seq(year_min, year_max, by = 1),
#     expand = expansion(mult = c(0, 0))
#     ) +
#   ylim(0, 4) +
#   theme_minimal() +
#   theme(
#     axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
#     plot.title = element_text(size = 15, face="bold", hjust = 0.5),
#     plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
#     axis.title = element_text(size = 12, face="bold"),
#     axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
#     axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
#     axis.text.y = element_text(size = 8),
#     panel.grid.minor = element_blank()
#     )  +
#   geom_vline(
#     xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
#     linetype = "dashed", 
#     color = "red"
#     )
# 
# p_diversity
```

```{r}
# p_cover_classic <- Cover_graph %>% 
#   filter(
#     Preferred_Lifeform %in% c(
#       "Nonvascular", "Lichenous", 
#       "Graminoid", "Grass-like",
#       "Forb/herb", "Fern", "Vine",
#       "Shrub", "Subshrub",
#       "Tree"
#       #"Substrate"
#       ),
#     Nativity %in% c(
#       "Native",
#       "Non-Native",
#       "Invasive"
#       #"Unknown"
#       )
#     ) %>% 
#   group_by(
#     AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
#     Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
#     #,Preferred_Lifeform, Genus, Nativity
#     ) %>% 
#   mutate(
#     Total_Cover = sum(PctCover),
#     Total_Abundance = sum(Abundance, na.rm = TRUE)
#     ) %>%  
#   
#   
# p_diversity <- sdi_results %>% 
#   ggplot(aes(x = SampleEvent_Date_Year, y = Shannon_Index)) +
#   geom_line() +
#   geom_point() +
#   #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
#   labs(
#     x = "Year",
#     y = "% Cover",
#     title = paste(target_park, target_type, "Native Grass Cover")
#     ) +
#   scale_x_continuous(
#     limits = c(year_min, year_max),
#     breaks = seq(year_min, year_max, by = 1),
#     expand = expansion(mult = c(0, 0))
#     ) +
#   theme_minimal() +
#   theme(
#     axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
#     plot.title = element_text(size = 15, face="bold", hjust = 0.5),
#     plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
#     axis.title = element_text(size = 12, face="bold"),
#     axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
#     axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
#     axis.text.y = element_text(size = 8),
#     panel.grid.minor = element_blank()
#     )  +
#   geom_vline(
#     xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
#     linetype = "dashed", 
#     color = "red"
#     )
```

### Native Grasses and Forbs

```{r}
kable(Objectives %>% 
      filter(Num == 6) %>% 
      select(Objective)
      )
```

```{r}
if(nrow(Cover_graph) == 0) {
  p_cover_classic <- "No data available for this selection."
} else {
p_cover_classic <- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      #"Nonvascular", "Lichenous", 
      "Graminoid", "Grass-like",
      "Forb/herb", "Fern"
      ,"Vine"
      #,"Shrub", "Subshrub",
      #"Tree",
      #"Substrate"
      ),
    Nativity %in% c(
      "Native"
      #"Non-Native",
      #"Invasive",
      #"Unknown"
      )
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    #,Preferred_Lifeform, Genus, Nativity
    ) %>% 
  mutate(
    Total_Cover = sum(PctCover)
    ) %>%  

  
  ggplot(aes(x = SampleEvent_Date_Year, y = Total_Cover)) +
  geom_line() +
  geom_point() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "% Cover",
    title = paste(target_park, target_type, "Native Grass and Forb Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  ylim(0, 100) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )  +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    ) +
  geom_hline(
    yintercept = target_Cover, 
    linetype = "dashed", 
    color = "forestgreen"
    )
}

#p_cover_classic
```

```{r}

p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Native Grass and Forb Cover"),
    fill = "Disturbance"
       )

p_cover_merge <- p_cover_classic +
  theme(plot.title = element_blank())

if(is.character(p_cover_classic)) {
  p_cover_classic
} else {
p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))
}
```

```{r}
# save when ready
p <-
  p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))

ggsave(filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Cover Classic.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
```

### Cover Lifeform

```{r}
if(nrow(Cover_graph) == 0) {
  p_cover_lifeform <- "No data available for this selection."
} else {
p_cover_lifeform <- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      "Nonvascular", "Lichenous"
      ,"Graminoid", "Grass-like"
      ,"Forb/herb", "Fern", "Vine"
      ,"Shrub" ,"Subshrub"
      ,"Tree"
      #,"Substrate"
      ),
    Nativity %in% c(
      "Native",
      "Non-Native",
      "Invasive",
      "Unknown"
      )
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Preferred_Lifeform
    #,Genus
    #,ScientificName
    #,Nativity
    ) %>% 
  dplyr::summarise(
    Total_Cover = sum(PctCover, na.rm = TRUE),
    .groups = "drop"
    ) %>%  
  
  ggplot() +
  geom_col(
    aes(
      x = SampleEvent_Date_Year,
      y = Total_Cover,
      fill = Preferred_Lifeform
      ),
    # position_dodge means the bars will display side by side
    position = "stack", stat = "identity"
    #position = position_dodge2(preserve = "single"), stat = "identity"
  ) +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "% Cover",
    fill = "Lifeform",
    title = paste(target_park, target_type, "Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  # scale_fill_manual(values = c("Graminoid" = "green",
  #                               "Grass-like" = "green",
  #                               "Forb/herb" = "blue",
  #                               "Fern" = "blue",
  #                               "Vine" = "blue",
  #                               "Shrub" = "orange",
  #                               "Subshrub" = "orange",
  #                               "Tree" = "red",
  #                               "Substrate" = "brown")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )
}

#p_cover_lifeform
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Cover"),
    fill = "Disturbance"
       )

p_cover_merge <- p_cover_lifeform +
  theme(plot.title = element_blank())

if(is.character(p_cover_lifeform)) {
  p_cover_lifeform
} else {
p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))
}
```

```{r}
# save when ready
p <-
  p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))

ggsave(filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Cover Lifeform.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
```

### Cover Height

```{r}
if(nrow(Cover_graph) == 0) {
  p_cover_height <- "No data available for this selection."
} else {
p_cover_height <- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      #"Nonvascular", "Lichenous"
      "Graminoid", "Grass-like"
      ,"Forb/herb", "Fern", "Vine"
      ,"Shrub" ,"Subshrub"
      ,"Tree"
      #,"Substrate"
      ),
    Nativity %in% c(
      "Native",
      "Non-Native",
      "Invasive"
      #"Unknown"
      )
    ) %>% 
  group_by(
    AdminUnit_Name, Macroplot_Purpose, Macroplot_Type, 
    Macroplot_UV1, Macroplot_UV2, MonitoringStatus_Name, SampleEvent_Date_Year
    ,Preferred_Lifeform
    #,Genus
    #,ScientificName
    #,Nativity
    ) %>% 
  dplyr::summarise(
    Total_Cover = sum(PctCover, na.rm = TRUE),
    Avg_Ht_m = mean(Avg_Ht_m),
    Avg_Ht_ft = mean(Avg_Ht_ft),
    .groups = "drop"
    ) %>%  
  
  ggplot() +
  geom_col(
    aes(
      x = SampleEvent_Date_Year,
      y = Avg_Ht_ft,
      fill = Preferred_Lifeform
      ),
    # position_dodge means the bars will display side by side
    #position = "stack", stat = "identity"
    position = position_dodge2(preserve = "single"), stat = "identity"
  ) +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Height (ft)",
    fill = "Lifeform",
    title = paste(target_park, target_type, "Understory Height")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  ylim(0, 6) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$Disturbance_Date_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )
}

#p_cover_height
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5)
        )+
  labs(
    title = paste(target_park, target_type, "Understory Height"),
    fill = "Disturbance"
       )

p_cover_merge <- p_cover_height +
  theme(plot.title = element_blank())

if(is.character(p_cover_height)) {
  p_cover_height
} else {
p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))
}
```

```{r}
# save when ready
p <-
  p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))

ggsave(filename = paste(path_save, target_park, target_ProjectUnit, target_MonitoringType, "Cover Height.jpg"),
       plot = p, width = 6, height = 4, units = "in", dpi = 300)
```

# Discussion

# References

## Tree List

```{r}
Species_trees <- Species_trees %>% 
  arrange(`Scientific Name`)
kable(Species_trees[,c("Scientific Name","Common Name","Fire Adaptedness")])
```

## Literature Cited

```{r}
WriteBib(bib, file = "zotero_refs.bib")
```
