---
title: Richmond National Battlefield Park Report - Forest Plots
author: NPS Northeast Region Fire Effects Monitoring Program
output:
  html_document:
    theme: readable
    highlight: null
    toc: false
    toc_depth: 2
    toc_float:
      smooth_scroll: true
    code_download: true
  pdf_document:
    toc: true
    toc_depth: 2
  word_document:
    toc: true
    toc_depth: 2
link-citations: true
bibliography: zotero_refs.bib
csl: chicago-author-date-17th-edition.csl
---

# Annual Report {.hidden}

### Setup {.hidden}

```{r}
## Markdown Options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r}
## Install packages (if needed)

# install.packages("tidyverse")
# install.packages("kableExtra")
# install.packages("ggplot2")
# install.packages("RefManageR")
# install.packages("vegan")
```

```{r}
## Load Packages

# "tidyverse" has lots of useful functions for data cleaning
library(tidyverse)
# "kableExtra" is used to produce formatted tables
library(kableExtra)
library(ggplot2)
library(stringr)
library(DT)
library(fs)
library(ggplot2)
#library(gganimate)
library(patchwork)
library(RefManageR)
# shannon diversity index
library(vegan)
```

### References

```{r}
ZoteroUserID <- "3306456"
ZoteroAPIkey <- "F7k8Rp07XhH9rIqiKP1ob0uB"
ZoteroFolderKey <- "DGJVBG7G"

bib <- ReadZotero(
  user = ZoteroUserID,
  .params = list(
    collection = ZoteroFolderKey,
    key = ZoteroAPIkey,
    limit = 100),
  temp.file = "zotero_refs.bib",
  delete.file = FALSE)
```

### Adjust File Paths {.hidden}

```{r}
## Adjust File Paths
#path_file <- "E:/Allie/FireFX_NER/FFI Data Management/R Outputs/"
path_file <- "C:/Users/alalor/OneDrive - DOI/NER/FireFX/FFI Data Management/R Outputs/"
path_data <- paste0(path_file, "ALL/Calculations/ALL_")
path_save <- "C:/Users/alalor/OneDrive - DOI/R/NER/output/graphs"
## Source Code for Gingrich Stocking Chart
source("C:/Users/alalor/OneDrive - DOI/R/NER/scripts/4_Reports/Gingrich Stocking Chart.R")
```

### Load Data {.hidden}

```{r}
# Load in data
MetadataReport <- read.csv(paste0(path_data, "MetadataReport.csv"))
Fuels <- read.csv(paste0(path_data, "Data_Surface Fuels.csv"))
Trees <- read.csv(paste0(path_data, "Data_Trees-Seedlings.csv"))
Cover <- read.csv(paste0(path_data, "Data_Cover_Points.csv"))
# Cover_SpComp <- read.csv(paste0(path_data, "Data_Cover_SpComp.csv"))
# PostBurn <- read.csv(paste0(path_data, "Data_Post Burn Severity (metric).csv"))
# Shrubs <- read.csv(paste0(path_data, "Data_Density - Belts (metric).csv"))
```

### Target Values {.hidden}

```{r}
target_park <- c("RICH")
target_type <- c("Forest")
target_purpose <- c("Fire Monitoring Handbook")
target_year <- c(2025)

    
    MetadataReport %>%
      filter(
        Purpose == target_purpose,
        AdministrationUnit_Name == target_park,
        Type == target_type
        ) %>% 
      select(Macroplot_UV1, Macroplot_UV2) %>% 
      unique()

target_ProjectUnit <- c("Cold Harbor I")
target_MonitoringType <- c("Pine Oak")


    MetadataReport_SampleEvents <- MetadataReport %>%
      filter(
        AdministrationUnit_Name == target_park,
        Type == target_type,
        Purpose == target_purpose,
        Macroplot_UV1 == target_ProjectUnit,
        Macroplot_UV2 == target_MonitoringType,
        !MonStatus %in% c("Burn", "Herbicide", "Mechanical", "Mow")
        )

    MetadataReport_Disturbances <- MetadataReport %>%
      filter(
        AdministrationUnit_Name == target_park,
        Type == target_type,
        Purpose == target_purpose,
        Macroplot_UV1 == target_ProjectUnit,
        Macroplot_UV2 == target_MonitoringType,
        MonStatus %in% c("Burn", "Herbicide", "Mechanical", "Mow")
        )

year_max <- as.numeric(format(Sys.Date(), "%Y"))
date_max <- as.Date(paste0(year_max, "-12-31"))
year_min <- as.numeric((min(MetadataReport_SampleEvents$SampleEventDate_Year)) - 1)
date_min <- as.Date(paste0(year_min, "-12-31"))
```

# Monitoring Objectives

### Resources

The current vegetation association of Richmond's forest is a Northern Coastal Plain Mixed Oak / Heath Forest [@noauthor_natureserve_nodate]. Recommendations for forest characteristics will be aimed at maintaining this community type.

1.  The fuel model most representative of this vegetation association is TL6 [@scott_standard_2005]. "Timber Litter" (TL) fuel models are primarily driven by dead and down woody fuel, and TL6 specifically represents moderate load broadleaf litter. Expected fine fuel loading for this model is 2.4 tons/acre, which serves as a target value to moderate fire spread potential.
2.  To promote oak and pine regeneration, duff depth should be maintained at 1.5 inches or below [@jenkins_yellow_2011].
3.  Oaks need abundant light and sun to have successful regeneration. To maintain open canopy woodlands, tree stocking density should be maintained within 30-70% [@ginrich_measuring_1967; @kabrick_silvicultural_2014]
4.  Fire-adapted oak-pine ecosystems contain a higher ratio of xeric species, which are drought tolerant and usually fire-adapted, compared to mesic species, which are tolerant of shadier and moister conditions [@alexander_mesophication_2021]. The species composition of younger pole-sized trees reflect the trajectory of forest change and can be targeted for thinning treatments.
5.   Diversity objective...

```{r}
Objectives <- data.frame(
  Objective = c(
    "1. Maintain fine fuel loading (litter?, 1-hr, 10-hr, and 100-hr fuels) at < 2.4 tons/acre",
    "2. Maintain duff depth to < 1.5 inch",
    "4. Maintain a stocking density of overstory trees (>15cm DBH) between 30-70%",
    "5. xeric:mesic pole-sized (2.5-15cm DBH) tree density objective...",
    "6. diversity of native grasses and forbs objective..."
    ))

kable(Objectives)
```

### Target Values {.hidden}

```{r}
# target_FineFuelLoading <- 1.12 * .5
# target_PoleDensity <- 380 * .5
# target_Cover <- 2.4 * 1.75

target_FineFuelLoading <- 2.4
target_Duff <- 1.5
target_PoleDensity <- 380 * .5
target_Cover <- 2.4 * 1.75
```

## Overview  {.hidden}

### Prep {.hidden}

```{r}
Disturbances_graph <- MetadataReport_Disturbances %>%
  group_by(
    Region, Zone, Unit, AdministrationUnit_Name, Plot_Type, 
    DisturbanceDate, DisturbanceDate_Year, SampleEventDate_Year, MonStatus
    ) %>%
  filter(
    DisturbanceDate_Year == SampleEventDate_Year
    ) %>%
  dplyr::summarize(
    n_Macroplot = n()
    ) %>%
  mutate(
    DisturbanceDate = as.Date(DisturbanceDate),
    Macroplot_Num = "All"
    ) %>%
  arrange(desc(MonStatus))
```

### Disturbance History

```{r}
p_disturbance <- MetadataReport_Disturbances %>%
  ggplot(aes(x = DisturbanceDate, y = Macroplot_Num)) +
  geom_line(aes(group = Macroplot_Num),
            data = Disturbances_graph) +
  geom_point(aes(X = DisturbanceDate, y = Macroplot_Num, fill = MonStatus),
             data = Disturbances_graph, shape = 21) +
  geom_line(aes(X = DisturbanceDate, y = Macroplot_Num, fill = MonStatus),
            data = Disturbances_graph) +
  geom_point(aes(X = DisturbanceDate, y = Macroplot_Num, fill = MonStatus),
             data = Disturbances_graph, shape = 21, size = 2.5) +
  facet_grid( ~ Macroplot_UV2) +
  labs(title = "Disturbance History",
       y = "",
       x = "Year",
       fill = "") +
  scale_x_date(
    limits = c(date_min, date_max),
    date_breaks = "1 year",
    date_labels = "%Y",
    expand = expansion(mult = c(0, 0))
  ) +
  theme_light() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        plot.title = element_text(size = 15, face="bold", hjust = 0.5),
        axis.title = element_text(size = 12, face="bold"),
        axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
        axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 8, angle = 90, vjust = 0.5, hjust=1),
        legend.position = "top")

p_disturbance
```

## Surface Fuels

### Prep {.hidden}

```{r}
Fuels_graph <- Fuels %>% 
  filter(
    AdministrationUnit_Name == target_park,
    Type == target_type,
    Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  mutate(
    SampleEventDate_Year = as.numeric(SampleEventDate_Year)
    ) %>%
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ) %>% 
  dplyr::summarise(
    n_plots = n_distinct(Macroplot),
    ThousHr_FuelLoad = mean(ThousHr_FuelLoad, na.rm = TRUE),
    ThousHrRott_FuelLoad = mean(ThousHrRott_FuelLoad, na.rm = TRUE),
    ThousHrSound_FuelLoad = mean(ThousHrSound_FuelLoad, na.rm = TRUE),
    Fine_FuelLoad = mean(Fine_FuelLoad, na.rm = TRUE),
    HunHr_FuelLoad = mean(HunHr_FuelLoad, na.rm = TRUE),
    TenHr_FuelLoad = mean(TenHr_FuelLoad, na.rm = TRUE),
    OneHr_FuelLoad = mean(OneHr_FuelLoad, na.rm = TRUE),
    Avg_LittDuff_FuelLoad = mean(Avg_LittDuff_FuelLoad, na.rm = TRUE),
    Avg_Litt_FuelLoad  = mean(Avg_Litt_FuelLoad, na.rm = TRUE),
    Avg_Duff_FuelLoad = mean(Avg_Duff_FuelLoad, na.rm = TRUE),
    .groups = "drop"
    ) %>% 
  pivot_longer(
    cols = c(
      ThousHr_FuelLoad,
      ThousHrRott_FuelLoad,
      ThousHrSound_FuelLoad,
      Fine_FuelLoad,
      HunHr_FuelLoad,
      TenHr_FuelLoad,
      OneHr_FuelLoad,
      Avg_LittDuff_FuelLoad,
      Avg_Litt_FuelLoad,
      Avg_Duff_FuelLoad
    ),
    names_to  = "FuelClass",
    values_to = "FuelLoad"
  ) %>% 
    mutate(
    FuelClass = factor(
      FuelClass,
      levels = c(
        "ThousHr_FuelLoad",
        "ThousHrRott_FuelLoad",
        "ThousHrSound_FuelLoad",
        "Fine_FuelLoad",
        "HunHr_FuelLoad",
        "TenHr_FuelLoad",
        "OneHr_FuelLoad",
        "Avg_LittDuff_FuelLoad",
        "Avg_Litt_FuelLoad",
        "Avg_Duff_FuelLoad"
      )
    )
  ) %>%
    mutate(
    FuelClass = recode(
      FuelClass,
      ThousHr_FuelLoad        = "1000-hr",
      ThousHrRott_FuelLoad    = "1000-hr Rotten",
      ThousHrSound_FuelLoad   = "1000-hr Sound",
      Fine_FuelLoad           = "Fine",
      HunHr_FuelLoad          = "100-hr",
      TenHr_FuelLoad          = "10-hr",
      OneHr_FuelLoad          = "1-hr",
      Avg_LittDuff_FuelLoad   = "Litter/Duff",
      Avg_Litt_FuelLoad       = "Litter",
      Avg_Duff_FuelLoad       = "Duff"
    )
  )
```

```{r}
FuelsDuff_graph <- Fuels %>% 
  filter(
    AdministrationUnit_Name == target_park,
    Type == target_type,
    Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  mutate(
    SampleEventDate_Year = as.numeric(SampleEventDate_Year)
    ) %>%
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ) %>% 
  dplyr::summarise(
    n_plots = n_distinct(Macroplot),
    Avg_LittDep = mean(Avg_LittDep, na.rm = TRUE),
    Avg_DuffDep = mean(Avg_DuffDep, na.rm = TRUE),
    .groups = "drop"
    ) %>% 
  pivot_longer(
    cols = c(
      Avg_LittDep,
      Avg_DuffDep
    ),
    names_to  = "FuelClass",
    values_to = "FuelDepth"
  ) %>% 
    mutate(
    FuelClass = factor(
      FuelClass,
      levels = c(
        "Avg_LittDep",
        "Avg_DuffDep"
      )
    )
  ) %>%
    mutate(
    FuelClass = recode(
      FuelClass,
      Avg_LittDep       = "Litter",
      Avg_DuffDep       = "Duff"
    )
  )
```

### Fine Fuels (with Litter)

```{r}
p_fuels <- Fuels_graph %>% 
  filter(
    FuelClass %in% c(
      #"1000-hr",
      #"1000-hr Rotten",
      #"1000-hr Sound",
      #"Fine",
      "100-hr",
      "10-hr",
      "1-hr",
      #"Litter/Duff",
      "Litter"
      #"Duff"
  )) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ) %>% 
  mutate(
    Total_FuelLoad = sum(FuelLoad, na.rm = TRUE)
    ) %>% 
  
  ggplot(aes(x = SampleEventDate_Year, y = Total_FuelLoad)) +
  geom_line() +
  geom_point() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Tons / Acre",
    fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Loading")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  ylim(0, 8) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    ) +
  geom_hline(
    yintercept = target_FineFuelLoading, 
    linetype = "dashed", 
    color = "forestgreen"
    )

#p_fuels
#ggsave("fuels_classic.jpg", p_fuels_classic, path = path_save, width = 12, height = 8, dpi = 300)
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_fuels_merge <- p_fuels +
  theme(plot.title = element_blank())

p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Fine Fuels (without Litter)

```{r}
p_fuels <- Fuels_graph %>% 
  filter(
    FuelClass %in% c(
      #"1000-hr",
      #"1000-hr Rotten",
      #"1000-hr Sound",
      "Fine"
      #"100-hr",
      #"10-hr",
      #"1-hr",
      #"Litter/Duff",
      #"Litter",
      #"Duff"
  )) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ) %>% 
  mutate(
    Total_FuelLoad = sum(FuelLoad)
    ) %>% 
  
  ggplot(aes(x = SampleEventDate_Year, y = Total_FuelLoad, fill = FuelClass)) +
  geom_line() +
  geom_point() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Tons / Acre",
    fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Loading")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  ylim(0, 8) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    ) +
  geom_hline(
    yintercept = target_FineFuelLoading, 
    linetype = "dashed", 
    color = "forestgreen"
    )

#p_fuels
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_fuels_merge <- p_fuels +
  theme(plot.title = element_blank())

p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Duff Depth

```{r}
p_fuels <- FuelsDuff_graph %>% 
  filter(
    FuelClass %in% c(
      "Litter",
      "Duff"
  )) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ) %>% 
  mutate(
    Total_FuelDepth = sum(FuelDepth)
    ) %>% 
  
  ggplot() +
  geom_bar(aes(x = SampleEventDate_Year, y = FuelDepth, fill = FuelClass),
           position = "stack", stat = "identity") + 
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Depth (inches)",
    fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Depth")
  ) +
  scale_x_continuous(
    limits = c((year_min), year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = c("Litter" = "#BFEFFF", "Duff" = "#619CFF")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    ) +
  geom_hline(
    yintercept = target_Duff, 
    linetype = "dashed", 
    color = "#619CFF",
    size = 0.7
    )

#p_fuels
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_fuels_merge <- p_fuels +
  theme(plot.title = element_blank())

p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Coarse Woody Debris  {.hidden}

```{r}
p_fuels <- Fuels_graph %>% 
  filter(
    FuelClass %in% c(
      #"1000-hr",
      "1000-hr Rotten",
      "1000-hr Sound",
      "Fine"
      #"100-hr",
      #"10-hr",
      #"1-hr",
      #"Litter/Duff",
      #"Litter",
      #"Duff"
  )) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ) %>% 
  mutate(
    Total_FuelLoad = sum(FuelLoad)
    ) %>% 
  
  ggplot() +
  geom_bar(aes(x = SampleEventDate_Year, y = FuelLoad, fill = FuelClass),
           position = "stack", stat = "identity") + 
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Tons / Acre",
    fill = "Fuel Class",
    title = paste(target_park, target_type, "Fuel Loading")
  ) +
  scale_x_continuous(
    limits = c((year_min), year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

#p_fuels
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Fuel Loading"),
    fill = "Disturbance"
       )

p_fuels_merge <- p_fuels +
  theme(plot.title = element_blank())

p_disturbance_merge / p_fuels_merge +
  plot_layout(heights = c(0.2, 1.4))
```

## Trees

### Prep {.hidden}

```{r}
Trees_graph <- Trees %>%
  filter(
    AdministrationUnit_Name == target_park,
    Type == target_type,
    Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  mutate(
    SampleEventDate_Year = as.numeric(SampleEventDate_Year)
    ) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Genus, Status
    ) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot),
    
    Seedling_Species = paste(na.omit(unique(Seedling_Species)), collapse = "; "),
    Seedling_Count  = sum(Seedling_Count),
    Seedling_Density_ac = round(mean(Seedling_Dens_ac, na.rm = TRUE)),
    Seedling_Density_ha = round(mean(Seedling_Dens_ha, na.rm = TRUE)),
    
    Sapling_Species = paste(na.omit(unique(Sapling_Species)), collapse = "; "),
    Sapling_Count = sum(Sapling_Count),
    Sapling_Density_ac = round(mean(Sapling_Dens_ac, na.rm = TRUE)),
    Sapling_Density_ha = round(mean(Sapling_Dens_ha, na.rm = TRUE)),
    
    Pole_Species = paste(na.omit(unique(Pole_Species)), collapse = "; "),
    Pole_Count = sum(Pole_Count),
    Pole_Density_ac = round(mean(Pole_Dens_ac, na.rm = TRUE)),
    Pole_Density_ha = round(mean(Pole_Dens_ha, na.rm = TRUE)),
    Pole_BA_ft2 = round((mean(Pole_BA_ft2, na.rm = TRUE)), 2),
    Pole_BA_m2 = round((mean(Pole_BA_m2, na.rm = TRUE)), 2),
    
    Overstory_Species = paste(na.omit(unique(Overstory_Species)), collapse = "; "),
    Overstory_Count = sum(Overstory_Count),
    Overstory_Density_ac = round(mean(Overstory_Dens_ac, na.rm = TRUE)),
    Overstory_Density_ha = round(mean(Overstory_Dens_ha, na.rm = TRUE)),
    Overstory_BA_ft2 = round((mean(Overstory_BA_ft2, na.rm = TRUE)), 2),
    Overstory_BA_m2 = round((mean(Overstory_BA_m2, na.rm = TRUE)), 2),
    
    .groups = "drop"
  ) %>% 
  pivot_longer(
    cols = matches("Seedling|Sapling|Pole|Overstory"),
    names_to = c("SizeClass", ".value"),
    names_pattern = "(Seedling|Sapling|Pole|Overstory)_(Species|Count|Density_[a-z]+|BA_[a-z0-9]+)"
  ) %>% 
  mutate(Legend  = ifelse(Genus == "Carya",
                          "Fire Tolerant",
                     ifelse(Genus %in% c("Liriodendron", "Liquidambar"),
                            "Fire Intolerant",
                                   ifelse(Genus %in% c("Pinus", "Quercus"),
                                          "Fire Adapted", "Unknown")))
         ) %>%
  mutate(
    SizeClass = factor(
      SizeClass,
      levels = c(
        "Overstory",
        "Pole",
        "Sapling",
        "Seedling"
      )),
    Genus = factor(
      Genus,
      levels = c(
        "Pinus",
        "Quercus",
        "Carya",
        "Liriodendron",
        "Liquidambar",
        "Carex"
      )),
    Legend = factor(
      Legend,
      levels = c(
        "Fire Adapted",
        "Fire Tolerant",
        "Fire Intolerant",
        "Unknown"
        )),
    BA_ft2  = replace_na(BA_ft2, 0),
    BA_m2   = replace_na(BA_m2, 0)
    )
```

### Seedlings  {.hidden}

```{r}
p_trees_seedlings <- Trees_graph %>% 
  filter(
    Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      "Seedling"
      #"Sapling",
      #"Pole",
      #"Overstory"
      )) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Genus, Species, Status
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha),
    Species = paste(na.omit(unique(Species)), collapse = "; "),
    ) %>% 
  filter(
    Total_Density_ac != 0
    ) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEventDate_Year, 
      y = Total_Density_ac, 
      fill = Genus
      ),
    position = "stack", stat = "identity") +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Seedling Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = c("#FF4040", "#EE6A50", "#FF8C00", "#00B2EE", "#009ACD", "#666666")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

#p_trees_seedlings
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Seedling Tree Density"),
    fill = "Disturbance"
       )

p_trees_merge <- p_trees_seedlings +
  theme(plot.title = element_blank())

p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Saplings  {.hidden}

```{r}
p_trees_saplings <- Trees_graph %>% 
  filter(
    Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      #"Seedling",
      "Sapling"
      #"Pole",
      #"Overstory"
      )) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Genus, Species, Status) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha),
    Species = paste(na.omit(unique(Species)), collapse = "; ")
    ) %>% 
  filter(
    Total_Density_ac != 0
    ) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEventDate_Year, 
      y = Total_Density_ac, 
      fill = Genus
      ),
    position = "stack", stat = "identity") +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Sapling Tree Density")
  ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
  ) +
  scale_fill_manual(values = c("#FF4040", "#EE6A50", "#FF8C00", "#00B2EE", "#009ACD", "#666666")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

#p_trees_saplings
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Sapling Tree Density"),
    fill = "Disturbance"
       )

p_trees_merge <- p_trees_saplings +
  theme(plot.title = element_blank())

p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Pole-Sized

```{r}
p_trees_poles <- Trees_graph %>% 
  filter(
    Status %in% c(
      "L"
      #"D"
      ),
    SizeClass %in% c(
      #"Seedling",
      #"Sapling",
      "Pole"
      #"Overstory"
      )) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Genus, Species, Status
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha),
    Species = paste(na.omit(unique(Species)), collapse = "; ")
    ) %>% 
  filter(
    Total_Density_ac != 0
    ) %>% 
    
  ggplot() +
  geom_bar(
    aes(
      x = SampleEventDate_Year, 
      y = Total_Density_ac, 
      fill = Legend
      ),
    position = "stack", stat = "identity") +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Stems / Acre",
    title = paste(target_park, target_type, "Pole Tree Density")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  scale_fill_manual(values = c("Fire Adapted" = "#EE6A50", "Fire Tolerant" = "#FF8C00", "Fire Intolerant" = "#00B2EE", "Unknown" = "#666666")) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

#p_trees_poles
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Pole Tree Density"),
    fill = "Disturbance"
       )

p_trees_merge <- p_trees_poles +
  theme(plot.title = element_blank())

p_disturbance_merge / p_trees_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Overstory - Gingrich Stocking Graph

```{r gingrich-plot, fig.width=10, fig.height=8}

p_trees_overstory_BA <- Trees_graph %>% 
  filter(
    Status %in% c(
      "L",
      "D"
      ),
    SizeClass %in% c(
      #"Seedling",
      #"Sapling",
      #"Pole",
      "Overstory"
      )) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    #,Genus, Status
    ) %>% 
  mutate(
    Total_Density_ac = sum(Density_ac),
    Total_Density_ha = sum(Density_ha),
    Total_BA_ft2 = sum(BA_ft2),
    Total_BA_m2 = sum(BA_m2)
    # k_english = 0.005454,
    # k_metric = 0.00007854,
    # QMD_english = round((sqrt((Total_BA_ft2)/(k_english * Total_Density_ac))),1),
    # QMD_metric = round((sqrt((Total_BA_m2)/(k_metric * Total_Density_ha))), 1)
    ) %>% 
  filter(
    Total_Density_ac != 0,
    SampleEventDate_Year %in% target_year
    )

source("C:/Users/alalor/OneDrive - DOI/R/NER/scripts/4_Reports/Gingrich Stocking Chart.R")
plot.gingrich.imperial(
  tpa = p_trees_overstory_BA$Total_Density_ac,
  ba = p_trees_overstory_BA$Total_BA_ft2,
  label = p_trees_overstory_BA$SampleEventDate_Year,
  color = TRUE,
  type = "p",
  main = paste(target_park, target_ProjectUnit, "\nOverstory Stand Structure")
)
```

## Cover  {.hidden}

### Prep {.hidden}

```{r}
Cover_graph <- Cover %>% 
  filter(
    AdministrationUnit_Name == target_park,
    Type == target_type,
    Purpose == target_purpose,
    Macroplot_UV1 == target_ProjectUnit,
    Macroplot_UV2 == target_MonitoringType
    ) %>% 
  mutate(
    SampleEventDate_Year = as.numeric(SampleEventDate_Year)
    ) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type,
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Preferred_Lifeform, Genus, Nativity, Species.Symbol
    ) %>%
  dplyr::summarise(
    n_plots = n_distinct(Macroplot),
    Avg_Ht_m = round(mean(Avg_Ht_m, na.rm = TRUE), 1),
    Avg_Ht_ft = round(mean(Avg_Ht_ft, na.rm = TRUE), 1),
    Abundance = sum(Hits, na.rm = TRUE),
    PctCover = round(mean(PctCover, na.rm = TRUE), 2),
    .groups = "drop"
    ) %>% 
  mutate(
    Preferred_Lifeform = ifelse(Preferred_Lifeform == "Undefined", "Substrate", Preferred_Lifeform),
    Preferred_Lifeform = factor(
      Preferred_Lifeform,
      levels = c(
        "Tree",
        "Shrub",
        "Subshrub",
        "Forb/herb",
        "Fern",
        "Vine",
        "Graminoid",
        "Grass-like",
        "Nonvascular", 
        "Lichenous", 
        "Substrate"
      )))
```

### Diversity

```{r}
wide_diversity <- Cover_graph %>%
  filter(
    Preferred_Lifeform %in% c(
      #"Nonvascular", "Lichenous", 
      "Graminoid", "Grass-like",
      "Forb/herb", "Fern", "Vine"
      #"Shrub", "Subshrub",
      #"Tree"
      #"Substrate"
      ),
    Nativity %in% c(
      "Native",
      "Non-Native",
      "Invasive"
      #"Unknown"
      )
    ) %>% 
  select(SampleEventDate_Year, Species.Symbol, Abundance) %>%
  tidyr::pivot_wider(
    names_from = Species.Symbol,
    values_from = Abundance,
    values_fill = 0
  )

shannon <- wide_diversity %>%
  mutate(
    Shannon_Index = diversity(select(., -SampleEventDate_Year),
                        index = "shannon")
  ) %>%
  select(SampleEventDate_Year, Shannon_Index)


p_diversity <- shannon %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Shannon_Index)) +
  geom_line() +
  geom_point() +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "Shannon-Wiener Diversity Index",
    title = paste(target_park, target_type, "Native Grass Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  ylim(0, 4) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )  +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

p_diversity
```

```{r}
p_cover_classic <- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      "Nonvascular", "Lichenous", 
      "Graminoid", "Grass-like",
      "Forb/herb", "Fern", "Vine",
      "Shrub", "Subshrub",
      "Tree"
      #"Substrate"
      ),
    Nativity %in% c(
      "Native",
      "Non-Native",
      "Invasive"
      #"Unknown"
      )
    ) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    #,Preferred_Lifeform, Genus, Nativity
    ) %>% 
  mutate(
    Total_Cover = sum(PctCover),
    Total_Abundance = sum(Abundance, na.rm = TRUE)
    ) %>%  
  
  
p_diversity <- sdi_results %>% 
  ggplot(aes(x = SampleEventDate_Year, y = Shannon_Index)) +
  geom_line() +
  geom_point() +
  #facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "% Cover",
    title = paste(target_park, target_type, "Native Grass Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )  +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )
```

### 2025 Report - Cover

**Objective #2:** \>75% increase in native grasses after four burns

```{r}
p_cover_classic <- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      #"Nonvascular", "Lichenous", 
      "Graminoid", "Grass-like"
      #"Forb/herb", "Fern", "Vine",
      #"Shrub", "Subshrub",
      #"Tree",
      #"Substrate"
      ),
    Nativity %in% c(
      "Native"
      #"Non-Native",
      #"Invasive",
      #"Unknown"
      )
    ) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    #,Preferred_Lifeform, Genus, Nativity
    ) %>% 
  mutate(
    Total_Cover = sum(PctCover)
    ) %>%  

  
  ggplot(aes(x = SampleEventDate_Year, y = Total_Cover)) +
  geom_line() +
  geom_point() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "% Cover",
    title = paste(target_park, target_type, "Native Grass Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    )  +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

p_cover_classic
```

### Cover Points

Same data as presented above, but broken down by species

```{r}
p_cover_points <- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      #"Nonvascular", "Lichenous", 
      "Graminoid", "Grass-like"
      #"Forb/herb", "Fern", "Vine",
      #"Shrub", "Subshrub",
      #"Tree",
      #"Substrate"
      ),
    Nativity %in% c(
      "Native"
      #"Non-Native",
      #"Invasive",
      #"Unknown"
      )
    ) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Preferred_Lifeform
    ,Genus
    ,Nativity
    ,Species.Symbol
    ) %>% 
  dplyr::summarise(
    Total_Cover = sum(PctCover, na.rm = TRUE),
    .groups = "drop"
    ) %>%  
  
  ggplot(aes(
      x = SampleEventDate_Year, 
      y = Total_Cover, 
      fill = Genus
      )) +
  geom_col() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "% Cover",
    title = paste(target_park, target_type, "Native Grass Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

#p_cover_points
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Native Grass Cover"),
    fill = "Disturbance"
       )

p_cover_merge <- p_cover_points +
  theme(plot.title = element_blank())

p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Cover Lifeform

```{r}
p_cover_lifeform <- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      #"Nonvascular", "Lichenous", 
      "Graminoid", "Grass-like",
      "Forb/herb", "Fern", "Vine",
      "Shrub" #"Subshrub",
      #"Tree",
      #"Substrate"
      ),
    Nativity %in% c(
      "Native",
      "Non-Native",
      "Invasive",
      "Unknown"
      )
    ) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Preferred_Lifeform
    ,Genus
    ,Nativity
    ,Species.Symbol
    ) %>% 
  dplyr::summarise(
    Total_Cover = sum(PctCover, na.rm = TRUE),
    .groups = "drop"
    ) %>%  
  
  ggplot(aes(
      x = SampleEventDate_Year, 
      y = Total_Cover, 
      fill = Preferred_Lifeform
      )) +
  geom_col() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "% Cover",
    fill = "Lifeform",
    title = paste(target_park, target_type, "Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

#p_cover_lifeform
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Cover"),
    fill = "Disturbance"
       )

p_cover_merge <- p_cover_lifeform +
  theme(plot.title = element_blank())

p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Cover Nativity

```{r}
p_cover_nativity <- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      "Nonvascular", "Lichenous", 
      "Graminoid", "Grass-like",
      "Forb/herb", "Fern", "Vine",
      "Shrub", "Subshrub",
      "Tree"
      #"Substrate"
      ),
    Nativity %in% c(
      "Native",
      "Non-Native",
      "Invasive"
      #"Unknown"
      )
    ) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Preferred_Lifeform
    ,Genus
    ,Nativity
    ,Species.Symbol
    ) %>% 
  dplyr::summarise(
    Total_Cover = sum(PctCover, na.rm = TRUE),
    .groups = "drop"
    ) %>%  
  
  ggplot(aes(
      x = SampleEventDate_Year, 
      y = Total_Cover, 
      fill = Nativity
      )) +
  geom_col() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "% Cover",
    fill = "Lifeform",
    title = paste(target_park, target_type, "Native Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

#p_cover_nativity
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Native Cover"),
    fill = "Disturbance"
       )

p_cover_merge <- p_cover_nativity +
  theme(plot.title = element_blank())

p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Cover Oaks

```{r}
p_cover_oaks <- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      #"Nonvascular", "Lichenous", 
      #"Graminoid", "Grass-like",
      #"Forb/herb", "Fern", "Vine",
      #"Shrub", "Subshrub",
      "Tree"
      #"Substrate"
      ),
    Nativity %in% c(
      "Native",
      "Non-Native",
      "Invasive"
      #"Unknown"
      ),
    Genus == "Quercus"
    ) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Preferred_Lifeform
    ,Genus
    ,Nativity
    #,Species.Symbol
    ) %>% 
  dplyr::summarise(
    Total_Cover = sum(PctCover, na.rm = TRUE),
    .groups = "drop"
    ) %>%  
  
  ggplot(aes(
      x = SampleEventDate_Year, 
      y = Total_Cover, 
      fill = Genus
      )) +
  geom_col() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "% Cover",
    fill = "Lifeform",
    title = paste(target_park, target_type, "Oak Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

#p_cover_oaks
```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Oak Cover"),
    fill = "Disturbance"
       )

p_cover_merge <- p_cover_oaks +
  theme(plot.title = element_blank())

p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))
```

### Cover {.hidden}

```{r}
p_cover<- Cover_graph %>% 
  filter(
    Preferred_Lifeform %in% c(
      #"Nonvascular", "Lichenous", 
      #"Graminoid", "Grass-like",
      "Forb/herb", "Fern", "Vine",
      "Shrub" #"Subshrub",
      #"Tree",
      #"Substrate"
      ),
    Nativity %in% c(
      "Native",
      "Non-Native",
      "Invasive",
      "Unknown"
      )
    ) %>% 
  group_by(
    AdministrationUnit_Name, Purpose, Type, 
    Macroplot_UV1, Macroplot_UV2, MonStatus, SampleEventDate_Year
    ,Preferred_Lifeform
    ,Genus
    ,Nativity
    ,Species.Symbol
    ) %>% 
  dplyr::summarise(
    Total_Cover = sum(PctCover, na.rm = TRUE),
    .groups = "drop"
    ) %>%  
  
  ggplot(aes(
      x = SampleEventDate_Year, 
      y = Total_Cover, 
      fill = Genus
      )) +
  geom_col() +
  facet_wrap( ~ Macroplot_UV1, ncol = 1) +
  labs(
    x = "Year",
    y = "% Cover",
    fill = "Genus",
    title = paste(target_park, target_type, "Cover")
    ) +
  scale_x_continuous(
    limits = c(year_min, year_max),
    breaks = seq(year_min, year_max, by = 1),
    expand = expansion(mult = c(0, 0))
    ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 8, angle = 90, hjust = 0.5, vjust = 0.5),
    plot.title = element_text(size = 15, face="bold", hjust = 0.5),
    plot.subtitle = element_text(size = 10, face="bold", hjust = 0.5),
    axis.title = element_text(size = 12, face="bold"),
    axis.title.y = element_text(margin = unit(c(0,4,0,0), "mm")),
    axis.title.x = element_text(margin = unit(c(4,0,0,0), "mm")),
    axis.text.y = element_text(size = 8),
    panel.grid.minor = element_blank()
    ) +
  geom_vline(
    xintercept = (MetadataReport_Disturbances$DisturbanceDate_Year) - 0.5, 
    linetype = "dashed", 
    color = "red"
    )

```

```{r}
p_disturbance_merge <- p_disturbance +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "right",
        plot.margin = margin(t = 5, r = 5, b = 0, l = 5)
        )+
  labs(
    title = paste(target_park, target_type, "Cover"),
    fill = "Disturbance"
       )

p_cover_merge <- p_cover +
  theme(plot.title = element_blank())

p_disturbance_merge / p_cover_merge +
  plot_layout(heights = c(0.2, 1.4))
```

## Herbs Species Comp {.hidden}

```{r}
# HerbsSpComp_graph <- HerbsSpComp %>%
#   filter(AdministrationUnit_Name == target_park,
#          Type == target_type) %>%
#   # group_by(AdministrationUnit_Name, Purpose, Type, MacroPlot.UV1, MonStatus, SampleEventDate_Year, Nativity) %>%
#   dplyr::summarise(n_species_ByNativity = mean(n_species_ByNativity),
#                    .groups = "drop")
```

```{r}
# HerbsSpComp_graph %>%
#   ggplot(aes(x = SampleEventDate_Year, y = n_species_ByNativity, fill = Nativity)) +
#   geom_bar(position = "stack", stat = "identity")
```

# Discussion {.hidden}

# References

```{r}
WriteBib(bib, file = "zotero_refs.bib")
```
